### 2018-02-23 BNS_manuscript.tex
First commit

\documentclass[11pt,a4paper]{article}

\usepackage{multicol}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsfonts,amssymb,amsmath}
     % use Times fonts if available on your TeX system
\usepackage{epsfig}
%\usepackage{empheq}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{rotating}
\usepackage[small,compact]{titlesec}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{multirow}
\usepackage{sidecap}
\usepackage{eurosym}
\usepackage{setspace}
\usepackage{caption}
\usepackage[usestackEOL]{stackengine} % package used to write several lines in one box
%\usepackage{subcaption}

\topmargin-14mm
\textheight250mm
\oddsidemargin1mm
\textwidth160mm

\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\renewcommand{\c}{\cos\theta}
\newcommand{\s}{\sin}
\renewcommand{\t}{\theta}
\renewcommand{\b}{\bar}
\newcommand{\f}{\frac}
\newcommand{\df}{\dfrac}
\newcommand{\pd}{\partial}
\newcommand{\bt}{\beta}
\newcommand{\D}{\Delta}
\newcommand{\Si}{\Sigma}
\newcommand{\p}{\rho}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\ph}{\phi}
\newcommand{\g}{\gamma}
\newcommand{\nn}{\nonumber}
\newcommand{\al}{\alpha}
\newcommand{\La}{\Lambda}
\newcommand{\el}{\ell}
\newcommand{\h}{\hat}
\newcommand{\mrm}{\mathrm}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{align}}
\newcommand{\ea}{\end{align}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bef}{\begin{frame}}
\newcommand{\ef}{\end{frame}}
\newcommand{\bs}{\begin{small}}
\newcommand{\es}{\end{small}}
\newcommand{\ord}{\mathcal{O}}
\newcommand{\Lim}[1]{\raisebox{0.5ex}{\scalebox{0.8}{$\displaystyle \lim_{#1}\;$}}}
\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut for vertical spacing in tables
\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut

\begin{document}
{\bf Title: Forecasting Gamma-ray Bursts using Gravitational Waves}
\section{Abstract}
We explore the intriguing possibility of employing future gravitational-wave interferometers to detect the inspiral of compact binaries early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
We quantify the ability to predict a GRB by computing the time a canonical binary neutron star (BNS) system takes to inspiral from a certain threshold frequency to its final merger. We define this threshold frequency to be the gravitational-wave frequency at which the RMS-averaged strain due to the BNS system accumulates a signal-to-noise (SNR) ratio of 15. For our computation of advance warning times, we consider BNS systems at luminosity distances of (i) $D\lesssim200\,$Mpc in a three-interferometer network with Advance LIGO's design sensitivity and (ii) $D \lesssim 1000\,$Mpc in a similar network, but with the Einstein Telescope's B configuration
sensitivity. We find in the case of that Advanced LIGO we may get a few minutes of warning time if we get lucky whereas the Einstein Telescope will provide us
with warning times as long as a few hours.

We also consider binary black hole neutron star systems with the hopes of observing a tidal disruption event in the future. However, our findings indicate that
witnessing such an event will be very unlikely even after the Einstein Telescope becomes operational.

\section{Introduction}\label{Sec:Intro}
We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital frequency $f_K$. 
Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
We employ the $\simeq$ symbol for quantities which we can compute exactly, but list finite digits and $\approx$ for quantities whose values we know approximately.
Overdots denote time derivative with respect to detector time, e.g., $\dot{E} =dE/dt$.

Mention {\bf KAGRA} \cite{KAGRA, KAGRA2}, starts 2018-2019, design at 2021-2022, 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)

Cosmic Explorer \cite{CE}, LIGO India, Australia China(?)

Ref.~\cite{Cannon:2011vi} already attemps some forecast, but they focus on the search algorithm side of things

We also disreagrd the fact that GRBs are collimated and will most often not point toward the Earth. Ref.~\cite{Patricelli:2016bkt} looks at this? (CHECK)

\section{Binary systems composed of neutron stars}\label{sec:BNS_inspiral}
\subsection{Newtonian evolution of BNS}
For us, the starting point for the evolution of a binary under the emission of GWs is the expression for the power generated given by 
%for the generated by the time-variance of the mass quadrupole moment
%
\be
\dot{E} = \f{G}{5c^5}\langle \dddot{Q}_{ij}\dddot{Q}_{ij} \rangle \label{eq:Edot_quadrupole}\, .
\ee
%
This is the celebrated Einstein quadrupole formula. 
Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
is the dominant contribution to the power generated %in gravitational radiation
by a system with changing mass moments.

Here, we are specifically interested in the motion of two point masses in bound motion around a common center of mass.
Labelling the masses by $m_1 \le m_2$, we have, for a binary in a circular orbit with Keplerian angular frequency $\Omega$ and separation $2r$,
%
\be
\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}\, r^4 \Omega^6\label{eq:Edot}
\ee
%
where $\mu= m_1 m_2/M$ is the reduced mass and $M=m_1+m_2$ is the total mass. 
We justify our simplification of motion to circular orbits in Sec.~\ref{sec:idealizations}.
%Our assumption of the circularity of the motion is well justified in

An important quantity in GW astronomy is the chirp mass of the binary given by
%
\be
M_c = \mu^{3/5} M^{2/5} = \f{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}} \label{eq:chirp_mass}\, ,
\ee
%
which turns Eq.~(\ref{eq:Edot}) into
%
\be
\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}, \label{eq:Edot2}
\ee
%
where, recall $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs. 
The quantity in parantheses in Eq.~(\ref{eq:Edot2}) is ubiquitous in post-Newtonian theory and is
referred to as the dimensionless inverse separation $x$.
As $x\sim v^2/c^2$, it is used to keep track of post-Newtonian orders and we can from in Eq.~(\ref{eq:Edot2}) that $\dot{E}\sim x^5$. 
%hence the common statement in the literature saying that gravitational radiation starts

The energy generated by the acceleration of the masses is radiated away in GWs,
which makes the total energy of the binary more negative, i.e., the orbit becomes more bound. 
Since the total energy is given by
%
\be
E_b = -\frac{G m_1 m_2}{2r}\, . \label{eq:binding_energy1}
\ee
%
$\dot{E}_b < 0$ implies the orbital radius must decrease in time. 
Using Kepler's third law, $ \Omega^2 = G M r^{-3}$ and Eq.~(\ref{eq:chirp_mass}) we obtain
%
\be
E_b = -\left(\f{G^2 M_c^5 \omega^2}{32}\right)^{1/3}, \label{eq:binding_energy2}
\ee
%
Energy conservation dictates that $\dot{E}=-\dot{E}_b$. Using the chain rule to determine $\dot{E}_b$ from Eq.~(\ref{eq:binding_energy2})
and setting the resulting expression equal to Eq.~(\ref{eq:Edot2}) yields $\dot{\omega}$ as a function of $\omega$ and various constants.
Translating this expression using $\omega=2\pi f$ we arrive at the standard expression for the GW frequency evolution
%%
%
\be
\dot{f} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, f^{11/3} \label{eq:fdot}
\ee
%
This can be integrated straightforwardly after defining a new time variable $\tau\equiv t_\text{coal}-t$ that equals zero when the neutron stars coalesce.
We can now define an inspiral time at a given GW frequency
%
\be
\tau_\text{insp}(f) = \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,f^{-8/3}\label{eq:tau_insp}\, ,
\ee
%
%
%\be
%\tau_\text{insp}(f) \equiv \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-8/3}-f_\text{ISCO}^{-8/3}\right]\label{eq:tau_insp} \, .
%\ee
%
which we can rewrite as follows
%
\be
\tau_\text{insp}(f) \simeq 2.18\,\text{s} \, \left(\f{1.21 M_\odot}{M_c}\right)^{5/3}\,\left(\f{100\,\text{Hz}}{f}\right)^{8/3}, \label{eq:tau_insp2}
\ee
%
where $1.21 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$.

We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T(t)$ varies over a much larger time scale than T itself
we can write
%
\be
\mathcal{N}_\text{cyc}(f) = \int_f^{f_\text{max}} \f{f}{\dot{f}}\, df =\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right] \label{eq:Ncyc1}
\ee
%
We now introduce a cut-off for the inspiral imposed by the frequency of the innermost stable circular (ISCO) orbit in Schwarzschild spacetime
\be
\Omega_\text{ISCO} = \f{c^3}{6^{3/2} G M} \label{eq:Sch_f_isco}.
\ee
%
%
We will see in Sec.~\ref{sec:idealizations} that $f_\text{ISCO} \sim \mathcal{O}(1000)\,$Hz for a system with $M\approx 2 M_\odot$. Moreover, the frequencies of interest for our advance warning time estimations will be $\lesssim \mathcal{O}(10)\,$Hz
meaning that $f^{-5/3} \gg f_\text{ISCO}^{-5/3}$. Therefore, at the leading (Newtonian) order, the number of GW cycles can be approximated by
%
\be
\mathcal{N}_\text{cyc}(f) \simeq \f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\, f^{-5/3} \, . \label{eq:Ncyc2}
\ee
%
Restoring some familiar numbers in this expression yields
%
\be
\mathcal{N}_\text{cyc}(f)\simeq 1.6\times 10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}\,\left(\f{1.21 M_\odot}{M_c}\right)^{5/3}\label{eq:Ncyc3}\, .
\ee
%
This expression is quite telling: if a ground-based interferometer picks up an
inspiralling BNS at $f=10\,$Hz then there will be $\gtrsim \ord(10^4)$ GW cycles in the detector's data stream until the merger.

Another useful relation is how the inspiral time scales with respect to the orbital radius corresponding to the observed GW frequency.
From Kepler's third law, we immediately have $\dot{r}/r= -2\dot{\Omega}/(3\Omega)=-2\dot{f}/(3f)$, which, via Eq.~(\ref{eq:tau_insp}),
yields $\dot{r}/r= -1/(4\tau)$ which integrates to
%
\be
r(\tau)=r_i \left(\f{\tau}{\tau_i}\right)^{1/4}\label{eq:r_of_tau},
\ee
%
where $r_i, \tau_i=t_\text{coal}-t_i$ are the initial radius and time that the BNS
is ``picked up'' by a detector. Solving $\tau(f_i)=\tau_i$ for $f_i=\Omega_i/\pi$ using Eq.~(\ref{eq:tau_insp}) and rewriting $\Omega_i$ as a function of $r_i$ via
Kepler's third law gives us
%
\be
\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 9.829\times 10^6\,\text{yrs}\, \left(\f{T}{1\,\text{hr}}\right)^{8/3} \left(\f{M_\odot}{M}\right)^{2/3}\,\left(\f{M_\odot}{\mu}\right) \label{eq:tau_of_r}.
\ee
%

Let us now turn our attention to the GWs generated by the inspiral.
The GWs themselves actually are tensor distortions $h_{\mu\nu}$ of the flat Minkowski
spacetime propagating at the speed of light.
In more technical terms, they satisfy $\Box h_{\mu\nu} = 0$, i.e., the flat spacetime sourceless wave equation
meaning that we are considering the solutions far from the GW source, in the so-called wave zone defined by the condition $ c/f \ll D$.
In a suitable gauge, such as the commonly used TT (transverse-traceless) gauge, it can be shown that
there exist only two physical degrees of freedom which manifest themselves
as two independent polarization amplitudes $h_+$ and $h_\times$. %when interacting with masses away from the source.
For a circular binary at a distance $D$ these states read
%
\begin{align}
 h_+(t) &= \f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi_\text{N}(t)],\label{eq:hplus_TD}\\
 h_\times(t) & = \f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\,\cos\iota \sin[\Phi_\text{N}(t)]\label{eq:hcross_TD},
\end{align}
%
%
where $\iota=\cos^{-1}(\mathbf{\hat{n}}\cdot{\mathbf{\hat{L}}}) $ is the inclination angle between the line of sight unit vector $\mathbf{\hat{n}} $ and the orbital angular momentum unit vector $\mathbf{\hat{L}}$. 
E.g., for an orbit seen edge on, $\iota = \pi/2$ which is actually the case of a purely plus-polarized wave, $h_\times=\cos(\pi/2)=0$.
When $\iota=0$ the orbit is seen face-on and we have a circularly-polarized wave: $\langle h_+ \rangle = \langle h_\times\rangle$ where $\langle \ldots \rangle$
denote time-averages over one orbit. Note that as $f$ increases in time, so does $h(t)$ hence the characteristic ``chirping'' of GW signals.

$\Phi_\text{N}(t)$ in Eqs.~(\ref{eq:hplus_TD}, \ref{eq:hcross_TD}) is the phase of the GWs given by
%
\begin{align}
\Phi_\text{N}(t) &=\int_{t_i}^t dt' \omega(t') \nn\\
&= -2\left(\f{5 G M_c}{c^3}\right)^{-5/8} (t_\text{coal}-t)^{5/8}+ \Phi_0 \, .\label{eq:Phase}
\end{align}
%
$\Phi_0 \equiv \Phi(t=t_\text{coal})$ is an integration constant. The subscript N denotes the Newtonian (leading-order) contribution. 
Higher-order contributions can be added in terms a post-Newtonian series which make up $\lesssim 2\%$ of the total phase.
Although we will include contributions up to and including 2PN to obtain the results of Sec.~\ref{sec:results}, we will not explicitly show these expressions 
which can be found in Ref.~\cite{Blanchet_LRR}.

The nomenclature ``plus'' ($+$) and ``cross'' ($\times$) follows from the effects that passing GWs have on the plane transverse to their direction of propagation.
If we were to conceive of an imaginary detector made up of a circular configuration of point-particles lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress the circular arrangement in a $+$ and $\times$ pattern which is the manifestation of the tidal strain of the GWs on the tranverse plane.
%which is why $h_{+},h_{\times}$ are often called GW strains. 
Next, let us briefly explore how a real detector, i.e., an interferometer, responds to passing GWs.

\section{Interferometer response to gravitational waves}\label{sec:IFO_response}
\subsection{LIGO-Virgo configuration: L-shaped topology}\label{sec:LIGO_topo}
We start by first considering the L-shaped interferometer topology dating back to Michelson.
Although the GWs are described by propagating tensor modes, an interferometer (IFO) can only measure a scalar quantity
known as the response function (or GW strain)
which is a linear combination of the polarizations given by
%
\be
h(t) = F_+(\theta,\phi,\psi) \,h_+(t)+F_\times(\theta,\phi,\psi)\, h_\times(t) , \label{eq:detector_strain}
\ee
%
where
%%
%
\begin{align}
 F_+ &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\cos 2\psi-\cos\theta \sin2\phi \sin2\psi \label{eq:F_plus},\\
 F_\times &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\sin2\psi+\cos\theta \sin2\phi \cos2\psi \label{eq:F_cross}
\end{align}
%
%%
%$F_+, F_\times$ 
are the antenna pattern functions of the detectors; $\theta,\phi$ are the sky coordinates; and $\psi$ is
an additional angle coming from the respective rotations of detectors' frames to source frame. %(there is no need for $\psi$ in the case of a single detector).
%In principle, $\psi$ can be aligned with the polarization of the incoming GWs 
%
We can't apriori know $\theta, \phi,\psi$. However, we can extract their values with some limited precision over the course of an inspiral (preferably of BNS) 
emitting GWs which sweep across the detection band of more than one interferometer over thousands of cycles. This was indeed the case of GW170817
with a source sky localization of 28\,deg$^2$ using data from three inteferometers \cite{GW170817}. 
For our estimations, we will use suitable averages of these angles.
For details on how to obtain Eqs.~(\ref{eq:F_plus}, \ref{eq:F_cross}) see, e.g., Sec.~4.2.1 of Ref.~\cite{SchutzLRR}.

To compute the advance warning times we will need to know how ``loud'' the binaries become as they sweep across the interferometers' band.
This is achieved by computing the signal-to-noise ratio (SNR) of the GWs in the detectors' data stream.
This is done in the frequency domain so we need the Fourier transforms of the time-domain strains of Eqs.~(\ref{eq:hplus_TD}) and (\ref{eq:hcross_TD})
%
\begin{align}
 \tilde{h}_+(f) &= A \, \f{c}{D}\, \left(\f{G M_c}{c^3}\right)^{5/6}\, e^{i \Psi_+(f)}\, \f{1}{f^{7/6}}\,  \f{1+\cos^2\iota}{2}  ,\label{eq:hplus_FD}\\
 \tilde{h}_\times(f) & = A \, \f{c}{D}\, \left(\f{G M_c}{c^3}\right)^{5/6}\, e^{i \Psi_\times(f)}\, \f{1}{f^{7/6}}\, \cos\iota \label{eq:hcross_FD},
\end{align}
%
%
where $A= \pi^{-2/3} \sqrt{5/24}$.
Explicit expressions for $\Psi_{+,\times}$ show that they are out of phase by $\pi/2$
(the details of the Fourier transformation can be found in Sec.~4.5 of Ref.~\cite{Maggiore}).
Accordingly, the Fourier transform of the detector strain (\ref{eq:detector_strain}) is given by
%%
%
\be
\tilde{h}(f) = A\, \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} f^{-7/6}\, e^{i\Psi_\text{N}}\, Q(\theta,\phi,\psi,\iota), \label{eq:strain_FD}
\ee
%
%%
where 
%
\be
Q(\theta,\phi,\psi,\iota) = F_+(\theta,\phi,\psi)\f{1+\cos^2\iota}{2}  + i F_\times(\theta,\phi,\psi) \cos\iota \label{eq:Q},
\ee
%
is the quality factor.
The $i$ in front of $F_\times$ in $Q(\theta,\phi,\psi,\iota)$ is due to the $\pi/2$ phase difference between $+$ and $\times$ modes.
$\Psi_\text{N}$ is the leading-order contribution to the frequency-domain phase
%
\be
\Psi_\text{N}=\Psi_+(f)|_\text{N} = 2\pi f (t_\text{coal}+D/c)-\Phi_0-\f{\pi}{4}+ \f{3}{128}\left(\pi f\,\f{G M_c}{c^3}\right)^{-5/3} \label{eq:phase_FD}.
\ee
%
%
Higher-order contributions up to and including 3.5PN can be found in Ref.~\cite{SchutzLRR}.

The detection criterion we will employ here is quantified in terms of the optimal signal-to-noise ratio (SNR) defined by
%%
%
\be
\rho=\left[ \int_0^\infty d\ln f\, \f{|2\tilde{h}(f)\sqrt{f}|^2}{S_n(f)}\right]^{1/2} \label{eq:SNR},
\ee
%
%%
where $\sqrt{S_n(f)}$ is the {\it amplitude spectral density} (ASD) [also called spectral strain sensitivity] of the detector.
It is usually this quantity that is shown in a typical interferometer strain sensitivity plot with the characteristic strain, $\tilde{h}_c(f)\equiv2\tilde{h}(f)\sqrt{f}$, 
due to various GW sources overlaid for comparison. 
%
%against the amplitudes of various GW sources whose
%ASDs are given by $2\tilde{h}(f)\sqrt{f}$. This particular combination is called the characteristic strain. 
We will show such plots in Sec.~\ref{sec:results}.

Substituting Eq.~(\ref{eq:strain_FD}) into Eq.~(\ref{eq:SNR}) yields
%%
%
\be
\rho^2 = \f{5}{6}\, \pi^{-4/3} \f{c^2}{D^2}\left(\f{G M_c}{c^3}\right)^{5/3}|Q(\theta,\phi,\psi,\iota)|^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\, \label{eq:SNR_v2},
\ee
%
%%
where we truncate the integral at the cut-off frequency of the inspiral $f_\text{ISCO}=\Omega_\text{ISCO}/\pi$.

It remains to compute $|Q(\theta,\phi,\psi,\iota)|^2$. 
Since we can not know the direction of the source a priori, it is appropriate to average over the angles $\theta,\phi,\psi,\iota$ which we compute
%For our computations, we will only work with one detector so we can set $\psi=0$ without loss of generality, which results in
%%
%
%\be
%F_+(\theta,\phi) = \f{1}{2}(1+\cos^2\theta)\cos2\phi, \qquad F_\times(\theta,\phi) = \cos\theta \sin2\phi.
%\ee
%
%%
via the following RMS-averaging integral
%%
%
\be
\langle F^2_{+}\rangle \equiv \f{1}{2\pi}\int_0^{2\pi}d\psi \,\f{1}{4\pi}\int_0^{2\pi} d\phi\,\int_0^\pi d\theta \sin\theta\ F^2_{+}(\theta,\phi,\psi)=\f{1}{5}\label{eq:ang_av}
\ee
%
%%
and likewise $\langle F^2_{\times}\rangle=1/5 $.
Finally, we average over the orbital inclination angle
%
\be
%\langle g(\iota) \rangle = 
\f{1}{2} \int_0^\pi d\iota\sin\iota\left[\left(\f{1+\cos^2\iota}{2}\right)^2+\cos^2\iota\right] = \f{4}{5} .\label{eq:inc_ang_av}
\ee
Thus we have that
%
\be
\langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_{\theta,\phi,\psi,\iota} = \f{4}{25}\label{eq:RMS_th_ph_ps_iota}.
\ee
%
As we will also consider the case of $\psi=0,\iota=0$, we additionally introduce the following $\theta,\phi$-only averages
%
\be
 \langle F_+^2\rangle_{\theta,\phi} = \frac{7}{30},\qquad \langle F_\times^2\rangle_{\theta,\phi} = \frac{1}{6}
\ee
yielding
%
\be
\langle |Q(\theta,\phi,\psi=0,\iota=0)|^2 \rangle_{\theta,\phi} = \f{2}{5} \label{eq:RMS_th_phi}.
\ee
Finally, we add the case of an optimally-oriented, purely $+$-polarized source ($\psi=0,\iota=0$) that is directly overhead ($\theta=0$) simply resulting in 
%
\be
\langle |Q(\theta=0,\phi=0,\psi=0,\iota=0)|^2 \rangle = 1.
\ee
%
%
%
%\be
%\tilde{H}(f)\equiv  A\,\left\langle\, |Q(\theta,\phi,\psi,\iota)|^2\,\right\rangle^{1/2}\, \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} f^{-7/6}\, . \label{eq:ang_av_strain_FD}
%\ee
%

%%

In a network of $N$ interferometers, we can define a total effective SNR as follows
%%
%
\be
\rho_\text{tot} = \left[{\sum_{i=1}^N \rho^2_i}\right]^{1/2} \label{eq:SNR_total}
\ee
%
%%
where Eq.~(\ref{eq:SNR_v2}) is employed to compute $\rho_i$ coming from individual interferometers each with a specific quality factor $Q_i$.
Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
an \emph{imaginary network} of three detectors ($N=3$), where one interferometer is optimally oriented/positioned, another one operates at the RMS average thus
its sensitivity is relatively suppressed by a factor $2/5$ (Eq.~\ref{eq:RMS_th_ph_ps_iota}) due to suboptimal configuration.
Our third detector has even lower sensitivity with a relative suppression factor of $4/5-\sqrt{2/5}\simeq 0.1675$ which is essentially a $\{\theta$-$\phi\}$-RMS away
from the overall RMS averaged value of 2/5.
This is our way of simulating a future detection in the Advanced-LIGO-Virgo network of 2020s where the three interferometers will yield varying SNRs
due to their differing quality factors.
%
Therefore, to represent our multi-interferometer network, we introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) for each interferometer
%%
%
\be
\tilde{H}_i(f)\equiv \tilde{A}_i\, h_0\, f^{-7/6}, \label{eq:Hi_s}
\ee
%
%%
where
%%
%
\begin{align}
%\tilde{A}_i &\equiv A \langle |Q|^2\rangle^{1/2}_i=\f{1}{2}\sqrt{\f{5}{6}}\, \pi^{-2/3} \left\langle\, |Q_i(\theta,\phi,\psi,\iota)|^2\,\right\rangle^{1/2}\quad\text{and} \label{eq:A_tilde}\\
h_0 &= \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} \label{eq:h0}
\end{align}
%
and the $\tilde{A}_i$ are given in Table~\ref{table:network_params}. %for $i=1,2,3$. %Clearly, the strain and thus the SNR at each of our imaginary interferometers scales as $\langle |Q|^2\rangle^{1/2}_i$, thus
%%
The SNR for each interferometer can now be written as
%%
%
\begin{align}
\rho_i &= 2\tilde{A}_i\, h_0 \left[\int_0^{f_\text{ISCO}} df\, \f{f^{-7/3}}{S_\text{n}(f)} \right]^{1/2}\label{eq:SNR_i}.
\end{align}
%
We arbitrarily make the following assignments for our network: $h=1, m=2, l=3$ representing high, medium, low strains/SNRs, respectively. 
We summarize our network in the following Table~\ref{table:network_params}.
%%

\begin{table}[h]
\centering
\begin{tabular}{c||c|c|l}
 IFO ($i$) & configuration %& $\langle |Q_i|^2\rangle$ 
 & $\tilde{A}_i$ & $\tilde{H}_i(f)$\\
 \hline
 \hline
 1 & high ($h$) &  A & $A h_0\, f^{-7/6}$ \T\\
 2 & medium ($m$) & $\tfrac{2}{5}A$ & $ \tfrac{2}{5}A h_0 \, f^{-7/6}$\B\T \\
 3 & low ($l$)  & $\left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A$ & $ \left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A h_0 \, f^{-7/6}$\B \\
 \hline
\end{tabular}
\caption{%The averaged quality factors $\langle|Q|^2\rangle$ of 
Our imaginary network of three L-shaped interferometers (IFOs). Column four lists the magnitude of the strain for each IFO via Eq.~(\ref{eq:Hi_s}).
``Configuration'' describes how ideally oriented/positioned an IFO is with respect to a compact binary source. High means ideal configuration maximizing $Q_i$.
Medium is the RMS-averaged response. Recall $A= \pi^{-2/3} \sqrt{5/24}$. 
%Note that for an interferometer where the angle between the arms is $\alpha$, $A$ rescales to $A\sin\alpha$.
}\label{table:network_params}
\end{table}
%
%
We can now write the total SNR for our network
%%
%
\begin{align}
\rho_\text{tot} &= \sqrt{\rho^2_h+\rho^2_m+\rho^2_l} \label{eq:SNR_total_3IFOs} .
%	      &= 2A h_0 \sqrt{1+\tfrac{2}{5}+\tfrac{4}{25}} \left[\int_0^{f_\text{ISCO}} df\, \f{f^{-7/3}}{S_\text{noise}(f)}\right]^{1/2}\nn\\
%	      &= \sqrt{\frac{13}{10}}\,\pi^{-2/3}\,\f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6}\left[\int_0^{f_\text{ISCO}} df\, \f{f^{-7/3}}{S_\text{noise}(f)}\right]^{1/2} \label{eq:SNR_total_3IFOs_v2}.
\end{align}
%
%%
%Although we made several simplifying assumptions to obtain $\rho_\text{tot}$, these should not affect our total SNR estimation too much.
%For example, averaging over all the angles underestimates the SNR of an interferometer with a near-ideal orientation with respect to the incoming GWs
%while also overestimating the SNR of a badly oriented detector. Rewriting Eq.~(\ref{eq:SNR_total}) as Eq.~(\ref{eq:SNR_total_3IFOs}) compensates
%for these.
We will start Sec.~\ref{sec:results} by testing our network with GW170817 whose signal got picked up by the LIGO detectors around $f=30$\,Hz.
So we will change the lower limit of the integral in Eq.~(\ref{eq:SNR_total_3IFOs}) from $0$ to $30$.
For our advance warning times we will further use separate initial frequencies for each inteferometer as we will explain in Sec.~\ref{sec:results}.

\subsection{Einstein Telescope configuration: triangular topology}\label{sec:ET_topo}
Current design of Einstein Telescope is based on a [equilateral] triangular configuration with 10\,km armlengths \cite{ET_doc}.
Within this equilateral triangle, ET will consist of three V-shaped cryogenic interferometers housed underground to
sigificantly reduce seismic and gravity-gradient noises \cite{ET_doc}.
This closed topology will allow the detector to form a null stream completely devoid of a signal \cite{Sathyaprakash:2012jk},
which can be used to rule out spurious events \cite{Wen:2005ui}.
As we will show below, the response function and the quality factor of the triangular configuration are independent of the azimuthal angle $\phi$
hence ET will have no blind spots \cite{Regimbau:2012ir}.
However, the $60^\circ$ arm separation reduces the strain of a V-shaped interferometer by a factor of $\sin 60^\circ=\sqrt{3}/2$ compared
to an L-shaped interferometer. So for a single V-IFO the antenna patterns of (\ref{eq:F_plus}, \ref{eq:F_cross}) become
%
\be
F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \qquad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi)\label{eq:F1plus_F1cross}\, ,
\ee
%
where the superscript $1$ labels one of the three V's of the triangle.
Since the other two V IFOs lie in the same plane as the first one, their antenna patterns can be obtained simply by rotating in the azimuthal
direction by $120^\circ, 240^\circ$, respectively
%
\begin{align}
 F^2_{+,\times}(\theta,\phi,\psi) &= F^1_{+,\times}(\theta,\phi+2\pi/3,\psi), \label{eq:F2plus_F2cross}\\
 F^3_{+,\times}(\theta,\phi,\psi) &= F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \label{eq:F3plus_F3cross}.
\end{align}
%
The invidual antenna responses combine to cancel the $\phi$ and $\psi$ dependence of the combined power pattern
%
\be
F^2_\bigtriangleup \equiv \sum_{A=1}^3 \left(F^A_+\right)^2+\left(F^A_\times\right)^2 = \f{9}{32}\left(1+6\cos^2\theta + \cos^4\theta\right). \label{eq:ET_power_pattern}
\ee
%
From this, we immediately have that the RMS average is given by $\langle F_\bigtriangleup\rangle =3/\sqrt{10}$ and the minium value is $F_\bigtriangleup(\pi/2)=3/\sqrt{32}$;
%As $F^2 > 0$ for all $\theta$ with its RMS average $\sqrt{2/5}\simeq 63.2\%$ of optimal $F$ and its
thus a triangular detector made-up of three V-IFOs has all-sky coverage.

For the total SNR accumulated in a triangular detector we have
%
\begin{align}
\rho^2_{\text{tot},\bigtriangleup} & = \sum_{A=1}^3 \rho_A^2 \nn \\
 & =  \f{5}{6}\, \pi^{-4/3} \f{c^2}{D^2}\left(\f{G M_c}{c^3}\right)^{5/3}|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \, ,\label{eq:ET_SNRsq}
\end{align}
where
%
\be
|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota \label{eq:Q_sq_ET}
\ee
%
which is independent of $\phi$ \cite{Regimbau:2012ir}. We once again take the RMS average of this quantity
%$Q(\theta,\phi,\psi,\iota)$ is the quality factor of the detector.
%
\be
\bar{Q}^2_\bigtriangleup\equiv\langle |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \rangle_{\theta,\phi,\psi,\iota} = \f{9}{25}\label{eq:RMS_ET}
\ee
%
which is $5/2$ times higher than a single L-shaped IFO's RMS average of 4/25 [cf. Eq.~(\ref{eq:RMS_th_ph_ps_iota})].

As we can not know the source sky position or orientation we will use the RMS-averaged SNR for our computations %(\ref{eq:ET_SNRsq})
%
\be
\rho_{\text{tot},\bigtriangleup} = \f{36}{25}A^2 h_0^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \label{eq:ET_SNR},
\ee
where $h_0$ is given by Eq.~(\ref{eq:h0}) and $A=\pi^{-2/3}\sqrt{5/24}$ as before. % from Sec.\ref{sec:LIGO_topo}. 
Accordingly, we define an RMS-averaged frequency-domain
strain
%
\begin{align}
\tilde{H}_\bigtriangleup(f, D)&\equiv A\,  \bar{Q}_\bigtriangleup\, h_0 f^{-7/6} \nn \\
   & = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} f^{-7/6}. \label{eq:H_delta}
\end{align}
%
It is this strain that we will use as a typical ET source; thus in this sense,
$\tilde{H}_\bigtriangleup(f,D)$ is like the $\tilde{H}_i(f)$ of Table~\ref{table:network_params}.
But whereas in the case of a three L-IFO network we represented the detector response due to a single source in terms of three different
values $\tilde{H}_i(f)$, for ET we will only consider $\tilde{H}_\bigtriangleup(f)$ as we have already angle-averaged over all three V-IFOs antenna patterns.
%$\tilde{H}_\bigtriangleup(f)$, as given by Eq.~(\ref{eq:H_delta}), depends only on the luminosity distance and the chirp mass.
In Sec.~\ref{Sec:ETB} we will consider BNS systems inspiralling at varying luminosity distances as typical sources for ET.
To compute the resulting SNRs, we will slightly modify Eq.~(\ref{eq:ET_SNR}) and use $\sqrt{S_n(f)}$ for the B and C configurations of ET.

Before we present our results, we list the various idealizations/simplifications that we adopt to simplify our computations.
For each idealization we present an estimated error. %that propa
Our overall conclusion is that our simplifications do not significantly change our estimations of the advance warning times.% which we quantify below.
%take full advantage of all the available analytical results.
%
%
%
%
\subsection{Simplifications and idealizations used in evolving the inspiral}\label{sec:idealizations}
In this section, we justify our simplifications with brief computations.
\begin{enumerate}
 \item {\it Neglecting strong-field gravity and finite-size effects.}
As our aim here is to provide a rough estimation for the advance warning times, we will model the neutron stars using point masses and carry out this treatment all the way to the merger. The point-particle treatment is severely inadequate for the strong-field evolution of the binary. However, these systems spend only roughly the last second of the inspiral in this regime, therefore our underestimation of the strong-field effects will not matter for timescales lasting dozens of minutes to hours.
For example, from $f=100\,$Hz, the inspiral lasts a mere $\approx 2.18\,$ seconds until merger. The canonical BNS above has separation $r\approx 155.5\,$km at $f=100\,$Hz, which translates to a dimensionless strength of gravity of $\approx 2.66\%$ for which the Newtonian evolution is adequate.
We will nonetheless supplement our Newtonian (leading order) evolution with post-Newtonian (pN) knowledge up to second post-Newtonian order (2pN). %, next-to-next to leading order). 
Though it is now possible to go up to 4pN, we suffice with 2pN here as higher-order contributions make miniscule changes to our estimations for advance warning times. 
%
\item {\it Truncating the inspiral at the Schwarzschild ISCO.}
We artificially end the inspirals at the Schwarz-schild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6M$ and angular frequency $\Omega_\text{ISCO} = (M/r^3_\text{ISCO})^{1/2}$ in natural units, which translates to the following dominant-mode (quadrupole) GW frequency
\be
f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571\,\text{Hz} \label{eq:f_isco},
\ee
where $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$, however, there is no simple expression for it.
Additionally, above $f \approx 200\,$Hz tidal effects are expected to show up in the GW signal.
%These further complicate to an already highly dynamic spacetime. 
A faithful evaluation of BNS systems above $f\gtrsim 100\,$Hz is a very active branch of general relativity today,
but beyond the scope of this article. As we showed above, our disregard for relativistic effects costs us a few seconds at most.%requires fully relativisticmagneto-hydrodynamic large-scale computing clusters.
%
\item {\it Setting} $m_1=m_2=1.4 M_\odot$.
Let us also briefly explore what the cost of setting $m_1=m_2=1.4 M_\odot$ will be for our calculations. 
Including the error bars, the known range for neutron star masses runs from $\sim 0.5 M_\odot$ to $ \sim 3 M_\odot$ with the actual values restricted
between $\sim 1 M_\odot$ and $\sim 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
Of these measured masses, a subset comprised of double neutron stars, such as the famed Hulse-Taylor binary, have the smallest error bars with masses
ranging from $\sim 1.2 M_\odot$ to $\sim 1.5 M_\odot$. 
Additionally, the masses involved in GW170817 are inferred to be between $1.17 M_\odot$ and $1.60 M_\odot$ \cite{GW170817}.
Therefore, let us restrict the masses to lie between $1.2 M_\odot$ and $1.6 M_\odot$ then focus on % ranges $R_{1,2} \in [1,2]/(1.4)$. 
the quantities of interest for us, which are %the GW/orbital frequency ($f/f_K$), %the radiated power in GWs ($\dot{E}$), the rate of change of GW/orbital frequencies ($\dot{f}$), 
the inspiral time ($\tau_\text{insp}$), the GW strain at the detector in the frequency domain ($\tilde{h}$) and
the frequency of the innermost stable circular orbit ($f_\text{ISCO}$) given by Eq.~(\ref{eq:f_isco}) above.
From the previous section, we know how these scale in terms $M_c, M$ thus $m_1, m_2$, all of which we summarize in Table \ref{tbl:scalings} below.
%%
%
\begin{center}
\begin{table}[ht]
\begin{tabular}{|l|ccc|}
\hline
 Quantity & Standard Scaling & Scaling in terms of $m_1,m_2$ & Min $\le$ Value$_{1.4} \le$ Max\\
\hline
%$\dot{E}$ & $ \mu^2 M^3 $ & $ m_1^2 m_2^2(m_1+m_2) $& $ 0.871\le2.83\le 9.86 $ \\
%$\dot{f}$ & $ M_c^{5/3} f^{11/3} $ & $m_1 m_2 (m_1+m_2)^{3/2} $&$ 0.372\le 2 \le 11.9 $ \\
%$f=2f_K$ & $M^{1/2}$& $(m_1+m_2)^{1/2}$& $1.2 \le 1.41 \le 1.69 $\\
$\tau_\text{insp}$ & $M_c^{-5/3} $ & $(m_1 m_2)^{-1}(m_1+m_2)^{-1} $& $0.335\le 0.5\le 0.794 $ \\
$\tilde{h}$ & $M_c^{5/6} $ & $(m_1 m_2)(m_1+m_2)^{3/2} $& $ 0.7834\le 0.891 \le 0.996 $ \\
$f_\text{ISCO}$ & $M^{-1} $ & $(m_1+m_2)^{-1} $& $0.4375\le 0.5\le 0.583 $\\
\hline
\end{tabular}
\caption{The scaling of the physical quantities of interest in this article in terms the binary masses $m_1, m_2$ restricted to lie between $1.2M_\odot$ and $1.6 M_\odot$. We used Kepler's third law to obtain $f \sim f_K \sim M^{1/2}$.
Value$_{1.4}$ represents the value of the quantities in column three evaluated at $m_1=m_2=1.4 M_\odot$.
Unlike the orbital frequency $f_K$, the ISCO frequency $f_\text{ISCO}$ scales as $M^{-1}$ as shown in Eq.~(\ref{eq:f_isco}).}
\label{tbl:scalings}
\end{table}
\end{center}
%
%%
%
The ranges in column four show that $\tilde{h}$ changes roughly by $\pm 10\%$ across our chosen NS mass range whereas the variation
in $f_\text{ISCO}$ matters not as it affects the advance warning times by less than second (see above).
The inspiral time seems to be more sensitive to our chosen mass values as indicated by roughly the ${}^{+60\%}_{-30\%}$ variation 
in Table \ref{tbl:scalings}. %$\tau_\text{insp}^{1.4}$ as shown in Table \ref{tbl:scalings}.
As our intent is to provide an estimation for advance warning times in terms of orders of magnitude, this variation is tolerable.
%
\item {\it Neglecting eccentricity.}
We further simplify our treatment by considering only quasi-circular inspirals meaning that at any given instant, 
the orbit can be treated as a circular orbit with constant Keplerian frequency $f_K = (GM/r^3)^{1/2}/(2\pi)$, where $r$ is the radius of the circular orbit.
It was Peters \& Matthews who first showed that eccentric binaries circularize in the weak field \cite{PM1963}. 
%For large eccentricities, i.e., $ 1-e\ll 1$, the circularization rate is quite steep: $ \dot{e}\sim -(1-e^2)^{3/2} $.
Using $\dot{a}=\dot{a}(a,e), \dot{e}=\dot{e}(a,e)$ they obtained
%
\be
a(e) = c_0\, \f{e^{12/19}}{1-e^2}\left(1 + \f{121}{304}e^2\right)^{870/2299} \equiv c_0\, g(e) \ , \label{eq:a_of_e}
\ee
%
where $a$ is the semi-major axis of the eccentric orbit and $c_0$ is a constant. Thus, for $e\ll 1$ we have $g(e)\approx e^{12/19}$, which means
that for a system with current parameters $a_i, e_i$, we can write $e\approx [a\, g(e_i)/a_i ]^{19/12}$.
Let us apply this to determine the eccentricity of the Hulse-Taylor binary pulsar when it will have $f=2f_K = 1\,$Hz, i.e., 
$a \simeq 810.5\,$km with currently observed parameters of $a_i \simeq 2\times 10^6\,$km and $e_i \simeq 0.617$. 
A quick calculation yields $e\simeq 1.09\times 10^{-10}$. 
Hence, we see that the BNS orbits will have circularized by the time they enter the interferometers' bandwidth.
%
\item {\it Quasi-circularity.}
Next, let us test the assumption that the motion is quasi-circular. 
This implies that that the timescale for the orbital radius to change is much longer than the orbital timescale, i.e., radial velocity $\ll$ tangential velocity during the inspiral. From $\Omega^2 = GM r^{-3}$ we can straightforwardly obtain 
%
%\be
%\f{\dot\Omega}{\Omega} = -\f{3 \dot{r}}{2 r} \label{eq:Omega_dot_to_r_dot}
%\ee
%
an expression for the ratio of radial velocity to tangential velocity
%
\be
\f{|\dot{r}|}{r\Omega}=\f{2}{3}\f{|\dot\Omega|}{\Omega^2} \label{eq:ratio_of_radial_vel_to_tang_vel} .
\ee
%
The quasi-circular approximation implies that $|\dot{r}| \ll r\Omega$ which translates to $|\dot\Omega| \ll \Omega^2$ which then gives
%
\be
\f{\dot\Omega}{\Omega^2} = \f{96}{5} \f{(G M_c)}{c^5}^{5/3}\Omega^{5/3} \ll 1 \label{eq:omega_dot_over_omegasq}
\ee
%
using Eq.~(\ref{eq:fdot}). %Assuming $\ll 1$ means $\le 10^{-3}$ 
For example, setting $\dot{\Omega}/\Omega^2 = 10^{-3}$ yields $f= \Omega/\pi \simeq 142.8\,$Hz which, as explained above, 
is practically the last second before the merger. Thus, we see that we can safely employ the quasi-circular motion assumption in our
estimations for advance warning times.
%
%What about our negligence of higher-order multipoles in the evolution of the binary under the emission of GWs? 
\item {\it Neglecting higher-order multipole moments.}
Another reasonable question is how much our estimation of advance warning times is
affected by neglecting higher-order contributions to the loss of energy coming from, e.g., the current quadrupole and the mass octupole moments.
It can be shown that the power radiated by the current
quadrupole ($\dot{E}_\text{cq}$) by a binary in a circular orbit is $\ord(v^2/c^2)$ smaller than the dominant quadrupole power. More precisely, we have \cite{Maggiore}
%
\be
\f{\dot{E}_\text{cur}}{\dot{E}} = \f{1215}{896} \f{v^2}{c^2}\left(\f{m_2-m_1}{M}\right)^2=\f{1215}{896}\f{(\pi G M f)^{2/3}}{c^2}\left(\f{m_2-m_1}{M}\right)^2\, . \label{eq:Oct_quad_ratio}
\ee
%
At $f=100\,$Hz, the first two factors $\simeq 3.6\times 10^{-2}$ for $M=2.8 M_\odot$ which tells us that even in the strong-field regime, 
the next-to-leading order contribution is a two orders of magnitude smaller.
The ratio in Eq.~(\ref{eq:Oct_quad_ratio}) is further supressed by $(m_2-m_1)/M^2$ which, for our idealized equal-mass system, 
yields zero so we can neglect the current-quadrupole radiation completely. In a similar fashion, it can be shown that the power radiated by the mass octupole ($\ell=3$)
scales the same way as in Eq.~(\ref{eq:Oct_quad_ratio}) with respect to the dominant mass quadrupole radiation, but is $\sim 50$ times smaller. 
Hence we can neglect it without worry for our work. Higher moments are suppressed by higher factors of $v^2/c^2$ as can be shown using post-Newtonian theory. 
Thus, our exclusiveness to keeping only the mass-quadrupole radiation is well justified.

%
\item {\it Neglecting the neutron star spins.}
It is generally believed that NSs do not have large enough angular momentum to impart interesting spin effects into the GWs emitted by the BNS systems.
The dominant effect due to the spins is the spin-orbit (SO) precession which contributes to the energy flux at the 1.5pN order [$\ord(v^3/c^3)$] with respect to the leading-order quadrupole $\dot{E}$ of Eq.~(\ref{eq:Edot}) \cite{Blanchet_LRR}. 
%Writing this contribution as a ratio to $\dot{E}$ and 
Restricting to the case of $m_1=m_2$ we obtain
%
\be
\f{\dot{E}_{\text{SO}}}{\dot{E}} \lesssim 4 \f{G\Omega m}{c^3}\chi + \ord\left(\f{v^5}{c^5}\right) \label{eq:spin_orbit}\, ,
\ee
%
where we introduced the dimensionless Kerr spin parameter $\chi\equiv {S}/({G m^2})$ which, for a NS with spin $S$, can be written as
%
\be
\chi=\f{c}{G} \f{I}{m^2} \f{2\pi}{P}, \label{eq:NS_spin}
\ee
%
where $m$ is the mass, $P$ is the spin period, and $ I = (2/5) m R^2 \kappa$ is the moment of inertia of the NS with $R$ being the radius of the NS and $\kappa \approx \ord(1)$ an intrinsic constant (see, e.g., Sec.~6.2 of \cite{Colpi_Sesana}). 
A rather compact NS with $m=1.4 M_\odot, R=11\,\text{km}, P= 10\,\text{ms}$ has $\chi\lesssim 0.05$ whereas
the fastest spinning known NS has $\chi\lesssim 0.04$ \cite{FastestNSspin}.
Therefore, at $f= 100\,$Hz, the first term in the RHS of Eq.~(\ref{eq:spin_orbit}) gives $4.252\times 10^{-4}$. 
On the other hand, the spin-spin effects contribute at $\ord(v^4/c^4)\times\dot{E}$ hence $\lesssim \dot{E}_\text{SO}$.
Thus, we have justified our negligence of the effects of NS spins.
%
\item {\it Neglecting cosmological effects.}
When we take into account the effects of the large-scale structure of the universe, many quantities of interest are scaled by $(1+z)^\alpha$ where $\alpha$
is the appropriate power. The standard treatment adopts a Friedmann-Robertson-Walker cosmology with scale factor $a(t)$ and curvature $k=\pm 1, \text{ or } 0$.
Introducing the subscript ${}_s$ to denote quantities evaluated at the source frame, we have the following cosmological corrections
%%
%
\begin{align}
 D & \rightarrow  (1+z)a(t) D,\\
 f & \rightarrow (1+z)^{-1} f_s\, .
 %M_c & \rightarrow (1+z) M_{s,c},
\end{align}
%
Given that $\dot{f}_s\sim f^{11/3}_s, h(t)\sim D^{-1} f_s^{2/3}$,
the observed frequency evolution and the GW strain change according to % in the detector frame
%%
\begin{align}
\dot{f}\ \ &\sim (1+z)^{5/3}{f}^{11/3},\\
h(t) & \sim (1+z)^{5/3} h(t).
\end{align}
%
Looking at Eqs.~(\ref{eq:fdot}, \ref{eq:hplus_TD}, \ref{eq:hcross_TD}) we spot a common factor of $M_c^{5/3}$ in all of them.
Therefore, we can accommodate the cosmological effects by introducing the redshifted chirp mass $\mathcal{M}_c\equiv (1+z) M_c$
which changes Eqs.~(\ref{eq:fdot}, \ref{eq:hplus_TD}, \ref{eq:hcross_TD}) to
%The effect of the cosmological redshift on our estimations of advance warning times manifests itself by modifying 
%
\begin{align}
\dot{f} &= \f{96}{5}\pi^{8/3} \f{(G \mathcal{M}_c)}{c^3}^{5/3}\, f^{11/3} \label{eq:fdot_redshifted},\\
h_c(t) & = \f{4}{D}\left(\f{G \mathcal{M}_c}{c^2}\right)^{5/3}\left(\frac{\pi f}{c}\right)^{2/3} \label{eq:strain_TD_redshifted}\, ,
\end{align}
%
where $f$ is the usual frequency in the observer/detector frame.
So we see that the effects of the cosmological redshifting can be accounted for by the transformation $M_c\rightarrow \mathcal{M}_c$.
This is because both $\dot{f}$ and the GW amplitude are governed by the time scale $G M_c/c^3$.
For our work here, the only important consequence is the redshifting of the frequency at which we truncate the inspiral, 
i.e., $f_\text{ISCO}\simeq 1571\,$Hz in the source frame.
For our work, we consider a maximum BNS distance of 1\,Gpc which is reasonable given the sensitivity
of A-LIGO and the ET. $D = 1\,$Gpc translates to $z \approx 0.25$.
Therefore, in the detector frame $f_\text{ISCO}$ is redshifted to $f \approx 1257\,$Hz. 
From our computations above, we know that this shift adds a negligible correction to the timescales that interest us here.
Thus we may safely disregard the effects cosmology.
%
%Furthermore, the physical quantities that we actually observe are blind to this redshift correction. Only after high-precision measurements of
%the chirp mass and the GW polarizations $h_+, h_\times$ can we extract $z$. 
% can be obtained to a very
%high precision in the case of BNSs from the data for $\dot{f}$; e.g., $\mathcal{M}_c = 1.188^{+0.004}_{-0.002}$ for GW170817.
%The ratio $h_+/ h_\times$ gives us the orbital inclination $\iota$.
\end{enumerate}
%
%

\section{GW170817 as a test of our model Advanced LIGO-Virgo network}\label{Sec:GW170817}
On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system were detected by the Advanced LIGO-Virgo network.
The event, first picked up by LIGO Hanford (H1), swept from $\sim 30\,$Hz to $\sim 2000\,$Hz in the detectors' frequency band with an accumulated total SNR of
%18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
$\rho_\text{tot} = 32.4$ \cite{GW170817}
The inferred duration of the event in the network bandwidth is $\sim 60\,$ seconds during which $\sim 3000$ cycles of GW were emitted \cite{GW170817_Facts}.
Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following values were inferred for the total mass, the chirp mass,
and the luminosity distance of the source with 90\% confidence:
%
\be
M = 2.74^{0.04}_{-0.01} M_\odot, M_c = 1.188^{+0.004}_{-0.002} M_\odot, D= 40^{+8}_{-14}\,\text{Mpc}. \label{eq:GW170817_params}
\ee
%
Note that the error bar for the chirp mass is very small
due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}).

How well does the ``naive'' formulation based on the quadrupole formula perform? 
To test this, let us first compute the inspiral time, $\tau_\text{insp}$, and the number of GW cycles, $\mathcal{N}_\text{cyc}$, for this BNS system with initial frequency $f_i=30\,$Hz and final frequency $f_\text{ISCO} \simeq 1605.37\,$Hz. 
Eqs.~(\ref{eq:tau_insp}) and (\ref{eq:Ncyc2}) provide us with the leading-order values
%%
%
\be
\tau_\text{insp}^{0\text{PN}} \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2680\,\label{eq:GW170817_values_0PN}. 
\ee
%
%%
If we wish to do better, we can add all of the known post-Newtonian contributions 
(up to 3.5PN\footnote{Though the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$ though we suspect that a few PN experts have already obtained these.}) resulting in
%%
%
\be
\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \label{eq:GW170817_values_3p5PN}\, .
\ee
%
%%
These are very close to the inferred values of $\tau_\text{insp}\approx 60$\,seconds and $\mathcal{N}_\text{cyc} \approx 3000$ which we can obtain if we use $f_i \approx 28-29\,$Hz.
%Our PN-only computation underestimates $\mathcal{N}_\text{cyc}$ because we artificially end the inspiral at the Schwarzschild ISCO whereas
%numerical simulations indicate that the inspiral carries on past the Schwarzschild ISCO separation of $6 G M/c^2$. 
%Reusing Eq.~(\ref{eq:Ncyc1}) from 1600 Hz to 2000 Hz only adds {\bf one} cycle.

We now test our imaginary network using the best-inferred values for $M,M_c,D$ from GW170817 given in Eq.(\ref{eq:GW170817_params}) above and 
neglecting the cosmological corrections as 40\,Mpc is in our ``local'' neighbourhood when considering cosmological distances.
The test involves computing the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
%%
%
\begin{align}
\bar{\rho}_i\equiv\rho_i(f_0,f_f) &= 2\tilde{A}_i\, h_0\left[ \int_{f_0}^{f_f} df\, \f{f^{-7/3}}{S_\text{n}(f)}\right]^{1/2} \label{eq:SNR_i_with_fi}.
\end{align}
%
where $f_0 =30\,\text{Hz}, f_f= f_\text{ISCO}$ for GW170817 and $\tilde{A}_i$ given in Table~\ref{table:network_params}.
For $S_\text{n}(f)$ we use actual [noise-subtracted] L1 data for GW170817 from LIGO's website \cite{LIGO_L1_data}.
The data, sampled at 4096\,Hz, is given as a discrete time series $h(t_i)$ for a duration of 2048\,seconds in time steps of $\Delta t=1/4096\simeq 2.44\times 10^{-4}\,$seconds.
%with the amplitude peaking at $1842.43\pm0.03\,$seconds.
We first Fourier-transform this data to frequency space and apply several high- and low-frequency filters to isolate a window of $f\in [10, f_\text{ISCO}]$.
The LIGO Open Science Center has a detailed Python-based tutorial on how to do this using the data from the very first GW detection (GW150914) \cite{LIGO_tutorial}. 
We use a $\verb|Mathematica|$ based code developed at UCD to do the same for GW170817.

Fig.~\ref{fig:figGW170817} shows our network. The red curve is L1's ASD (sensitivity) during GW170817. We assume our three IFOs to identically have this sensitivity,
but because their orientations and response functions differ, their sensitivity to a localized source is reduced. We represent this reduction by lowering the
amplitude of the incoming GWs by appropriate factors explained in Sec.~\ref{sec:BNS_inspiral} and shown in Table~\ref{table:network_params}.
The amplitude-adjusted strains $ \tilde{H}_i(f)$ are represented by the solid ($i=h$), dashed ($i=m$), and dotted ($i=l$) lines in the figure where we actually plot
$2\sqrt{f} \tilde{H}_i(f)$ as explained above.
Using Eq.~(\ref{eq:SNR_i_with_fi}) we can immediately compute the SNRs accumulated by our network
%%
%
\be
\bar\rho_h = 35.8,\quad \bar\rho_m = 14.3,\quad \bar\rho_l = 6.00 \label{eq:GW170817_SNRs}.
\ee
%
%%
These are comparable to actual SNRs of L1, H1, and V1 for GW170817, which are, 26.4, 18.8, and 2.0, respectively\footnote{At the time of GW170817, Virgo's sensitivity had not reached the level of LIGO's. Hence it accumulated a much smaller SNR for GW170817. By 2020, Virgo should be operating at nearly the same sensitivity of LIGO.}.
To accommodate more realistic orientations, we show two shaded regions in Fig.~\ref{fig:figGW170817}. The inspirals in the lighter region yield SNR$\ge 22.34$ as
they sweep from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz whereas inspirals in the darker region accumulate $ \bar\rho_l \le \text{SNR} \le 22.34$.
Given a network of three equally sensitive, randomly oriented IFOs we expect that a single BNS inspiral would produce two detector strains in the darker region 
and one in the lighter region.
%
%
\begin{figure}[h!]
\includegraphics[height=9cm]{Figures/GW170817_strains.pdf}
\caption{GW170817 as it sweeps from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz across our network with ASD (sensitivity) of LIGO Livingstone (L1) during the event (red curve).
We also show the Hanford detector's sensitivity for comparison. The dashed, solid and dotted lines represent the strains 
$2\sqrt{f} \tilde{H}_i(f)$ (see, e.g,. Eq.~(\ref{eq:Hi_s}) and Table~\ref{table:network_params}) due to the inspiral of
a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}). The change in strain amplitudes is the result of a
given interferometer's orientation and the sky position of the source. In other words, the dashed line is how ``loud'' GW170817 
is at an optimally oriented IFO with L1's sensitivity
%would be if L1was optimally positioned and oriented 
(quality factor $Q=1$). Similarly, the solid line is the strain in a randomly oriented IFO with randomized source sky location, hence
we use the RMS-averaged L1 sensitivity which effectively lowers the solid line by a factor of $2/5$. %, but with RMS-average over all angles 
%determining source orientation and position. 
Finally, the dotted line represents a pessimistic IFO orientation and source location (sub-optimal configuration)
resulting in a reduction of amplitude to $ 16.7\%$ of the optimal case. 
The shading represents the region of likelihood for where the strain due to an inspiralling BNS would be. In the case of a three-IFO
network, we expect all three strains to exist somewhere in the shaded region.
%The darker region marks $\text{RMS}\pm(\sqrt{2/5}-2/5)$ translating to an amplitude range of $ 16.7\% - 63.2\%$ of the maximum $\tilde{H}_h(f)$.
%For a randomly located, oriented BNS inspiral, we expect its strain to sweep in the lighter region for one IFO and in the darker region for the other two IFOs.
The dot-dashed (green) curve shows a more realistic strain constructed with data from numerical simulations of Ref.~\cite{Read:2009yp}.
The breakdown of the leading-order $\sqrt{f}f^{-7/6}=f^{-2/3}$ behavior around $f\sim100\,$Hz due to tidal effects is clear.
%Note that although we extend the $\sqrt{f}f^{-7/6}=f^{-2/3}$ power law behavior of the strains all the way to ISCO, in actuality, this  starts breaking down .
}
\label{fig:figGW170817}
\end{figure}
%
%

We can now compute the total SNR of GW170817 as inferred by our network
%%
%
\be
\bar\rho_\text{tot}= \sqrt{\bar\rho^2_h+\bar\rho^2_m+\bar\rho^2_l}= 39.1 \, \label{eq:SNR_total_GW170817} .
\ee
%
%%
This also compares well with the actual value of 32.4. Therefore, we conclude that our imaginary network performs realistically enough to make predictions on the performance of IFOs in the 2020s and 2030s.
%
%
%
%
%
\section{Results: Advance warning times for inspiralling neutron stars}\label{sec:results}
 %\subsection{BNS inspirals at Advanced LIGO-Virgo and the Einstein Telescope}\label{Sec:BNS_2020_2030}
 %Recall that we are interested in the advance warning times that the (near)-future ground-based interferometers can provide for the optical astronomers before the prompt GRB at the end of the merger. 
 Our aim is to foretell GRBs using our network made up of three IFOs with A-LIGO design sensitivity in the 2020s and the Einstein Telescope sensitivity in the 2030s.
 Our predictive capabilities depend on how much advance warning the future networks will give us prior to the prompt merger/GRB.
 Our definition of advance warning is the inspiral time to the merger from a certain threshold instant $\bar{t}$ at which point the network ``agrees'' that there is an inspiral 
 event statistically significant enough to issue warnings to electromagnetic telescopes.
 We define this threshold instant to be given at a frequency $\bar{f}$ when the total SNR equals 15. 
 More specifically, in the case of the Advanced-LIGO-Virgo network (ALV), our statement is that there exists a frequency $\bar{f} < f_\text{ISCO}$ such that
 %
 \be
 \bar\rho_\text{tot}= \sqrt{\left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2}=15, \label{eq:SNR_bar}%2\tilde{A}_m\, h_0\left[ \int_{f_0}^{{\bar{f}}} df'\, \f{f'^{-7/3}}{S_\text{noise}(f')}\right]^{1/2} =15 .
 \ee
 %
 where $f_0^i$ are given by the solution set to
 %there exists some frequency $f_0 < \bar{f}$ such that
 \be
 \sqrt{S_\text{n}(f_0^i)} = 2\sqrt{f_0^i}\, \tilde{H}_i(f_0^i) \label{eq:f0},\qquad i=h,m,l
 \ee
 %
 with $f_0^i < \bar{f}$. In other words, $f_0^i$ are the initial GW frequencies at which a given inspiral enters the $i$th IFO's sensitivity band. 
 Once we know $\bar{f}$, we can compute the remaining time to the merger, $\tau_\text{insp}(\bar{f})$, using Eq.~(\ref{eq:tau_insp})
 and its 3.5PN-enhanced version from Ref.~\cite{Blanchet_LRR}. This is what we call our advance warning time $T_\text{AW}$.
 For simplicity, we set $m_1=m_2=1.4 M_\odot \implies M_c\simeq 1.219 M_\odot$, which we justified in
 Point 3 of Sec.~\ref{sec:idealizations}. 
 With the masses fixed, the only variable determining $h_0$ is the luminosity distance $D$ as can be seen from Eq.~(\ref{eq:h0}).
 We summarize our procedure in the flow diagram below.
 %
 %
  \begin{figure}[h!]
 \framebox{\Longstack[l]{Pick $D$}}$\longrightarrow$\framebox{\Longstack[l]{Construct\\ $\tilde{H}_i(f)$}} 
 $\longrightarrow$  \framebox{\Longstack[l]{Compute $f_0^i$\\ from Eq.(\ref{eq:f0})}} $\longrightarrow$  \framebox{\Longstack[l]{Compute $\bar{f}$\\ from Eq.(\ref{eq:SNR_bar})}}
 $\longrightarrow$  \framebox{\Longstack[l]{Compute $T_{AW}=\tau_\text{insp}(\bar{f})$\\ from Eq.~(\ref{eq:tau_insp})}}
  \caption{Flow diagram summarizing our procedure for computing advance warning times $T_\text{AW}$ with the Advanced-LIGO-Virgo network. 
  We will compute $T_\text{AW}$ for the case of $M=2.8M_\odot$ BNS system inspiralling at $D=50,100,200\,$Mpc. 
  %for A-LIGO and $D=200,400,1000\,$Mpc for the ET.
  }\label{fig:flow}
\end{figure}

%
 %\noindent
 %$ \boxed{{\scriptstyle \text{Pick $D$}}} \longrightarrow\boxed{\scriptstyle\text{Construct $\tilde{H}_m(f)$}}\longrightarrow\boxed{{\scriptstyle \text{Compute $f_0$ from Eq.(\ref{eq:f0})}}}\longrightarrow\boxed{\scriptstyle\text{Compute $\bar{f}$ from Eq.(\ref{eq:SNR_bar})}}\longrightarrow\boxed{{\scriptstyle \text{Compute }T_{AW}=\tau_\text{insp}(\bar{f})}} $\\
 %
 %
 We consider inspiralling BNS systems at $D=50,100,200\,$Mpc as our canonical sources for the ALV network.  
 %and BNS systems at $D=200, 400, 1000\,$Mpc for the ET network. 
 For each case, we compute $\bar{f}$ from Eq.(\ref{eq:SNR_bar}) with which we then compute $T_\text{AW}=\tau_\text{insp}(\bar{f})$.
  %
%\be
%\bar{\rho}_\text{tot}\equiv{\rho}_\text{tot}(f_0,\bar{f})= \sqrt{\left[{\rho}_h(f_0,\bar{f})\right]^2+\left[{\rho}_m(f_0,%\bar{f})\right]^2+\left[{\rho}_l(f_0,\bar{f})\right]^2} \label{eq:SNR_bar_total} 
%\ee
%
%to further strengthen our detection criterion (\ref{eq:SNR_bar}). 
%Finally, we will present 
We additionally calculate 
the total accumulated SNR from $f_0$ to $f_\text{ISCO}$ for each inspiral using%sweeping the A-LIGO and ET network bandwidths
 %
\be
\bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2} \label{eq:SNR_bar_FINAL} .
\ee
%
%
We will introduce the expressions for ET's $\bar\rho_\text{tot},\bar\rho_F$ in Sec.~\ref{Sec:ETB}.
To compute the SNRs defined above for the ALV network we require IFO noise data for which
we use the ASD for the BNS-optimized A-LIGO design sensitivity expected to be attained ca. 2020 \cite{LIGO2020}. 
This is plotted as the thick red solid curve in Fig.~\ref{fig:LIGO2020}.
Sweeping across the detector's frequency bands are RMS-averaged GW strains ($\tilde{H}_m$) due to BNS inspirals at various luminosity distances.
Each RMS-averaged strain is accompanied by its shaded region ranging from an optimally oriented strain ($\tilde{H}_h$) to a sub-optimally oriented strain ($\tilde{H}_l$). These regions were first explained in Sec.~\ref{Sec:GW170817} and shown in Fig.~\ref{fig:figGW170817}.
Recall that this is our way of representing the response of a three-IFO network to a single source, i.e., we map three different IFO responses due to a single source to a single IFO's response to three different sources differing in amplitudes as listed in Table~\ref{table:network_params}.
The height of a given strain above the detector sensitivity provides a good \emph{visual} estimation for the corresponding SNR,
but the reader should keep in mind that the actual computation involves a ratio, not a difference, as shown, e.g., in Eq.~(\ref{eq:SNR}).
%
%
%
\subsubsection{Forecasting GRBs in the 2020s with the Advanced LIGO-Virgo Network}\label{Sec:ALIGO2020}
We now compute the advance warning times that A-LIGO can provide us in the case of BNS inspirals at $D=50, 100,200\,$Mpc.
Fig.~\ref{fig:LIGO2020} displays the strains due to these inspirals in the same fashion as
Fig.~\ref{fig:figGW170817}: the solid (black), dotted (blue), and dashed (green) lines represent the RMS-averaged characteristic strains, $2\sqrt{f}\tilde{H}_m(f)$, at luminosity distances of $D=50, 100, 200\,$Mpc, respectively, with the shaded regions covering the range
between the optimally oriented case and the sub-optimal case.
%
%
\begin{figure}[h!]
\includegraphics[width=\linewidth]{Figures/ALigo_strains.pdf}
\caption{Typical $M=2.8 M_\odot$ BNS inspirals sweeping across the Advanced LIGO-Virgo network in the 2020s.
These may be the harbingers of short GRBs.
%inspiralling BNS systems sweeping across the most sensitive interferometer frequencies.
The solid (black), dotted (blue), and dashed (green) lines are the RMS-averaged strains ($2\sqrt{f}\tilde{H}_m(f)$) at luminosity distances of $D=50, 100, 200\,$Mpc, respectively. The accompanying shaded regions cover the region of likelihood for a three-IFO network as explained in Fig.~\ref{fig:figGW170817}.
The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals,
but as can be seen, the SNR hardly increases beyond $\sim 1000\,$Hz.
%Recall that we deliberately neglect the tidal and strong-field effects that modify the plotted $f^{-2/3}$ power law beyond $\sim 100\,$Hz.
%we artificially extend the leading-order $f^{-2/3}$ power law past $f\sim 100\,$Hz at which point tidal effects actually visibly modify this behavior.}
}
\label{fig:LIGO2020}
\end{figure}
%
%

The computation follows the procedure outlined in Fig.~\ref{fig:flow}. We use numerical root finding to determine $\bar{f}$ and $f_0^i$ for all three values of $D$. 
The computation of SNRs and advance warning times is straightforward. 
We summarize our results in Table \ref{table:LIGO2020} where we present both the 0PN and the 3.5PN results for the advance warning times
$T_\text{AW}$. As can be seen from the values for $T_\text{AW}$ in the table, we can at best expect 100\,seconds of early warning time.
This time increases to 2.5\,minutes in the case of another GW170817-like event with $D=40\,$Mpc.
The current best estimate for the event rate of BNS inspirals is $ 1540^{+3200}_{-1220}\,$Gpc$^{-3}$yr$^{-1}$, inferred from the O1 and O2 observing periods of Advanced LIGO \cite{GW170817}.
This translates to $\approx 0.1$ event per (40-Mpc)$^3$ per year, or taking the upper limit $\approx 0.3$. So we can at best hope to detect
one 40-Mpc inspiral per three years or longer.
Therefore, we do not expect to be able forecast GRBs in the Advance LIGO-Virgo era given that we might at best have a couple of minutes of warning time. 
However, given Moore's law and new search approaches based on deep learning (\cite{Gabbard:2017lja}) 
we prefer to remain optimistic about the prospects of forecasting at least one GRB in the 2020s. %that this latency can be reduced to minutes.
%if we dare to entertain peak CPU computation rates of $\sim 10^{13}\,$flops/sec for 2020 then $\sim 100$ computing cores would suffice to match-filter $10^5$ templates {\bf in how much time?} extrapolating on the results of Ref.~\cite{Cannon:2011vi}.
%
%Regardless of the future capabilities of search algorithms, 
%So if the automated warning routines in the 2020s become sophisticated enough to send out alerts in $\sim 1\,$minute then
%there might be hope to electromagnetically observe one to three GRBs or the resulting optical transient using 
%the Large Synoptic Survey Telescope \cite{LSST} might observe the resulting optical transient. 
%In the case of GW170817 it took nearly 11 hours to find this optical transient \cite{GBM:2017lvd}. 
%As is clear from Table~\ref{table:LIGO2020} we can hope to electromagnetically observe only the $D\lesssim 50\,$Mpc GRBs.
%
\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\hline
$D\,$(Mpc) & $\bar{f}\,$(Hz) & $T^{0PN}_\text{AW}$(sec) & $T^{3.5PN}_\text{AW}$(sec)& $\bar{\rho}_F$\T\B\\
\hline
50 & 22.8 &111.1 & 113.1 & 84.2 \T\\
100 & 36.2 & 32.41 & 33.08 & 42.1 \\
200 & 79.3 & 4.859 & 4.948 & 21.0 \\
\hline
\end{tabular}
\caption{The Advanced LIGO-Virgo (ALV) network's potential for providing advance warning times, $T_\text{AW}$, 
to electromagnetic observatories for inspiralling binary neutron stars at luminosity distances of $D=50,100,200\,$Mpc. 
$\bar{f}$ is the frequency at which the  signal-to-noise ratio (SNR) accumulated by the ALV network reaches 15. 
$\bar{\rho}_F$ is the total accumulated network SNR for each inspiral. We present both the Newtonian (0PN) 
and the 3.5 post-Newtonian result for the advance warning times.}\label{table:LIGO2020}
\end{table}
%

In addition to potentially alerting the E\,\&\,M community, the ALV network will accumulate impressive SNRs 
(see $\bar{\rho}_F$ in Table~\ref{table:LIGO2020}) for BNS inspirals out to 100\,Mpc.
Monte-Carlo simulations of BNS systems indicate that the measurement errors for the system parameters are proportional to $\bar\rho^{-1}_F$ \cite{Cutler:1994ys}.
Therefore, systems that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
$M_c, M$ \cite{Farr:2015lna}; (ii) sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};
(iii) $ \lesssim 10\%$ precision in the inferred NS masses \cite{Rodriguez:2013oaa} and the effective spin parameter $\chi_\text{eff}$ \cite{Zhu:2017znf}; and
(iv) restrictions on the equation of state and the tidal deformability
parameters of neutron stars \cite{Read:2009yp, Andersson:2009yt, PhysRevD.89.103012, PhysRevD.91.043002}.
We should caution the reader that such systems will make up $\lesssim 1\%$ of the population of BNSs detected by 
the ALV network \cite{Sathyaprakash:2012jk}.

\subsubsection{Forecasting GRBs in the 2030s using the Einstein Telescope}\label{Sec:ETB}
We now wish to quantify the forecasting capabilities of Einstein Telescope. To this end, we consider the inspiral of BNS systems
at luminosity distances of $100,200,400,1000\,$Mpc entering the ET band. The SNR accumulated at ET by each inspiral is given
by a slight modification to Eq.~(\ref{eq:ET_SNR})

%
\be
\bar\rho_{\text{tot,ET}} = \f{36}{25}A^2 h_0^2 \int_{f_0}^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \label{eq:ET_SNRv2},
\ee
where $f_0$ is the GW frequency at which the emitted GWs enter ET's detection band, i.e, $f_0 < f_\text{ISCO}$ such that
%
 \be
 \sqrt{S_\text{n}(f_0)} = 2\sqrt{f_0}\, \tilde{H}_\bigtriangleup(f_0, D) \label{eq:f0_ET}\,
 \ee
 %
with $\tilde{H}_\bigtriangleup(f, D)$ given by Eq.~(\ref{eq:H_delta}).
For the detector noise $\sqrt{S_n(f)}$, we adopt the ASD for the B and C configurations known as ET-B and ET-C, respectively \cite{Hild:2010id} which we plot as the solid dark (red) and light (brown) curves in Fig.~\ref{fig:ETB2030}.
Sweeping across these are four BNS inspirals at $D=100,200,400,1000\,$Mpc represented by solid (black), dotted (blue), dashed (green),
and dot-dashed lines (gray), respectively. These strains sit much higher than the detector noise
comparred with those in Fig.~\ref{fig:LIGO2020} which foretells us that the SNRs in the ET band will be much higher, 
thus the resulting advance warning times will be much longer.

\begin{figure}[h!]
\includegraphics[width=\linewidth]{Figures/ET_strains.pdf}
\caption{Typical GW sources that may be harbingers of GRBs in the 2030s: $M=2.8 M_\odot$ inspiralling BNS systems sweeping across 
the Einstein Telescope's sensitivity band for both B and C configurations.
The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the RMS-averaged strains, $2\sqrt{f}\tilde{H}_\bigtriangleup(f,D)$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
The vertical dashed (black) line marks $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals,
but numerical simulations indicate that the actual ISCO is smaller than the Schwarzschild value $6GM/c^2$ hence the true ISCO
frequency is greater than $f_\text{ISCO}$ used here.
As the plot shows, Einstein Telescope is sensitive enough in this regime to accumulate more SNR.
%Once again, keep in mind that we artificially extended the leading-order $f^{-2/3}$ power law past $f\sim 100\,$Hz at which point tidal effects actually visibly modify this behavior.
}
\label{fig:ETB2030}
\end{figure}
%
%
To determine $T_\text{AW}$ we once again impose the threshold SNR of 15 which is our criterion for sending out warnings to electromagnetic
observatories. Thus, rewriting Eq.~(\ref{eq:SNR_bar}) in the case of ET, we define $\bar{f}_\text{ET}$ as the solution to
%
\be
15=\f{36}{25}A^2 h_0^2 \int_{\bar{f}_\text{ET}}^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} .\label{eq:ET_fbar}
\ee
%
This gives us our advance warning time $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp}) which we
can slightly improve by using the 3.5PN expression. Therefore we will proceed in a manner similar to the procedure summarized in 
Fig.~\ref{fig:flow}) and compute the 0PN and 3.5PN advance warning times for all four inspirals in both the ET-B and ET-C bands.
We define the final accumulated SNR as
%
\be
\bar\rho_{F,\,\text{ET}}\equiv \f{36}{25}A^2 h_0^2 \int_{f_0}^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}  .\label{eq:rhoF_ET}
\ee
%

\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\hline
$D\,$(Mpc) & $\bar{f}\,$(Hz) & $T^{0PN}_\text{AW}$(sec) & $T^{3.5PN}_\text{AW}$(sec)& $\bar{\rho}_{F,\,\text{ET}}$\T\B\\
\hline
100 & 1.1435 & 2909 & 2942 & 307.1 \T\\
200  \\
\hline
\end{tabular}
\caption{ET-B}\label{table:ET}
\end{table}

\section{Binary black hole neutron star systems}
Tidal disruption, minimum BH mass $5 M_\odot$. Tidal force $\sim M/r^3 \sim M^{-2}$ hence the smaller the BH the more TD there will be.
Also need highly spinning BH to decreases the ISCO radius.

\begin{thebibliography}{}
\bibitem{Regimbau:2012ir}
\bibitem{KAGRA} \url{http://gwcenter.icrr.u-tokyo.ac.jp/en/}
\bibitem{KAGRA2} Akutsu et al. see bibtex
\bibitem{Patricelli:2016bkt}
\bibitem{CE} https://arxiv.org/pdf/1607.08697.pdf
\bibitem{Ozel_Freire} 1603.02698 [astro-ph.HE]
\bibitem{Freire_et_al_2007} The Astrophysical Journal, Volume 675, Issue 1, article id. 670-682, pp. (2008)., arXiv:0711.0925.  
\bibitem{GW170817}
\bibitem{PM1963}
\bibitem{Colpi_Sesana} 1610.05309 [astro-h.HE]
\bibitem{Maggiore}
\bibitem{Blanchet_LRR}
\bibitem{FastestNSspin} J. W. T. Hessels, S. M. Ransom, I. H. Stairs, P. C. C. Freire,
V. M. Kaspi, and F. Camilo, Science 311, 1901 (2006).
\bibitem{SchutzLRR} Schutz, Satyaprakash, LRR
\bibitem{GW170817_Facts} GW170817 Factsheet \url{https://www.ligo.org/detections/GW170817/images-GW170817/GW170817_Factsheet.pdf}.
\bibitem{4PN_EoM_paper} L. Bernard et al., [gr-qc:1711.00283]
\bibitem{Reid} J. Reid, the NS inspiral figure tidal corrections
\bibitem{LIGO_L1_data} Data release for GW170817 \url{https://losc.ligo.org/events/GW170817/}
\bibitem{LIGO_tutorial} LIGO Open Science Center signal processing tutorial at \url{https://losc.ligo.org/s/events/GW150914/GW150914_tutorial.html}
\bibitem{LIGO2020} Advanced LIGO anticipated sensitivity curves at \url{https://dcc.ligo.org/LIGO-T0900288/public}
\bibitem{Hild:2010id} S. Hild et al. Class.Quant.Grav. 28 (2011) 094013  arXiv:1012.0908 [gr-qc]  (see bixtex below)
\bibitem{LSST} LSST
\bibitem{GBM:2017lvd} ApJ paper
\bibitem{Cutler:1994ys}
\bibitem{Farr:2015lna}
\bibitem{Rodriguez:2013oaa}
\bibitem{Read:2009yp}
\bibitem{Andersson:2009yt}
\bibitem{PhysRevD.89.103012}
\bibitem{PhysRevD.91.043002}
\bibitem{Zhu:2017znf}
\bibitem{Cannon:2011vi}
\bibitem{Gabbard:2017lja}
\bibitem{Sathyaprakash:2012jk}
\bibitem{ET_doc}
\bibitem{Sathyaprakash:2012jk}
\bibitem{Wen:2005ui}
\end{thebibliography}

\end{document}

@article{Regimbau:2012ir,
      author         = "Regimbau, Tania and others",
      title          = "{A Mock Data Challenge for the Einstein
                        Gravitational-Wave Telescope}",
      journal        = "Phys. Rev.",
      volume         = "D86",
      year           = "2012",
      pages          = "122001",
      doi            = "10.1103/PhysRevD.86.122001",
      eprint         = "1201.3563",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = ARXIV:1201.3563;%%"
}

@article{Wen:2005ui,
      author         = "Wen, Linqing and Schutz, Bernard F",
      title          = "{Coherent network detection of gravitational waves: The
                        Redundancy veto}",
      booktitle      = "{Gravitational wave data analysis. Proceedings, 9th
                        Workshop, GWDAW 2004, Annecy, France, December 15-18,
                        2004}",
      journal        = "Class. Quant. Grav.",
      volume         = "22",
      year           = "2005",
      pages          = "S1321-S1336",
      doi            = "10.1088/0264-9381/22/18/S46",
      eprint         = "gr-qc/0508042",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = GR-QC/0508042;%%"
}

@article{Sathyaprakash:2012jk,
      author         = "Sathyaprakash, B. and others",
      title          = "{Scientific Objectives of Einstein Telescope}",
      booktitle      = "{Gravitational waves. Numerical relativity - data
                        analysis. Proceedings, 9th Edoardo Amaldi Conference,
                        Amaldi 9, and meeting, NRDA 2011, Cardiff, UK, July 10-15,
                        2011}",
      journal        = "Class. Quant. Grav.",
      volume         = "29",
      year           = "2012",
      pages          = "124013",
      doi            = "10.1088/0264-9381/29/12/124013,
                        10.1088/0264-9381/30/7/079501",
      note           = "[Erratum: Class. Quant. Grav.30,079501(2013)]",
      eprint         = "1206.0331",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = ARXIV:1206.0331;%%"
}

@techreport{ET_doc,
     title = {{Einstein gravitational wave Telescope Conceptual Design Study}},
     author = {M Abernathy et al.},
     group = {EU},
     year = {2011},
     institution = {European Commission},
     month = {06},
     Date-Added = {2011-06-28},
     Date-Modified = {2011-06-28}
}

@article{Sathyaprakash:2012jk,
      author         = "Sathyaprakash, B. and others",
      title          = "{Scientific Objectives of Einstein Telescope}",
      booktitle      = "{Gravitational waves. Numerical relativity - data
                        analysis. Proceedings, 9th Edoardo Amaldi Conference,
                        Amaldi 9, and meeting, NRDA 2011, Cardiff, UK, July 10-15,
                        2011}",
      journal        = "Class. Quant. Grav.",
      volume         = "29",
      year           = "2012",
      pages          = "124013",
      doi            = "10.1088/0264-9381/29/12/124013,
                        10.1088/0264-9381/30/7/079501",
      note           = "[Erratum: Class. Quant. Grav.30,079501(2013)]",
      eprint         = "1206.0331",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = ARXIV:1206.0331;%%"
}

@article{Patricelli:2016bkt,
      author         = "Patricelli, Barbara and Razzano, Massimiliano and Cella,
                        Giancarlo and Fidecaro, Francesco and Pian, Elena and
                        Branchesi, Marica and Stamerra, Antonio",
      title          = "{Prospects for joint observations of gravitational waves
                        and gamma rays from merging neutron star binaries}",
      journal        = "JCAP",
      volume         = "1611",
      year           = "2016",
      number         = "11",
      pages          = "056",
      doi            = "10.1088/1475-7516/2016/11/056",
      eprint         = "1606.06124",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.HE",
      SLACcitation   = "%%CITATION = ARXIV:1606.06124;%%"
}

@article{Gabbard:2017lja,
      author         = "Gabbard, Hunter and Williams, Michael and Hayes, Fergus
                        and Messenger, Chris",
      title          = "{Matching matched filtering with deep networks in
                        gravitational-wave astronomy}",
      year           = "2017",
      eprint         = "1712.06041",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.IM",
      SLACcitation   = "%%CITATION = ARXIV:1712.06041;%%"
}

@article{Cannon:2011vi,
      author         = "Cannon, Kipp and others",
      title          = "{Toward Early-Warning Detection of Gravitational Waves
                        from Compact Binary Coalescence}",
      journal        = "Astrophys. J.",
      volume         = "748",
      year           = "2012",
      pages          = "136",
      doi            = "10.1088/0004-637X/748/2/136",
      eprint         = "1107.2665",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.IM",
      reportNumber   = "LIGO-P0900004, LIGO-P0900004-V34",
      SLACcitation   = "%%CITATION = ARXIV:1107.2665;%%"
}

@article{Zhu:2017znf,
      author         = "Zhu, Xingjiang and Thrane, Eric and Oss, Stefan and
                        Levin, Yuri and Lasky, Paul D.",
      title          = "{Inferring the population properties of binary neutron
                        stars with gravitational-wave measurements of spin}",
      year           = "2017",
      eprint         = "1711.09226",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.HE",
      reportNumber   = "LIGO-P1700400",
      SLACcitation   = "%%CITATION = ARXIV:1711.09226;%%"
}

@article{Cutler:1994ys,
      author         = "Cutler, Curt and Flanagan, Eanna E.",
      title          = "{Gravitational waves from merging compact binaries: How
                        accurately can one extract the binary's parameters from
                        the inspiral wave form?}",
      journal        = "Phys. Rev.",
      volume         = "D49",
      year           = "1994",
      pages          = "2658-2697",
      doi            = "10.1103/PhysRevD.49.2658",
      eprint         = "gr-qc/9402014",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      reportNumber   = "GRP-369",
      SLACcitation   = "%%CITATION = GR-QC/9402014;%%"
}

@article{Rodriguez:2013oaa,
      author         = "Rodriguez, Carl L. and Farr, Benjamin and Raymond, Vivien
                        and Farr, Will M. and Littenberg, Tyson B. and Fazi, Diego
                        and Kalogera, Vicky",
      title          = "{Basic Parameter Estimation of Binary Neutron Star
                        Systems by the Advanced LIGO/Virgo Network}",
      journal        = "Astrophys. J.",
      volume         = "784",
      year           = "2014",
      pages          = "119",
      doi            = "10.1088/0004-637X/784/2/119",
      eprint         = "1309.3273",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.HE",
      SLACcitation   = "%%CITATION = ARXIV:1309.3273;%%"
}

@article{Farr:2015lna,
      author         = "Farr, Ben and others",
      title          = "{Parameter estimation on gravitational waves from
                        neutron-star binaries with spinning components}",
      journal        = "Astrophys. J.",
      volume         = "825",
      year           = "2016",
      number         = "2",
      pages          = "116",
      doi            = "10.3847/0004-637X/825/2/116",
      eprint         = "1508.05336",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.HE",
      reportNumber   = "LIGO-P1500117",
      SLACcitation   = "%%CITATION = ARXIV:1508.05336;%%"
}

@article{Read:2009yp,
      author         = "Read, Jocelyn S. and Markakis, Charalampos and Shibata,
                        Masaru and Uryu, Koji and Creighton, Jolien D. E. and
                        Friedman, John L.",
      title          = "{Measuring the neutron star equation of state with
                        gravitational wave observations}",
      journal        = "Phys. Rev.",
      volume         = "D79",
      year           = "2009",
      pages          = "124033",
      doi            = "10.1103/PhysRevD.79.124033",
      eprint         = "0901.3258",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = ARXIV:0901.3258;%%"
}

@article{Andersson:2009yt,
      author         = "Andersson, N. and Ferrari, V. and Jones, D. I. and
                        Kokkotas, K. D. and Krishnan, B. and Read, J. S. and
                        Rezzolla, L. and Zink, B.",
      title          = "{Gravitational waves from neutron stars: Promises and
                        challenges}",
      journal        = "Gen. Rel. Grav.",
      volume         = "43",
      year           = "2011",
      pages          = "409-436",
      doi            = "10.1007/s10714-010-1059-4",
      eprint         = "0912.0384",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.SR",
      SLACcitation   = "%%CITATION = ARXIV:0912.0384;%%"
}

@article{PhysRevD.91.043002,
  title = {Reconstructing the neutron-star equation of state with gravitational-wave detectors from a realistic population of inspiralling binary neutron stars},
  author = {Lackey, Benjamin D. and Wade, Leslie},
  journal = {Phys. Rev. D},
  volume = {91},
  issue = {4},
  pages = {043002},
  numpages = {20},
  year = {2015},
  month = {Feb},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevD.91.043002},
  url = {https://link.aps.org/doi/10.1103/PhysRevD.91.043002}
}

@article{PhysRevD.89.103012,
  title = {Systematic and statistical errors in a Bayesian approach to the estimation of the neutron-star equation of state using advanced gravitational wave detectors},
  author = {Wade, Leslie and Creighton, Jolien D. E. and Ochsner, Evan and Lackey, Benjamin D. and Farr, Benjamin F. and Littenberg, Tyson B. and Raymond, Vivien},
  journal = {Phys. Rev. D},
  volume = {89},
  issue = {10},
  pages = {103012},
  numpages = {14},
  year = {2014},
  month = {May},
  publisher = {American Physical Society},
  doi = {10.1103/PhysRevD.89.103012},
  url = {https://link.aps.org/doi/10.1103/PhysRevD.89.103012}
}

@article{GBM:2017lvd,
      author         = "Abbott, B. P. and others",
      title          = "{Multi-messenger Observations of a Binary Neutron Star
                        Merger}",
      collaboration  = "GROND, SALT Group, OzGrav, DFN, INTEGRAL, Virgo,
                        Insight-Hxmt, MAXI Team, Fermi-LAT, J-GEM, RATIR, IceCube,
                        CAASTRO, LWA, ePESSTO, GRAWITA, RIMAS, SKA South
                        Africa/MeerKAT, H.E.S.S., 1M2H Team, IKI-GW Follow-up,
                        Fermi GBM, Pi of Sky, DWF (Deeper Wider Faster Program),
                        Dark Energy Survey, MASTER, AstroSat Cadmium Zinc
                        Telluride Imager Team, Swift, Pierre Auger, ASKAP,
                        VINROUGE, JAGWAR, Chandra Team at McGill University,
                        TTU-NRAO, GROWTH, AGILE Team, MWA, ATCA, AST3, TOROS,
                        Pan-STARRS, NuSTAR, ATLAS Telescopes, BOOTES, CaltechNRAO,
                        LIGO Scientific, High Time Resolution Universe Survey,
                        Nordic Optical Telescope, Las Cumbres Observatory Group,
                        TZAC Consortium, LOFAR, IPN, DLT40, Texas Tech University,
                        HAWC, ANTARES, KU, Dark Energy Camera GW-EM, CALET, Euro
                        VLBI Team, ALMA",
      journal        = "Astrophys. J.",
      volume         = "848",
      year           = "2017",
      number         = "2",
      pages          = "L12",
      doi            = "10.3847/2041-8213/aa91c9",
      eprint         = "1710.05833",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.HE",
      reportNumber   = "LIGO-P1700294, VIR-0802A-17, FERMILAB-PUB-17-478-A-AE-CD",
      SLACcitation   = "%%CITATION = ARXIV:1710.05833;%%"
}

% For \cite{LSST}
@ARTICLE{LSST,
   author = {{LSST Science Collaboration} and {Abell}, P.~A. and {Allison}, J. and 
	{Anderson}, S.~F. and {Andrew}, J.~R. and {Angel}, J.~R.~P. and 
	{Armus}, L. and {Arnett}, D. and {Asztalos}, S.~J. and {Axelrod}, T.~S. and et al.},
    title = "{LSST Science Book, Version 2.0}",
  journal = {ArXiv e-prints},
archivePrefix = "arXiv",
   eprint = {0912.0201},
 primaryClass = "astro-ph.IM",
 keywords = {Astrophysics - Instrumentation and Methods for Astrophysics, Astrophysics - Cosmology and Extragalactic Astrophysics, Astrophysics - Earth and Planetary Astrophysics, Astrophysics - Galaxy Astrophysics, Astrophysics - Solar and Stellar Astrophysics},
     year = 2009,
    month = dec,
   adsurl = {http://adsabs.harvard.edu/abs/2009arXiv0912.0201L},
  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}

% For \cite{CE}
@article{Evans:2016mbw,
      author         = "Abbott, Benjamin P. and others",
      title          = "{Exploring the Sensitivity of Next Generation
                        Gravitational Wave Detectors}",
      collaboration  = "LIGO Scientific",
      journal        = "Class. Quant. Grav.",
      volume         = "34",
      year           = "2017",
      number         = "4",
      pages          = "044001",
      doi            = "10.1088/1361-6382/aa51f4",
      eprint         = "1607.08697",
      archivePrefix  = "arXiv",
      primaryClass   = "astro-ph.IM",
      reportNumber   = "LIGO-P1600143",
      SLACcitation   = "%%CITATION = ARXIV:1607.08697;%%"
}

% For \cite{Kagra2}
@article{Akutsu:2017kpk,
      author         = "Akutsu, T. and others",
      title          = "{Construction of KAGRA: an Underground Gravitational Wave
                        Observatory}",
      collaboration  = "KAGRA",
      year           = "2017",
      eprint         = "1712.00148",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = ARXIV:1712.00148;%%"
}

% For \cite{ETB}
@article{Hild:2010id,
      author         = "Hild, S. and others",
      title          = "{Sensitivity Studies for Third-Generation Gravitational
                        Wave Observatories}",
      journal        = "Class. Quant. Grav.",
      volume         = "28",
      year           = "2011",
      pages          = "094013",
      doi            = "10.1088/0264-9381/28/9/094013",
      eprint         = "1012.0908",
      archivePrefix  = "arXiv",
      primaryClass   = "gr-qc",
      SLACcitation   = "%%CITATION = ARXIV:1012.0908;%%"
}

### 2018-02-23 Paper/Manuscript.tex
First commit

--- 2018-02-23 BNS_manuscript.tex
@@
-\documentclass[11pt,a4paper]{article}
-
-\usepackage{multicol}
-\usepackage{wrapfig}
-\usepackage{graphicx}
+\documentclass[amsmath,amssymb,aps,floats,amsfonts,notitlepage,superscriptaddress,eqsecnum,nofootinbib,10pt]{revtex4-1}
+\linespread{1.2}
+%\usepackage{booktabs} % for tabular improvments
+\usepackage{graphicx}       % Include figure files
+\usepackage{dcolumn}        % Align table columns on decimal point
+\usepackage{bm}             % bold math
+\usepackage{tensor}
+\usepackage{url}
+\usepackage[colorlinks]{hyperref}
 \usepackage{color}
-\usepackage{amsfonts,amssymb,amsmath}
-     % use Times fonts if available on your TeX system
-\usepackage{epsfig}
-%\usepackage{empheq}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+\usepackage{float}
+\usepackage[usestackEOL]{stackengine} % package used to write several lines in one box
+\allowdisplaybreaks[1]
+
+     % Sarp's extra packages
+\usepackage{dcolumn}
+	\newcolumntype{.}{D{.}{.}{13}}
+	\newcolumntype{d}[1]{D{.}{.}{#1}}
+\usepackage{longtable}
 \usepackage{subfigure}
-\usepackage{hyperref}
 \usepackage{rotating}
 \usepackage[small,compact]{titlesec}
-\usepackage{fancyhdr}
+%%%%%%%%%% New few lines of code are added to fix the TexLive titlesec bug in Ubuntu >= 14.04
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd{\ttlh@hang}{\parindent\z@}{\parindent\z@\leavevmode}{}{}
+\patchcmd{\ttlh@hang}{\noindent}{}{}{}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{fancyhdr,amsfonts}
 \usepackage{times}
@@
 \usepackage{setspace}
-\usepackage{caption}
-\usepackage[usestackEOL]{stackengine} % package used to write several lines in one box
-%\usepackage{subcaption}
-
-\topmargin-14mm
-\textheight250mm
-\oddsidemargin1mm
-\textwidth160mm
-
+%\bibliographystyle{apsrev4-1}
+
+\definecolor{CiteColor}{rgb}{0,0.5,0}
+\hypersetup{citecolor=CiteColor}
+\definecolor{RefColor}{rgb}{0.55,0,0}
+\hypersetup{linkcolor=RefColor}
+\definecolor{darkgreen}{rgb}{0.2,0.7,0.2}
+
+\newcommand{\beq}{\begin{equation}}
+\newcommand{\eeq}{\end{equation}}
+
+\newcommand{\bs}{\mathbf{s}}
+\newcommand{\bS}{\mathbf{S}}
+\newcommand{\bp}{\mathbf{p}}
+\newcommand{\bn}{\mathbf{n}}
+\newcommand{\bom}{\boldsymbol{\omega}}
+\newcommand{\bOm}{\boldsymbol{\Omega}}
+\newcommand{\tilE}{\tilde{E}}
+\newcommand{\tilL}{\tilde{L}}
+\newcommand{\nn}{\nonumber}
+\newcommand{\EE}{E}
+\newcommand{\LL}{L}
+\newcommand{\KK}{\mathcal{K}}
+
+% Sarp's new commands
+\newcommand{\ord}{\mathcal{O}}
 \newcommand{\la}{\langle}
 \newcommand{\ra}{\rangle}
-\renewcommand{\c}{\cos\theta}
-\newcommand{\s}{\sin}
+\renewcommand{\c}{\cos}
 \renewcommand{\t}{\theta}
@@
 \newcommand{\f}{\frac}
-\newcommand{\df}{\dfrac}
 \newcommand{\pd}{\partial}
 \newcommand{\bt}{\beta}
-\newcommand{\D}{\Delta}
-\newcommand{\Si}{\Sigma}
-\newcommand{\p}{\rho}
-\renewcommand{\L}{\mathcal{L}}
+%\newcommand{\s}{\sin}
 \newcommand{\ph}{\phi}
 \newcommand{\g}{\gamma}
-\newcommand{\nn}{\nonumber}
 \newcommand{\al}{\alpha}
@@
 \newcommand{\mrm}{\mathrm}
+\newcommand{\Om}{\Omega}
+\newcommand{\veps}{\varepsilon}
 \newcommand{\be}{\begin{equation}}
 \newcommand{\ee}{\end{equation}}
-\newcommand{\ba}{\begin{align}}
-\newcommand{\ea}{\end{align}}
+\newcommand{\ba}{\begin{eqnarray}}
+\newcommand{\ea}{\end{eqnarray}}
 \newcommand{\bi}{\begin{itemize}}
@@
 \newcommand{\ef}{\end{frame}}
-\newcommand{\bs}{\begin{small}}
 \newcommand{\es}{\end{small}}
-\newcommand{\ord}{\mathcal{O}}
 \newcommand{\Lim}[1]{\raisebox{0.5ex}{\scalebox{0.8}{$\displaystyle \lim_{#1}\;$}}}
@@
 
+\newcommand{\Delhat}{\hat{\delta}}
+\newcommand{\vsp}{\vspace{0.2cm}}
+
+\def\D{\displaystyle}
+\def\etal{\textit{et al.}}
+
+\providecommand{\SA}[1]{{\textcolor{DarkBlue}{\texttt{SA: #1}}}}
+\providecommand{\SD}[1]{{\textcolor{DarkRed}{\texttt{SD: #1}}}}
+
 \begin{document}
-{\bf Title: Forecasting Gamma-ray Bursts using Gravitational Waves}
-\section{Abstract}
+
+\title{Forecasting Gamma-ray Bursts using Gravitational Waves}
+
+\author{Sarp Akcay}
+\affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland.}
+
+\date{\today}
+
+\begin{abstract}
 We explore the intriguing possibility of employing future gravitational-wave interferometers to detect the inspiral of compact binaries early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
@@
 with warning times as long as a few hours.
-
-We also consider binary black hole neutron star systems with the hopes of observing a tidal disruption event in the future. However, our findings indicate that
-witnessing such an event will be very unlikely even after the Einstein Telescope becomes operational.
+Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)
+
+\end{abstract}
+\maketitle
 
@@
 Cosmic Explorer \cite{CE}, LIGO India, Australia China(?)
+
+Cite the BNS Living review many times \cite{Faber:2012rw}.
 
@@
 \begin{align}
- h_+(t) &= \f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi_\text{N}(t)],\label{eq:hplus_TD}\\
- h_\times(t) & = \f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\,\cos\iota \sin[\Phi_\text{N}(t)]\label{eq:hcross_TD},
+ h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi_\text{N}(t)],\label{eq:hplus_TD}\\
+ h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi_\text{N}(t)]\label{eq:hcross_TD},
 \end{align}
@@
 %
-where $\iota=\cos^{-1}(\mathbf{\hat{n}}\cdot{\mathbf{\hat{L}}}) $ is the inclination angle between the line of sight unit vector $\mathbf{\hat{n}} $ and the orbital angular momentum unit vector $\mathbf{\hat{L}}$.
+where
+%
+\be
+h_c(t) =\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3} \label{eq:h_c}
+\ee
+is the characteristic strain.
+$\iota=\cos^{-1}(\mathbf{\hat{n}}\cdot{\mathbf{\hat{L}}}) $ is the inclination angle between the line of sight unit vector $\mathbf{\hat{n}} $ and the orbital angular momentum unit vector $\mathbf{\hat{L}}$.
 E.g., for an orbit seen edge on, $\iota = \pi/2$ which is actually the case of a purely plus-polarized wave, $h_\times=\cos(\pi/2)=0$.
@@
 \ee
-where $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$, however, there is no simple expression for it.
+where $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$ with frequency possibly up to 1.7\,kHz \cite{Marronetti:2003hx}, 
+however, there is no simple expression for it.
 Additionally, above $f \approx 200\,$Hz tidal effects are expected to show up in the GW signal.
@@
 is the appropriate power. The standard treatment adopts a Friedmann-Robertson-Walker cosmology with scale factor $a(t)$ and curvature $k=\pm 1, \text{ or } 0$.
-Introducing the subscript ${}_s$ to denote quantities evaluated at the source frame, we have the following cosmological corrections
+Introducing the subscript $s$ to denote quantities evaluated at the source frame, we have the following cosmological corrections
 %%
@@
 \begin{align}
+dt& \rightarrow (1+z) dt_s, \\
  D & \rightarrow  (1+z)a(t) D,\\
@@
 %
-Given that $\dot{f}_s\sim f^{11/3}_s, h(t)\sim D^{-1} f_s^{2/3}$,
-the observed frequency evolution and the GW strain change according to % in the detector frame
+Given that $\dot{f}_s=df_s/dt_s\sim f^{11/3}_s, h_s(t)\sim D^{-1} f_s^{2/3}$, and $\tau_{\text{insp},s}\sim f_s^{-8/3}$,
+the observed frequency evolution, the GW strain, and the inspiral time change according to % in the detector frame
 %%
@@
 \dot{f}\ \ &\sim (1+z)^{5/3}{f}^{11/3},\\
-h(t) & \sim (1+z)^{5/3} h(t).
+h(t) & \sim (1+z)^{5/3} h(t),\\
+\tau_\text{insp}& \sim (1+z)^{-5/3} \tau_{\text{insp}}
 \end{align}
 %
-Looking at Eqs.~(\ref{eq:fdot}, \ref{eq:hplus_TD}, \ref{eq:hcross_TD}) we spot a common factor of $M_c^{5/3}$ in all of them.
+Looking at Eqs.~(\ref{eq:fdot}, \ref{eq:tau_insp}, \ref{eq:h_c}) we spot a common factor of $M_c^{5/3}$ in all of them.
 Therefore, we can accommodate the cosmological effects by introducing the redshifted chirp mass $\mathcal{M}_c\equiv (1+z) M_c$
-which changes Eqs.~(\ref{eq:fdot}, \ref{eq:hplus_TD}, \ref{eq:hcross_TD}) to
+which changes Eqs.~(\ref{eq:fdot}, \ref{eq:tau_insp}, \ref{eq:h_c}) to
 %The effect of the cosmological redshift on our estimations of advance warning times manifests itself by modifying 
@@
 \dot{f} &= \f{96}{5}\pi^{8/3} \f{(G \mathcal{M}_c)}{c^3}^{5/3}\, f^{11/3} \label{eq:fdot_redshifted},\\
-h_c(t) & = \f{4}{D}\left(\f{G \mathcal{M}_c}{c^2}\right)^{5/3}\left(\frac{\pi f}{c}\right)^{2/3} \label{eq:strain_TD_redshifted}\, ,
+h_c(t) & = \f{4}{D}\left(\f{G \mathcal{M}_c}{c^2}\right)^{5/3}\left(\frac{\pi f}{c}\right)^{2/3} \label{eq:strain_TD_redshifted}\\
+\tau_\text{insp}(f) &= \f{5}{256\pi}\f{c^5}{(\pi G \mathcal{M}_c)^{5/3}} \,f^{-8/3}\label{eq:tau_insp_redshifted}\, ,
 \end{align}
@@
 This is because both $\dot{f}$ and the GW amplitude are governed by the time scale $G M_c/c^3$.
-For our work here, the only important consequence is the redshifting of the frequency at which we truncate the inspiral, 
-i.e., $f_\text{ISCO}\simeq 1571\,$Hz in the source frame.
-For our work, we consider a maximum BNS distance of 1\,Gpc which is reasonable given the sensitivity
-of A-LIGO and the ET. $D = 1\,$Gpc translates to $z \approx 0.25$.
-Therefore, in the detector frame $f_\text{ISCO}$ is redshifted to $f \approx 1257\,$Hz. 
-From our computations above, we know that this shift adds a negligible correction to the timescales that interest us here.
-Thus we may safely disregard the effects cosmology.
+Therefore, the inspiral evolves faster in the lab frame %because $\dot{f}$ has increased and the cut-off frequency has decreased.
+and we must now terminate it at a redshifted GW ISCO frequency which is less than $f_\text{ISCO}$ of Eq.~(\ref{eq:f_isco}).
+On the other hand, the Fourier transform of $h_c(t)$ changes to 
+%
+\be
+\tilde{H}(f) = A\, \f{c}{D} \f{1}{(1+z)} \left(\f{G \mathcal{M}_c}{c^3}\right)^{5/6} f^{-7/6}
+\ee
+indicating that the frequency-domain strain in the detector frame decreases by a factor of $(1+z)^{-1/6}$. %\approx 1 -z/6$ for small $z$.
+%
+For the Advanced-LIGO-Virgo network,
+we consider a maximum BNS luminosity distance of 200\,Mpc, 
+i.e., $z \approx 0.022$ which redshifts $f_\text{ISCO}$ by $\approx 2\%$ and reduces $\tau_\text{insp}$ by $\approx 7\%$.
+Therefore, we will neglect the effects of cosmological redshifting on the less sensitive ALV network.
+On the other hand, for Einstein Telescope, we will go out to $D=1\,\text{Gpc}\implies z\approx 0.2$
+which reduces $\tau_\text{insp}$ by $1/4$, thus we shall include the redshift effects in our computations of advance warning times and SNRs
+for which we provide the details in Sec.~\ref{Sec:ETB} (additional details can be found in, e.g., Ref.~\cite{Phinney:2001di}).
+
 %
@@
 \begin{figure}[h!]
-\includegraphics[height=9cm]{Figures/GW170817_strains.pdf}
+\includegraphics[height=9cm]{../Figures/GW170817_strains.pdf}
 \caption{GW170817 as it sweeps from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz across our network with ASD (sensitivity) of LIGO Livingstone (L1) during the event (red curve).
@@
 \begin{figure}[h!]
-\includegraphics[width=\linewidth]{Figures/ALigo_strains.pdf}
+\includegraphics[width=\linewidth]{../Figures/ALigo_strains.pdf}
 \caption{Typical $M=2.8 M_\odot$ BNS inspirals sweeping across the Advanced LIGO-Virgo network in the 2020s.
@@
 We now wish to quantify the forecasting capabilities of Einstein Telescope. To this end, we consider the inspiral of BNS systems
-at luminosity distances of $100,200,400,1000\,$Mpc entering the ET band. The SNR accumulated at ET by each inspiral is given
-by a slight modification to Eq.~(\ref{eq:ET_SNR})
-
-%
-\be
-\bar\rho_{\text{tot,ET}} = \f{36}{25}A^2 h_0^2 \int_{f_0}^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \label{eq:ET_SNRv2},
+at luminosity distances of $100,200,400,1000\,$Mpc entering the ET band. 
+These correspond to cosmological redshifts of $z\approx 0.0222,0.0437, 0.085, 0.198$, respectively.
+To compute these, we used a flat $\Lambda$CDM model ($\Omega_k=0$) with the latest Planck satellite parameters: 
+$\Omega_\Lambda = 0.6911, \Omega_m = 0.3089, H_0 = 67.74\,$km\,s$^{-1}\,$Mpc$^{-1}$ \cite{Planck2015}. % with negligible ra yielding and $\Omega_r \lesssim 10^{-4}$.
+It is then straightforward to translate $D$ to $z$ (cf. Ref.~\cite{Hogg:1999ad}).
+
+The SNR accumulated in ET from each inspiral is obtained by a modification to Eq.~(\ref{eq:ET_SNR})
+
+%
+\be
+\bar\rho_{\text{ET}}(f_0,f)\equiv \f{36}{25}A^2 h_0^2\, (1+z)^{-1/3}\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')} \label{eq:ET_SNRv2},
 \ee
@@
  \be
- \sqrt{S_\text{n}(f_0)} = 2\sqrt{f_0}\, \tilde{H}_\bigtriangleup(f_0, D) \label{eq:f0_ET}\,
- \ee
- %
-with $\tilde{H}_\bigtriangleup(f, D)$ given by Eq.~(\ref{eq:H_delta}).
-For the detector noise $\sqrt{S_n(f)}$, we adopt the ASD for the B and C configurations known as ET-B and ET-C, respectively \cite{Hild:2010id} which we plot as the solid dark (red) and light (brown) curves in Fig.~\ref{fig:ETB2030}.
+ \sqrt{S^\text{ET}_\text{n}(f_0)} = 2\sqrt{f_0}\, \tilde{H}_\text{ET}(f_0, D) \label{eq:f0_ET}\,
+ \ee
+ %
+with $\tilde{H}_\text{ET}(f, D)$ given by the redshifted version of Eq.~(\ref{eq:H_delta})
+%
+\be
+\tilde{H}_\text{ET}(f, D) = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\f{1}{(1+z)}\left(\f{G \mathcal{M}_c}{c^3}\right)^{5/6} f^{-7/6}\, , \label{eq:H_delta_redshifted}
+\ee
+%
+where recall $\mathcal{M}_c = (1+z)M_c$.
+For the detector noise $\sqrt{S^\text{ET}_n(f)}$, we adopt the ASD for the B and C configurations known as ET-B and ET-C, respectively \cite{Hild:2010id} which we plot as the solid dark (red) and light (brown) curves in Fig.~\ref{fig:ETB2030}.
 Sweeping across these are four BNS inspirals at $D=100,200,400,1000\,$Mpc represented by solid (black), dotted (blue), dashed (green),
 and dot-dashed lines (gray), respectively. These strains sit much higher than the detector noise
-comparred with those in Fig.~\ref{fig:LIGO2020} which foretells us that the SNRs in the ET band will be much higher, 
-thus the resulting advance warning times will be much longer.
+compared with those in Fig.~\ref{fig:LIGO2020} which foretells us that the SNRs accumulated in the ET band will be much higher, 
+thus yielding much longer advance warning times as we show in Table~\ref{table:ET}.
+%As shown, Einstein Telescope is sensitive enough to accumulate more SNR in this $f>f_\text{ISCO}$ regime.
 
 \begin{figure}[h!]
-\includegraphics[width=\linewidth]{Figures/ET_strains.pdf}
-\caption{Typical GW sources that may be harbingers of GRBs in the 2030s: $M=2.8 M_\odot$ inspiralling BNS systems sweeping across 
+\includegraphics[width=\linewidth]{../Figures/ET_strains_redshifted.pdf}
+\caption{Typical GW sources that may be harbingers of GRBs in the 2030s: $1.4 M_\odot-1.4 M_\odot$ inspiralling BNS systems sweeping across 
 the Einstein Telescope's sensitivity band for both B and C configurations.
-The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the RMS-averaged strains, $2\sqrt{f}\tilde{H}_\bigtriangleup(f,D)$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively.
-The vertical dashed (black) line marks $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals,
-but numerical simulations indicate that the actual ISCO is smaller than the Schwarzschild value $6GM/c^2$ hence the true ISCO
-frequency is greater than $f_\text{ISCO}$ used here.
-As the plot shows, Einstein Telescope is sensitive enough in this regime to accumulate more SNR.
+The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the redshift-corrected
+RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}(f,D)$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
+The vertical lines with correspondingly identical patterns (colors) mark the redshifted ISCO frequencies ($(1+z)^{-1} f_\text{ISCO}$) at which point we terminate each inspiral.
+As the true ISCO frequency is likely larger than $f_\text{ISCO}$ \cite{Marronetti:2003hx}, the inspirals would continue to nearly 2\,kHz indicated by the 
+faded lines in the plot (drawn to 5\,kHz for aesthetic reasons).
+%However, numerical simulations indicate that the actual ISCO is smaller than the Schwarzschild value $6GM/c^2$ hence the true ISCO
+%frequency is greater than $f_\text{ISCO}$ used here.
+%As shown, Einstein Telescope is sensitive enough to accumulate more SNR in this $f>f_\text{ISCO}$ regime.
 %Once again, keep in mind that we artificially extended the leading-order $f^{-2/3}$ power law past $f\sim 100\,$Hz at which point tidal effects actually visibly modify this behavior.
@@
 %
-To determine $T_\text{AW}$ we once again impose the threshold SNR of 15 which is our criterion for sending out warnings to electromagnetic
-observatories. Thus, rewriting Eq.~(\ref{eq:SNR_bar}) in the case of ET, we define $\bar{f}_\text{ET}$ as the solution to
-%
-\be
-15=\f{36}{25}A^2 h_0^2 \int_{\bar{f}_\text{ET}}^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} .\label{eq:ET_fbar}
-\ee
-%
-This gives us our advance warning time $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp}) which we
-can slightly improve by using the 3.5PN expression. Therefore we will proceed in a manner similar to the procedure summarized in 
-Fig.~\ref{fig:flow}) and compute the 0PN and 3.5PN advance warning times for all four inspirals in both the ET-B and ET-C bands.
-We define the final accumulated SNR as
-%
-\be
-\bar\rho_{F,\,\text{ET}}\equiv \f{36}{25}A^2 h_0^2 \int_{f_0}^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}  .\label{eq:rhoF_ET}
-\ee
-%
+To determine $T_\text{AW}$ we once again impose the threshold SNR of 15 which, the reader may recall, 
+is our detection criterion for sending out warnings to electromagnetic observatories. Thus, rewriting Eq.~(\ref{eq:SNR_bar}) in the case of ET, we define $\bar{f}_\text{ET}$ as the solution to
+%
+\be
+\bar\rho_\text{ET}(f_0,\bar{f}_\text{ET}) = 15 \label{eq:ET_fbar},
+\ee
+%
+where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively.
+$\bar{f}_\text{ET}$ then gives us our redshift-accounted advance warning time via $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp_redshifted}) which we can slightly improve by using the 3.5PN expression.
+Therefore, we proceed as summarized in Fig.~\ref{fig:flow} and compute the 0PN and 3.5PN advance warning times 
+for all four inspirals in both the ET-B and ET-C bands.
+The latter computation involves rescaling the PN parameters $x$ and $\Theta$ to $(1+z)^{2/3} x$ and $(1+z)^{-1}\Theta $ (see Sec.~9.3 of 
+Blanchet's review \cite{Blanchet_LRR} for details).
+The final accumulated SNR is given by
+%
+\be
+\bar\rho_{F}\equiv \bar\rho_\text{ET}(f_0,f_\text{ISCO})  .\label{eq:rhoF_ET}
+\ee
+%
+Table~\ref{table:ET} summarizes our results for both ET-B and ET-C where we chose to only display the 3.5PN-accurate inspiral time as $T_\text{AW}$,
+but we computed this quantity via both 0PN and 2PN expressions as a check.
 
@@
 \centering
-\begin{tabular}{lcccc}
-\hline
-$D\,$(Mpc) & $\bar{f}\,$(Hz) & $T^{0PN}_\text{AW}$(sec) & $T^{3.5PN}_\text{AW}$(sec)& $\bar{\rho}_{F,\,\text{ET}}$\T\B\\
-\hline
-100 & 1.1435 & 2909 & 2942 & 307.1 \T\\
-200  \\
-\hline
+\begin{tabular}{l|ccccccc}
+%toprule
+\hline
+$D\,$(Mpc) & \multicolumn{3}{c}{ET-B} &  & \multicolumn{3}{c}{ET-C}\T\B\\
+\hline
+{}& $\bar{f}\,$(Hz) & \ $T_\text{AW}$(sec) \ & $\bar{\rho}_{F}$ &{} & $\bar{f}\,$(Hz) & \ $T_\text{AW}$(sec)\ & $\bar{\rho}_{F}$\T\B\\
+%midrule
+
+100 & 6.7237 &  2818 & 306.0 &{\qquad} & 3.2692 & 19212 & 365.4\T\\
+200 & 11.2104 & 698.6 & 152.4 &{\qquad} & 4.1028 & 10138 & 182.1 \\
+400 & 18.2234 & 179.8 & 75.74 &{\qquad} & 5.0607 & 5437 & 90.48\\
+1000 & 41.3537 &17.2 & 29.79& \qquad & 6.7553 & 2138 & 35.60  \\
+\hline
+%bottomrule
 \end{tabular}
-\caption{ET-B}\label{table:ET}
+\caption{Forecasting capabilities of Einstein Telescope summarized. We can expect over \emph{five} hours of early warning for nearby sources. 
+ET-B and ET-C refer the different configurations shown in Fig.~\ref{fig:ETB2030}.
+For the advance warning times, we only present the result of the more accurate 3.5PN computation.
+$\bar{f}$ is the threshold frequency at which
+ET-B/C accumulate SNR of 15 which we take to be our detection criterion. Note that both $T_\text{AW}$ and $\bar\rho_F$ are larger for ET-C
+due to its improved sensitivity in the $f\lesssim 30\,$Hz regime compared to ET-B as it is clear in Fig.~\ref{fig:ETB2030}.
+These results and those of Table.~\ref{table:LIGO2020} are summarized in Fig.~\ref{fig:summary}.}\label{table:ET}
 \end{table}
+%
+%
+As the results of Table~\ref{table:ET} indicate, ET-B will provide $\sim 10 - 50\,$ minutes of warning time for BNS inspirals at $D\lesssim 200\,$Mpc.
+Instead of speculating whether or not this is enough to forecast GRBs, we turn our attention to ET-C's forecasting capabilities.
+As can be seen from Fig.~\ref{fig:ETB2030}, ET-C's increased sensitivity in the $f\lesssim 30\,$Hz regime will significantly lengthen the advance warning times.
+This is best highlighted by the sixth colum of Table~\ref{table:ET}, 
+where we show that ET-C will provide up to five hours of early warning time for nearby ($D\lesssim 100\,$Mpc) neutron star mergers.
+Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's horizon distance) will persist in the ET-C sensitivity band for a few hours after their initial detection.
+Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET.
+Speculating that the advances in the detection, localization and early-warning algorithms in the next decade will reduce the required early
+warning time to less than an hour, we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS horizon distances of $D_H=87,613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
+In other words, all inspiralling BNSs closer than $D_H$ will give us more than an hour's leeway before the GRB (assuming detection SNR of 15 as always).
+The volume set by $D=D_H$ translates to a BNS merger rate of $\mathcal{O}(1)$ for ET-B and
+$\approx 355^{+730}_{-280}\,\text{year}^{-1}$ for ET-C. Additionally, each source within $D_H$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
+in the ET-B, ET-C bands, respectively. These are summarized in Table~\ref{table:horizon}.
+
+Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. Given that
+it takes $\gtrsim \mathcal{O}(1)\,$\emph{day} for a BNS source to inspiral from $f_0\sim 1\,$Hz to $\bar{f}$ of Eq.~(\ref{eq:ET_fbar}),
+we can expect ET to localize sources within the horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
+As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
+(this is roughly in line with LISA's timeline).
+It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
+to alert the electromagnetic observatories within an hour of the initial detection (SNR = 15). 
+Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens of gamma ray bursts.
+We summarize our major findings for both the ALV network and ET-B/C in Fig.~\ref{fig:summary}.
+%
+%
+%
+\begin{table}[h]
+\centering
+\begin{tabular}{l|ccc}
+%toprule
+\hline
+ & ET-B & & ET-C\T\B\\
+\hline
+  $D_H $& 87\,Mpc& &{613\,Mpc}\T\\
+  $R(D_H) $& $1^{+2}_{-1}\,\text{yr}^{-1}$&\hspace{5mm} &{$355^{+730}_{-280}\,\text{yr}^{-1}$}\T\\
+  $\bar\rho_F(D_H)$ & 420 &&{58}\T\B\\
+\hline
+\end{tabular}
+\caption{Horizon distances of ET-B and ET-C assuming $T_\text{AW} =1\,$hour. $R(D_H)$ is the BNS merger rate within a volume of $D_H^3$
+obtained by rescaling the rate inferred from GW170817 \cite{GW170817}.
+$\bar\rho_F(D_H)$ is the total SNR accumulated in ET by a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
+\end{table}
+%
+%
+%
+\begin{figure}[h!]
+\includegraphics[width=\linewidth]{../Figures/Main_results.pdf}
+\caption{Summary of our major findings for both the Advanced-LIGO-Virgo (ALV) network circa 2020 and the Einstein Telescope's B and C configurations
+ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV network (dotted), ET-B (dashed), and ET-C (solid), respectively.
+The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (brown) lines coming from the $D^{-2}$ powerlaw in the SNR [see Eq.~(\ref{eq:ET_SNRsq}] which is plotted on the right axis.
+We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D\ge 100\,$Mpc for the ET results.}\label{fig:summary}
+\label{fig:summary}
+\end{figure}
+
+% LISA does not see these sources, not sensitive enough!
 
 \section{Binary black hole neutron star systems}
+In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star as it falls into a black hole. 
+The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
+such as the black hole mass and spin. The evolution of black hole-neutron star (BH-NS) binaries is a very active branch of numerical relativity
+(see Ref. \cite{Shibata:2011jka} for a comprehensive review).
+
 Tidal disruption, minimum BH mass $5 M_\odot$. Tidal force $\sim M/r^3 \sim M^{-2}$ hence the smaller the BH the more TD there will be.
 Also need highly spinning BH to decreases the ISCO radius.
+
+\bibliographystyle{apsrev4-1}
+%\bibliographystyle{plain}
+\bibliography{references}
+
+\end{document}
 
@@
 \end{thebibliography}
-
-\end{document}
-
-@article{Regimbau:2012ir,
-      author         = "Regimbau, Tania and others",
-      title          = "{A Mock Data Challenge for the Einstein
-                        Gravitational-Wave Telescope}",
-      journal        = "Phys. Rev.",
-      volume         = "D86",
-      year           = "2012",
-      pages          = "122001",
-      doi            = "10.1103/PhysRevD.86.122001",
-      eprint         = "1201.3563",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = ARXIV:1201.3563;%%"
-}
-
-@article{Wen:2005ui,
-      author         = "Wen, Linqing and Schutz, Bernard F",
-      title          = "{Coherent network detection of gravitational waves: The
-                        Redundancy veto}",
-      booktitle      = "{Gravitational wave data analysis. Proceedings, 9th
-                        Workshop, GWDAW 2004, Annecy, France, December 15-18,
-                        2004}",
-      journal        = "Class. Quant. Grav.",
-      volume         = "22",
-      year           = "2005",
-      pages          = "S1321-S1336",
-      doi            = "10.1088/0264-9381/22/18/S46",
-      eprint         = "gr-qc/0508042",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = GR-QC/0508042;%%"
-}
-
-@article{Sathyaprakash:2012jk,
-      author         = "Sathyaprakash, B. and others",
-      title          = "{Scientific Objectives of Einstein Telescope}",
-      booktitle      = "{Gravitational waves. Numerical relativity - data
-                        analysis. Proceedings, 9th Edoardo Amaldi Conference,
-                        Amaldi 9, and meeting, NRDA 2011, Cardiff, UK, July 10-15,
-                        2011}",
-      journal        = "Class. Quant. Grav.",
-      volume         = "29",
-      year           = "2012",
-      pages          = "124013",
-      doi            = "10.1088/0264-9381/29/12/124013,
-                        10.1088/0264-9381/30/7/079501",
-      note           = "[Erratum: Class. Quant. Grav.30,079501(2013)]",
-      eprint         = "1206.0331",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = ARXIV:1206.0331;%%"
-}
-
-@techreport{ET_doc,
-     title = {{Einstein gravitational wave Telescope Conceptual Design Study}},
-     author = {M Abernathy et al.},
-     group = {EU},
-     year = {2011},
-     institution = {European Commission},
-     month = {06},
-     Date-Added = {2011-06-28},
-     Date-Modified = {2011-06-28}
-}
-
-@article{Sathyaprakash:2012jk,
-      author         = "Sathyaprakash, B. and others",
-      title          = "{Scientific Objectives of Einstein Telescope}",
-      booktitle      = "{Gravitational waves. Numerical relativity - data
-                        analysis. Proceedings, 9th Edoardo Amaldi Conference,
-                        Amaldi 9, and meeting, NRDA 2011, Cardiff, UK, July 10-15,
-                        2011}",
-      journal        = "Class. Quant. Grav.",
-      volume         = "29",
-      year           = "2012",
-      pages          = "124013",
-      doi            = "10.1088/0264-9381/29/12/124013,
-                        10.1088/0264-9381/30/7/079501",
-      note           = "[Erratum: Class. Quant. Grav.30,079501(2013)]",
-      eprint         = "1206.0331",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = ARXIV:1206.0331;%%"
-}
-
-@article{Patricelli:2016bkt,
-      author         = "Patricelli, Barbara and Razzano, Massimiliano and Cella,
-                        Giancarlo and Fidecaro, Francesco and Pian, Elena and
-                        Branchesi, Marica and Stamerra, Antonio",
-      title          = "{Prospects for joint observations of gravitational waves
-                        and gamma rays from merging neutron star binaries}",
-      journal        = "JCAP",
-      volume         = "1611",
-      year           = "2016",
-      number         = "11",
-      pages          = "056",
-      doi            = "10.1088/1475-7516/2016/11/056",
-      eprint         = "1606.06124",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.HE",
-      SLACcitation   = "%%CITATION = ARXIV:1606.06124;%%"
-}
-
-@article{Gabbard:2017lja,
-      author         = "Gabbard, Hunter and Williams, Michael and Hayes, Fergus
-                        and Messenger, Chris",
-      title          = "{Matching matched filtering with deep networks in
-                        gravitational-wave astronomy}",
-      year           = "2017",
-      eprint         = "1712.06041",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.IM",
-      SLACcitation   = "%%CITATION = ARXIV:1712.06041;%%"
-}
-
-@article{Cannon:2011vi,
-      author         = "Cannon, Kipp and others",
-      title          = "{Toward Early-Warning Detection of Gravitational Waves
-                        from Compact Binary Coalescence}",
-      journal        = "Astrophys. J.",
-      volume         = "748",
-      year           = "2012",
-      pages          = "136",
-      doi            = "10.1088/0004-637X/748/2/136",
-      eprint         = "1107.2665",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.IM",
-      reportNumber   = "LIGO-P0900004, LIGO-P0900004-V34",
-      SLACcitation   = "%%CITATION = ARXIV:1107.2665;%%"
-}
-
-@article{Zhu:2017znf,
-      author         = "Zhu, Xingjiang and Thrane, Eric and Oss, Stefan and
-                        Levin, Yuri and Lasky, Paul D.",
-      title          = "{Inferring the population properties of binary neutron
-                        stars with gravitational-wave measurements of spin}",
-      year           = "2017",
-      eprint         = "1711.09226",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.HE",
-      reportNumber   = "LIGO-P1700400",
-      SLACcitation   = "%%CITATION = ARXIV:1711.09226;%%"
-}
-
-@article{Cutler:1994ys,
-      author         = "Cutler, Curt and Flanagan, Eanna E.",
-      title          = "{Gravitational waves from merging compact binaries: How
-                        accurately can one extract the binary's parameters from
-                        the inspiral wave form?}",
-      journal        = "Phys. Rev.",
-      volume         = "D49",
-      year           = "1994",
-      pages          = "2658-2697",
-      doi            = "10.1103/PhysRevD.49.2658",
-      eprint         = "gr-qc/9402014",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      reportNumber   = "GRP-369",
-      SLACcitation   = "%%CITATION = GR-QC/9402014;%%"
-}
-
-@article{Rodriguez:2013oaa,
-      author         = "Rodriguez, Carl L. and Farr, Benjamin and Raymond, Vivien
-                        and Farr, Will M. and Littenberg, Tyson B. and Fazi, Diego
-                        and Kalogera, Vicky",
-      title          = "{Basic Parameter Estimation of Binary Neutron Star
-                        Systems by the Advanced LIGO/Virgo Network}",
-      journal        = "Astrophys. J.",
-      volume         = "784",
-      year           = "2014",
-      pages          = "119",
-      doi            = "10.1088/0004-637X/784/2/119",
-      eprint         = "1309.3273",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.HE",
-      SLACcitation   = "%%CITATION = ARXIV:1309.3273;%%"
-}
-
-@article{Farr:2015lna,
-      author         = "Farr, Ben and others",
-      title          = "{Parameter estimation on gravitational waves from
-                        neutron-star binaries with spinning components}",
-      journal        = "Astrophys. J.",
-      volume         = "825",
-      year           = "2016",
-      number         = "2",
-      pages          = "116",
-      doi            = "10.3847/0004-637X/825/2/116",
-      eprint         = "1508.05336",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.HE",
-      reportNumber   = "LIGO-P1500117",
-      SLACcitation   = "%%CITATION = ARXIV:1508.05336;%%"
-}
-
-@article{Read:2009yp,
-      author         = "Read, Jocelyn S. and Markakis, Charalampos and Shibata,
-                        Masaru and Uryu, Koji and Creighton, Jolien D. E. and
-                        Friedman, John L.",
-      title          = "{Measuring the neutron star equation of state with
-                        gravitational wave observations}",
-      journal        = "Phys. Rev.",
-      volume         = "D79",
-      year           = "2009",
-      pages          = "124033",
-      doi            = "10.1103/PhysRevD.79.124033",
-      eprint         = "0901.3258",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = ARXIV:0901.3258;%%"
-}
-
-@article{Andersson:2009yt,
-      author         = "Andersson, N. and Ferrari, V. and Jones, D. I. and
-                        Kokkotas, K. D. and Krishnan, B. and Read, J. S. and
-                        Rezzolla, L. and Zink, B.",
-      title          = "{Gravitational waves from neutron stars: Promises and
-                        challenges}",
-      journal        = "Gen. Rel. Grav.",
-      volume         = "43",
-      year           = "2011",
-      pages          = "409-436",
-      doi            = "10.1007/s10714-010-1059-4",
-      eprint         = "0912.0384",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.SR",
-      SLACcitation   = "%%CITATION = ARXIV:0912.0384;%%"
-}
-
-@article{PhysRevD.91.043002,
-  title = {Reconstructing the neutron-star equation of state with gravitational-wave detectors from a realistic population of inspiralling binary neutron stars},
-  author = {Lackey, Benjamin D. and Wade, Leslie},
-  journal = {Phys. Rev. D},
-  volume = {91},
-  issue = {4},
-  pages = {043002},
-  numpages = {20},
-  year = {2015},
-  month = {Feb},
-  publisher = {American Physical Society},
-  doi = {10.1103/PhysRevD.91.043002},
-  url = {https://link.aps.org/doi/10.1103/PhysRevD.91.043002}
-}
-
-@article{PhysRevD.89.103012,
-  title = {Systematic and statistical errors in a Bayesian approach to the estimation of the neutron-star equation of state using advanced gravitational wave detectors},
-  author = {Wade, Leslie and Creighton, Jolien D. E. and Ochsner, Evan and Lackey, Benjamin D. and Farr, Benjamin F. and Littenberg, Tyson B. and Raymond, Vivien},
-  journal = {Phys. Rev. D},
-  volume = {89},
-  issue = {10},
-  pages = {103012},
-  numpages = {14},
-  year = {2014},
-  month = {May},
-  publisher = {American Physical Society},
-  doi = {10.1103/PhysRevD.89.103012},
-  url = {https://link.aps.org/doi/10.1103/PhysRevD.89.103012}
-}
-
-@article{GBM:2017lvd,
-      author         = "Abbott, B. P. and others",
-      title          = "{Multi-messenger Observations of a Binary Neutron Star
-                        Merger}",
-      collaboration  = "GROND, SALT Group, OzGrav, DFN, INTEGRAL, Virgo,
-                        Insight-Hxmt, MAXI Team, Fermi-LAT, J-GEM, RATIR, IceCube,
-                        CAASTRO, LWA, ePESSTO, GRAWITA, RIMAS, SKA South
-                        Africa/MeerKAT, H.E.S.S., 1M2H Team, IKI-GW Follow-up,
-                        Fermi GBM, Pi of Sky, DWF (Deeper Wider Faster Program),
-                        Dark Energy Survey, MASTER, AstroSat Cadmium Zinc
-                        Telluride Imager Team, Swift, Pierre Auger, ASKAP,
-                        VINROUGE, JAGWAR, Chandra Team at McGill University,
-                        TTU-NRAO, GROWTH, AGILE Team, MWA, ATCA, AST3, TOROS,
-                        Pan-STARRS, NuSTAR, ATLAS Telescopes, BOOTES, CaltechNRAO,
-                        LIGO Scientific, High Time Resolution Universe Survey,
-                        Nordic Optical Telescope, Las Cumbres Observatory Group,
-                        TZAC Consortium, LOFAR, IPN, DLT40, Texas Tech University,
-                        HAWC, ANTARES, KU, Dark Energy Camera GW-EM, CALET, Euro
-                        VLBI Team, ALMA",
-      journal        = "Astrophys. J.",
-      volume         = "848",
-      year           = "2017",
-      number         = "2",
-      pages          = "L12",
-      doi            = "10.3847/2041-8213/aa91c9",
-      eprint         = "1710.05833",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.HE",
-      reportNumber   = "LIGO-P1700294, VIR-0802A-17, FERMILAB-PUB-17-478-A-AE-CD",
-      SLACcitation   = "%%CITATION = ARXIV:1710.05833;%%"
-}
-
-% For \cite{LSST}
-@ARTICLE{LSST,
-   author = {{LSST Science Collaboration} and {Abell}, P.~A. and {Allison}, J. and 
-	{Anderson}, S.~F. and {Andrew}, J.~R. and {Angel}, J.~R.~P. and 
-	{Armus}, L. and {Arnett}, D. and {Asztalos}, S.~J. and {Axelrod}, T.~S. and et al.},
-    title = "{LSST Science Book, Version 2.0}",
-  journal = {ArXiv e-prints},
-archivePrefix = "arXiv",
-   eprint = {0912.0201},
- primaryClass = "astro-ph.IM",
- keywords = {Astrophysics - Instrumentation and Methods for Astrophysics, Astrophysics - Cosmology and Extragalactic Astrophysics, Astrophysics - Earth and Planetary Astrophysics, Astrophysics - Galaxy Astrophysics, Astrophysics - Solar and Stellar Astrophysics},
-     year = 2009,
-    month = dec,
-   adsurl = {http://adsabs.harvard.edu/abs/2009arXiv0912.0201L},
-  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
-}
-
-% For \cite{CE}
-@article{Evans:2016mbw,
-      author         = "Abbott, Benjamin P. and others",
-      title          = "{Exploring the Sensitivity of Next Generation
-                        Gravitational Wave Detectors}",
-      collaboration  = "LIGO Scientific",
-      journal        = "Class. Quant. Grav.",
-      volume         = "34",
-      year           = "2017",
-      number         = "4",
-      pages          = "044001",
-      doi            = "10.1088/1361-6382/aa51f4",
-      eprint         = "1607.08697",
-      archivePrefix  = "arXiv",
-      primaryClass   = "astro-ph.IM",
-      reportNumber   = "LIGO-P1600143",
-      SLACcitation   = "%%CITATION = ARXIV:1607.08697;%%"
-}
-
-% For \cite{Kagra2}
-@article{Akutsu:2017kpk,
-      author         = "Akutsu, T. and others",
-      title          = "{Construction of KAGRA: an Underground Gravitational Wave
-                        Observatory}",
-      collaboration  = "KAGRA",
-      year           = "2017",
-      eprint         = "1712.00148",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = ARXIV:1712.00148;%%"
-}
-
-% For \cite{ETB}
-@article{Hild:2010id,
-      author         = "Hild, S. and others",
-      title          = "{Sensitivity Studies for Third-Generation Gravitational
-                        Wave Observatories}",
-      journal        = "Class. Quant. Grav.",
-      volume         = "28",
-      year           = "2011",
-      pages          = "094013",
-      doi            = "10.1088/0264-9381/28/9/094013",
-      eprint         = "1012.0908",
-      archivePrefix  = "arXiv",
-      primaryClass   = "gr-qc",
-      SLACcitation   = "%%CITATION = ARXIV:1012.0908;%%"
-}

### 2018-02-24 Paper/Manuscript.tex
Started writing Sec VI

@@
 \usepackage{float}
+\usepackage{enumerate}
 \usepackage[usestackEOL]{stackengine} % package used to write several lines in one box
@@
 %
-As we will also consider the case of $\psi=0,\iota=0$, we additionally introduce the following $\theta,\phi$-only averages
-%
-\be
- \langle F_+^2\rangle_{\theta,\phi} = \frac{7}{30},\qquad \langle F_\times^2\rangle_{\theta,\phi} = \frac{1}{6}
-\ee
-yielding
-%
-\be
-\langle |Q(\theta,\phi,\psi=0,\iota=0)|^2 \rangle_{\theta,\phi} = \f{2}{5} \label{eq:RMS_th_phi}.
-\ee
-Finally, we add the case of an optimally-oriented, purely $+$-polarized source ($\psi=0,\iota=0$) that is directly overhead ($\theta=0$) simply resulting in 
-%
-\be
-\langle |Q(\theta=0,\phi=0,\psi=0,\iota=0)|^2 \rangle = 1.
-\ee
+As angles have zero averages in general, we can think of the RMS as the standard deviation ($\sigma =2/5$). 
+Therefore, $2\sigma= 4/5$ above the average (zero in this case) should statistically cover 95\% of the four-dimensional angle space. 
+%Finally, we add the case of an optimally-oriented, purely $+$-polarized source ($\psi=0,\iota=0$) that is directly overhead ($\theta=0$) simply resulting in 
+%
+%\be
+%\langle |Q(\theta=0,\phi=0,\psi=0,\iota=0)|^2 \rangle = 1.
+%\ee
 %
@@
 %
-
-%%
-
-In a network of $N$ interferometers, we can define a total effective SNR as follows
+%%
+
+In a network of $N$ interferometers, the total SNR is defined as follows
 %%
@@
 Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
-an \emph{imaginary network} of three detectors ($N=3$), where one interferometer is optimally oriented/positioned, another one operates at the RMS average thus
-its sensitivity is relatively suppressed by a factor $2/5$ (Eq.~\ref{eq:RMS_th_ph_ps_iota}) due to suboptimal configuration.
-Our third detector has even lower sensitivity with a relative suppression factor of $4/5-\sqrt{2/5}\simeq 0.1675$ which is essentially a $\{\theta$-$\phi\}$-RMS away
-from the overall RMS averaged value of 2/5.
-This is our way of simulating a future detection in the Advanced-LIGO-Virgo network of 2020s where the three interferometers will yield varying SNRs
-due to their differing quality factors.
-%
-Therefore, to represent our multi-interferometer network, we introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) for each interferometer
-%%
-%
-\be
-\tilde{H}_i(f)\equiv \tilde{A}_i\, h_0\, f^{-7/6}, \label{eq:Hi_s}
-\ee
-%
-%%
-where
+an \emph{model network} of three detectors ($N=3$), where one interferometer is near-optimally oriented/positioned thus it is at $2\sigma$ above the average.
+The second IFO operates at the RMS average; thus its sensitivity is suppressed by a factor $2/5$ compared with $\langle|Q|^2\rangle =1$ case.
+It remains to assign a quality factor for the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
+but it would be pointless to simply set its $\langle|Q|^2\rangle$ equal to zero. We therefore somewhat arbitrarily set $\psi=0,\iota=0$
+and introduce the following $\theta,\phi$-only averages
+%
+\be
+ \langle F_+^2\rangle_{\theta,\phi} = \frac{7}{30},\qquad \langle F_\times^2\rangle_{\theta,\phi} = \frac{1}{6}\, 
+\ee
+yielding
+%
+\be
+\langle |Q(\theta,\phi,\psi=0,\iota=0)|^2 \rangle_{\theta,\phi} = \f{2}{5} \label{eq:RMS_th_phi}.
+\ee
+Using this value, we assign our below-average third IFO $\langle|Q|^2\rangle^{1/2}=4/5-\sqrt{2/5}\simeq 0.1675$.
+%which is essentially a $\{\theta$-$\phi\}$-RMS awayfrom the overall RMS averaged value of 2/5.
+This may seem somewhat ad hoc, but it is our way of modeling the Advanced-LIGO-Virgo network of 2020s in which 
+the three IFOs will accumulate varying SNRs due to their differing quality factors.
+%
+
+Therefore, to represent our multi-interferometer network, we introduce % the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
+%%
+%
+\be
+\tilde{H}_i(f)\equiv \tilde{A}_i\, h_0\, f^{-7/6} \label{eq:Hi_s}
+\ee
+%
+%%
+for each interferometer, where
 %%
@@
 %\tilde{A}_i &\equiv A \langle |Q|^2\rangle^{1/2}_i=\f{1}{2}\sqrt{\f{5}{6}}\, \pi^{-2/3} \left\langle\, |Q_i(\theta,\phi,\psi,\iota)|^2\,\right\rangle^{1/2}\quad\text{and} \label{eq:A_tilde}\\
-h_0 &= \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} \label{eq:h0}
+h_0 &= \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} \label{eq:h0}\, .
 \end{align}
 %
-and the $\tilde{A}_i$ are given in Table~\ref{table:network_params}.
+and the $\tilde{A}_i =A\langle|Q|^2\rangle^{1/2}_i $ are given in Table~\ref{table:network_params}.
 %for $i=1,2,3$.
@@
 \centering
-\begin{tabular}{c||c|c|l}
- IFO ($i$) & configuration %& $\langle |Q_i|^2\rangle$ 
+\begin{tabular}{c|c|c|c}
+ IFO$_i$ & configuration %& $\langle |Q_i|^2\rangle$ 
  & $\tilde{A}_i$ & $\tilde{H}_i(f)$\\
- \hline
+ %\hline
  \hline
@@
 \caption{%The averaged quality factors $\langle|Q|^2\rangle$ of 
-Our imaginary network of three L-shaped interferometers (IFOs). Column four lists the magnitude of the strain for each IFO via Eq.~(\ref{eq:Hi_s}).
-``Configuration'' describes how ideally oriented/positioned an IFO is with respect to a compact binary source. High means ideal configuration maximizing $Q_i$.
-Medium is the RMS-averaged response. Recall $A= \pi^{-2/3} \sqrt{5/24}$. 
+Our model for the Advanced-LIGO-Virgo network ca. 2020. %of three L-shaped interferometers (IFOs). 
+Column four lists the magnitude of the strain for each IFO via Eq.~(\ref{eq:Hi_s}).
+``Configuration'' describes how ideally oriented/positioned an IFO is with respect to a compact binary source. 
+High is $2\sigma$ above the average as explained above.
+Medium is the RMS-averaged (one $\sigma$) response. Recall $A= \pi^{-2/3} \sqrt{5/24}$. 
 %Note that for an interferometer where the angle between the arms is $\alpha$, $A$ rescales to $A\sin\alpha$.
@@
 amplitude of the incoming GWs by appropriate factors explained in Sec.~\ref{sec:BNS_inspiral} and shown in Table~\ref{table:network_params}.
-The amplitude-adjusted strains $ \tilde{H}_i(f)$ are represented by the solid ($i=h$), dashed ($i=m$), and dotted ($i=l$) lines in the figure where we actually plot
-$2\sqrt{f} \tilde{H}_i(f)$ as explained above.
+The amplitude-adjusted strains $ \tilde{H}_i(f)$ are represented by the dashed ($i=h$), solid ($i=m$), and dotted ($i=l$) lines in the figure where we actually plot
+$2\sqrt{f} \tilde{H}_i(f)$ as is standard. 
 Using Eq.~(\ref{eq:SNR_i_with_fi}) we can immediately compute the SNRs accumulated by our network
@@
 \be
-\bar\rho_h = 35.8,\quad \bar\rho_m = 14.3,\quad \bar\rho_l = 6.00 \label{eq:GW170817_SNRs}.
+\bar\rho_h = 29.2,\quad \bar\rho_m = 14.6,\quad \bar\rho_l = 6.11 \label{eq:GW170817_SNRs}.
 \ee
@@
 By 2020, Virgo should be operating at nearly the same sensitivity of LIGO.}.
-To accommodate more realistic orientations, we show two shaded regions in Fig.~\ref{fig:figGW170817}. The inspirals in the lighter region yield SNR$\ge 22.34$ as
-they sweep from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz whereas inspirals in the darker region accumulate $ \bar\rho_l \le \text{SNR} \le 22.34$.
-Given a network of three equally sensitive, randomly oriented IFOs we expect that a single BNS inspiral would produce two detector strains in the darker region 
-and one in the lighter region.
+%To accommodate more realistic orientations, we show two shaded regions in Fig.~\ref{fig:figGW170817}. The inspirals in the lighter region yield SNR$\ge 22.34$ as
+%they sweep from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz whereas inspirals in the darker region accumulate $ \bar\rho_l \le \text{SNR} \le 22.34$.
+The shaded region in Fig.~\ref{fig:figGW170817} covers strains between $\tilde{H}_l(f)$ and $\tilde{H}_h(f)$. %which we expect to represent mo
+Given a network of three equally sensitive, randomly oriented IFOs we expect that a single BNS inspiral would produce three distinct detector
+response strains in this shaded region.
 %
@@
 \includegraphics[height=9cm]{../Figures/GW170817_strains.pdf}
-\caption{GW170817 as it sweeps from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz across our network with ASD (sensitivity) of LIGO Livingstone (L1) during the event (red curve).
-We also show the Hanford detector's sensitivity for comparison. The dashed, solid and dotted lines represent the strains 
-$2\sqrt{f} \tilde{H}_i(f)$ (see, e.g,. Eq.~(\ref{eq:Hi_s}) and Table~\ref{table:network_params}) due to the inspiral of
-a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}). The change in strain amplitudes is the result of a
-given interferometer's orientation and the sky position of the source. In other words, the dashed line is how ``loud'' GW170817 
-is at an optimally oriented IFO with L1's sensitivity
+\caption{GW170817 as it sweeps from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz across our network with ASD (sensitivity) of 
+LIGO Livingstone (L1) during the event (the darker red curve).
+We also show the Hanford detector's sensitivity in light blue for comparison. The dashed, solid and dotted lines represent the 
+response of each interferometer's frequency-domain response ($2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$) to the inspiral of
+a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}).
+The variation in strain amplitudes is the result of a given interferometer's orientation and the sky position of the source 
+as explained in Sec.~\ref{sec:LIGO_topo} and summarized in Table~\ref{table:network_params}.
+In other words, the dashed line is how ``loud'' GW170817 would appear in the data stream of a near optimally oriented IFO with L1's sensitivity
 %would be if L1was optimally positioned and oriented 
-(quality factor $Q=1$). Similarly, the solid line is the strain in a randomly oriented IFO with randomized source sky location, hence
-we use the RMS-averaged L1 sensitivity which effectively lowers the solid line by a factor of $2/5$. %, but with RMS-average over all angles 
+(quality factor $Q=4/5$). Similarly, the solid line represents the strain in %a randomly oriented IFO with randomized source sky location, hence
+the RMS-averaged IFO with L1's sensitivity ($Q=2/5$). %, but with RMS-average over all angles 
 %determining source orientation and position. 
 Finally, the dotted line represents a pessimistic IFO orientation and source location (sub-optimal configuration)
-resulting in a reduction of amplitude to $ 16.7\%$ of the optimal case. 
+resulting in a reduction of amplitude to $ 16.7\%$ of the $Q=1$ case. 
 The shading represents the region of likelihood for where the strain due to an inspiralling BNS would be. In the case of a three-IFO
-network, we expect all three strains to exist somewhere in the shaded region.
+network, we would expect all three strains to exist somewhere in the shaded region most of the time and two out of three every time.
 %The darker region marks $\text{RMS}\pm(\sqrt{2/5}-2/5)$ translating to an amplitude range of $ 16.7\% - 63.2\%$ of the maximum $\tilde{H}_h(f)$.
@@
 \be
-\bar\rho_\text{tot}= \sqrt{\bar\rho^2_h+\bar\rho^2_m+\bar\rho^2_l}= 39.1 \, \label{eq:SNR_total_GW170817} .
+\bar\rho_\text{tot}= \sqrt{\bar\rho^2_h+\bar\rho^2_m+\bar\rho^2_l}= 32.6 \, \label{eq:SNR_total_GW170817} .
 \ee
@@
 We summarize our results in Table \ref{table:LIGO2020} where we present both the 0PN and the 3.5PN results for the advance warning times
-$T_\text{AW}$. As can be seen from the values for $T_\text{AW}$ in the table, we can at best expect 100\,seconds of early warning time.
-This time increases to 2.5\,minutes in the case of another GW170817-like event with $D=40\,$Mpc.
+$T_\text{AW}$. As can be seen from the values for $T_\text{AW}$ in the table, we can at best expect 85\,seconds of early warning time.
+This time increases to 2\,minutes in the case of another GW170817-like event with $D=40\,$Mpc.
 The current best estimate for the event rate of BNS inspirals is $ 1540^{+3200}_{-1220}\,$Gpc$^{-3}$yr$^{-1}$, inferred from the O1 and O2 observing periods of Advanced LIGO \cite{GW170817}.
-This translates to $\approx 0.1$ event per (40-Mpc)$^3$ per year, or taking the upper limit $\approx 0.3$. So we can at best hope to detect
-one 40-Mpc inspiral per three years or longer.
+This translates to $\approx 0.1$ event per (40-Mpc)$^3$ per year with the upper limit $\approx 0.3$. So we can at best hope to detect
+one 40-Mpc inspiral per a three-year period.
 Therefore, we do not expect to be able forecast GRBs in the Advance LIGO-Virgo era given that we might at best have a couple of minutes of warning time. 
-However, given Moore's law and new search approaches based on deep learning (\cite{Gabbard:2017lja}) 
-we prefer to remain optimistic about the prospects of forecasting at least one GRB in the 2020s. %that this latency can be reduced to minutes.
+%we prefer to remain optimistic about the prospects of forecasting at least one GRB in the 2020s. %that this latency can be reduced to minutes.
 %if we dare to entertain peak CPU computation rates of $\sim 10^{13}\,$flops/sec for 2020 then $\sim 100$ computing cores would suffice to match-filter $10^5$ templates {\bf in how much time?} extrapolating on the results of Ref.~\cite{Cannon:2011vi}.
@@
 \centering
-\begin{tabular}{lcccc}
+\begin{tabular}{lcccccc}
 \hline
-$D\,$(Mpc) & $\bar{f}\,$(Hz) & $T^{0PN}_\text{AW}$(sec) & $T^{3.5PN}_\text{AW}$(sec)& $\bar{\rho}_F$\T\B\\
+$D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}$(sec)& $\bar{\rho}_F$\T\B\\
 \hline
-50 & 22.8 &111.1 & 113.1 & 84.2 \T\\
-100 & 36.2 & 32.41 & 33.08 & 42.1 \\
-200 & 79.3 & 4.859 & 4.948 & 21.0 \\
+50 & 25.3 & & 84.25 & & 85.86 & 70.3 \T\\
+100 & 41.6 & & 22.39 & & 22.86 & 35.2 \\
+200 & 121.3 & & 1.291 &\quad & 1.300 & 17.6 \\
 \hline
@@
 %
-
-In addition to potentially alerting the E\,\&\,M community, the ALV network will accumulate impressive SNRs 
+%
+Be that as it may,
+%In addition to potentially alerting the E\,\&\,M community, 
+the ALV network will accumulate impressive SNRs 
 (see $\bar{\rho}_F$ in Table~\ref{table:LIGO2020}) for BNS inspirals out to 100\,Mpc.
-Monte-Carlo simulations of BNS systems indicate that the measurement errors for the system parameters are proportional to $\bar\rho^{-1}_F$ \cite{Cutler:1994ys}.
-Therefore, systems that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
+%Monte-Carlo simulations of BNS systems indicate that 
+As the measurement errors for the system parameters are proportional to $\bar\rho^{-1}_F$ \cite{Cutler:1994ys},
+systems that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
 $M_c, M$ \cite{Farr:2015lna}; (ii) sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};
@@
 parameters of neutron stars \cite{Read:2009yp, Andersson:2009yt, PhysRevD.89.103012, PhysRevD.91.043002}.
-We should caution the reader that such systems will make up $\lesssim 1\%$ of the population of BNSs detected by 
+We should caution the reader that such high-SNR systems will make up $\lesssim 1\%$ of the population of BNSs detected by 
 the ALV network \cite{Sathyaprakash:2012jk}.
@@
 Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET.
-Speculating that the advances in the detection, localization and early-warning algorithms in the next decade will reduce the required early
-warning time to less than an hour, we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS horizon distances of $D_H=87,613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
+Given Moore's law and new search approaches based on deep learning (\cite{Gabbard:2017lja}) we speculate
+that the advances in the detection, localization and early-warning algorithms in the next decade will reduce the required early
+warning time to less than an hour; thus we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS horizon distances of $D_H=87,613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
 In other words, all inspiralling BNSs closer than $D_H$ will give us more than an hour's leeway before the GRB (assuming detection SNR of 15 as always).
@@
 The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
-such as the black hole mass and spin. The evolution of black hole-neutron star (BH-NS) binaries is a very active branch of numerical relativity
-(see Ref. \cite{Shibata:2011jka} for a comprehensive review).
+such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $C_\text{NS}\equiv G m_\text{NS}/(R_\text{NS}c^2)$. 
+The evolution of black hole-neutron star (BH-NS) binaries is a very active branch of numerical relativity
+(see Ref. \cite{Shibata:2011jka} for a comprehensive review) and is beyond the scope of this article, however the numerical simulaitions
+have verified certain qualitative principles that will guide us:{\bf fix this sentence}
+%
+\begin{enumerate}[(i)]
+ \item Small separations. The Newtonian tidal force due to the black hole (BH) is proportional to $M_\text{BH}/r^3$. Therefore, $r$ has to be
+ minimized to ensure maximum tide.
+ \item ISCO as a lower bound. However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
+ \item Small black hole masses. In the geodecis case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}^{-2}$. 
+ \item High black hole spins. Moreover, $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
+ For instance, for the maximum spin value of $a=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value whereas for
+ $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
+\end{enumerate}
+
+We will set $a=0.9$ cite, $M_\text{BH} =5 M_\odot$ cite(Morgan's email)
+
+The less massive BHs are also desirable as 
+ $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv m_2/m_1 > 1$.
 

### 2018-02-26 Paper/Manuscript.tex
Wrote more in the BH-NS section, added one new reference.

@@
 such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $C_\text{NS}\equiv G m_\text{NS}/(R_\text{NS}c^2)$. 
-The evolution of black hole-neutron star (BH-NS) binaries is a very active branch of numerical relativity
-(see Ref. \cite{Shibata:2011jka} for a comprehensive review) and is beyond the scope of this article, however the numerical simulaitions
-have verified certain qualitative principles that will guide us:{\bf fix this sentence}
+The evolution of black hole-neutron star (BH-NS) binaries is a very active branch of numerical relativity and high-energy astrophysics
+(see Ref. \cite{Shibata:2011jka} for a comprehensive review) requiring fully general relativistic magnetohydrodynamic codes with neutrino transport
+running on large-scale clusters. As such, the details are beyond the scope of this article. %, however the numerical simulationshave verified
+
+A necessary, but insufficient, condition for tidal disruption (TD) is that
+\be
+\f{2 G M_\text{BH} (c_R R_\text{NS})}{r^3} \gtrsim \f{G M_\text{NS}}{(c_R R_\text{NS})^2} \label{eq:TD_cond1},
+\ee
+where $r$ is the orbital separation, $R_\text{NS}$ is the mass of the NS and $M$ denotes masses. 
+$c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to first order with
+$c_R >1 $. Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$ , we can roughly take the above condition to be
+%
+\be
+\f{m_2}{m_1} \gtrsim \left(\f{r}{r_1}\right)^3 \label{eq:TD_cond2}.
+\ee
+
+We wish to maximize the chances of observing a TD event, therefore we impose certain desirable features on our BH-NS binaries, 
+some of which can be deduced from Eq.~(\ref{eq:TD_cond2}). These are
+
 %
 \begin{enumerate}[(i)]
- \item Small separations. The Newtonian tidal force due to the black hole (BH) is proportional to $M_\text{BH}/r^3$. Therefore, $r$ has to be
- minimized to ensure maximum tide.
- \item ISCO as a lower bound. However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
+ \item Small separations. As the Newtonian tidal force due to the black hole (BH) is proportional to $M_\text{BH}/r^3$, $r$ has to be
+ minimized to provide maximum tidal force. 
+ However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
  \item Small black hole masses. In the geodecis case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}^{-2}$. 
+ Hence, $M_\text{BH}$ must also be minimized.
  \item High black hole spins. Moreover, $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
- For instance, for the maximum spin value of $a=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value whereas for
+ For instance, for the maximum dimensionless spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value whereas for
  $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
+ \item Less compact neutron stars. Eq.~(\ref{eq:TD_cond1}) can be rearranged to isolate the dimensionless quantity $ G M_\text{NS}/(c^2 R_\text{NS})$
+ on the right hand side. This is known as the neturon star compacteness parameter $c_\text{NS}$. The smaller $c_\text{NS}$ the easier it is for TD to occur.
 \end{enumerate}
 
-We will set $a=0.9$ cite, $M_\text{BH} =5 M_\odot$ cite(Morgan's email)
+ISCO location from NR 
+\be
+\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
+\ee
+
+If we now naively insert the Schwarzschild value for theISCO we get $m_2 \approx 4.1 M_\odot$.
+
+We will set $a=0.9$ cite, $M_\text{BH} =5 M_\odot$ cite(Morgan's email), $R_\text{NS} = 12\,$km
 
 The less massive BHs are also desirable as 
- $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv m_2/m_1 > 1$.
+ $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q\to Q^{-2/3}$ as $Q\to\infty$ for $Q\equiv m_2/m_1 > 1$.
+ As $\tilde{H}(f) \propto M_c^{5/6}$ SNR$\propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$.
 
@@
 Also need highly spinning BH to decreases the ISCO radius.
+
+Morgan: \\
+What I worry is whether the requirements of as low a mass as possible, and as high a spin as possible, can in fact be simultaneously satisfied.
+Assuming that the BH is spun up by accretion from the secondary in the binary (that will later on become a NS), it will have to gain mass.
+The question is then whether the mass gain is going to push up the value of Q so much that it kills any advance warning you might get.
+However, if the spin of the BH comes from the supernova explosion mechanism itself (as argued for G1915 in \cite{McClintock:2006xd} then this is not a problem.
 

### 2018-02-26 Paper/Manuscript.tex
Added a few more lines

@@
 
-We will set $a=0.9$ cite, $M_\text{BH} =5 M_\odot$ cite(Morgan's email), $R_\text{NS} = 12\,$km
+We will set $M_\text{BH} =5 M_\odot$ cite(Morgan's email) $a=0.9$ cite,, $R_\text{NS} = 12\,$km
+For inspiral timescales it doesn't actually matter where the ISCO is as the time difference between a plunge at 6M vs. one at M is (compute).
+What matter is mass of the black hole, we will simply make the assmpution that there exist black holes with high spins at that mass scale.
 

### 2018-02-27 Paper/Manuscript.tex
Sec. VI and references from home

@@
 \usepackage{tensor}
+\usepackage[utf8]{inputenc}
 \usepackage{url}
@@
 \section{Binary black hole neutron star systems}
-In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star as it falls into a black hole. 
+In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
 The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
-such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $C_\text{NS}\equiv G m_\text{NS}/(R_\text{NS}c^2)$. 
-The evolution of black hole-neutron star (BH-NS) binaries is a very active branch of numerical relativity and high-energy astrophysics
-(see Ref. \cite{Shibata:2011jka} for a comprehensive review) requiring fully general relativistic magnetohydrodynamic codes with neutrino transport
-running on large-scale clusters. As such, the details are beyond the scope of this article. %, however the numerical simulationshave verified
+such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $c_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$. 
+The evolution of black hole-neutron star (BH-NS) binaries is a very active field of research at the interface of numerical relativity and high-energy astrophysics
+(see Ref. \cite{Shibata:2011jka} for a comprehensive review) requiring fully general relativistic magnetohydrodynamic treatment including neutrino transport equations.
+The complexity of evolving the dynamics of these systems require large computational resources and long runtimes.
+%running on large-scale clusters.
+As such, the details are beyond the scope of this article, but we can use a mostly Newtonian treatment to serve our purposes. %, however the numerical simulationshave verified
 
@@
 \ee
-where $r$ is the orbital separation, $R_\text{NS}$ is the mass of the NS and $M$ denotes masses. 
-$c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to first order with
-$c_R >1 $. Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$ , we can roughly take the above condition to be
+where $r$ is the orbital separation, $R_\text{NS}$ is the radius of the NS and $M$ denotes masses. 
+$c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to leading order with
+$c_R >1 $. Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, we can roughly take the above condition to be
 %
@@
 \ee
-
-We wish to maximize the chances of observing a TD event, therefore we impose certain desirable features on our BH-NS binaries, 
-some of which can be deduced from Eq.~(\ref{eq:TD_cond2}). These are
-
+%
+We wish to maximize the chances of observing a TD event, therefore we ingrain the BH-NS binary with certain desirable features
+some of which can be deduced from Eqs.~(\ref{eq:TD_cond1}, \ref{eq:TD_cond2}). These are
+%
 %
 \begin{enumerate}[(i)]
- \item Small separations. As the Newtonian tidal force due to the black hole (BH) is proportional to $M_\text{BH}/r^3$, $r$ has to be
+ \item Small separation. As the Newtonian tidal force due to the black hole is proportional to $M_\text{BH}/r^3$, $r$ has to be
  minimized to provide maximum tidal force. 
  However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
- \item Small black hole masses. In the geodecis case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}^{-2}$. 
- Hence, $M_\text{BH}$ must also be minimized.
- \item High black hole spins. Moreover, $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
- For instance, for the maximum dimensionless spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value whereas for
- $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
- \item Less compact neutron stars. Eq.~(\ref{eq:TD_cond1}) can be rearranged to isolate the dimensionless quantity $ G M_\text{NS}/(c^2 R_\text{NS})$
- on the right hand side. This is known as the neturon star compacteness parameter $c_\text{NS}$. The smaller $c_\text{NS}$ the easier it is for TD to occur.
+ \item Low black hole mass. In the geodesic case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}^{-2}$. 
+ Hence, $M_\text{BH}$ must also be minimized. Once again, there is a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models.
+ Current consensus for this lower bound yields $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua}.
+ \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
+ For instance, for the maximum dimensionless spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value ($6GM_\text{BH}/c^2$) whereas for $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
+ With smaller ISCO separation, there is much more tidal force exerted on the NS before it plunges in.
+ \item Less compact neutron stars. Eq.~(\ref{eq:TD_cond1}) can be rearranged to isolate $c_\text{NS}$
+ on the right hand side. Smaller values for $c_\text{NS}$ mean that TD can occur for $r>r_\text{ISCO}$.
 \end{enumerate}
+%
+We are thus led to set $M_\text{BH} =5 M_\odot$. There is additional motivation to choose low BH mass as 
+ $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q\to Q^{-2/3}$ as $Q\to\infty$ for $Q\equiv m_2/m_1 > 1$, i.e., heavier binaries inspiral faster.
+Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
+but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
+%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
+
+The mass bound we set above is only fully consistent with spinning black holes. This can be seen by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
+into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
 
@@
 \ee
-
-If we now naively insert the Schwarzschild value for theISCO we get $m_2 \approx 4.1 M_\odot$.
 
@@
 What matter is mass of the black hole, we will simply make the assmpution that there exist black holes with high spins at that mass scale.
-
-The less massive BHs are also desirable as 
- $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q\to Q^{-2/3}$ as $Q\to\infty$ for $Q\equiv m_2/m_1 > 1$.
- As $\tilde{H}(f) \propto M_c^{5/6}$ SNR$\propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$.
 
@@
 However, if the spin of the BH comes from the supernova explosion mechanism itself (as argued for G1915 in \cite{McClintock:2006xd} then this is not a problem.
+
+ LIGO O1 merger rate  $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx}
 

### 2018-02-27 Paper/Manuscript.tex
Sec. VI + refs.

@@
  $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q\to Q^{-2/3}$ as $Q\to\infty$ for $Q\equiv m_2/m_1 > 1$, i.e., heavier binaries inspiral faster.
-Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
-but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
+ As we set $M_\text{NS}=1.4 M_\odot$, $c_\text{NS}$ is determined by the radius of the NS constrained in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
+ which translates to $0.13\lesssim c_\text{NS} \lesssim 0.15$. We also have $Q  \simeq 3.571$.
+%As we wish to avoid discussing the details of the strong-field evolution of the binary, we borrow certain results from the literature to
+%justify our choice for the chosen parameters above. 
+If we pick the more pessimistic $c_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $a\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}.
+and $Q< 3$ in the case of $a=0$ \cite{Kyutoku:2011vz}.
+Although the results from each numerical study may somewhat vary what is clear is that we must have high spin and low black hole mass.
+This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
+they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, it will have to gain mass.
+It is possible that the mass gain pushes $Q$ too high to either cause a direct plunge of the NS before TD or decrease $\tau_\text{insp}$ considerably
+to eliminate any chances of getting an advance warning.
+However, if the spin of the BH comes from the supernova explosion mechanism itself (as argued for G1915 in Ref.~\cite{McClintock:2006xd} then this is not a problem.
+
+So we will simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
+A quick calculation using the above scaling of $\tau_\text{insp}$ shows that even the largest value for $T_\text{AW}$ in Table \ref{table:LIGO2020}
+is now less than $ 40\,$ seconds which is too little. Therefore, we simply focus on the capabilities of ET-C.
+
+The LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx}.
+%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
+%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
+%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
 %and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
-
-The mass bound we set above is only fully consistent with spinning black holes. This can be seen by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
-into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
+%
+%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
+%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
 
@@
 \ee
-
-We will set $M_\text{BH} =5 M_\odot$ cite(Morgan's email) $a=0.9$ cite,, $R_\text{NS} = 12\,$km
-For inspiral timescales it doesn't actually matter where the ISCO is as the time difference between a plunge at 6M vs. one at M is (compute).
-What matter is mass of the black hole, we will simply make the assmpution that there exist black holes with high spins at that mass scale.
-
-Tidal disruption, minimum BH mass $5 M_\odot$. Tidal force $\sim M/r^3 \sim M^{-2}$ hence the smaller the BH the more TD there will be.
-Also need highly spinning BH to decreases the ISCO radius.
-
-Morgan: \\
-What I worry is whether the requirements of as low a mass as possible, and as high a spin as possible, can in fact be simultaneously satisfied.
-Assuming that the BH is spun up by accretion from the secondary in the binary (that will later on become a NS), it will have to gain mass.
-The question is then whether the mass gain is going to push up the value of Q so much that it kills any advance warning you might get.
-However, if the spin of the BH comes from the supernova explosion mechanism itself (as argued for G1915 in \cite{McClintock:2006xd} then this is not a problem.
-
- LIGO O1 merger rate  $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx}
 

### 2018-03-10 Paper/Manuscript.tex
Updated paper, Mathematica sections regarding BH-NS

@@
 So we will simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
-A quick calculation using the above scaling of $\tau_\text{insp}$ shows that even the largest value for $T_\text{AW}$ in Table \ref{table:LIGO2020}
-is now less than $ 40\,$ seconds which is too little. Therefore, we simply focus on the capabilities of ET-C.
-
-The LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx}.
+A quick calculation shows that these systems yield $T_\text{AW} \lesssim 30\,$seconds in the ALV network of 2020s. %in Table \ref{table:LIGO2020}is now less than $ 40\,$ seconds. 
+Therefore, we simply focus on the capabilities of ET which we summarize in Table~\ref{table:ET_BH_NS} below.
+%
+%
+%
+\begin{table}[h]
+\centering
+\begin{tabular}{l|ccccc}
+%toprule
+\hline
+$D\,$(Mpc) & \multicolumn{2}{c}{ET-B} &  & \multicolumn{2}{c}{ET-C}\T\B\\
+\hline
+{}&  \ \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$ &{}  & \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$\T\B\\
+%midrule
+
+100 &   28.2 minutes & 503 &{\qquad} &  2.15 hours & 601\T\\
+200 & 8.2 minutes & 251  &{\qquad} & 1.1 hours & 300 \\
+400 &  2 minutes & 124 &{\qquad} & 34 minutes & 148\\
+1000 & 14.3 seconds & 49 &{\qquad} & 14 minutes& 58.5\\
+\hline
+%bottomrule
+\end{tabular}
+\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
+The SNR is even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
+\end{table}
+%
+%
+\\
+\noindent
+From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
+Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
+there could be 28.8 such mergers per year within ET-C's horizon distance. We must emphasize that this should be viewed
+as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
+Therefore, we realistically expect ET-C to forecast $\sim \mathcal{O}(1)$ tidal disruption event per year.
+A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
+however, all of these come with rather large error bars {\bf CITE}.
 %and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
@@
 %into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
-
-ISCO location from NR 
-\be
-\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
-\ee
+%ISCO location from NR 
+%\be
+%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
+%\ee
 
@@
 
-\begin{thebibliography}{}
-\bibitem{Regimbau:2012ir}
-\bibitem{KAGRA} \url{http://gwcenter.icrr.u-tokyo.ac.jp/en/}
-\bibitem{KAGRA2} Akutsu et al. see bibtex
-\bibitem{Patricelli:2016bkt}
-\bibitem{CE} https://arxiv.org/pdf/1607.08697.pdf
-\bibitem{Ozel_Freire} 1603.02698 [astro-ph.HE]
-\bibitem{Freire_et_al_2007} The Astrophysical Journal, Volume 675, Issue 1, article id. 670-682, pp. (2008)., arXiv:0711.0925.  
-\bibitem{GW170817}
-\bibitem{PM1963}
-\bibitem{Colpi_Sesana} 1610.05309 [astro-h.HE]
-\bibitem{Maggiore}
-\bibitem{Blanchet_LRR}
-\bibitem{FastestNSspin} J. W. T. Hessels, S. M. Ransom, I. H. Stairs, P. C. C. Freire,
-V. M. Kaspi, and F. Camilo, Science 311, 1901 (2006).
-\bibitem{SchutzLRR} Schutz, Satyaprakash, LRR
-\bibitem{GW170817_Facts} GW170817 Factsheet \url{https://www.ligo.org/detections/GW170817/images-GW170817/GW170817_Factsheet.pdf}.
-\bibitem{4PN_EoM_paper} L. Bernard et al., [gr-qc:1711.00283]
-\bibitem{Reid} J. Reid, the NS inspiral figure tidal corrections
-\bibitem{LIGO_L1_data} Data release for GW170817 \url{https://losc.ligo.org/events/GW170817/}
-\bibitem{LIGO_tutorial} LIGO Open Science Center signal processing tutorial at \url{https://losc.ligo.org/s/events/GW150914/GW150914_tutorial.html}
-\bibitem{LIGO2020} Advanced LIGO anticipated sensitivity curves at \url{https://dcc.ligo.org/LIGO-T0900288/public}
-\bibitem{Hild:2010id} S. Hild et al. Class.Quant.Grav. 28 (2011) 094013  arXiv:1012.0908 [gr-qc]  (see bixtex below)
-\bibitem{LSST} LSST
-\bibitem{GBM:2017lvd} ApJ paper
-\bibitem{Cutler:1994ys}
-\bibitem{Farr:2015lna}
-\bibitem{Rodriguez:2013oaa}
-\bibitem{Read:2009yp}
-\bibitem{Andersson:2009yt}
-\bibitem{PhysRevD.89.103012}
-\bibitem{PhysRevD.91.043002}
-\bibitem{Zhu:2017znf}
-\bibitem{Cannon:2011vi}
-\bibitem{Gabbard:2017lja}
-\bibitem{Sathyaprakash:2012jk}
-\bibitem{ET_doc}
-\bibitem{Sathyaprakash:2012jk}
-\bibitem{Wen:2005ui}
-\end{thebibliography}
+Table 6
+{}&  \ $T_\text{AW}$(sec) \ & $\bar{\rho}_{F}$ &{}  & \ $T_\text{AW}$(sec)\ & $\bar{\rho}_{F}$\T\B\\
+%midrule
+
+100 &   1691 & 503 &{\qquad} &  7834 & 601\T\\
+200 & 493 & 251  &{\qquad} & 3975 & 300 \\
+400 &  118 & 124 &{\qquad} & 2051 & 148\\
+1000 & 14.3 & 49 &{\qquad} & 833& 58.5\\

### 2018-03-13 Paper/Manuscript.tex
2 lines to intro

@@
 \section{Introduction}\label{Sec:Intro}
+The 6.9 gravitational-wave merger events detected by the ALV network have firmly established gravitational-wave astronomy
+as observational astronomy. Though the first event of 14 September 2015 will always be the ``poster-child'' of this field,
+the icing on the cake was the 17 August 2017 event involving the inspiral and merger of a binary neutron star system with a concordant gamma-ray burst detected 1.4 seconds after the coalescence.
+
 We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital frequency $f_K$. 
@@
 \hline
-{}& $\bar{f}\,$(Hz) & \ $T_\text{AW}$(sec) \ & $\bar{\rho}_{F}$ &{} & $\bar{f}\,$(Hz) & \ $T_\text{AW}$(sec)\ & $\bar{\rho}_{F}$\T\B\\
+{}& $\bar{f}\,$(Hz) & \ \hspace{7mm} $T_\text{AW}$ \ \hspace{7mm} & $\bar{\rho}_{F}$ &{} & $\bar{f}\,$(Hz) & \ \hspace{5mm} $T_\text{AW}\hspace{12mm}$& $\bar{\rho}_{F}$\T\B\\
 %midrule
-
-100 & 6.7237 &  2818 & 306.0 &{\qquad} & 3.2692 & 19212 & 365.4\T\\
-200 & 11.2104 & 698.6 & 152.4 &{\qquad} & 4.1028 & 10138 & 182.1 \\
-400 & 18.2234 & 179.8 & 75.74 &{\qquad} & 5.0607 & 5437 & 90.48\\
-1000 & 41.3537 &17.2 & 29.79& \qquad & 6.7553 & 2138 & 35.60  \\
+100 & $\approx\,$6.72 &  47.0\,minutes & 306.0 &{\qquad} & $\approx\,$3.27 & 5.34\,hours\ & 365.4\T\\
+200 & $\approx\,$11.2 & 11.6\,minutes & 152.4 &{\qquad} & $\approx\,$4.10 & 2.87\,hours\ & 182.1 \\
+400 & $\approx\,$18.2 & 3.00\,minutes & 75.74 &{\qquad} & $\approx\,$5.06 & 1.51\,hours\ & 90.48\\
+1000 & $\approx\,$41.3 &17.2\,seconds & 29.79& \qquad &    $\approx\,$6.76 & 35.6\,minutes & 35.60  \\
+% OLD version
+%100 & 6.7237 &  2818 & 306.0 &{\qquad} & 3.2692 & 19212 & 365.4\T\\
+%200 & 11.2104 & 698.6 & 152.4 &{\qquad} & 4.1028 & 10138 & 182.1 \\
+%400 & 18.2234 & 179.8 & 75.74 &{\qquad} & 5.0607 & 5437 & 90.48\\
+%1000 & 41.3537 &17.2 & 29.79& \qquad & 6.7553 & 2138 & 35.60  \\
 \hline
@@
 \hline
-{}&  \ \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$ &{}  & \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$\T\B\\
+{}&  \ \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$ &{}  & $\hspace{6mm}T_\text{AW} \hspace{10mm}$ & $\bar{\rho}_{F}$\T\B\\
 %midrule
 
-100 &   28.2 minutes & 503 &{\qquad} &  2.15 hours & 601\T\\
-200 & 8.2 minutes & 251  &{\qquad} & 1.1 hours & 300 \\
-400 &  2 minutes & 124 &{\qquad} & 34 minutes & 148\\
-1000 & 14.3 seconds & 49 &{\qquad} & 14 minutes& 58.5\\
+100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
+200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
+400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
+1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
 \hline

### 2018-03-15 Paper/Manuscript.tex
Introduction, added references.

@@
 \section{Introduction}\label{Sec:Intro}
-The 6.9 gravitational-wave merger events detected by the ALV network have firmly established gravitational-wave astronomy
-as observational astronomy. Though the first event of 14 September 2015 will always be the ``poster-child'' of this field,
-the icing on the cake was the 17 August 2017 event involving the inspiral and merger of a binary neutron star system with a concordant gamma-ray burst detected 1.4 seconds after the coalescence.
+The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \approx 90\%$ significance hence 6.95 overall.}
+gravitational-wave merger events detected by the Advanced Ligo-Virgo network have firmly established gravitational-wave astronomy
+as an observational science \cite{TheLIGOScientific:2016pea, Abbott:2017gyy, Abbott:2017oio, Abbott:2017vtc, GW170817}. 
+Though the first event of 14 September 2015 (GW150914 \cite{GW150914}) will always be the ``poster-child'' of this field,
+the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor {\bf cite} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}.
+The ALV network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
+enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993 less than 11 hours after the merger, 
+first picked up by the One-Meter, Two Hemisphere team {\bf cite}.
+This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum still ongoing
+more than half a year after the initial GRB \cite{GBM:2017lvd}.
+
+GW170817 was initially identified by the LIGO-Hanford interferometer (H1) 
+using a template bank of gravitational waveforms computed within the framework of post-Newtonian theory \cite{Buonanno:2009zt, Blanchet_LRR}.
+The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from $\sim 30\,$Hz to $\sim 2\,$kHz in 57 seconds
+executing $\sim 3000$ GW cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
+The total mass of the system was inferred to be $2.74^{+0.04}_{-0.01} M_\odot$ with component masses in the range $1.17-1.60 M_\odot$ consistent
+with neutron stars.
+Moreover, both the GW and EM observations are consistent with a source luminosity distance of $\sim 40\,$Mpc
+and support the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
+which was promptly followed by a short-hard gamma-ray burst (GRB170817A) in NGC4993.
+
+One week after GW170817, the ALV network was taken offline for upgrades for the third observation run (O3) 
+scheduled to start in Autumn 2018 with roughly twice the sensitivity of O2.
+In addition, the Japanese cryogenic interferometer KAGRA (\cite{KAGRA, KAGRA2}) will start its test runs in 2018-2019 and reach design sensitivity circa 2021-2022 \cite{Akutsu:2017thy, Aasi:2013wya}.
+By 2025, LIGO-India detector will join the global IFO network hence improving both the overall sensitivity and the sky-localization capabilities \cite{Aasi:2013wya}.
+Around this time, the construction of the first third-generation ground-based IFO, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
+The US is currently considering a mid-2020s update called LIGO-Voyager \cite{LIGO_Voy} and a more ambitious 40\,km long IFO dubbed The Cosmic Explorer \cite{CE}.
+All of these near-future improvements to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
+early enough to witness a gamma-ray burst as it happens? In other words, can we forecast GRBs using the GW detections?
+
+KAGRA 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)
+
+Cite the BNS Living review many times \cite{Faber:2012rw}.
+
+Ref.~\cite{Cannon:2011vi} already attemps some forecast, but they focus on the search algorithm side of things
+
+We also disreagrd the fact that GRBs are collimated and will most often not point toward the Earth. Ref.~\cite{Patricelli:2016bkt} looks at this? (CHECK)
 
@@
 Overdots denote time derivative with respect to detector time, e.g., $\dot{E} =dE/dt$.
-
-Mention {\bf KAGRA} \cite{KAGRA, KAGRA2}, starts 2018-2019, design at 2021-2022, 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)
-
-Cosmic Explorer \cite{CE}, LIGO India, Australia China(?)
-
-Cite the BNS Living review many times \cite{Faber:2012rw}.
-
-Ref.~\cite{Cannon:2011vi} already attemps some forecast, but they focus on the search algorithm side of things
-
-We also disreagrd the fact that GRBs are collimated and will most often not point toward the Earth. Ref.~\cite{Patricelli:2016bkt} looks at this? (CHECK)
 
@@
 We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D\ge 100\,$Mpc for the ET results.}\label{fig:summary}
-\label{fig:summary}
 \end{figure}

### 2018-03-16 Paper/Manuscript.tex
Intro, refs

@@
 Though the first event of 14 September 2015 (GW150914 \cite{GW150914}) will always be the ``poster-child'' of this field,
-the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor {\bf cite} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}.
+the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}.
 The ALV network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
@@
 and support the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
-which was promptly followed by a short-hard gamma-ray burst (GRB170817A) in NGC4993.
+which then caused the prompt short-hard gamma-ray burst (GRB170817A) in NGC4993 as first suggested by Ref.~\cite{Eichler:1989ve}.
 
@@
 All of these near-future improvements to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
-early enough to witness a gamma-ray burst as it happens? In other words, can we forecast GRBs using the GW detections?
-
-KAGRA 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)
+early enough to witness a gamma-ray burst as it happens? In other words, can we forecast GRBs using GW detections?
+
+The short answer is in the affirmative.
+The long answer is still affirmative, but depends on many factors such as source distance and sky position, detector sensitivity and orientation.
+One also needs to account for the fact that GRBs are thought to be collimated emissions with narrow outburst angles \cite{Kumar:2014upa}.
+As such, most GRBs that occur in the universe are electromagnetically undetectable. Fortunately, this was not the case with GRB170817A, 
+but even for a reasonable GRB jet opening angle of $\sim 10^\circ$, we expect to observe $\sim 10\%$ of neutron star mergers as GRBs \cite{Patricelli:2016bkt}. 
+However, it is possible that some of the near-Earth pointing short hard GRBs may be observed as long-duration GRBs or X-ray flashes thus increasing this percentage \cite{Bucciantini:2011kx}.
+
+Given the sensitivities of IFOs to date, efforts have thus far mostly focused on reducing the latency of EM follow-ups, 
+i.e., the lag time between the merger and the alerting of the EM observatories. 
+LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30\,$minutes \cite{Abbott:2011ys} (no detections).
+In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd} 
+with an additional $\sim 10$ hours to locate the optical transient now designated as AT 2017gfo.
+
+Here, we turn this around and focus instead on how much advance warning times near-future ground-based GW detectors can provide us.
+Ref.~\cite{Cannon:2011vi} took up this challenge algorithmically and focused on developing inexpensive methods to detect inspiral
+signals in GW data to provide early-warning triggers \emph{before} the merger.
+
+%KAGRA 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)
 
@@
 
-Ref.~\cite{Cannon:2011vi} already attemps some forecast, but they focus on the search algorithm side of things
-
-We also disreagrd the fact that GRBs are collimated and will most often not point toward the Earth. Ref.~\cite{Patricelli:2016bkt} looks at this? (CHECK)
+ already attemps some forecast, but they focus on the search algorithm side of things
 

### 2018-03-16 Paper/Manuscript.tex
Intro

@@
 LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30\,$minutes \cite{Abbott:2011ys} (no detections).
-In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd} 
-with an additional $\sim 10$ hours to locate the optical transient now designated as AT 2017gfo.
+In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd}.
+It then took an additional $\sim 10$ hours to locate the optical transient designated AT 2017gfo.
 
 Here, we turn this around and focus instead on how much advance warning times near-future ground-based GW detectors can provide us.
-Ref.~\cite{Cannon:2011vi} took up this challenge algorithmically and focused on developing inexpensive methods to detect inspiral
+Ref.~\cite{Cannon:2011vi} considered this by focussing on developing computationally inexpensive methods to detect inspiral
 signals in GW data to provide early-warning triggers \emph{before} the merger.
+We instead focus on the forecasting capabilities of the ground-based IFOs at their full design sensitivity.
+To this end, we consider the $\sim 2020$-design sensitivity of the Advanced-LIGO-Virgo (ALV) network composed of three IFOs and the $\sim 2030$-design
+sensitivity of Einstein Telescope.
 
@@
 
- already attemps some forecast, but they focus on the search algorithm side of things
+Sec.~ blah blah, Sec.~ does so and so, results are presented in Sec.~
 

### 2018-03-19 Paper/Manuscript.tex
Intro + refs

@@
-\documentclass[amsmath,amssymb,aps,floats,amsfonts,notitlepage,superscriptaddress,eqsecnum,nofootinbib,10pt]{revtex4-1}
+\documentclass[prd,amsmath,amssymb,aps,floats,amsfonts,notitlepage,superscriptaddress,eqsecnum,nofootinbib,10pt]{revtex4-1}
 \linespread{1.2}
@@
 the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}.
-The ALV network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
+The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
 enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993 less than 11 hours after the merger, 
@@
 In addition, the Japanese cryogenic interferometer KAGRA (\cite{KAGRA, KAGRA2}) will start its test runs in 2018-2019 and reach design sensitivity circa 2021-2022 \cite{Akutsu:2017thy, Aasi:2013wya}.
-By 2025, LIGO-India detector will join the global IFO network hence improving both the overall sensitivity and the sky-localization capabilities \cite{Aasi:2013wya}.
-Around this time, the construction of the first third-generation ground-based IFO, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
-The US is currently considering a mid-2020s update called LIGO-Voyager \cite{LIGO_Voy} and a more ambitious 40\,km long IFO dubbed The Cosmic Explorer \cite{CE}.
+By 2025, LIGO-India detector will join the global interferometer network hence improving both the overall sensitivity and the sky-localization capabilities \cite{Aasi:2013wya}.
+Around this time, the construction of the first third-generation ground-based interferometer, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
+The US is currently considering a mid-2020s update called LIGO-Voyager \cite{LIGO_Voy} and a more ambitious 40\,km long interferometer dubbed The Cosmic Explorer \cite{CE}.
 All of these near-future improvements to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
@@
 
-Given the sensitivities of IFOs to date, efforts have thus far mostly focused on reducing the latency of EM follow-ups, 
+Given the sensitivities of interferometers to date, efforts have thus far mostly focused on reducing the latency of EM follow-ups, 
 i.e., the lag time between the merger and the alerting of the EM observatories. 
-LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30\,$minutes \cite{Abbott:2011ys} (no detections).
+LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30$ to $60\,$minutes \cite{Abbott:2011ys} (no detections).
 In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd}.
@@
 
-Here, we turn this around and focus instead on how much advance warning times near-future ground-based GW detectors can provide us.
-Ref.~\cite{Cannon:2011vi} considered this by focussing on developing computationally inexpensive methods to detect inspiral
+Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors and leave the task of reducing the latency to the experts.
+More specifically, we wish to find out how much early warning the GW detectors can provide us before the merger/GRB.
+Ref.~\cite{Cannon:2011vi} approached this from an algorithmic perspective by developing computationally inexpensive methods to detect inspiral
 signals in GW data to provide early-warning triggers \emph{before} the merger.
-We instead focus on the forecasting capabilities of the ground-based IFOs at their full design sensitivity.
-To this end, we consider the $\sim 2020$-design sensitivity of the Advanced-LIGO-Virgo (ALV) network composed of three IFOs and the $\sim 2030$-design
-sensitivity of Einstein Telescope.
-
+We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time lag
+between the merger and the detection time defined in terms of a certain threshold SNR.
+To this end, we consider the $\sim 2020$ ALV network composed of three L-shaped interferometers operating at their design sensitivities
+and Einstein Telescope of 2030s.
+Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distance
+to inspiralling BNSs and their sky-localization of these sources. Our work here is somewhat complementary in the sense that we are mostly concerned with
+advance warning times.
+
+We compute the advance warning times via the following procedure: 
+(${i}$) We start with a GW source presumed to be an inspiralling BNS at a certain luminosity distance. %$D$.
+(${ii}$) We determine the frequency at which the source enters a given interferometer's bandwidth. 
+In order to more faithfully represent a network such as ALV --- consisting of three separate interferometers which have different
+orientations and positions --- we employ root-mean-square averages over sky-position and polarization angles,
+and assign the interferometers angle-averaged sensitivities.
+%which reduce an individual interferometer's sensitivity to a particular source. 
+(${iii}$) We determine the detection time by computing the frequency at which the network's accumulated SNR for the BNS inspiral equals 15.
+($iv$) We define the advance warning time to be the remaining inspiral time to the merger from the instant of detection.
+We repeat this procedure for BNSs at luminosity distances varying from 50\,Mpc to 1\,Gpc with the smaller values intended for the ALV network and 
+the larger ones for Einstein Telescope.
 %KAGRA 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)
 
-Cite the BNS Living review many times \cite{Faber:2012rw}.
-
-Sec.~ blah blah, Sec.~ does so and so, results are presented in Sec.~
+Our computation is based on the leading-order Newtonian evolution of the quadrupole moment of a binary system 
+composed of two point masses in a quasi-circular orbit.
+We supplement this with results from post-Newtonian theory up to 3.5 post-Newtonian order \cite{Blanchet_LRR}.
+The strong-field dynamics of BNS evolution is a very complex and complicated problem requiring fully relativistic, magnetohydrodynamic codes 
+with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
+(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Kyutoku:2017voj, Zappa:2017xba} for the latest developments and references therein).
+Despite its simplicity, our leading-order treatment is more than sufficient to provide reliable estimations of advance warning times.
+We back this claim up with an extensive list of computations showing how much each of our approximations affects the inspiral time.
+Let us emphasize that this article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
+Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the basics.
+Be that as it may, even the experts might find our results motivating and exciting.
+
+We proceed as follows: Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
+Sec.~\ref{sec:IFO_response} IFO response
+
+Sec.~\ref{sec:idealizations} idealizations
 
@@
 %
-\subsection{Simplifications and idealizations used in evolving the inspiral}\label{sec:idealizations}
+\section{Simplifications and idealizations used in evolving the inspiral}\label{sec:idealizations}
 In this section, we justify our simplifications with brief computations.

### 2018-03-19 Paper/Manuscript.tex
Finished a very first draft.

@@
 \begin{abstract}
-We explore the intriguing possibility of employing future gravitational-wave interferometers to detect the inspiral of compact binaries early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
-We quantify the ability to predict a GRB by computing the time a canonical binary neutron star (BNS) system takes to inspiral from a certain threshold frequency to its final merger.
-We define this threshold frequency to be the gravitational-wave frequency at which the RMS-averaged strain due to the BNS system accumulates a signal-to-noise (SNR) ratio of 15.
-For our computation of advance warning times, we consider BNS systems at luminosity distances of (i) $D\lesssim200\,$Mpc in a three-interferometer network with Advance LIGO's design sensitivity and (ii) $D \lesssim 1000\,$Mpc in a similar network, but with the Einstein Telescope's B configuration
-sensitivity. We find in the case of that Advanced LIGO we may get a few minutes of warning time if we get lucky whereas the Einstein Telescope will provide us
-with warning times as long as a few hours.
-Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)
+We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
+We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from a its moment of detection to its final merger.
+We define the moment of detection to be given when the inteferometer network accumulates a signal-to-noise ratio of 15.
+%for the BNS inspiral.
+For our computations, %of advance warning times, 
+we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc in the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc in the Einstein Telescope's B and C configurations.
+In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
+On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours, more specifically, greater than an hour
+for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
+we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s using the C configuration of Einstein Telescope.
+We reapply our computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
+to be forecast by the same detector.
+%Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)
 
@@
 \section{Introduction}\label{Sec:Intro}
-The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \approx 90\%$ significance hence 6.95 overall.}
+The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \simeq 95\%$ significance hence 6.95 overall.}
 gravitational-wave merger events detected by the Advanced Ligo-Virgo network have firmly established gravitational-wave astronomy
@@
 
-Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors and leave the task of reducing the latency to the experts.
+Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors thus leave the task of reducing the latency to the experts.
 More specifically, we wish to find out how much early warning the GW detectors can provide us before the merger/GRB.
@@
 
-We proceed as follows: Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
-Sec.~\ref{sec:IFO_response} IFO response
-
-Sec.~\ref{sec:idealizations} idealizations
-
-We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital frequency $f_K$. 
+This article is organized as follows. Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
+Sec.~\ref{sec:IFO_response} details the interferometer response to GWs based on topology.
+Sec.~\ref{sec:idealizations} lists the various idealizations we employ to simplify our treatment and supplies justification for each.
+Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding GW data.
+Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020}, \ref{table:ET} 
+as well horizon distances and event rates in Table~\ref{table:horizon}.
+In Sec.~\ref{sec:BH_NS}, we reapply the above procedure to black hole - neutron star inspirals to see whether or not 
+future detectors can forecast a tidal disruption event, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
+
+We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
 Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
-We employ the $\simeq$ symbol for quantities which we can compute exactly, but list finite digits and $\approx$ for quantities whose values we know approximately.
-Overdots denote time derivative with respect to detector time, e.g., $\dot{E} =dE/dt$.
+We employ the $\simeq$ symbol for the numerical values of quantities with infinite decimal expansions which we usually truncate at four significant digits,
+e.g., $\pi \simeq 3.142$.
+The $\approx$ symbol is reserved for approximations, whereas $\sim$ denotes rather rough order-of-magnitude equalities, e.g., $\pi \sim \ord(1)$. %Kepler's third law: $f_K^2\sim r^{-3}$.
+Overdots denote time derivative with respect to detector-frame time, e.g., $\dot{E} =dE/dt$. Unless otherwise noted, we use standard SI units.
 
@@
 
-\section{GW170817 as a test of our model Advanced LIGO-Virgo network}\label{Sec:GW170817}
+\section{GW170817 as a test of our model Advanced LIGO-Virgo network}\label{sec:GW170817}
 On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system were detected by the Advanced LIGO-Virgo network.
@@
 Each RMS-averaged strain is accompanied by its shaded region ranging from an optimally oriented strain ($\tilde{H}_h$) to a sub-optimally oriented strain ($\tilde{H}_l$).
-These regions were first explained in Sec.~\ref{Sec:GW170817} and shown in Fig.~\ref{fig:figGW170817}.
+These regions were first explained in Sec.~\ref{sec:GW170817} and shown in Fig.~\ref{fig:figGW170817}.
 Recall that this is our way of representing the response of a three-IFO network to a single source, i.e., we map three different IFO responses due to a single source to a single IFO's response to three different sources differing in amplitudes as listed in Table~\ref{table:network_params}.
@@
 As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
-(this is roughly in line with LISA's timeline).
+(this is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}).
 It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
@@
 
-\section{Binary black hole neutron star systems}
+\section{Binary black hole neutron star systems}\label{sec:BH_NS}
 In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
@@
 $c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to leading order with
-$c_R >1 $. Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, we can roughly take the above condition to be
-%
-\be
-\f{m_2}{m_1} \gtrsim \left(\f{r}{r_1}\right)^3 \label{eq:TD_cond2}.
+$c_R >1 $. %Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, 
+We can roughly take the above condition to be
+%
+\be
+\f{M_\text{BH}}{M_\text{NS}} \gtrsim \left(\f{r}{R_\text{NS}}\right)^3 \label{eq:TD_cond2}.
 \ee
@@
 Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
-there could be 28.8 such mergers per year within ET-C's horizon distance. We must emphasize that this should be viewed
+there could be 28.8 such mergers per year within ET-C's horizon distance of $\approx 200\,$Mpc corresponding roughly to $T_\text{AW}\approx1\,$hour.
+We must emphasize that this should be viewed
 as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
-Therefore, we realistically expect ET-C to forecast $\sim \mathcal{O}(1)$ tidal disruption event per year.
-A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
-however, all of these come with rather large error bars {\bf CITE}.
+Theoretical studies indicate that $\lesssim 10\%$ stellar-mass BHs have masses $\lesssim 5 M_\odot$ \cite{Fryer:1999ht}.
+This seems to be supported at least by observations of galactic black holes \cite{Ozel:2010su}.
+Therefore, we realistically expect ET-C to forecast $\lesssim 3$ tidal disruption events per year.
+%A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
+%however, all of these come with rather large error bars.
 %and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
@@
 %\ee
+\section{Outlook}
+By constructing representative models of the near-future ground-based gravitational-wave interferometers, we investigated the possibility of
+forecasting gamma-ray burts resulting from the merger of two neutron stars.
+We showed that we do not expect the Advanced-LIGO-Virgo network to provide such a forecast in the 2020s unless we get extremely lucky
+and detect a BNS inspiral in our galaxy which is roughly a one-in-a-trillion shot (in years). %($\sim 1$ per trillion years lucky).
+However, the odds completely change in our favour with Einstein Telescope's B and especially C configurations, 
+the latter of which is expected to forecast $\gtrsim \ord(10^2)$ GRBs per year as we show in Table~\ref{table:horizon}. 
+The same configuration should also forecast up to three tidal disruption events per year in which a high-spin, low-stellar-mass
+black hole tidally tears apart its companion neutron star.
+The beginning of operation for the C configuration will roughly coincide with the launch of the LISA mission.
+Additionally, there are proposals to launch another space interferometer called DECIGO which will operate
+between $0.1$ and 10 Hz thus bridging the gap between LISA and the ground-based interferometers \cite{Sato:2009zzb, Kawamura:2006zz}.
+With the gravitational-wave sky virtually covered from $10^{-4}$ to $10^3\,$Hz, we will suffer from the 
+embarassment of the riches in the 2030s. In short, the future of gravitational and multi-messenger astronomy is bright.
+
+\acknowledgements 
+SA thanks Conor O'Toole for endless feedback and Niels Warburton for a careful reading of this article.
 

### 2018-03-19 Paper/Manuscript.tex
Added references to Intro

@@
 Though the first event of 14 September 2015 (GW150914 \cite{GW150914}) will always be the ``poster-child'' of this field,
-the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory {\bf cite}.
+the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory (\cite{Savchenko:2017ffs}, {\bf Svinkin, D., et al.
+2017, GCN, 21515; Savchenko, V., et al.
+2017, GRB
+Coordinates Network, 21507}).
 The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
 enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993 less than 11 hours after the merger, 
-first picked up by the One-Meter, Two Hemisphere team {\bf cite}.
+first picked up by the One-Meter, Two Hemisphere team \cite{Coulter:2017wya} {\bf Coulter, D. A., et al. 2017, GCN, 21529, 21567}.
 This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum still ongoing
@@
 %
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \includegraphics[height=9cm]{../Figures/GW170817_strains.pdf}
@@
  %
-  \begin{figure}[h!]
+  \begin{figure}[ht!]
  \framebox{\Longstack[l]{Pick $D$}}$\longrightarrow$\framebox{\Longstack[l]{Construct\\ $\tilde{H}_i(f)$}} 
@@
 %
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \includegraphics[width=\linewidth]{../Figures/ALigo_strains.pdf}
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \includegraphics[width=\linewidth]{../Figures/ET_strains_redshifted.pdf}
@@
 %
-\begin{figure}[h!]
+\begin{figure}[ht!]
 \includegraphics[width=\linewidth]{../Figures/Main_results.pdf}

### 2018-03-20 Paper/Manuscript.tex
abstract fix

@@
 We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
-We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from a its moment of detection to its final merger.
-We define the moment of detection to be given when the inteferometer network accumulates a signal-to-noise ratio of 15.
+We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger.
+We define the moment of detection to be the instant at which the inteferometer network accumulates a signal-to-noise ratio of 15.
 %for the BNS inspiral.
@@
 In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
-On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours, more specifically, greater than an hour
-for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
-we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s using the C configuration of Einstein Telescope.
-We reapply our computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
+On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours.  
+Taking one hour as a benchmark warning time, we obtain a corresponding horizon
+distance of roughly 600 Mpc for Einstein C.
+%, more specifically, greater than an hour
+%for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
+Using current BNS event rates within this horizon distance, we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s with the C configuration of Einstein Telescope.
+We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
 to be forecast by the same detector.

### 2018-03-21 Paper/Manuscript.tex
First read through of Abs+Intro, added few more refs.

@@
 Taking one hour as a benchmark warning time, we obtain a corresponding horizon
-distance of roughly 600 Mpc for Einstein C.
+distance of roughly 600 Mpc for the Einstein C configuration.
 %, more specifically, greater than an hour
 %for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
-Using current BNS event rates within this horizon distance, we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s with the C configuration of Einstein Telescope.
+Using current BNS event rates within this horizon distance, we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s. %with the C configuration of Einstein Telescope.
 We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
@@
 Though the first event of 14 September 2015 (GW150914 \cite{GW150914}) will always be the ``poster-child'' of this field,
-the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system with a prompt gamma-ray burst (GRB170817A) detected 1.7 seconds after the coalescence by the Fermi Gamma-ray Burst Monitor \cite{Fermi}{\bf FIX ME} and by the International Gamma-Ray Astrophysics Laboratory (\cite{Savchenko:2017ffs}, {\bf Svinkin, D., et al.
-2017, GCN, 21515; Savchenko, V., et al.
-2017, GRB
-Coordinates Network, 21507}).
+the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system 
+promptly followed, 1.7 seconds later, by a gamma-ray burst (GRB170817A) detected by the Fermi Gamma-ray Burst Monitor \cite{Fermi} and by the International Gamma-Ray Astrophysics Laboratory (\cite{Svinkin, Savchenko:2017ffs}.
 The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
-enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993 less than 11 hours after the merger, 
-first picked up by the One-Meter, Two Hemisphere team \cite{Coulter:2017wya} {\bf Coulter, D. A., et al. 2017, GCN, 21529, 21567}.
-This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum still ongoing
+enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993, 
+first picked up by the One-Meter, Two Hemisphere team less than 11 hours after the merger \cite{Coulter2017, Coulter:2017wya}.
+This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum which is still ongoing
 more than half a year after the initial GRB \cite{GBM:2017lvd}.
@@
 The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from $\sim 30\,$Hz to $\sim 2\,$kHz in 57 seconds
-executing $\sim 3000$ GW cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
+executing $\sim 3000$ gravitational wave cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
 The total mass of the system was inferred to be $2.74^{+0.04}_{-0.01} M_\odot$ with component masses in the range $1.17-1.60 M_\odot$ consistent
-with neutron stars.
-Moreover, both the GW and EM observations are consistent with a source luminosity distance of $\sim 40\,$Mpc
+with neutron stars (assuming low spin priors, see Sec.~\ref{sec:idealizations}).
+Moreover, both the gravitational wave (GW) and EM observations are consistent with a source luminosity distance of $\sim 40\,$Mpc
 and support the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
-which then caused the prompt short-hard gamma-ray burst (GRB170817A) in NGC4993 as first suggested by Ref.~\cite{Eichler:1989ve}.
-
-One week after GW170817, the ALV network was taken offline for upgrades for the third observation run (O3) 
+causing the prompt short-hard gamma-ray burst (GRB170817A) in NGC4993 as first suggested by Ref.~\cite{Eichler:1989ve}.
+
+A week after GW170817, the ALV network was taken offline for upgrades for the third observation run (O3) 
 scheduled to start in Autumn 2018 with roughly twice the sensitivity of O2.
@@
 Around this time, the construction of the first third-generation ground-based interferometer, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
-The US is currently considering a mid-2020s update called LIGO-Voyager \cite{LIGO_Voy} and a more ambitious 40\,km long interferometer dubbed The Cosmic Explorer \cite{CE}.
+Meanwhile, the US is currently considering a mid-2020s update to LIGO called Voyager \cite{LIGO_Voy} and the construction of a more ambitious 40\,km long interferometer dubbed The Cosmic Explorer \cite{CE}.
 All of these near-future improvements to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
@@
 In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd}.
-It then took an additional $\sim 10$ hours to locate the optical transient designated AT 2017gfo.
+It then took an additional $\sim 10$ hours to locate the optical transient. %designated AT 2017gfo.
 
@@
 Ref.~\cite{Cannon:2011vi} approached this from an algorithmic perspective by developing computationally inexpensive methods to detect inspiral
-signals in GW data to provide early-warning triggers \emph{before} the merger.
-We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time lag
-between the merger and the detection time defined in terms of a certain threshold SNR.
+signals in GW data to provide early-warning triggers \emph{before} the merger (also see Ref.~\cite{Knowles:2018hqq} for a very recent improvement to what is currently being
+used in the ALV pipeline).
+We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time difference
+between the merger and the instant of detection (detector trigger) defined in terms of a certain threshold signal-to-noise ratio.
 To this end, we consider the $\sim 2020$ ALV network composed of three L-shaped interferometers operating at their design sensitivities
 and Einstein Telescope of 2030s.
-Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distance
+Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distances
 to inspiralling BNSs and their sky-localization of these sources. Our work here is somewhat complementary in the sense that we are mostly concerned with
-advance warning times.
+how early the GW networks can detect the inspiral before the merger.
 
@@
 (${ii}$) We determine the frequency at which the source enters a given interferometer's bandwidth. 
-In order to more faithfully represent a network such as ALV --- consisting of three separate interferometers which have different
+%which reduce an individual interferometer's sensitivity to a particular source. 
+(${iii}$) We determine the detection time by computing the frequency at which the network's accumulated signal-to-noise ratio (SNR) for the BNS inspiral equals 15.
+($iv$) We define the advance warning time, $T_\text{AW}$, to be the remaining inspiral time to the merger from the instant of detection.
+We repeat this procedure for BNSs at luminosity distances varying from 50\,Mpc to 1\,Gpc with the smaller values intended for the ALV network and 
+the larger ones for Einstein Telescope.
+In order to more faithfully represent an interferometer network such as ALV --- consisting of three separate interferometers which have different
 orientations and positions --- we employ root-mean-square averages over sky-position and polarization angles,
 and assign the interferometers angle-averaged sensitivities.
-%which reduce an individual interferometer's sensitivity to a particular source. 
-(${iii}$) We determine the detection time by computing the frequency at which the network's accumulated SNR for the BNS inspiral equals 15.
-($iv$) We define the advance warning time to be the remaining inspiral time to the merger from the instant of detection.
-We repeat this procedure for BNSs at luminosity distances varying from 50\,Mpc to 1\,Gpc with the smaller values intended for the ALV network and 
-the larger ones for Einstein Telescope.
 %KAGRA 152Mpc range (K. Somiya, ET meeting at Birmingham, 2017)
 
-Our computation is based on the leading-order Newtonian evolution of the quadrupole moment of a binary system 
-composed of two point masses in a quasi-circular orbit.
-We supplement this with results from post-Newtonian theory up to 3.5 post-Newtonian order \cite{Blanchet_LRR}.
-The strong-field dynamics of BNS evolution is a very complex and complicated problem requiring fully relativistic, magnetohydrodynamic codes 
+Our computation for $T_\text{AW}$ is based on the Newtonian evolution of a binary system composed of two point masses in a quasi-circular Keplerian orbit. 
+The long-term dynamics is governed by radiation reaction of GW emission from the system due to the time variance of the quadrupole moment of the binary.
+We nonetheless supplement our Newtonian (leading-order) time evolution with results from post-Newtonian theory up to 3.5 post-Newtonian order \cite{Blanchet_LRR}.
+The evolution of a BNS system in the strong-field regime, where speeds $\gtrsim 0.1c$, is a very complex and complicated problem requiring fully relativistic, magnetohydrodynamic codes 
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
@@
 Despite its simplicity, our leading-order treatment is more than sufficient to provide reliable estimations of advance warning times.
-We back this claim up with an extensive list of computations showing how much each of our approximations affects the inspiral time.
+We support this claim in Sec.~\ref{sec:idealizations} with an extensive list of computations showing how much each of our approximations affects the inspiral time.
+
 Let us emphasize that this article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
-Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the basics.
+Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
 Be that as it may, even the experts might find our results motivating and exciting.
@@
 Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding GW data.
-Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020}, \ref{table:ET} 
-as well horizon distances and event rates in Table~\ref{table:horizon}.
+Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020}, \ref{table:ET}; 
+and as horizon distances and event rates in Table~\ref{table:horizon}.
 In Sec.~\ref{sec:BH_NS}, we reapply the above procedure to black hole - neutron star inspirals to see whether or not 
@@
 
-We reserve the symbol $f$ to denote the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
-Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
-We employ the $\simeq$ symbol for the numerical values of quantities with infinite decimal expansions which we usually truncate at four significant digits,
+Throughout the text, $f$ denotes the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
+%Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
+We employ the $\simeq$ symbol when displaying the numerical values of quantities %with infinite decimal expansions 
+which we usually truncate at four significant digits,
 e.g., $\pi \simeq 3.142$.
@@
  Hence, $M_\text{BH}$ must also be minimized. Once again, there is a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models.
- Current consensus for this lower bound yields $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua}.
+ Current consensus for this lower bound yields $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
  \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.

### 2018-03-22 Paper/Manuscript.tex
Continuing with revisions, + few more refs.

@@
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
-(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Kyutoku:2017voj, Zappa:2017xba} for the latest developments and references therein).
+(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm} for the latest developments and references therein).
 Despite its simplicity, our leading-order treatment is more than sufficient to provide reliable estimations of advance warning times.
@@
 We employ the $\simeq$ symbol when displaying the numerical values of quantities %with infinite decimal expansions 
-which we usually truncate at four significant digits,
-e.g., $\pi \simeq 3.142$.
-The $\approx$ symbol is reserved for approximations, whereas $\sim$ denotes rather rough order-of-magnitude equalities, e.g., $\pi \sim \ord(1)$. %Kepler's third law: $f_K^2\sim r^{-3}$.
-Overdots denote time derivative with respect to detector-frame time, e.g., $\dot{E} =dE/dt$. Unless otherwise noted, we use standard SI units.
+which we usually truncate at four significant digits.
+The $\approx$ symbol is reserved for approximations whereas $\sim$ denotes rough, order-of-magnitude equalities,
+e.g., $\pi \simeq 3.142$, $\pi \approx 3$, $\pi \sim \ord(1)$. %Kepler's third law: $f_K^2\sim r^{-3}$.
+Overdots denote time derivative with respect to detector-frame time, e.g., $\dot{E} =dE/dt$, and $\propto$ denotes proportionalities. 
+Unless otherwise noted, we use standard SI units.
 
@@
 \subsection{Newtonian evolution of BNS}
-For us, the starting point for the evolution of a binary under the emission of GWs is the expression for the power generated given by 
+For us, the starting point for the evolution of a binary under gravitational radiation reaction
+%the emission of GWs 
+is the expression for the power emitted in GWs given by 
 %for the generated by the time-variance of the mass quadrupole moment
@@
 %
-This is the celebrated Einstein quadrupole formula. 
+This is the celebrated Einstein quadrupole formula \cite{1918SPAW}. 
 Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
@@
 \be
-\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}\, r^4 \Omega^6\label{eq:Edot}
+\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}\, r^4 \Omega^6\label{eq:Edot},
 \ee
@@
 referred to as the dimensionless inverse separation $x$.
-As $x\sim v^2/c^2$, it is used to keep track of post-Newtonian orders and we can from in Eq.~(\ref{eq:Edot2}) that $\dot{E}\sim x^5$. 
+As $x\sim v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from in Eq.~(\ref{eq:Edot2}) that $\dot{E}\sim x^5$. 
 %hence the common statement in the literature saying that gravitational radiation starts
 
-The energy generated by the acceleration of the masses is radiated away in GWs,
-which makes the total energy of the binary more negative, i.e., the orbit becomes more bound. 
+The energy radiated away in GWs decreases the total energy of the binary thus making the orbit more bound. 
 Since the total energy is given by
@@
 \be
-E_b = -\frac{G m_1 m_2}{2r}\, . \label{eq:binding_energy1}
-\ee
-%
-$\dot{E}_b < 0$ implies the orbital radius must decrease in time. 
-Using Kepler's third law, $ \Omega^2 = G M r^{-3}$ and Eq.~(\ref{eq:chirp_mass}) we obtain
-%
-\be
-E_b = -\left(\f{G^2 M_c^5 \omega^2}{32}\right)^{1/3}, \label{eq:binding_energy2}
+E_b = -\frac{G m_1 m_2}{2r}\,  \label{eq:binding_energy1}
+\ee
+%
+we have $\dot{E}_b \propto \dot{r}/r$; hence $\dot{E}_b < 0$ implies $\dot{r}<0$.
+Using Kepler's third law, i.e., $ \Omega^2 = G M r^{-3}$ and Eq.~(\ref{eq:chirp_mass}) we obtain
+%
+\be
+E_b = -\left(\f{G^2 M_c^5 \omega^2}{32}\right)^{1/3}\, . \label{eq:binding_energy2}
 \ee
@@
 \be
-\tau_\text{insp}(f) \simeq 2.18\,\text{s} \, \left(\f{1.21 M_\odot}{M_c}\right)^{5/3}\,\left(\f{100\,\text{Hz}}{f}\right)^{8/3}, \label{eq:tau_insp2}
-\ee
-%
-where $1.21 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$.
-
-We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T(t)$ varies over a much larger time scale than T itself
+\tau_\text{insp}(f) \simeq 16.72\,\text{minutes} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\left(\f{10\,\text{Hz}}{f}\right)^{8/3}, \label{eq:tau_insp2}
+\ee
+%
+where $\simeq 1.219 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$.
+
+We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T_K(t)$ varies over a much larger time scale than $T_K$ itself
 we can write
@@
 \be
-\mathcal{N}_\text{cyc}(f) = \int_f^{f_\text{max}} \f{f}{\dot{f}}\, df =\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right] \label{eq:Ncyc1}
+\mathcal{N}_\text{cyc}(f) = \int_f^{f_\text{max}} \f{f'}{\dot{f'}}\, df' =\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right] \label{eq:Ncyc1}
 \ee
@@
 %
-We will see in Sec.~\ref{sec:idealizations} that $f_\text{ISCO} \sim \mathcal{O}(1000)\,$Hz for a system with $M\approx 2 M_\odot$.
-Moreover, the frequencies of interest for our advance warning time estimations will be $\lesssim \mathcal{O}(10)\,$Hz
+We will see in Sec.~\ref{sec:idealizations} that $f_\text{ISCO} \sim 1000\,$Hz for a system with $M\approx 2 M_\odot$. 
+On the other hand, the frequencies of interest for our advance warning time estimations will be $\lesssim 10\,$Hz
 meaning that $f^{-5/3} \gg f_\text{ISCO}^{-5/3}$. Therefore, at the leading (Newtonian) order, the number of GW cycles can be approximated by
@@
 \be
-\mathcal{N}_\text{cyc}(f) \simeq \f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\, f^{-5/3} \, . \label{eq:Ncyc2}
+\mathcal{N}_\text{cyc}(f) \approx \f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\, f^{-5/3} \, . \label{eq:Ncyc2}
 \ee
@@
 \be
-\mathcal{N}_\text{cyc}(f)\simeq 1.6\times 10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}\,\left(\f{1.21 M_\odot}{M_c}\right)^{5/3}\label{eq:Ncyc3}\, .
+\mathcal{N}_\text{cyc}(f)\approx 1.605\times 10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\label{eq:Ncyc3}\, .
 \ee
@@
 \be
-\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 9.829\times 10^6\,\text{yrs}\, \left(\f{T}{1\,\text{hr}}\right)^{8/3} \left(\f{M_\odot}{M}\right)^{2/3}\,\left(\f{M_\odot}{\mu}\right) \label{eq:tau_of_r}.
+\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 20.37\,\text{hours}\, \left(\f{T_K}{1\,\text{s}}\right)^{8/3} \left(\f{2.8M_\odot}{M}\right)^{2/3}\,\left(\f{0.7M_\odot}{\mu}\right) \label{eq:tau_of_r}.
 \ee
@@
 Let us now turn our attention to the GWs generated by the inspiral.
-The GWs themselves actually are tensor distortions $h_{\mu\nu}$ of the flat Minkowski
-spacetime propagating at the speed of light.
-In more technical terms, they satisfy $\Box h_{\mu\nu} = 0$, i.e., the flat spacetime sourceless wave equation
-meaning that we are considering the solutions far from the GW source, in the so-called wave zone defined by the condition $ c/f \ll D$.
-In a suitable gauge, such as the commonly used TT (transverse-traceless) gauge, it can be shown that
-there exist only two physical degrees of freedom which manifest themselves
-as two independent polarization amplitudes $h_+$ and $h_\times$. %when interacting with masses away from the source.
-For a circular binary at a distance $D$ these states read
+These are actually tensorial perturbations of flat (Minkowski) spacetime propagating at the speed of light.
+In the so-called wave zone, defined by the condition $ c/f \ll D$, where $D$ is the distance to the GW source, 
+these tensor modes satisfy the flat spacetime sourceless wave equation $\Box\bar{h}_{\mu\nu} = 0$.
+%meaning that we are considering the solutions far from the GW source, 
+In a suitable gauge, such as the commonly used transverse-traceless gauge, 
+it can be shown that there exist only two physical degrees of freedom which manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$.
+%when interacting with masses away from the source.
+For a binary in a circular orbit, these states read
 %
@@
 $\iota=\cos^{-1}(\mathbf{\hat{n}}\cdot{\mathbf{\hat{L}}}) $ is the inclination angle between the line of sight unit vector $\mathbf{\hat{n}} $ and the orbital angular momentum unit vector $\mathbf{\hat{L}}$.
-E.g., for an orbit seen edge on, $\iota = \pi/2$ which is actually the case of a purely plus-polarized wave, $h_\times=\cos(\pi/2)=0$.
+For an orbit seen edge on, $\iota = \pi/2$ giving $h_\times=0$, i.e,  a purely plus-polarized wave.
 When $\iota=0$ the orbit is seen face-on and we have a circularly-polarized wave: $\langle h_+ \rangle = \langle h_\times\rangle$ where $\langle \ldots \rangle$
@@
 Higher-order contributions can be added in terms a post-Newtonian series which make up $\lesssim 2\%$ of the total phase.
-Although we will include contributions up to and including 2PN to obtain the results of Sec.~\ref{sec:results}, we will not explicitly show these expressions 
-which can be found in Ref.~\cite{Blanchet_LRR}.
+Although we will include contributions up to and including 3.5PN to obtain the results of Sec.~\ref{sec:results}, 
+we do not explicitly show these expressions, but they can be found in Ref.~\cite{Blanchet_LRR}.
 
@@
 \subsection{LIGO-Virgo configuration: L-shaped topology}\label{sec:LIGO_topo}
-We start by first considering the L-shaped interferometer topology dating back to Michelson.
+We start by first considering the L-shaped interferometer topology dating back to Michelson \cite{Michelson:1887zz}.
 Although the GWs are described by propagating tensor modes, an interferometer (IFO) can only measure a scalar quantity
-known as the response function (or GW strain)
-which is a linear combination of the polarizations given by
+known as the response function (or GW strain) which is a linear combination of the polarizations given by
 %
@@
 %
-We can't apriori know $\theta, \phi,\psi$. However, we can extract their values with some limited precision over the course of an inspiral (preferably of BNS) 
-emitting GWs which sweep across the detection band of more than one interferometer over thousands of cycles. This was indeed the case of GW170817
-with a source sky localization of 28\,deg$^2$ using data from three inteferometers \cite{GW170817}. 
-For our estimations, we will use suitable averages of these angles.
+We can't apriori know $\theta, \phi,\psi$, however, we can extract their values with some limited precision over the course of an inspiral.
+The longer the inspiral stays in the detector bandwidth, the better we can estimate these angles.
+%Thus, BNS inspirals which would sweep across the detection band over thousands of cycles are preferable. 
+In the the case of GW170817 which swept the ALV network over roughly 3000 GW cycles, 
+the source sky localization was 28\,deg$^2$ using data from three IFOs \cite{GW170817}. 
+For our estimations, we employ suitable averages of these angles as explained below.
 For details on how to obtain Eqs.~(\ref{eq:F_plus}, \ref{eq:F_cross}) see, e.g., Sec.~4.2.1 of Ref.~\cite{SchutzLRR}.
 
-To compute the advance warning times we will need to know how ``loud'' the binaries become as they sweep across the interferometers' band.
-This is achieved by computing the signal-to-noise ratio (SNR) of the GWs in the detectors' data stream.
-This is done in the frequency domain so we need the Fourier transforms of the time-domain strains of Eqs.~(\ref{eq:hplus_TD}) and (\ref{eq:hcross_TD})
+To compute the advance warning times we will need to know how ``loud'' the binaries become as they sweep across the IFO's detection bandwidth.
+This is given by the signal-to-noise ratio (SNR) of the GWs in the detectors' data stream.
+The SNR is computed in the frequency domain so we Fourier-transform the time-domain strains of Eqs.~(\ref{eq:hplus_TD}) and (\ref{eq:hcross_TD}) to obtain
 %
@@
 
-The detection criterion we will employ here is quantified in terms of the optimal signal-to-noise ratio (SNR) defined by
+The detection criterion we will employ here is quantified in terms of the optimal signal-to-noise ratio SNR defined by
 %%
@@
 where $\sqrt{S_n(f)}$ is the {\it amplitude spectral density} (ASD) [also called spectral strain sensitivity] of the detector.
-It is usually this quantity that is shown in a typical interferometer strain sensitivity plot with the characteristic strain, $\tilde{h}_c(f)\equiv2\tilde{h}(f)\sqrt{f}$, 
+It is usually this quantity that is shown in a typical interferometer strain sensitivity plot with the characteristic strain, $\tilde{H}_c(f)\equiv|2\tilde{h}(f)\sqrt{f}|$, 
 due to various GW sources overlaid for comparison. 
@@
 %ASDs are given by $2\tilde{h}(f)\sqrt{f}$. This particular combination is called the characteristic strain. 
-We will show such plots in Sec.~\ref{sec:results}.
+We will show such plots in Secs.~\ref{sec:GW170817} and \ref{sec:results}.
 
@@
 %\langle g(\iota) \rangle = 
-\f{1}{2} \int_0^\pi d\iota\sin\iota\left[\left(\f{1+\cos^2\iota}{2}\right)^2+\cos^2\iota\right] = \f{4}{5} .\label{eq:inc_ang_av}
+\f{1}{2} \int_{-1}^1 d(\cos\iota)\left[\left(\f{1+\cos^2\iota}{2}\right)^2+\cos^2\iota\right] = \f{4}{5} .\label{eq:inc_ang_av}
 \ee
@@
 Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
-an \emph{model network} of three detectors ($N=3$), where one interferometer is near-optimally oriented/positioned thus it is at $2\sigma$ above the average.
-The second IFO operates at the RMS average; thus its sensitivity is suppressed by a factor $2/5$ compared with $\langle|Q|^2\rangle =1$ case.
-It remains to assign a quality factor for the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
-but it would be pointless to simply set its $\langle|Q|^2\rangle$ equal to zero. We therefore somewhat arbitrarily set $\psi=0,\iota=0$
+a \emph{model network} of three IFOs ($N=3$), where one is near-optimally oriented/positioned thus it is at $2\sigma$ above the average.
+The second IFO operates at the RMS average; thus its sensitivity is suppressed by a factor $2/5$ compared with the optimal $Q =1$ case.
+It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
+but it would be pointless to simply set $Q=0$. We therefore somewhat arbitrarily set $\psi=0,\iota=0$
 and introduce the following $\theta,\phi$-only averages
@@
 
-Therefore, to represent our multi-interferometer network, we introduce % the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
+To represent our model three-IFO network, we introduce % the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
 %%
@@
 %%
-for each interferometer, where
+for each IFO labelled by $i$, where
 %%
@@
 %
-and the $\tilde{A}_i =A\langle|Q|^2\rangle^{1/2}_i $ are given in Table~\ref{table:network_params}.
+and $\tilde{A}_i =A\langle|Q|^2\rangle^{1/2}_i $ are given in Table~\ref{table:network_params}.
 %for $i=1,2,3$.
@@
 %
-We arbitrarily make the following assignments for our network: $h=1, m=2, l=3$ representing high, medium, low strains/SNRs, respectively. 
-We summarize our network in the following Table~\ref{table:network_params}.
+We arbitrarily make the following assignments for our network: $h=1, m=2, l=3$ representing high, medium, low strain sensitivity, respectively. 
+We summarize our network in the following table.
 %%
@@
  \hline
- 1 & high ($h$) &  A & $A h_0\, f^{-7/6}$ \T\\
+ 1 & high ($h$) &  $\tfrac{4}{5}A$ & $\tfrac{4}{5}A h_0\, f^{-7/6}$ \T\\
  2 & medium ($m$) & $\tfrac{2}{5}A$ & $ \tfrac{2}{5}A h_0 \, f^{-7/6}$\B\T \\
@@
 Our model for the Advanced-LIGO-Virgo network ca. 2020. %of three L-shaped interferometers (IFOs). 
-Column four lists the magnitude of the strain for each IFO via Eq.~(\ref{eq:Hi_s}).
+Column four lists the magnitude of the frequency-domain strain at each IFO via Eq.~(\ref{eq:Hi_s}).
 ``Configuration'' describes how ideally oriented/positioned an IFO is with respect to a compact binary source. 
@@
 \begin{align}
-\rho_\text{tot} &= \sqrt{\rho^2_h+\rho^2_m+\rho^2_l} \label{eq:SNR_total_3IFOs} .
+\rho_\text{tot} &= \sqrt{\rho^2_h+\rho^2_m+\rho^2_l} \label{eq:SNR_total_3IFOs} 
 %	      &= 2A h_0 \sqrt{1+\tfrac{2}{5}+\tfrac{4}{25}} \left[\int_0^{f_\text{ISCO}} df\, \f{f^{-7/3}}{S_\text{noise}(f)}\right]^{1/2}\nn\\
@@
 %%
+with $\rho_h, \rho_m,\rho_l$ given by Eq.~(\ref{eq:SNR_i}) and Table~\ref{table:network_params}.
 %Although we made several simplifying assumptions to obtain $\rho_\text{tot}$, these should not affect our total SNR estimation too much.
@@
 %for these.
-We will start Sec.~\ref{sec:results} by testing our network with GW170817 whose signal got picked up by the LIGO detectors around $f=30$\,Hz.
-So we will change the lower limit of the integral in Eq.~(\ref{eq:SNR_total_3IFOs}) from $0$ to $30$.
-For our advance warning times we will further use separate initial frequencies for each inteferometer as we will explain in Sec.~\ref{sec:results}.
+%
+%In Sec.~\ref{sec:GW170817} we test our model network with GW170817 whose signal got picked up by the LIGO detectors around $f=30$\,Hz.
+%To do so we will change the lower limit of the integral in Eq.~(\ref{eq:SNR_total_3IFOs}) from $0$ to $30$.
+%For our advance warning times we will further use separate initial frequencies for each inteferometer as we will explain in Sec.~\ref{sec:results}.
 

### 2018-03-23 Paper/Manuscript.tex
mods

@@
 
-To represent our model three-IFO network, we introduce % the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
+To represent our model three-IFO network, we introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
 %%
@@
 %
-We can now write the total SNR for our network
+We can now write the total SNR for our three L-IFO network
 %%
@@
 \subsection{Einstein Telescope configuration: triangular topology}\label{sec:ET_topo}
-Current design of Einstein Telescope is based on a [equilateral] triangular configuration with 10\,km armlengths \cite{ET_doc}.
+Current design of Einstein Telescope (ET) is based on a [equilateral] triangular configuration with 10\,km armlengths \cite{ET_doc}.
 Within this equilateral triangle, ET will consist of three V-shaped cryogenic interferometers housed underground to
@@
 hence ET will have no blind spots \cite{Regimbau:2012ir}.
-However, the $60^\circ$ arm separation reduces the strain of a V-shaped interferometer by a factor of $\sin 60^\circ=\sqrt{3}/2$ compared
-to an L-shaped interferometer. So for a single V-IFO the antenna patterns of (\ref{eq:F_plus}, \ref{eq:F_cross}) become
+However, the $60^\circ$ arm separation reduces the strain sensitivity of a V-shaped interferometer by a factor of $\sin 60^\circ=\sqrt{3}/2$ compared
+to an L-shaped interferometer with the same armlength. So for a single V-IFO the antenna patterns of (\ref{eq:F_plus}, \ref{eq:F_cross}) become
 %
@@
 where the superscript $1$ labels one of the three V's of the triangle.
-Since the other two V IFOs lie in the same plane as the first one, their antenna patterns can be obtained simply by rotating in the azimuthal
+Since the other two V-IFOs lie in the same plane as the first one, their antenna patterns can be obtained simply by rotating in the azimuthal
 direction by $120^\circ, 240^\circ$, respectively
@@
 %
-From this, we immediately have that the RMS average is given by $\langle F_\bigtriangleup\rangle =3/\sqrt{10}$ and the minium value is $F_\bigtriangleup(\pi/2)=3/\sqrt{32}$;
+From this, we immediately have that the RMS average is given by $\langle F^2_\bigtriangleup\rangle^{1/2} =3/\sqrt{10}$ and the minium value is $F_\bigtriangleup(\pi/2)=3/\sqrt{32}$;
 %As $F^2 > 0$ for all $\theta$ with its RMS average $\sqrt{2/5}\simeq 63.2\%$ of optimal $F$ and its
@@
 \begin{align}
-\rho^2_{\text{tot},\bigtriangleup} & = \sum_{A=1}^3 \rho_A^2 \nn \\
- & =  \f{5}{6}\, \pi^{-4/3} \f{c^2}{D^2}\left(\f{G M_c}{c^3}\right)^{5/3}|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \, ,\label{eq:ET_SNRsq}
+\rho^2_{\text{tot},\bigtriangleup} & = \sum_{A=1}^3 \rho_A^2 \nn \\ % \f{c^2}{D^2}\left(\f{G M_c}{c^3}\right)^{5/3}
+ & =  \f{5}{6}\, \pi^{-4/3} h_0^2\,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \, ,\label{eq:ET_SNRsq}
 \end{align}
@@
 %
-which is $5/2$ times higher than a single L-shaped IFO's RMS average of 4/25 [cf. Eq.~(\ref{eq:RMS_th_ph_ps_iota})].
-
-As we can not know the source sky position or orientation we will use the RMS-averaged SNR for our computations %(\ref{eq:ET_SNRsq})
-%
-\be
-\rho_{\text{tot},\bigtriangleup} = \f{36}{25}A^2 h_0^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \label{eq:ET_SNR},
+which is larger than a single L-shaped IFO's RMS average of 4/25 given in Eq.~(\ref{eq:RMS_th_ph_ps_iota}).
+
+As we can not a priori know the source sky position or orientation we will model the response of ET using the RMS-averaged SNR %(\ref{eq:ET_SNRsq})
+%
+\be
+\rho_{\text{tot},\bigtriangleup} = \f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \label{eq:ET_SNR},
 \ee
 where $h_0$ is given by Eq.~(\ref{eq:h0}) and $A=\pi^{-2/3}\sqrt{5/24}$ as before. % from Sec.\ref{sec:LIGO_topo}. 
-Accordingly, we define an RMS-averaged frequency-domain
-strain
+Accordingly, we define an RMS-averaged frequency-domain strain
 %
 \begin{align}
-\tilde{H}_\bigtriangleup(f, D)&\equiv A\,  \bar{Q}_\bigtriangleup\, h_0 f^{-7/6} \nn \\
+\tilde{H}_\bigtriangleup(f)&\equiv A\,  \bar{Q}_\bigtriangleup\, h_0 f^{-7/6} \nn \\
    & = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} f^{-7/6}. \label{eq:H_delta}
@@
 %
-It is this strain that we will use as a typical ET source; thus in this sense,
-$\tilde{H}_\bigtriangleup(f,D)$ is like the $\tilde{H}_i(f)$ of Table~\ref{table:network_params}.
-But whereas in the case of a three L-IFO network we represented the detector response due to a single source in terms of three different
-values $\tilde{H}_i(f)$, for ET we will only consider $\tilde{H}_\bigtriangleup(f)$ as we have already angle-averaged over all three V-IFOs antenna patterns.
+This is ET's sky-averaged response to a BNS inspiral at luminosity distance $D$ and chirp mass $M_c$.
+%It is this strain that we use as a typical ET BNS source; 
+Thus, $\tilde{H}_\bigtriangleup(f)$ is like the $\tilde{H}_i(f)$ of Table~\ref{table:network_params},
+but different in that  $\tilde{H}_\bigtriangleup(f)$ represents the total response of the entire three V-IFO network whereas $\tilde{H}_i(f)$
+is the response of the $i^\text{th}$ L-IFO.
+%whereas in the case of a three L-IFO network we represented the detector response due to a single source in terms of three different
+%values $\tilde{H}_i(f)$, for ET we will only consider $\tilde{H}_\bigtriangleup(f)$ as we have already angle-averaged over all three V-IFOs antenna patterns.
 %$\tilde{H}_\bigtriangleup(f)$, as given by Eq.~(\ref{eq:H_delta}), depends only on the luminosity distance and the chirp mass.
-In Sec.~\ref{Sec:ETB} we will consider BNS systems inspiralling at varying luminosity distances as typical sources for ET.
-To compute the resulting SNRs, we will slightly modify Eq.~(\ref{eq:ET_SNR}) and use $\sqrt{S_n(f)}$ for the B and C configurations of ET.
-
-Before we present our results, we list the various idealizations/simplifications that we adopt to simplify our computations.
+
+In Sec.~\ref{sec:results} we will consider BNS systems inspiralling at varying luminosity distances as typical sources for the ALV and ET networks.
+To compute the resulting SNRs, we will slightly modify the integrals in Eqs.~(\ref{eq:SNR_i}, \ref{eq:ET_SNR}) and 
+use design sensitivities of A-LIGO and ET's B and C configurations for $\sqrt{S_n(f)}$.
+Before we present our results, we list the various idealizations that we have adopted to simplify our computations.
 For each idealization we present an estimated error. %that propa

### 2018-03-30 Paper/Manuscript.tex
Updates during Cotswold weekend

@@
 \begin{abstract}
-We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert the electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
+We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
 We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger.
@@
 In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
-On the other hand, we demonstrate that Einstein Telescope will provide us with warning times as long as a few hours.  
+On the other hand, Einstein Telescope will provide us with advance warning times up to five hours.  
 Taking one hour as a benchmark warning time, we obtain a corresponding horizon
-distance of roughly 600 Mpc for the Einstein C configuration.
+distance of roughly 600 Mpc for the Einstein Telescope C configuration.
 %, more specifically, greater than an hour
 %for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
-Using current BNS event rates within this horizon distance, we show that we expect to forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s. %with the C configuration of Einstein Telescope.
+Using current BNS event rates within this horizon distance, we show that this translates to forecasts of $\gtrsim \ord(10^2)$ GRBs in the 2030s.
+%with Einstein C.
+%with the C configuration of Einstein Telescope.
 We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
@@
 the icing on the cake was the 17 August 2017 (GW170817 \cite{GW170817}) event involving the inspiral and merger of a binary neutron star system 
-promptly followed, 1.7 seconds later, by a gamma-ray burst (GRB170817A) detected by the Fermi Gamma-ray Burst Monitor \cite{Fermi} and by the International Gamma-Ray Astrophysics Laboratory (\cite{Svinkin, Savchenko:2017ffs}.
+promptly followed, 1.7 seconds later, by a gamma-ray burst (GRB170817A) detected by the Fermi Gamma-ray Burst Monitor \cite{Fermi} and by the International Gamma-Ray Astrophysics Laboratory \cite{Svinkin, Savchenko:2017ffs}.
 The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
@@
 In addition, the Japanese cryogenic interferometer KAGRA (\cite{KAGRA, KAGRA2}) will start its test runs in 2018-2019 and reach design sensitivity circa 2021-2022 \cite{Akutsu:2017thy, Aasi:2013wya}.
-By 2025, LIGO-India detector will join the global interferometer network hence improving both the overall sensitivity and the sky-localization capabilities \cite{Aasi:2013wya}.
+By 2025, LIGO-India detector will join the global interferometer network hence improving both the overall sensitivity and the sky-localization capabilities of the interferometer network \cite{Aasi:2013wya}.
 Around this time, the construction of the first third-generation ground-based interferometer, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
@@
 
-Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors thus leave the task of reducing the latency to the experts.
+Here, we are interested  in exploring the predictive power of near-future ground-based GW detectors. 
+%thus leave the task of reducing the latency to the experts.
 More specifically, we wish to find out how much early warning the GW detectors can provide us before the merger/GRB.
@@
 between the merger and the instant of detection (detector trigger) defined in terms of a certain threshold signal-to-noise ratio.
-To this end, we consider the $\sim 2020$ ALV network composed of three L-shaped interferometers operating at their design sensitivities
-and Einstein Telescope of 2030s.
+To this end, we consider the ALV network of 2020s composed of three L-shaped interferometers operating at their design sensitivities
+and Einstein Telescope of 2030s made up of triangular interferometers.
 Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distances
@@
 Our computation for $T_\text{AW}$ is based on the Newtonian evolution of a binary system composed of two point masses in a quasi-circular Keplerian orbit. 
-The long-term dynamics is governed by radiation reaction of GW emission from the system due to the time variance of the quadrupole moment of the binary.
-We nonetheless supplement our Newtonian (leading-order) time evolution with results from post-Newtonian theory up to 3.5 post-Newtonian order \cite{Blanchet_LRR}.
+The long-term dynamics is governed by the radiation reaction of 
+the GW emission from the system due to the time variance of the quadrupole moment of the binary.
+Though the Newtonian (leading-order) evolution is better than $ 95\%$ accurate
+we nonetheless supplement it with results from post-Newtonian theory up to 3.5 post-Newtonian order \cite{Blanchet_LRR}.
 The evolution of a BNS system in the strong-field regime, where speeds $\gtrsim 0.1c$, is a very complex and complicated problem requiring fully relativistic, magnetohydrodynamic codes 
@@
 (see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm} for the latest developments and references therein).
-Despite its simplicity, our leading-order treatment is more than sufficient to provide reliable estimations of advance warning times.
+Despite its simplicity, our quadrupole radiation driven adiabatic
+evolution is more than sufficient to provide reliable estimations of advance warning times.
 We support this claim in Sec.~\ref{sec:idealizations} with an extensive list of computations showing how much each of our approximations affects the inspiral time.
@@
 and as horizon distances and event rates in Table~\ref{table:horizon}.
-In Sec.~\ref{sec:BH_NS}, we reapply the above procedure to black hole - neutron star inspirals to see whether or not 
+In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of black hole - neutron star inspirals to see whether or not 
 future detectors can forecast a tidal disruption event, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
@@
 
-\section{Binary systems composed of neutron stars}\label{sec:BNS_inspiral}
-\subsection{Newtonian evolution of BNS}
+\section{Binary neutron star inspirals}\label{sec:BNS_inspiral}
+\subsection{Newtonian evolution}
 For us, the starting point for the evolution of a binary under gravitational radiation reaction
@@
 Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
-is the dominant contribution to the power generated %in gravitational radiation
+is the dominant contribution to the power emitted %in gravitational radiation
 by a system with changing mass moments.
@@
 %
-where, recall $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs. 
+where $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs. 
 The quantity in parantheses in Eq.~(\ref{eq:Edot2}) is ubiquitous in post-Newtonian theory and is
@@
 
-The energy radiated away in GWs decreases the total energy of the binary thus making the orbit more bound. 
-Since the total energy is given by
+The emission of power in GWs decreases the total energy of the binary thus making the orbit more bound. 
+The total (binding) energy of the binary is given by
 %
@@
 %
-we have $\dot{E}_b \propto \dot{r}/r$; hence $\dot{E}_b < 0$ implies $\dot{r}<0$.
-Using Kepler's third law, i.e., $ \Omega^2 = G M r^{-3}$ and Eq.~(\ref{eq:chirp_mass}) we obtain
+giving $\dot{E}_b \propto \dot{r}/r$; hence $\dot{E}_b < 0$ implies $\dot{r}<0$, i.e, the orbital separation decreases in time.
+Using Kepler's third law, $ \Omega^2 = G M r^{-3}$, and Eq.~(\ref{eq:chirp_mass}) we obtain
 %
@@
 %
-where $\simeq 1.219 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$.
-
-We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T_K(t)$ varies over a much larger time scale than $T_K$ itself
+where $1.219 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$.
+
+We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T_K(t)$ varies over a time scale much larger than $T_K$ itself
 we can write
@@
 \be
-\mathcal{N}_\text{cyc}(f) \approx \f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\, f^{-5/3} \, . \label{eq:Ncyc2}
-\ee
-%
-Restoring some familiar numbers in this expression yields
-%
+\mathcal{N}_\text{cyc}(f) \approx \f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\, f^{-5/3} \,  \label{eq:Ncyc2}
+\ee
+%
+%Restoring some familiar numbers in this expression yields
+%
+which can be rewritten as
 \be
@@
 \be
-\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 20.37\,\text{hours}\, \left(\f{T_K}{1\,\text{s}}\right)^{8/3} \left(\f{2.8M_\odot}{M}\right)^{2/3}\,\left(\f{0.7M_\odot}{\mu}\right) \label{eq:tau_of_r}.
-\ee
-%
+\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 20.37\,\text{hours}\, \left(\f{T_K}{1\,\text{s}}\right)^{8/3} \left(\f{2.8M_\odot}{M}\right)^{2/3}\,\left(\f{0.7M_\odot}{\mu}\right) \label{eq:tau_of_r},
+\ee
+%
+where the seemingly arbitrary $0.7M_\odot$ is the value of $\mu$ for $m_1=m_2=1.4M_\odot$.
 
 Let us now turn our attention to the GWs generated by the inspiral.
-These are actually tensorial perturbations of flat (Minkowski) spacetime propagating at the speed of light.
+These are tensorial perturbations propagating at the speed of light in flat (Minkowski) spacetime.
 In the so-called wave zone, defined by the condition $ c/f \ll D$, where $D$ is the distance to the GW source, 
-these tensor modes satisfy the flat spacetime sourceless wave equation $\Box\bar{h}_{\mu\nu} = 0$.
+these tensor modes satisfy the flat spacetime sourceless wave equation. %$\Box\bar{h}_{\mu\nu} = 0$.
 %meaning that we are considering the solutions far from the GW source, 
@@
 \ee
-is the characteristic strain.
+is the characteristic strain and
 $\iota=\cos^{-1}(\mathbf{\hat{n}}\cdot{\mathbf{\hat{L}}}) $ is the inclination angle between the line of sight unit vector $\mathbf{\hat{n}} $ and the orbital angular momentum unit vector $\mathbf{\hat{L}}$.
@@
 \Phi_\text{N}(t) &=\int_{t_i}^t dt' \omega(t') \nn\\
-&= -2\left(\f{5 G M_c}{c^3}\right)^{-5/8} (t_\text{coal}-t)^{5/8}+ \Phi_0 \, .\label{eq:Phase}
+&= -2\left(\f{5 G M_c}{c^3}\right)^{-5/8} (t_\text{coal}-t)^{5/8}+ \Phi_0 \, ,\label{eq:Phase}
 \end{align}
 %
-$\Phi_0 \equiv \Phi(t=t_\text{coal})$ is an integration constant. The subscript N denotes the Newtonian (leading-order) contribution. 
-Higher-order contributions can be added in terms a post-Newtonian series which make up $\lesssim 2\%$ of the total phase.
+where $\Phi_0 \equiv \Phi(t=t_\text{coal})$ is an integration constant. The subscript N denotes the Newtonian (leading-order) contribution. 
+Higher-order contributions can be added in terms a post-Newtonian series, which make up $\lesssim 2\%$ of the total phase.
 Although we will include contributions up to and including 3.5PN to obtain the results of Sec.~\ref{sec:results}, 
-we do not explicitly show these expressions, but they can be found in Ref.~\cite{Blanchet_LRR}.
+we will not show these expressions here, but they can be found in Ref.~\cite{Blanchet_LRR}.
 
 The nomenclature ``plus'' ($+$) and ``cross'' ($\times$) follows from the effects that passing GWs have on the plane transverse to their direction of propagation.
-If we were to conceive of an imaginary detector made up of a circular configuration of point-particles lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress the circular arrangement in a $+$ and $\times$ pattern which is the manifestation of the tidal strain of the GWs on the tranverse plane.
+If we were to conceive of an ``toy'' detector made up of a circular configuration of test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress the circular arrangement in a $+$ and $\times$ pattern which is the manifestation of the tidal strain of the GWs on the tranverse plane.
 %which is why $h_{+},h_{\times}$ are often called GW strains. 
-Next, let us briefly explore how a real detector, i.e., an interferometer, responds to passing GWs.
+Next, let us briefly explore how an actual detector, i.e., an interferometer, responds to passing GWs.
 
@@
 
-To compute the advance warning times we will need to know how ``loud'' the binaries become as they sweep across the IFO's detection bandwidth.
+To compute the advance warning times we need to know how ``loud'' the binaries become as they sweep across the IFO's detection bandwidth.
 This is given by the signal-to-noise ratio (SNR) of the GWs in the detectors' data stream.
@@
 
-The detection criterion we will employ here is quantified in terms of the optimal signal-to-noise ratio SNR defined by
+The detection criterion we employ here is quantified in terms of the optimal signal-to-noise ratio SNR defined by
 %%
@@
 %%
-where $\sqrt{S_n(f)}$ is the {\it amplitude spectral density} (ASD) [also called spectral strain sensitivity] of the detector.
+where $\sqrt{S_n(f)}$ is the {\it amplitude spectral density} (ASD) of the detector (also called spectral strain sensitivity, or simply, detector noise).
 It is usually this quantity that is shown in a typical interferometer strain sensitivity plot with the characteristic strain, $\tilde{H}_c(f)\equiv|2\tilde{h}(f)\sqrt{f}|$, 
@@
 It remains to compute $|Q(\theta,\phi,\psi,\iota)|^2$. 
-Since we can not know the direction of the source a priori, it is appropriate to average over the angles $\theta,\phi,\psi,\iota$ which we compute
+Since we can not a priori know the direction of the source, it is appropriate to average over the angles $\theta,\phi,\psi,\iota$ which we compute
 %For our computations, we will only work with one detector so we can set $\psi=0$ without loss of generality, which results in
@@
 a \emph{model network} of three IFOs ($N=3$), where one is near-optimally oriented/positioned thus it is at $2\sigma$ above the average.
-The second IFO operates at the RMS average; thus its sensitivity is suppressed by a factor $2/5$ compared with the optimal $Q =1$ case.
+The second IFO operates at the RMS average; thus its sensitivity is suppressed by a factor $2/5$ compared with the optimal $|Q| =1$ case.
 It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
@@
 \ee
-Using this value, we assign our below-average third IFO $\langle|Q|^2\rangle^{1/2}=4/5-\sqrt{2/5}\simeq 0.1675$.
+Using this value, we assign our below-average third IFO %$\langle|Q|^2\rangle^{1/2}
+$|Q|=4/5-\sqrt{2/5}\simeq 0.1675$.
 %which is essentially a $\{\theta$-$\phi\}$-RMS awayfrom the overall RMS averaged value of 2/5.
-This may seem somewhat ad hoc, but it is our way of modeling the Advanced-LIGO-Virgo network of 2020s in which 
-the three IFOs will accumulate varying SNRs due to their differing quality factors.
-%
-
-To represent our model three-IFO network, we introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
+This may seem somewhat ad hoc, 
+but it is our way of representing the response of a three-IFO network to a single source.
+In other words, we map the three different IFO responses due to a single source to a single IFO's response to three different sources differing in amplitudes
+from the optimal case by quality factors $|Q_i|= 4/5,2/5,$ and $4/5-\sqrt{2/5}$.
+
+%as listed in Table~\ref{table:network_params}.
+%
+%but it is our way of modeling the Advanced-LIGO-Virgo network of 2020s in which 
+%the three IFOs will accumulate varying SNRs due to their %
+%
+To this, we introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
 %%
@@
 %\tilde{A}_i &\equiv A \langle |Q|^2\rangle^{1/2}_i=\f{1}{2}\sqrt{\f{5}{6}}\, \pi^{-2/3} \left\langle\, |Q_i(\theta,\phi,\psi,\iota)|^2\,\right\rangle^{1/2}\quad\text{and} \label{eq:A_tilde}\\
-h_0 &= \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} \label{eq:h0}\, .
+h_0 &= \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} \label{eq:h0}\, 
 \end{align}
 %
-and $\tilde{A}_i =A\langle|Q|^2\rangle^{1/2}_i $ are given in Table~\ref{table:network_params}.
-%for $i=1,2,3$.
-%Clearly, the strain and thus the SNR at each of our imaginary interferometers scales as $\langle |Q|^2\rangle^{1/2}_i$, thus
+and $\tilde{A}_i\equiv A |Q_i|$ %\langle|Q|^2\rangle^{1/2}_i $ 
+are given in Table~\ref{table:network_params}. %for $i=1,2,3$. %Clearly, the strain and thus the SNR at each of our imaginary interferometers scales as $\langle |Q|^2\rangle^{1/2}_i$, thus
 %%
@@
 %
-We arbitrarily make the following assignments for our network: $h=1, m=2, l=3$ representing high, medium, low strain sensitivity, respectively. 
+We arbitrarily make the following assignments for our network: $h=1, m=2, l=3$ representing high, medium, low signal strain
+at IFO$_i$, respectively. 
 We summarize our network in the following table.
@@
 \begin{tabular}{c|c|c|c}
- IFO$_i$ & configuration %& $\langle |Q_i|^2\rangle$ 
+ IFO$_i$ & GW strain %& $\langle |Q_i|^2\rangle$ 
  & $\tilde{A}_i$ & $\tilde{H}_i(f)$\\
@@
 Column four lists the magnitude of the frequency-domain strain at each IFO via Eq.~(\ref{eq:Hi_s}).
-``Configuration'' describes how ideally oriented/positioned an IFO is with respect to a compact binary source. 
-High is $2\sigma$ above the average as explained above.
-Medium is the RMS-averaged (one $\sigma$) response. Recall $A= \pi^{-2/3} \sqrt{5/24}$. 
+The second column shows how loud the GW strain is at a given IFO due source sky position and IFO orientation. 
+%oriented/positioned an IFO is with respect to a compact binary source. 
+%High is $2\sigma$ above the average as explained above.
+%Medium is the RMS-averaged (one $\sigma$) response. 
+Recall $A= \pi^{-2/3} \sqrt{5/24}$. Maximum value for $\tilde{A}_i$ is 1, and minimum is 0.
 %Note that for an interferometer where the angle between the arms is $\alpha$, $A$ rescales to $A\sin\alpha$.
@@
 %
-The invidual antenna responses combine to cancel the $\phi$ and $\psi$ dependence of the combined power pattern
+The invidual antenna responses combine to cancel the $\phi$ and $\psi$ dependence of the total power pattern
 %
@@
 For each idealization we present an estimated error. %that propa
-Our overall conclusion is that our simplifications do not significantly change our estimations of the advance warning times.% which we quantify below.
+Our overall conclusion is that our simplifications do not significantly change our estimations of advance warning times.% which we quantify below.
 %take full advantage of all the available analytical results.
@@
 \section{Simplifications and idealizations used in evolving the inspiral}\label{sec:idealizations}
-In this section, we justify our simplifications with brief computations.
+%In this section, we justify our simplifications with brief computations.
+%We list our simplifications and 
 \begin{enumerate}
  \item {\it Neglecting strong-field gravity and finite-size effects.}
-As our aim here is to provide a rough estimation for the advance warning times, we will model the neutron stars using point masses and carry out this treatment all the way to the merger.
-The point-particle treatment is severely inadequate for the strong-field evolution of the binary.
-However, these systems spend only roughly the last second of the inspiral in this regime, therefore our underestimation of the strong-field effects will not matter for timescales lasting dozens of minutes to hours.
-For example, from $f=100\,$Hz, the inspiral lasts a mere $\approx 2.18\,$ seconds until merger.
-The canonical BNS above has separation $r\approx 155.5\,$km at $f=100\,$Hz, which translates to a dimensionless strength of gravity of $\approx 2.66\%$ for which the Newtonian evolution is adequate.
-We will nonetheless supplement our Newtonian (leading order) evolution with post-Newtonian (pN) knowledge up to second post-Newtonian order (2pN). %, next-to-next to leading order). 
-Though it is now possible to go up to 4pN, we suffice with 2pN here as higher-order contributions make miniscule changes to our estimations for advance warning times. 
+As our aim here is to provide a good order-of-magnitude estimation for the advance warning times, we model the neutron stars as point masses %and carry out this treatment 
+all the way to the merger.
+The point-particle treatment is severely inadequate for the strong-field evolution of the binary, but these systems spend only the last few seconds of the inspiral in this regime, e.g., the inspiral time from $f=100\,$Hz to the merger is
+$\tau_\text{insp}(f=100\,\text{Hz})\simeq 2.161\,$seconds according to Eq.~(\ref{eq:tau_insp}).
+And even at $f=100\,$Hz, a $m_1=m_2=1.4M_\odot$ neutron-star binary has separation $2r\approx 310\,$km, which translates to a dimensionless strength of gravity of $\approx 1.3\%$.
+This percentage is mostly accounted for by the post-Newtonian
+corrections to our Newtonian (leading order) evolution. 
+Here, we will go up to 3.5 post-Newtonian order (3.5pN) for our
+advance warning time computations.
+Therefore, given that strong-field effects may at most change
+$T_\text{AW}$ by a second, we can neglect them for our purposes,
+but let us add that a faithful evaluation of BNS systems above $f\gtrsim 100\,$Hz is a very active and important branch of general relativity and gravitational-wave astronomy.
+%, but beyond the scope of this article.
+%negligence of the strong-field effects will not matter for timgescales lasting minutes to hours.
+%, next-to-next to leading order). 
+%Though it is now possible to go up to 4pN, we suffice with 2pN here as higher-order contributions make miniscule changes to our estimations for advance warning times. 
 %
 \item {\it Truncating the inspiral at the Schwarzschild ISCO.}
-We artificially end the inspirals at the Schwarz-schild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6M$ and angular frequency $\Omega_\text{ISCO} = (M/r^3_\text{ISCO})^{1/2}$ in natural units, which translates to the following dominant-mode (quadrupole) GW frequency
-\be
-f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571\,\text{Hz} \label{eq:f_isco},
-\ee
-where $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$ with frequency possibly up to 1.7\,kHz \cite{Marronetti:2003hx}, 
+We artificially end the inspirals at the Schwarzschild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6M$ and angular frequency $\Omega_\text{ISCO}$ %= (M/r^3_\text{ISCO})^{1/2}$ in natural units,
+given by Eq.~(\ref{eq:Sch_f_isco}) which translates to the following dominant-mode (quadrupole) GW frequency
+\be
+f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571\,\text{Hz} \label{eq:f_isco}
+\ee
+for $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$ with frequency possibly up to 1.7\,kHz \cite{Marronetti:2003hx}, 
 however, there is no simple expression for it.
-Additionally, above $f \approx 200\,$Hz tidal effects are expected to show up in the GW signal.
+Therefore, we employ Eq.~(\ref{eq:f_isco}) as our cut-off for
+inspirals throughout this work.
+%Additionally, above $f \approx 200\,$Hz tidal effects are expected to show up in the GW signal.
 %These further complicate to an already highly dynamic spacetime. 
-A faithful evaluation of BNS systems above $f\gtrsim 100\,$Hz is a very active branch of general relativity today,
-but beyond the scope of this article.
-As we showed above, our disregard for relativistic effects costs us a few seconds at most.%requires fully relativisticmagneto-hydrodynamic large-scale computing clusters.
+% As we showed above, our disregard for relativistic effects costs us a few seconds at most.%requires fully relativisticmagneto-hydrodynamic large-scale computing clusters.
 %
 \item {\it Setting} $m_1=m_2=1.4 M_\odot$.
-Let us also briefly explore what the cost of setting $m_1=m_2=1.4 M_\odot$ will be for our calculations. 
+Let us briefly explore what the cost of setting $m_1=m_2=1.4 M_\odot$ is for our calculations. 
 Including the error bars, the known range for neutron star masses runs from $\sim 0.5 M_\odot$ to $ \sim 3 M_\odot$ with the actual values restricted
 between $\sim 1 M_\odot$ and $\sim 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
-Of these measured masses, a subset comprised of double neutron stars, such as the famed Hulse-Taylor binary, have the smallest error bars with masses
+Of these measured masses, a subset comprised of double neutron stars (NSs), such as the famed Hulse-Taylor binary, have the smallest error bars with masses
 ranging from $\sim 1.2 M_\odot$ to $\sim 1.5 M_\odot$. 
@@
 the quantities of interest for us, which are %the GW/orbital frequency ($f/f_K$), %the radiated power in GWs ($\dot{E}$), the rate of change of GW/orbital frequencies ($\dot{f}$), 
-the inspiral time ($\tau_\text{insp}$), the GW strain at the detector in the frequency domain ($\tilde{h}$) and
+the inspiral time ($\tau_\text{insp}$), the GW strain at the detector in the frequency domain ($\tilde{H}$) and
 the frequency of the innermost stable circular orbit ($f_\text{ISCO}$) given by Eq.~(\ref{eq:f_isco}) above.
-From the previous section, we know how these scale in terms $M_c, M$ thus $m_1, m_2$, all of which we summarize in Table \ref{tbl:scalings} below.
+We summarize how these scale in terms $M_c, M$, thus $m_1, m_2$, in Table \ref{tbl:scalings} below.
 %%
@@
 \begin{table}[ht]
-\begin{tabular}{|l|ccc|}
+\begin{tabular}{|l|cccc|}
 \hline
- Quantity & Standard Scaling & Scaling in terms of $m_1,m_2$ & Min $\le$ Value$_{1.4} \le$ Max\\
+ Quantity & Standard Scaling & \hspace{3mm}Scaling in terms of $m_1,m_2$ & &\hspace{0.5cm} Min $\le$ Value$_{1.4M_\odot} \le$ Max\T\B\\
 \hline
@@
 %$f=2f_K$ & $M^{1/2}$& $(m_1+m_2)^{1/2}$& $1.2 \le 1.41 \le 1.69 $\\
-$\tau_\text{insp}$ & $M_c^{-5/3} $ & $(m_1 m_2)^{-1}(m_1+m_2)^{-1} $& $0.335\le 0.5\le 0.794 $ \\
-$\tilde{h}$ & $M_c^{5/6} $ & $(m_1 m_2)(m_1+m_2)^{3/2} $& $ 0.7834\le 0.891 \le 0.996 $ \\
-$f_\text{ISCO}$ & $M^{-1} $ & $(m_1+m_2)^{-1} $& $0.4375\le 0.5\le 0.583 $\\
+$\tau_\text{insp}$ & $M_c^{-5/3} $ & $(m_1 m_2)^{-1}(m_1+m_2)^{-1} $&\quad& $0.335\le 0.5\le 0.794 $ \\
+$\tilde{H}$ & $M_c^{5/6} $ & $(m_1 m_2)(m_1+m_2)^{3/2} $&\quad& $ 0.7834\le 0.891 \le 0.996 $ \\
+$f_\text{ISCO}$ & $M^{-1} $ & $(m_1+m_2)^{-1} $&\quad& $0.4375\le 0.5\le 0.583 $\\
 \hline
@@
 \caption{The scaling of the physical quantities of interest in this article in terms the binary masses $m_1, m_2$ restricted to lie between $1.2M_\odot$ and $1.6 M_\odot$. 
-We used Kepler's third law to obtain $f \sim f_K \sim M^{1/2}$.
-Value$_{1.4}$ represents the value of the quantities in column three evaluated at $m_1=m_2=1.4 M_\odot$.
-Unlike the orbital frequency $f_K$, the ISCO frequency $f_\text{ISCO}$ scales as $M^{-1}$ as shown in Eq.~(\ref{eq:f_isco}).}
+%We used Kepler's third law to obtain $f \sim f_K \sim M^{1/2}$.
+Value$_{1.4M_\odot}$ represents the value of the quantities in column three evaluated at $m_1=m_2=1\, \text{mass unit}$ corresponding to $1.4 M_\odot$.
+%Unlike the orbital frequency $f_K$, the ISCO frequency $f_\text{ISCO}$ scales as $M^{-1}$ as shown in Eq.~(\ref{eq:f_isco}).
+}
 \label{tbl:scalings}
@@
 %%
-%
-The ranges in column four show that $\tilde{h}$ changes roughly by $\pm 10\%$ across our chosen NS mass range whereas the variation
-in $f_\text{ISCO}$ matters not as it affects the advance warning times by less than second (see above).
-The inspiral time seems to be more sensitive to our chosen mass values as indicated by roughly the ${}^{+60\%}_{-30\%}$ variation 
+\vspace{-11mm}
+The ranges in column four show that $\tilde{H}$ changes roughly by $\pm 10\%$ across the $1.2M_\odot-1.6M_\odot$ mass range whereas the variation
+in $f_\text{ISCO}$ matters not as it affects the advance warning times by less than a second (see above).
+The inspiral time seems to be more sensitive to our chosen mass values as indicated by the $\sim{}^{+60\%}_{-30\%}$ variation 
 in Table \ref{tbl:scalings}. %$\tau_\text{insp}^{1.4}$ as shown in Table \ref{tbl:scalings}.
 As our intent is to provide an estimation for advance warning times in terms of orders of magnitude, this variation is tolerable.
+Moreoever, it seems that the variation in mass tends to lengthen $\tau_\text{insp}$ more than shorten it thus our setting
+$m_1=m_2=1.4 M_\odot$ is more likely to underestimate $T_\text{AW}$ than overestimate it which is something we can live with.
+So we set the NS masses to equal $1.4 M_\odot$ henceforth.
 %
@@
 We further simplify our treatment by considering only quasi-circular inspirals meaning that at any given instant, 
-the orbit can be treated as a circular orbit with constant Keplerian frequency $f_K = (GM/r^3)^{1/2}/(2\pi)$, where $r$ is the radius of the circular orbit.
-It was Peters \& Matthews who first showed that eccentric binaries circularize in the weak field \cite{PM1963}. 
+the orbit can be treated as circular with the corresponding Keplerian frequency $f_K = (GM/r^3)^{1/2}/(2\pi)$. %, where $r$ is the radius. % of the circular orbit.
+It was Peters and Matthews who first showed that eccentric binaries circularize in the weak field \cite{PM1963}. 
 %For large eccentricities, i.e., $ 1-e\ll 1$, the circularization rate is quite steep: $ \dot{e}\sim -(1-e^2)^{3/2} $.
@@
 %
-where $a$ is the semi-major axis of the eccentric orbit and $c_0$ is a constant. Thus, for $e\ll 1$ we have $g(e)\approx e^{12/19}$, which means
-that for a system with current parameters $a_i, e_i$, we can write $e\approx [a\, g(e_i)/a_i ]^{19/12}$.
-Let us apply this to determine the eccentricity of the Hulse-Taylor binary pulsar when it will have $f=2f_K = 1\,$Hz, i.e., 
-$a \simeq 810.5\,$km with currently observed parameters of $a_i \simeq 2\times 10^6\,$km and $e_i \simeq 0.617$. 
-A quick calculation yields $e\simeq 1.09\times 10^{-10}$. 
-Hence, we see that the BNS orbits will have circularized by the time they enter the interferometers' bandwidth.
+where $a$ is the semi-major axis of the eccentric orbit and $c_0$ is a constant. For $e\ll 1$ we have $g(e)\approx e^{12/19}$, thus we may write $e\approx [a\, g(e_i)/a_i ]^{19/12}$ 
+for a system with initial parameters $a_i, e_i$.
+Let us apply this to the Hulse-Taylor binary pulsar \cite{Hulse:1974eb,Weisberg:2010zz} to show that the BNS orbits circularize by the time they enter the interferometers' bandwidth.
+Letting $f = 1\,\text{Hz}=2f_K$, i.e., 
+$a \simeq 3352\,$km and using the currently observed values $a_i \approx 1.95\times 10^6\,$km and $e_i \approx 0.617$,
+we obtain $e\approx 6\times 10^{-5}$. Thus our setting $e=0$ is very reasonable.
+%
 %
 \item {\it Quasi-circularity.}
-Next, let us test the assumption that the motion is quasi-circular. 
-This implies that that the timescale for the orbital radius to change is much longer than the orbital timescale, i.e., radial velocity $\ll$ tangential velocity during the inspiral.
-From $\Omega^2 = GM r^{-3}$ we can straightforwardly obtain
+%Next, let us test the assumption that the motion is quasi-circular. 
+This implies that the timescale for the orbital radius to decrease is much longer than the orbital timescale, i.e., 
+$|\dot{r}|\ll r\Omega$ during the inspiral. From $\Omega^2 = GM r^{-3}$ we can straightforwardly obtain 
 %
@@
 %
-an expression for the ratio of radial velocity to tangential velocity
-%
-\be
-\f{|\dot{r}|}{r\Omega}=\f{2}{3}\f{|\dot\Omega|}{\Omega^2} \label{eq:ratio_of_radial_vel_to_tang_vel} .
-\ee
-%
-The quasi-circular approximation implies that $|\dot{r}| \ll r\Omega$ which translates to $|\dot\Omega| \ll \Omega^2$ which then gives
+an expression for the ratio of radial speed to tangential speed
+%
+\be
+\f{|\dot{r}|}{r\Omega}=\f{2}{3}\f{|\dot\Omega|}{\Omega^2} \label{eq:ratio_of_radial_vel_to_tang_vel} ,
+\ee
+%
+which translates the quasi-circularity condition above to $|\dot\Omega| \ll \Omega^2$ which, via Eq.~(\ref{eq:fdot}), gives
 %
@@
 %
-using Eq.~(\ref{eq:fdot}). %Assuming $\ll 1$ means $\le 10^{-3}$ 
-For example, setting $\dot{\Omega}/\Omega^2 = 10^{-3}$ yields $f= \Omega/\pi \simeq 142.8\,$Hz which, as explained above, 
-is practically the last second before the merger. Thus, we see that we can safely employ the quasi-circular motion assumption in our
-estimations for advance warning times.
+%using Eq.~(\ref{eq:fdot}). %Assuming $\ll 1$ means $\le 10^{-3}$ 
+%Setting $\dot{\Omega}/\Omega^2 = 10^{-3}$ yields $f= \Omega/\pi %\simeq 443.4\,$Hz which, as explained above, 
+This expression yields $\dot{\Omega}/\Omega^2\approx 5.5\times 10^{-4}$ at $f=100\,$Hz, which, as shown above, is a few seconds
+before the merger so the quasi-circularity assumption seems to
+hold almost until the plunge at $f=f_\text{ISCO}$.
+%is less than a second before the merger. 
+Thus, we can treat the binary's motion
+as quasi-circular for our estimations of advance warning times.
 %
@@
 affected by neglecting higher-order contributions to the loss of energy coming from, e.g., the current quadrupole and the mass octupole moments.
-It can be shown that the power radiated by the current
-quadrupole ($\dot{E}_\text{cq}$) by a binary in a circular orbit is $\ord(v^2/c^2)$ smaller than the dominant quadrupole power. More precisely, we have \cite{Maggiore}
-%
-\be
-\f{\dot{E}_\text{cur}}{\dot{E}} = \f{1215}{896} \f{v^2}{c^2}\left(\f{m_2-m_1}{M}\right)^2=\f{1215}{896}\f{(\pi G M f)^{2/3}}{c^2}\left(\f{m_2-m_1}{M}\right)^2\, . \label{eq:Oct_quad_ratio}
+The power radiated by the current
+quadrupole ($\dot{E}_\text{cur}$) by a binary in a circular orbit is $\ord(v^2/c^2)$ smaller than the dominant quadrupole-mode power emission. More precisely, we have \cite{Maggiore}
+%
+\be
+\f{\dot{E}_\text{cur}}{\dot{E}} = \f{1215}{896} \f{v^2}{c^2}\left(\f{m_2-m_1}{M}\right)^2=\f{1215}{896}\f{(\pi\, G M f)^{2/3}}{c^2}\left(\f{m_2-m_1}{M}\right)^2\, . \label{eq:Oct_quad_ratio}
 \ee
@@
 At $f=100\,$Hz, the first two factors $\simeq 3.6\times 10^{-2}$ for $M=2.8 M_\odot$ which tells us that even in the strong-field regime, 
-the next-to-leading order contribution is a two orders of magnitude smaller.
+the next-to-leading order contribution is two orders of magnitude smaller.
 The ratio in Eq.~(\ref{eq:Oct_quad_ratio}) is further supressed by $(m_2-m_1)/M^2$ which, for our idealized equal-mass system, 
-yields zero so we can neglect the current-quadrupole radiation completely. In a similar fashion, it can be shown that the power radiated by the mass octupole ($\ell=3$)
-scales the same way as in Eq.~(\ref{eq:Oct_quad_ratio}) with respect to the dominant mass quadrupole radiation, but is $\sim 50$ times smaller. 
-Hence we can neglect it without worry for our work. Higher moments are suppressed by higher factors of $v^2/c^2$ as can be shown using post-Newtonian theory. 
-Thus, our exclusiveness to keeping only the mass-quadrupole radiation is well justified.
-
-%
-\item {\it Neglecting the neutron star spins.}
-It is generally believed that NSs do not have large enough angular momentum to impart interesting spin effects into the GWs emitted by the BNS systems.
+yields zero, but if we consider $m_1=1.2 M_\odot, m_2=1.6 M_\odot$ then it gives $\approx 2\times 10^{-2}$ hence the ratio in Eq.~(\ref{eq:Oct_quad_ratio}) $\lesssim 10^{-3}$.
+Thus, we can neglect the current-quadrupole radiation completely. In a similar fashion, it can be shown that the power radiated by the mass octupole ($\ell=3$)
+scales the same way as in Eq.~(\ref{eq:Oct_quad_ratio}) with respect to the dominant mass quadrupole radiation, but is $\sim 50$ times smaller hence we can neglect it as well \cite{Maggiore}.
+%without worry for our work. 
+Higher moments are suppressed by higher factors of $v^2/c^2$ as can be shown using post-Newtonian theory. 
+Thus, our exclusiveness to the mass-quadrupole radiation is justified.
+% 
+%
+\item {\it Neglecting neutron star spins.}
+It is generally believed that NSs do not have large enough angular momentum to impart detectable spin effects into the GWs emitted by the BNS systems.
 The dominant effect due to the spins is the spin-orbit (SO) precession which contributes to the energy flux at the 1.5pN order [$\ord(v^3/c^3)$] with respect to the leading-order quadrupole $\dot{E}$ of Eq.~(\ref{eq:Edot}) \cite{Blanchet_LRR}.
@@
 %
-where we introduced the dimensionless Kerr spin parameter $\chi\equiv {S}/({G m^2})$ which, for a NS with spin $S$, can be written as
+where we introduced the dimensionless Kerr spin parameter $\chi\equiv {S}/({G m^2})$ which, for a NS with spin $S$ and mass $m$, can be written as
 %
@@
 %
-where $m$ is the mass, $P$ is the spin period, and $ I = (2/5) m R^2 \kappa$ is the moment of inertia of the NS with $R$ being the radius of the NS and $\kappa \approx \ord(1)$ an intrinsic constant (see, e.g., Sec.~6.2 of \cite{Colpi_Sesana}).
+where $P$ is the spin period, and $ I = (2/5) m R^2 \kappa$ is the moment of inertia of the NS with $R$ being the radius of the NS and $\kappa \sim \ord(1)$ an intrinsic constant (see, e.g., Sec.~6.2 of Ref.~\cite{Colpi_Sesana}).
 A rather compact NS with $m=1.4 M_\odot, R=11\,\text{km}, P= 10\,\text{ms}$ has $\chi\lesssim 0.05$ whereas
-the fastest spinning known NS has $\chi\lesssim 0.04$ \cite{FastestNSspin}.
-Therefore, at $f= 100\,$Hz, the first term in the RHS of Eq.~(\ref{eq:spin_orbit}) gives $4.252\times 10^{-4}$. 
+the fastest observed NS spin $\lesssim 0.04$ \cite{FastestNSspin}.
+Therefore, at $f= 100\,$Hz, the first term on the right-hand-side of Eq.~(\ref{eq:spin_orbit}) gives $\approx 4\times 10^{-4}$. 
 On the other hand, the spin-spin effects contribute at $\ord(v^4/c^4)\times\dot{E}$ hence $\lesssim \dot{E}_\text{SO}$.
-Thus, we have justified our negligence of the effects of NS spins.
+Thus, NS spins do not significantly affect our estimation of advance warning times. %$T_\text{AW}$.
+%we have justified our negligence of the effects of NS spins.
 %
@@
 dt& \rightarrow (1+z) dt_s, \\
- D & \rightarrow  (1+z)a(t) D,\\
- f & \rightarrow (1+z)^{-1} f_s\, .
+ f & \rightarrow (1+z)^{-1} f_s\, 
  %M_c & \rightarrow (1+z) M_{s,c},
 \end{align}
+and the luminosity distance gets rescaled as
+\be
+D  \rightarrow  (1+z)a(t) D.
+\ee
 %
 Given that $\dot{f}_s=df_s/dt_s\sim f^{11/3}_s, h_s(t)\sim D^{-1} f_s^{2/3}$, and $\tau_{\text{insp},s}\sim f_s^{-8/3}$,
-the observed frequency evolution, the GW strain, and the inspiral time change according to % in the detector frame
+the observed frequency evolution, the inspiral time, 
+and the GW strain change according to % in the detector frame
 %%
@@
 \dot{f}\ \ &\sim (1+z)^{5/3}{f}^{11/3},\\
-h(t) & \sim (1+z)^{5/3} h(t),\\
-\tau_\text{insp}& \sim (1+z)^{-5/3} \tau_{\text{insp}}
+\tau_\text{insp}& \sim (1+z)^{-5/3} \tau_{\text{insp}},\\
+h(t) & \sim (1+z)^{5/3} h(t).
 \end{align}
@@
 \begin{align}
-\dot{f} &= \f{96}{5}\pi^{8/3} \f{(G \mathcal{M}_c)}{c^3}^{5/3}\, f^{11/3} \label{eq:fdot_redshifted},\\
-h_c(t) & = \f{4}{D}\left(\f{G \mathcal{M}_c}{c^2}\right)^{5/3}\left(\frac{\pi f}{c}\right)^{2/3} \label{eq:strain_TD_redshifted}\\
-\tau_\text{insp}(f) &= \f{5}{256\pi}\f{c^5}{(\pi G \mathcal{M}_c)^{5/3}} \,f^{-8/3}\label{eq:tau_insp_redshifted}\, ,
+\dot{f} &= \f{96}{5}\pi^{8/3} \f{(G \mathcal{M}_c)}{c^5}^{5/3}\, f^{11/3} \label{eq:fdot_redshifted},\\
+\tau_\text{insp}(f) &= \f{5}{256\pi}\f{c^5}{(\pi G \mathcal{M}_c)^{5/3}} \,f^{-8/3}\label{eq:tau_insp_redshifted}, \\
+h_c(t) & = \f{4}{D}\left(\f{G \mathcal{M}_c}{c^2}\right)^{5/3}\left(\frac{\pi f}{c}\right)^{2/3} \label{eq:strain_TD_redshifted},
 \end{align}
@@
 For the Advanced-LIGO-Virgo network,
-we consider a maximum BNS luminosity distance of 200\,Mpc, 
-i.e., $z \approx 0.022$ which redshifts $f_\text{ISCO}$ by $\approx 2\%$ and reduces $\tau_\text{insp}$ by $\approx 7\%$.
-Therefore, we will neglect the effects of cosmological redshifting on the less sensitive ALV network.
+we consider a maximum value of 200\,Mpc for $D$,
+which corresponds to $z \approx 0.022$ which redshifts $f_\text{ISCO}$ by $\approx 2\%$ and reduces $\tau_\text{insp}$ by $\approx 7\%$.
+Therefore, we will neglect the effects of cosmological redshift 
+when considering sources for the ALV network.
 On the other hand, for Einstein Telescope, we will go out to $D=1\,\text{Gpc}\implies z\approx 0.2$
-which reduces $\tau_\text{insp}$ by $1/4$, thus we shall include the redshift effects in our computations of advance warning times and SNRs
+which reduces $\tau_\text{insp}$ by $\sim 25\%$, thus we shall include the redshift effects in our computations of advance warning times and SNRs
 for which we provide the details in Sec.~\ref{Sec:ETB} (additional details can be found in, e.g., Ref.~\cite{Phinney:2001di}).
@@
 
-\section{GW170817 as a test of our model Advanced LIGO-Virgo network}\label{sec:GW170817}
-On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system were detected by the Advanced LIGO-Virgo network.
-The event, first picked up by LIGO Hanford (H1), swept from $\sim 30\,$Hz to $\sim 2000\,$Hz in the detectors' frequency band with an accumulated total SNR of
+\section{GW170817 as a test of our model for the Advanced LIGO-Virgo network}\label{sec:GW170817}
+On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system %were detected by the Advanced LIGO-Virgo network.
+%The event, first picked up by LIGO Hanford (H1), 
+swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz accumulating a total SNR of
 %18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
 $\rho_\text{tot} = 32.4$ \cite{GW170817}
-The inferred duration of the event in the network bandwidth is $\sim 60\,$ seconds during which $\sim 3000$ cycles of GW were emitted \cite{GW170817_Facts}.
+The inferred duration of the event in the network bandwidth was $\approx 57\,$ seconds during which $\approx 3000$ cycles of GW were emitted \cite{GW170817_Facts}.
 Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following values were inferred for the total mass, the chirp mass,
@@
 \be
-M = 2.74^{0.04}_{-0.01} M_\odot, M_c = 1.188^{+0.004}_{-0.002} M_\odot, D= 40^{+8}_{-14}\,\text{Mpc}. \label{eq:GW170817_params}
+M = 2.74^{+0.04}_{-0.01} M_\odot,\quad M_c = 1.188^{+0.004}_{-0.002} M_\odot,\quad D= 40^{+8}_{-14}\,\text{Mpc}. \label{eq:GW170817_params}
 \ee
@@
 
-How well does the ``naive'' formulation based on the quadrupole formula perform? 
-To test this, let us first compute the inspiral time, $\tau_\text{insp}$, and the number of GW cycles, $\mathcal{N}_\text{cyc}$, for this BNS system with initial frequency $f_i=30\,$Hz and final frequency $f_\text{ISCO} \simeq 1605.37\,$Hz.
-Eqs.~(\ref{eq:tau_insp}) and (\ref{eq:Ncyc2}) provide us with the leading-order values
+How well does the ``naive'' Newtonian evolution based on the quadrupole formula perform? 
+To test this, let us first compute the inspiral time, $\tau_\text{insp}$, and the number of GW cycles, $\mathcal{N}_\text{cyc}$, for this BNS system with initial frequency $f_i=30\,$Hz and final frequency $f_\text{ISCO} \simeq 1605\,$Hz.
+Eqs.~(\ref{eq:tau_insp}) and (\ref{eq:Ncyc1}) provide us with the leading-order values
 %%
@@
 \be
-\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \label{eq:GW170817_values_3p5PN}\, .
-\ee
-%
-%%
-These are very close to the inferred values of $\tau_\text{insp}\approx 60$\,seconds and $\mathcal{N}_\text{cyc} \approx 3000$ which we can obtain if we use $f_i \approx 28-29\,$Hz.
+\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \label{eq:GW170817_values_3p5PN}\, ,
+\ee
+%
+%%
+which more or less match the values above. %of $\tau_\text{insp}\approx 60$\,seconds and $\mathcal{N}_\text{cyc} \approx 3000$ which we can obtain if we use $f_i \approx 28-29\,$Hz.
 %Our PN-only computation underestimates $\mathcal{N}_\text{cyc}$ because we artificially end the inspiral at the Schwarzschild ISCO whereas
@@
 
-We now test our imaginary network using the best-inferred values for $M,M_c,D$ from GW170817 given in Eq.(\ref{eq:GW170817_params}) above and 
-neglecting the cosmological corrections as 40\,Mpc is in our ``local'' neighbourhood when considering cosmological distances.
-The test involves computing the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
+We now put our model three-IFO network to the test
+by computing the SNRs accumulated by each individual IFO and by the entire network.
+To do so, we take the best-inferred values for $M,M_c,D$ from GW170817 given in Eq.(\ref{eq:GW170817_params}) above and compute the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
 %%
@@
 where $f_0 =30\,\text{Hz}, f_f= f_\text{ISCO}$ for GW170817 and $\tilde{A}_i$ given in Table~\ref{table:network_params}.
-For $S_\text{n}(f)$ we use actual [noise-subtracted] L1 data for GW170817 from LIGO's website \cite{LIGO_L1_data}.
+For this computation, we have neglected the cosmological corrections as 40\,Mpc is in our ``local'' neighbourhood.
+
+For $S_\text{n}(f)$ we use actual [noise-subtracted] LIGO-Livingstone (L1) data for GW170817 from LIGO's website \cite{LIGO_L1_data}.
 The data, sampled at 4096\,Hz, is given as a discrete time series $h(t_i)$ for a duration of 2048\,seconds in time steps of $\Delta t=1/4096\simeq 2.44\times 10^{-4}\,$seconds.
 %with the amplitude peaking at $1842.43\pm0.03\,$seconds.
-We first Fourier-transform this data to frequency space and apply several high- and low-frequency filters to isolate a window of $f\in [10, f_\text{ISCO}]$.
+We first Fourier-transform the data to frequency space and apply several high and low-frequency filters to isolate a window of $f\in [10, f_\text{ISCO}]$.
 The LIGO Open Science Center has a detailed Python-based tutorial on how to do this using the data from the very first GW detection (GW150914) \cite{LIGO_tutorial}. 
@@
 but because their orientations and response functions differ, their sensitivity to a localized source is reduced. We represent this reduction by lowering the
-amplitude of the incoming GWs by appropriate factors explained in Sec.~\ref{sec:BNS_inspiral} and shown in Table~\ref{table:network_params}.
+amplitude of the GW strain by appropriate quality factors ($|Q_i|$) explained in Sec.~\ref{sec:BNS_inspiral} and shown in Table~\ref{table:network_params}.
 The amplitude-adjusted strains $ \tilde{H}_i(f)$ are represented by the dashed ($i=h$), solid ($i=m$), and dotted ($i=l$) lines in the figure where we actually plot
@@
 The shaded region in Fig.~\ref{fig:figGW170817} covers strains between $\tilde{H}_l(f)$ and $\tilde{H}_h(f)$. %which we expect to represent mo
-Given a network of three equally sensitive, randomly oriented IFOs we expect that a single BNS inspiral would produce three distinct detector
-response strains in this shaded region.
+Given a randomly positioned/oriented BNS inspiral at 40 Mpc, we would in general expect a randomly oriented IFO's response to lie in this shaded region.
+%Given a network of three equally sensitive, randomly oriented IFOs we expect that a single 40-Mpc BNS inspiral would produce three distinct detector response strains that fall within this shaded region.
 %
@@
 We also show the Hanford detector's sensitivity in light blue for comparison. The dashed, solid and dotted lines represent the 
-response of each interferometer's frequency-domain response ($2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$) to the inspiral of
-a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}).
+frequency-domain GW strains due to the inspiral of
+a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}) ($2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$).
+%each interferometer's frequency-domain response
 The variation in strain amplitudes is the result of a given interferometer's orientation and the sky position of the source 
 as explained in Sec.~\ref{sec:LIGO_topo} and summarized in Table~\ref{table:network_params}.
-In other words, the dashed line is how ``loud'' GW170817 would appear in the data stream of a near optimally oriented IFO with L1's sensitivity
+More specifically, the dashed line is how ``loud'' GW170817 would appear in the data stream of an IFO with L1's sensitivity
+with near optimal orientation
 %would be if L1was optimally positioned and oriented 
-(quality factor $Q=4/5$). Similarly, the solid line represents the strain in %a randomly oriented IFO with randomized source sky location, hence
-the RMS-averaged IFO with L1's sensitivity ($Q=2/5$). %, but with RMS-average over all angles 
+(quality factor $|Q|=4/5=80\%$). Similarly, the solid line represents the strain in an identical inteferometer with 
+%a randomly oriented IFO with randomized source sky location, hence
+%the RMS-averaged IFO with L1's sensitivity 
+$|Q|=2/5=40\%$ (RMS-averaged response). %, but with RMS-average over all angles 
 %determining source orientation and position. 
 Finally, the dotted line represents a pessimistic IFO orientation and source location (sub-optimal configuration)
-resulting in a reduction of amplitude to $ 16.7\%$ of the $Q=1$ case. 
-The shading represents the region of likelihood for where the strain due to an inspiralling BNS would be. In the case of a three-IFO
-network, we would expect all three strains to exist somewhere in the shaded region most of the time and two out of three every time.
+resulting in a reduction of $|Q|$ to $\simeq 16.7\%$.
+%of the $Q=1$ case. 
+The shading represents the region of likelihood for the strain due to an inspiralling BNS. In the case of a three-IFO
+network, we would expect all three strains to exist somewhere in the shaded region most of the time for an inspiral with GW170817's intrinsic parameters. %.and two out of three every time.
 %The darker region marks $\text{RMS}\pm(\sqrt{2/5}-2/5)$ translating to an amplitude range of $ 16.7\% - 63.2\%$ of the maximum $\tilde{H}_h(f)$.
 %For a randomly located, oriented BNS inspiral, we expect its strain to sweep in the lighter region for one IFO and in the darker region for the other two IFOs.
-The dot-dashed (green) curve shows a more realistic strain constructed with data from numerical simulations of Ref.~\cite{Read:2009yp}.
-The breakdown of the leading-order $\sqrt{f}f^{-7/6}=f^{-2/3}$ behavior around $f\sim100\,$Hz due to tidal effects is clear.
+The dot-dashed (green) curve shows a more realistic strain constructed with data from numerical simulations of Ref.~\cite{Read:2009yp}
+and rescaled to match our solid line at $f=10\,$Hz.
+The breakdown of the $\sqrt{f}f^{-7/6}=f^{-2/3}$ behavior of
+the strain around $f\sim100\,$Hz due to tidal effects is clear.
 %Note that although we extend the $\sqrt{f}f^{-7/6}=f^{-2/3}$ power law behavior of the strains all the way to ISCO, in actuality, this  starts breaking down .
@@
 %%
-This also compares well with the actual value of 32.4.
-Therefore, we conclude that our imaginary network performs realistically enough to make predictions on the performance of IFOs in the 2020s and 2030s.
-%
-%
-%
-%
-%
-\section{Results: Advance warning times for inspiralling neutron stars}\label{sec:results}
+This matches the actual value of 32.4 very well. Therefore, we conclude that our model network performs well enough to 
+act as our future ALV network of the 2020s once we change
+the ASD from the August 2017 value to design sensitivity.
+%make predictions on the performance of IFOs in the 2020s and 2030s.
+%
+%
+%
+%
+%
+\section{Results: Advance warning times for future binary neutron star inspirals}\label{sec:results}
  %\subsection{BNS inspirals at Advanced LIGO-Virgo and the Einstein Telescope}\label{Sec:BNS_2020_2030}
  %Recall that we are interested in the advance warning times that the (near)-future ground-based interferometers can provide for the optical astronomers before the prompt GRB at the end of the merger.
- Our aim is to foretell GRBs using our network made up of three IFOs with A-LIGO design sensitivity in the 2020s and the Einstein Telescope sensitivity in the 2030s.
- Our predictive capabilities depend on how much advance warning the future networks will give us prior to the prompt merger/GRB.
- Our definition of advance warning is the inspiral time to the merger from a certain threshold instant $\bar{t}$ at which point the network ``agrees'' that there is an inspiral 
- event statistically significant enough to issue warnings to electromagnetic telescopes.
+ Our aim is to forecast GRBs using our model networks for the ALV era in the 2020s
+ and the Einstein Telescope era in the 2030s.
+ Our predictive capabilities depend on how much advance warning the future networks will give us prior to the merger/GRB.
+ Our definition of advance warning is the inspiral time to the merger from a certain threshold instant $\bar{t}$ at which point the network ``agrees'' that there is a GW transient
+ statistically significant enough to issue warnings to electromagnetic telescopes.
  We define this threshold instant to be given at a frequency $\bar{f}$ when the total SNR equals 15. 
- More specifically, in the case of the Advanced-LIGO-Virgo network (ALV), our statement is that there exists a frequency $\bar{f} < f_\text{ISCO}$ such that
+ More specifically, in the case of the ALV network, our statement is that there exists a frequency $\bar{f} < f_\text{ISCO}$ such that
  %
@@
  %
- where $f_0^i$ are given by the solution set to
+ where $f_0^i$ are the initial GW frequencies at which a given inspiral enters the $i^\text{th}$ IFO's sensitivity band, and
+ are given by the solution set to
  %there exists some frequency $f_0 < \bar{f}$ such that
@@
  %
- with $f_0^i < \bar{f}$. In other words, $f_0^i$ are the initial GW frequencies at which a given inspiral enters the $i$th IFO's sensitivity band. 
+ with $f_0^i < \bar{f}$.
  Once we know $\bar{f}$, we can compute the remaining time to the merger, $\tau_\text{insp}(\bar{f})$, using Eq.~(\ref{eq:tau_insp})
@@
  Point 3 of Sec.~\ref{sec:idealizations}. 
- With the masses fixed, the only variable determining $h_0$ is the luminosity distance $D$ as can be seen from Eq.~(\ref{eq:h0}).
+ With the masses fixed, the only remaining variable is the 
+ luminosity distance $D$.
+For the ALV network, we consider $D=50,100,200\,$Mpc 
+ as A-LIGO horizon will be slightly over 200\,Mpc and A-Virgo's around 130\,Mpc.
+ %and BNS systems at $D=200, 400, 1000\,$Mpc for the ET network. 
+ For each value of $D$, we compute $\bar{f}$ from Eq.~(\ref{eq:SNR_bar}) with which we then compute $T_\text{AW}=\tau_\text{insp}(\bar{f})$.
+ %which we set to values of our choosing. %as can be seen from Eq.~(\ref{eq:h0}).
  We summarize our procedure in the flow diagram below.
@@
  \framebox{\Longstack[l]{Pick $D$}}$\longrightarrow$\framebox{\Longstack[l]{Construct\\ $\tilde{H}_i(f)$}} 
- $\longrightarrow$  \framebox{\Longstack[l]{Compute $f_0^i$\\ from Eq.(\ref{eq:f0})}} $\longrightarrow$  \framebox{\Longstack[l]{Compute $\bar{f}$\\ from Eq.(\ref{eq:SNR_bar})}}
+ $\longrightarrow$  \framebox{\Longstack[l]{Compute $f_0^i$\\ from Eq.~(\ref{eq:f0})}} $\longrightarrow$  \framebox{\Longstack[l]{Compute $\bar{f}$\\ from Eq.~(\ref{eq:SNR_bar})}}
  $\longrightarrow$  \framebox{\Longstack[l]{Compute $T_{AW}=\tau_\text{insp}(\bar{f})$\\ from Eq.~(\ref{eq:tau_insp})}}
   \caption{Flow diagram summarizing our procedure for computing advance warning times $T_\text{AW}$ with the Advanced-LIGO-Virgo network. 
-  We will compute $T_\text{AW}$ for the case of $M=2.8M_\odot$ BNS system inspiralling at $D=50,100,200\,$Mpc. 
+  We compute $T_\text{AW}$ for BNS systems with $M=2.8M_\odot$ inspiralling at $D=50,100,200\,$Mpc. 
   %for A-LIGO and $D=200,400,1000\,$Mpc for the ET.
@@
  %
- We consider inspiralling BNS systems at $D=50,100,200\,$Mpc as our canonical sources for the ALV network.  
- %and BNS systems at $D=200, 400, 1000\,$Mpc for the ET network. 
- For each case, we compute $\bar{f}$ from Eq.(\ref{eq:SNR_bar}) with which we then compute $T_\text{AW}=\tau_\text{insp}(\bar{f})$.
   %
@@
 \be
-\bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2} \label{eq:SNR_bar_FINAL} .
-\ee
-%
-%
-We will introduce the expressions for ET's $\bar\rho_\text{tot},\bar\rho_F$ in Sec.~\ref{Sec:ETB}.
+\bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2} \label{eq:SNR_bar_FINAL}\, .
+\ee
+%
+%
+We will introduce the corresponding expressions for ET in Sec.~\ref{Sec:ETB}.
 To compute the SNRs defined above for the ALV network we require IFO noise data for which
-we use the ASD for the BNS-optimized A-LIGO design sensitivity expected to be attained ca. 2020 \cite{LIGO2020}. 
-This is plotted as the thick red solid curve in Fig.~\ref{fig:LIGO2020}.
-Sweeping across the detector's frequency bands are RMS-averaged GW strains ($\tilde{H}_m$) due to BNS inspirals at various luminosity distances.
-Each RMS-averaged strain is accompanied by its shaded region ranging from an optimally oriented strain ($\tilde{H}_h$) to a sub-optimally oriented strain ($\tilde{H}_l$).
-These regions were first explained in Sec.~\ref{sec:GW170817} and shown in Fig.~\ref{fig:figGW170817}.
-Recall that this is our way of representing the response of a three-IFO network to a single source, i.e., we map three different IFO responses due to a single source to a single IFO's response to three different sources differing in amplitudes as listed in Table~\ref{table:network_params}.
+we use the ASD for the BNS-optimized A-LIGO design sensitivity expected to be attained ca.~2020 from Ref.~\cite{LIGO2020},
+which is plotted as the thick solid (red) curve in Fig.~\ref{fig:LIGO2020}.
+Sweeping across the detector's frequency band are RMS-averaged GW strains ($\tilde{H}_m$) due to BNS inspirals at $D=50,100,200\,$Mpc plotted from top to bottom, respectively (recall we plot $2\sqrt{f}\tilde{H}_i$ against detector noise).
+Each RMS-averaged strain is accompanied by its shaded region ranging from a near-optimally oriented strain ($\tilde{H}_h$) to a sub-optimally oriented strain ($\tilde{H}_l$) which were explained in Sec.~\ref{sec:GW170817} and first shown in Fig.~\ref{fig:figGW170817}.
 The height of a given strain above the detector sensitivity provides a good \emph{visual} estimation for the corresponding SNR,
-but the reader should keep in mind that the actual computation involves a ratio, not a difference, as shown, e.g., in Eq.~(\ref{eq:SNR}).
+but the reader should keep in mind that the actual computation involves the integral of a ratio, not a difference [cf. Eq.~(\ref{eq:SNR})].
 %
@@
 \subsubsection{Forecasting GRBs in the 2020s with the Advanced LIGO-Virgo Network}\label{Sec:ALIGO2020}
-We now compute the advance warning times that A-LIGO can provide us in the case of BNS inspirals at $D=50, 100,200\,$Mpc.
-Fig.~\ref{fig:LIGO2020} displays the strains due to these inspirals in the same fashion as
-Fig.~\ref{fig:figGW170817}: the solid (black), dotted (blue), and dashed (green) lines represent the RMS-averaged characteristic strains, $2\sqrt{f}\tilde{H}_m(f)$, at luminosity distances of $D=50, 100, 200\,$Mpc, respectively, with the shaded regions covering the range
-between the optimally oriented case and the sub-optimal case.
+%We now compute the advance warning times that the ALV network can provide us in the case of BNS inspirals at luminosity distances of $50, 100,200\,$Mpc.
+%Fig.~\ref{fig:LIGO2020} displays the strains due to these inspirals in the same fashion as
+%Fig.~\ref{fig:figGW170817}: the solid (black), dotted (blue), and dashed (green) lines represent the RMS-averaged characteristic strains, $2\sqrt{f}\tilde{H}_m(f)$, at %luminosity distances of
+%$D=50, 100, 200\,$Mpc, respectively, with the shaded regions covering the range
+%between the near-optimal and the sub-optimal cases.
 %
@@
 \includegraphics[width=\linewidth]{../Figures/ALigo_strains.pdf}
-\caption{Typical $M=2.8 M_\odot$ BNS inspirals sweeping across the Advanced LIGO-Virgo network in the 2020s.
-These may be the harbingers of short GRBs.
+\caption{Typical $m_1=m_2=1.4 M_\odot$ BNS inspirals sweeping across the Advanced LIGO-Virgo network in the 2020s.
+These may be the harbingers of short-hard GRBs.
 %inspiralling BNS systems sweeping across the most sensitive interferometer frequencies.
 The solid (black), dotted (blue), and dashed (green) lines are the RMS-averaged strains ($2\sqrt{f}\tilde{H}_m(f)$) at luminosity distances of $D=50, 100, 200\,$Mpc, respectively.
-The accompanying shaded regions cover the region of likelihood for a three-IFO network as explained in Fig.~\ref{fig:figGW170817}.
+The accompanying shaded regions span from the near-optimally oriented IFO
+($2\sqrt{f}\tilde{H}_h(f)$) to
+sub-optimally oriented IFO ($2\sqrt{f}\tilde{H}_l(f)$) as explained in Fig.~\ref{fig:figGW170817}.
 The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals,
-but as can be seen, the SNR hardly increases beyond $\sim 1000\,$Hz.
+but as can be seen, the SNRs hardly increase beyond $\sim 1000\,$Hz.
 %Recall that we deliberately neglect the tidal and strong-field effects that modify the plotted $f^{-2/3}$ power law beyond $\sim 100\,$Hz.
@@
 
-The computation follows the procedure outlined in Fig.~\ref{fig:flow}. We use numerical root finding to determine $\bar{f}$ and $f_0^i$ for all three values of $D$. 
-The computation of SNRs and advance warning times is straightforward. 
+The advance warning time computation follows the procedure outlined in Fig.~\ref{fig:flow}. We use numerical root finding to determine $\bar{f}$ and $f_0^i$ for all three values of $D$. 
+The computation of SNRs and $T_\text{AW}$ is then straightforward. 
 We summarize our results in Table \ref{table:LIGO2020} where we present both the 0PN and the 3.5PN results for the advance warning times
 $T_\text{AW}$. As can be seen from the values for $T_\text{AW}$ in the table, we can at best expect 85\,seconds of early warning time.
-This time increases to 2\,minutes in the case of another GW170817-like event with $D=40\,$Mpc.
-The current best estimate for the event rate of BNS inspirals is $ 1540^{+3200}_{-1220}\,$Gpc$^{-3}$yr$^{-1}$, inferred from the O1 and O2 observing periods of Advanced LIGO \cite{GW170817}.
+This time increases to approximately two\,minutes in the case of another GW170817-like event with $D=40\,$Mpc.
+We can estimate the likelihood of such an event happening again
+using the current best estimate for the BNS inspiral rate 
+inferred from the O1 and O2 observing periods of Advanced LIGO: $ R=1540^{+3200}_{-1220}\,$Gpc$^{-3}$yr$^{-1}$ \cite{GW170817}.
 This translates to $\approx 0.1$ event per (40-Mpc)$^3$ per year with the upper limit $\approx 0.3$. So we can at best hope to detect
 one 40-Mpc inspiral per a three-year period.
-Therefore, we do not expect to be able forecast GRBs in the Advance LIGO-Virgo era given that we might at best have a couple of minutes of warning time. 
+Therefore, we do not expect to be able forecast GRBs in the Advanced LIGO-Virgo era given that we might at best have a couple of minutes of warning time. 
 %we prefer to remain optimistic about the prospects of forecasting at least one GRB in the 2020s. %that this latency can be reduced to minutes.
@@
 \hline
-50 & 25.3 & & 84.25 & & 85.86 & 70.3 \T\\
-100 & 41.6 & & 22.39 & & 22.86 & 35.2 \\
-200 & 121.3 & & 1.291 &\quad & 1.300 & 17.6 \\
+50 & $\approx\,$25.3 & & 84.25 & & 85.86 & 70.3 \T\\
+100 & $\approx\,$41.6 & & 22.39 & & 22.86 & 35.2 \\
+200 & $\approx\,$121 & & 1.291 &\quad & 1.300 & 17.6 \\
 \hline
 \end{tabular}
-\caption{The Advanced LIGO-Virgo (ALV) network's potential for providing advance warning times, $T_\text{AW}$, 
-to electromagnetic observatories for inspiralling binary neutron stars at luminosity distances of $D=50,100,200\,$Mpc. 
-$\bar{f}$ is the frequency at which the  signal-to-noise ratio (SNR) accumulated by the ALV network reaches 15. 
-$\bar{\rho}_F$ is the total accumulated network SNR for each inspiral. We present both the Newtonian (0PN) 
-and the 3.5 post-Newtonian result for the advance warning times.}\label{table:LIGO2020}
+\caption{The ALV network's potential for providing advance warning times, $T_\text{AW}$, 
+to electromagnetic observatories for the case of $m_1=m_2=1.4 M_\odot$ BNS inspirals at luminosity distances of $D=50,100,200\,$Mpc. 
+$\bar{f}$ is the frequency at which the  %signal-to-noise ratio
+SNR accumulated by the network reaches 15. 
+$\bar{\rho}_F$ is the total accumulated network SNR. %for each inspiral. 
+We present both the Newtonian (0PN) 
+and the 3.5PN result for the advance warning times.}\label{table:LIGO2020}
 \end{table}
@@
 As the measurement errors for the system parameters are proportional to $\bar\rho^{-1}_F$ \cite{Cutler:1994ys},
-systems that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
+inspirals that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
 $M_c, M$ \cite{Farr:2015lna}; (ii) sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};
@@
 \be
-\bar\rho_{\text{ET}}(f_0,f)\equiv \f{36}{25}A^2 h_0^2\, (1+z)^{-1/3}\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')} \label{eq:ET_SNRv2},
+\bar\rho_{\text{ET}}(f_0,f)\equiv \f{6}{5}A h_0\, (1+z)^{-1/6}\left[\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')}\right]^{1/2} \label{eq:ET_SNRv2},
 \ee
@@
  \be
- \sqrt{S^\text{ET}_\text{n}(f_0)} = 2\sqrt{f_0}\, \tilde{H}_\text{ET}(f_0, D) \label{eq:f0_ET}\,
- \ee
- %
-with $\tilde{H}_\text{ET}(f, D)$ given by the redshifted version of Eq.~(\ref{eq:H_delta})
-%
-\be
-\tilde{H}_\text{ET}(f, D) = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\f{1}{(1+z)}\left(\f{G \mathcal{M}_c}{c^3}\right)^{5/6} f^{-7/6}\, , \label{eq:H_delta_redshifted}
+ \sqrt{S^\text{ET}_\text{n}(f_0)} = 2\sqrt{f_0}\, \tilde{H}_\text{ET}(f_0) \label{eq:f0_ET}\,
+ \ee
+ %
+with $\tilde{H}_\text{ET}(f)$ given by the redshifted version of Eq.~(\ref{eq:H_delta})
+%
+\be
+\tilde{H}_\text{ET}(f) = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\f{1}{(1+z)}\left(\f{G \mathcal{M}_c}{c^3}\right)^{5/6} f^{-7/6}\, , \label{eq:H_delta_redshifted}
 \ee
@@
 The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the redshift-corrected
-RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}(f,D)$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
+RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}(f)$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
 The vertical lines with correspondingly identical patterns (colors) mark the redshifted ISCO frequencies ($(1+z)^{-1} f_\text{ISCO}$) at which point we terminate each inspiral.
@@
 %
-where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively.
-$\bar{f}_\text{ET}$ then gives us our redshift-accounted advance warning time via $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp_redshifted}) which we can slightly improve by using the 3.5PN expression.
+%
+which then gives us our redshift-accounted advance warning time via $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp_redshifted}) which we can slightly improve by using the 3.5PN expression.
 Therefore, we proceed as summarized in Fig.~\ref{fig:flow} and compute the 0PN and 3.5PN advance warning times 
 for all four inspirals in both the ET-B and ET-C bands.
-The latter computation involves rescaling the PN parameters $x$ and $\Theta$ to $(1+z)^{2/3} x$ and $(1+z)^{-1}\Theta $ (see Sec.~9.3 of 
+The 3.5PN computation requires rescaling of the PN parameters $x$ and $\Theta$ to $(1+z)^{2/3} x$ and $(1+z)^{-1}\Theta $ (see Sec.~9.3 of 
 Blanchet's review \cite{Blanchet_LRR} for details).
@@
 %
+where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively for $D=100,200,400, 1000\,$Mpc.
 Table~\ref{table:ET} summarizes our results for both ET-B and ET-C where we chose to only display the 3.5PN-accurate inspiral time as $T_\text{AW}$,
-but we computed this quantity via both 0PN and 2PN expressions as a check.
+but we computed this quantity using both 0PN and 2PN expressions as a consistency check.
 
@@
 \hline
-{}& $\bar{f}\,$(Hz) & \ \hspace{7mm} $T_\text{AW}$ \ \hspace{7mm} & $\bar{\rho}_{F}$ &{} & $\bar{f}\,$(Hz) & \ \hspace{5mm} $T_\text{AW}\hspace{12mm}$& $\bar{\rho}_{F}$\T\B\\
+{}& $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{7mm} $T_\text{AW}$ \ \hspace{7mm} & $\bar{\rho}_{F}$ &{} & $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{5mm} $T_\text{AW}\hspace{12mm}$& $\bar{\rho}_{F}$\T\B\\
 %midrule
-100 & $\approx\,$6.72 &  47.0\,minutes & 306.0 &{\qquad} & $\approx\,$3.27 & 5.34\,hours\ & 365.4\T\\
-200 & $\approx\,$11.2 & 11.6\,minutes & 152.4 &{\qquad} & $\approx\,$4.10 & 2.87\,hours\ & 182.1 \\
-400 & $\approx\,$18.2 & 3.00\,minutes & 75.74 &{\qquad} & $\approx\,$5.06 & 1.51\,hours\ & 90.48\\
-1000 & $\approx\,$41.3 &17.2\,seconds & 29.79& \qquad &    $\approx\,$6.76 & 35.6\,minutes & 35.60  \\
+100 & $\approx\,$6.72 &  47.0\,minutes & 306 &{\qquad} & $\approx\,$3.27 & 5.34\,hours\ & 365\T\\
+200 & $\approx\,$11.2 & 11.6\,minutes & 152 &{\qquad} & $\approx\,$4.10 & 2.87\,hours\ & 182 \\
+400 & $\approx\,$18.2 & 3.00\,minutes & 75.7 &{\qquad} & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
+1000 & $\approx\,$41.3 &17.2\,seconds & 29.8& \qquad &    $\approx\,$6.76 & 35.6\,minutes & 35.6  \\
 % OLD version
@@
 \end{tabular}
-\caption{Forecasting capabilities of Einstein Telescope summarized. We can expect over \emph{five} hours of early warning for nearby sources. 
-ET-B and ET-C refer the different configurations shown in Fig.~\ref{fig:ETB2030}.
+\caption{Forecasting capabilities of Einstein Telescope summarized. 
+%We can expect over \emph{five} hours of early warning for nearby sources. 
+ET-B and ET-C refer to the different configurations shown in Fig.~\ref{fig:ETB2030}.
 For the advance warning times, we only present the result of the more accurate 3.5PN computation.
-$\bar{f}$ is the threshold frequency at which
+$\bar{f}_\text{ET}$ is the threshold frequency at which
 ET-B/C accumulate SNR of 15 which we take to be our detection criterion. Note that both $T_\text{AW}$ and $\bar\rho_F$ are larger for ET-C
@@
 %
-As the results of Table~\ref{table:ET} indicate, ET-B will provide $\sim 10 - 50\,$ minutes of warning time for BNS inspirals at $D\lesssim 200\,$Mpc.
+As the results of Table~\ref{table:ET} indicate, ET-B will provide $\gtrsim 10\,$ minutes of warning time for BNS inspirals at $D\lesssim 200\,$Mpc.
 Instead of speculating whether or not this is enough to forecast GRBs, we turn our attention to ET-C's forecasting capabilities.
@@
 This is best highlighted by the sixth colum of Table~\ref{table:ET}, 
-where we show that ET-C will provide up to five hours of early warning time for nearby ($D\lesssim 100\,$Mpc) neutron star mergers.
+where we show that ET-C will provide up to \emph{five hours} of early warning time for nearby ($D\lesssim 100\,$Mpc) neutron star mergers.
 Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's horizon distance) will persist in the ET-C sensitivity band for a few hours after their initial detection.
 Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET.
-Given Moore's law and new search approaches based on deep learning (\cite{Gabbard:2017lja}) we speculate
-that the advances in the detection, localization and early-warning algorithms in the next decade will reduce the required early
-warning time to less than an hour; thus we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS horizon distances of $D_H=87,613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
-In other words, all inspiralling BNSs closer than $D_H$ will give us more than an hour's leeway before the GRB (assuming detection SNR of 15 as always).
-The volume set by $D=D_H$ translates to a BNS merger rate of $\mathcal{O}(1)$ for ET-B and
+
+Given Moore's law and new search approaches (e.g., see Ref.~\cite{Gabbard:2017lja} for one based on deep learning) 
+we speculate that the advances in the detection, localization and early-warning algorithms in the next decade will reduce the required advance
+warning time to less than an hour; thus we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS horizon distances of $D_H=87$ and $613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
+In other words, all inspiralling BNSs closer than $D_H$ will give us more than an hour's leeway before the GRB (employing the detection criterion $\text{SNR} =15$ as before).
+The volume set by $D=D_H$ translates to a BNS merger rate of $\sim\mathcal{O}(1)$ for ET-B and
 $\approx 355^{+730}_{-280}\,\text{year}^{-1}$ for ET-C. Additionally, each source within $D_H$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
@@
 Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. Given that
-it takes $\gtrsim \mathcal{O}(1)\,$\emph{day} for a BNS source to inspiral from $f_0\sim 1\,$Hz to $\bar{f}$ of Eq.~(\ref{eq:ET_fbar}),
-we can expect ET to localize sources within the horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
-As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
-(this is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}).
-It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
-to alert the electromagnetic observatories within an hour of the initial detection (SNR = 15). 
-Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens of gamma ray bursts.
-We summarize our major findings for both the ALV network and ET-B/C in Fig.~\ref{fig:summary}.
+it takes $\gtrsim \mathcal{O}(1)\,$\emph{day} for a BNS source to inspiral from $f_0\sim 1\,$Hz to $\bar{f}_\text{ET}$ of Eq.~(\ref{eq:ET_fbar}),
+we can expect ET to localize sources within its horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
+Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens of gamma ray bursts
+\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
+(this is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}).}.
+%It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
+%to alert the electromagnetic observatories within an hour of the initial detection (SNR = 15). 
+%
+We summarize our main findings for both the ALV network and ET-B/C in Fig.~\ref{fig:summary}.
 %
@@
 \caption{Horizon distances of ET-B and ET-C assuming $T_\text{AW} =1\,$hour. $R(D_H)$ is the BNS merger rate within a volume of $D_H^3$
-obtained by rescaling the rate inferred from GW170817 \cite{GW170817}.
-$\bar\rho_F(D_H)$ is the total SNR accumulated in ET by a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
+obtained by rescaling the rate inferred from Advanced LIGO's O1, O2 observing periods \cite{GW170817}.
+$\bar\rho_F(D_H)$ is the total SNR accumulated in ET due to a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
 \end{table}
@@
 \caption{Summary of our major findings for both the Advanced-LIGO-Virgo (ALV) network circa 2020 and the Einstein Telescope's B and C configurations
-ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV network (dotted), ET-B (dashed), and ET-C (solid), respectively.
-The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (brown) lines coming from the $D^{-2}$ powerlaw in the SNR [see Eq.~(\ref{eq:ET_SNRsq}] which is plotted on the right axis.
-We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D\ge 100\,$Mpc for the ET results.}\label{fig:summary}
+ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV2020 (dotted), ET-B (dashed), and ET-C (solid), respectively.
+The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (brown) lines coming from the $D^{-1}$ powerlaw of the SNR [see Eq.~(\ref{eq:ET_SNRv2})] which is plotted on the right axis.
+We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D=100,200,400,1000\,$Mpc for the ET results.}\label{fig:summary}
 \end{figure}
-
+%
+%
+%
 % LISA does not see these sources, not sensitive enough!
-
+%
+%
 \section{Binary black hole neutron star systems}\label{sec:BH_NS}
@@
 \ee
-where $r$ is the orbital separation, $R_\text{NS}$ is the radius of the NS and $M$ denotes masses. 
+where $r$ is the orbital radius, $R_\text{NS}$ is the radius of the NS and $M$ denotes masses. 
 $c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to leading order with
 $c_R >1 $. %Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, 
-We can roughly take the above condition to be
+The above conditions roughly implies
 %
@@
  However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
- \item Low black hole mass. In the geodesic case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}^{-2}$. 
- Hence, $M_\text{BH}$ must also be minimized. Once again, there is a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models.
- Current consensus for this lower bound yields $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
+ \item Low black hole mass. In the geodesic case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
+ Hence, $M_\text{BH}$ must also be minimized. 
+ As was the case with $r$, there is also a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models, which currently yield $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
  \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
- For instance, for the maximum dimensionless spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value ($6GM_\text{BH}/c^2$) whereas for $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
+ For instance, for the maximum dimensionless BH spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value ($6GM_\text{BH}/c^2$) whereas for $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
  With smaller ISCO separation, there is much more tidal force exerted on the NS before it plunges in.
  \item Less compact neutron stars. Eq.~(\ref{eq:TD_cond1}) can be rearranged to isolate $c_\text{NS}$
- on the right hand side. Smaller values for $c_\text{NS}$ mean that TD can occur for $r>r_\text{ISCO}$.
+ on the right hand side. Smaller values for $c_\text{NS}$ mean that TD is more likely to occur for $r>r_\text{ISCO}$.
 \end{enumerate}
@@
  $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q\to Q^{-2/3}$ as $Q\to\infty$ for $Q\equiv m_2/m_1 > 1$, i.e., heavier binaries inspiral faster.
- As we set $M_\text{NS}=1.4 M_\odot$, $c_\text{NS}$ is determined by the radius of the NS constrained in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
- which translates to $0.13\lesssim c_\text{NS} \lesssim 0.15$. We also have $Q  \simeq 3.571$.
+ We once again set $M_\text{NS}=1.4 M_\odot$ thus $Q=5/1.4  \simeq 3.571$. $c_\text{NS}$ is determined by the radius of the NS constrained in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
+ which results in $0.13\lesssim c_\text{NS} \lesssim 0.15$ 
+ for our chosen NS mass.
 %As we wish to avoid discussing the details of the strong-field evolution of the binary, we borrow certain results from the literature to
 %justify our choice for the chosen parameters above. 
-If we pick the more pessimistic $c_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $a\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}.
+If we pick the more pessimistic $c_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $a\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}
 and $Q< 3$ in the case of $a=0$ \cite{Kyutoku:2011vz}.
+
 Although the results from each numerical study may somewhat vary what is clear is that we must have high spin and low black hole mass.
 This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
-they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, it will have to gain mass.
+they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, thus they will have to gain mass.
 It is possible that the mass gain pushes $Q$ too high to either cause a direct plunge of the NS before TD or decrease $\tau_\text{insp}$ considerably
 to eliminate any chances of getting an advance warning.
-However, if the spin of the BH comes from the supernova explosion mechanism itself (as argued for G1915 in Ref.~\cite{McClintock:2006xd} then this is not a problem.
-
-So we will simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
+However, if the spin of the BH comes from the supernova explosion mechanism itself as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
+low-mass BH in a binary system.
+
+Therefore, we simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
 A quick calculation shows that these systems yield $T_\text{AW} \lesssim 30\,$seconds in the ALV network of 2020s. %in Table \ref{table:LIGO2020}is now less than $ 40\,$ seconds. 
@@
 \caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
-The SNR is even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
+The SNRs are even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
 \end{table}
@@
 %
-\\
-\noindent
+
 From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
 Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
-there could be 28.8 such mergers per year within ET-C's horizon distance of $\approx 200\,$Mpc corresponding roughly to $T_\text{AW}\approx1\,$hour.
+there could be $\approx 30$ such mergers per year within ET-C's horizon distance of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
 We must emphasize that this should be viewed
@@
 We showed that we do not expect the Advanced-LIGO-Virgo network to provide such a forecast in the 2020s unless we get extremely lucky
-and detect a BNS inspiral in our galaxy which is roughly a one-in-a-trillion shot (in years). %($\sim 1$ per trillion years lucky).
+and detect a binary neutron star inspiral in our galaxy, which is roughly a one-in-a-trillion shot (in years). %($\sim 1$ per trillion years lucky).
 However, the odds completely change in our favour with Einstein Telescope's B and especially C configurations, 
-the latter of which is expected to forecast $\gtrsim \ord(10^2)$ GRBs per year as we show in Table~\ref{table:horizon}. 
+the latter of which is expected to forecast $\gtrsim \ord(10^2)$ gamma-ray bursts per year as we show in Table~\ref{table:horizon}. 
 The same configuration should also forecast up to three tidal disruption events per year in which a high-spin, low-stellar-mass
@@
 Additionally, there are proposals to launch another space interferometer called DECIGO which will operate
-between $0.1$ and 10 Hz thus bridging the gap between LISA and the ground-based interferometers \cite{Sato:2009zzb, Kawamura:2006zz}.
+in the $0.1 - 10\,$Hz range thus bridging the gap between LISA and the ground-based interferometers \cite{Sato:2009zzb, Kawamura:2006zz}.
 With the gravitational-wave sky virtually covered from $10^{-4}$ to $10^3\,$Hz, we will suffer from the 

### 2018-04-02 Paper/Manuscript.tex
Updates

@@
 %
-We are thus led to set $M_\text{BH} =5 M_\odot$. There is additional motivation to choose low BH mass as 
- $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q\to Q^{-2/3}$ as $Q\to\infty$ for $Q\equiv m_2/m_1 > 1$, i.e., heavier binaries inspiral faster.
- We once again set $M_\text{NS}=1.4 M_\odot$ thus $Q=5/1.4  \simeq 3.571$. $c_\text{NS}$ is determined by the radius of the NS constrained in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
+
+Although the results from each numerical study may somewhat vary what is clear is that we must have high spin and low black hole mass. We are thus led to set $M_\text{BH} =5 M_\odot$. 
+This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
+they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, thus they will have to gain mass.
+It is possible that the mass gain pushes $M_\text{BH}$ too high to either cause a direct plunge of the NS before TD or decrease $\tau_\text{insp}$ considerably
+to eliminate any chances of getting an advance warning.
+However, if the spin of the BH comes from the supernova explosion mechanism itself as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
+low-mass BH in a binary system\footnote{We thank Dr. Morgan Fraser
+for pointing this out.}.
+
+There is additional motivation to choose low BH mass as 
+ $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv M_\text{BH}/M_text{NS} > 1$, which scales as $Q^{-2/3}$ as $Q\to\infty$ , i.e., heavier binaries inspiral faster.
+ We once again set $M_\text{NS}=1.4 M_\odot$ giving $Q=5/1.4  \simeq 3.571$. $c_\text{NS}$ is determined by the radius of the NS constrained in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
  which results in $0.13\lesssim c_\text{NS} \lesssim 0.15$ 
@@
 
-Although the results from each numerical study may somewhat vary what is clear is that we must have high spin and low black hole mass.
-This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
-they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, thus they will have to gain mass.
-It is possible that the mass gain pushes $Q$ too high to either cause a direct plunge of the NS before TD or decrease $\tau_\text{insp}$ considerably
-to eliminate any chances of getting an advance warning.
-However, if the spin of the BH comes from the supernova explosion mechanism itself as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
-low-mass BH in a binary system.
-
-Therefore, we simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
+So, we simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
 A quick calculation shows that these systems yield $T_\text{AW} \lesssim 30\,$seconds in the ALV network of 2020s. %in Table \ref{table:LIGO2020}is now less than $ 40\,$ seconds. 

### 2018-04-03 Paper/Manuscript.tex
Finished 2nd read through

@@
 
-\title{Forecasting Gamma-ray Bursts using Gravitational Waves}
+\title{Forecasting Gamma-Ray Bursts using Gravitational Waves}
 
@@
 promptly followed, 1.7 seconds later, by a gamma-ray burst (GRB170817A) detected by the Fermi Gamma-ray Burst Monitor \cite{Fermi} and by the International Gamma-Ray Astrophysics Laboratory \cite{Svinkin, Savchenko:2017ffs}.
-The Advanced-LIGO-Virgo network's initial source localization to within $\sim 31\,\text{degree}^2$ in the Southern skies
+The Advanced-LIGO-Virgo network's initial source localization to within $ 31\,\text{degree}^2$ in the Southern skies
 enabled astronomers to locate the electromagnetic counterpart in the galaxy NGC 4993, 
@@
 using a template bank of gravitational waveforms computed within the framework of post-Newtonian theory \cite{Buonanno:2009zt, Blanchet_LRR}.
-The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from $\sim 30\,$Hz to $\sim 2\,$kHz in 57 seconds
-executing $\sim 3000$ gravitational wave cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
+The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from approximately $ 30\,$Hz to about $ 2\,$kHz in 57 seconds
+executing nearly $ 3000$ gravitational wave cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
 The total mass of the system was inferred to be $2.74^{+0.04}_{-0.01} M_\odot$ with component masses in the range $1.17-1.60 M_\odot$ consistent
 with neutron stars (assuming low spin priors, see Sec.~\ref{sec:idealizations}).
-Moreover, both the gravitational wave (GW) and EM observations are consistent with a source luminosity distance of $\sim 40\,$Mpc
-and support the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
+Moreover, both the gravitational wave (GW) and EM observations were consistent with a source luminosity distance of $\sim 40\,$Mpc
+and supported the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
 causing the prompt short-hard gamma-ray burst (GRB170817A) in NGC4993 as first suggested by Ref.~\cite{Eichler:1989ve}.
@@
 scheduled to start in Autumn 2018 with roughly twice the sensitivity of O2.
-In addition, the Japanese cryogenic interferometer KAGRA (\cite{KAGRA, KAGRA2}) will start its test runs in 2018-2019 and reach design sensitivity circa 2021-2022 \cite{Akutsu:2017thy, Aasi:2013wya}.
-By 2025, LIGO-India detector will join the global interferometer network hence improving both the overall sensitivity and the sky-localization capabilities of the interferometer network \cite{Aasi:2013wya}.
+In addition, the Japanese cryogenic interferometer KAGRA (\cite{KAGRA, KAGRA2}) will start its test runs in 2018-2019 and reach its design sensitivity circa 2021-2022 \cite{Akutsu:2017thy, Aasi:2013wya}.
+By 2025, LIGO-India detector will join the global interferometer network hence improving both the overall sensitivity and the sky-localization capabilities \cite{Aasi:2013wya}.
 Around this time, the construction of the first third-generation ground-based interferometer, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
 Meanwhile, the US is currently considering a mid-2020s update to LIGO called Voyager \cite{LIGO_Voy} and the construction of a more ambitious 40\,km long interferometer dubbed The Cosmic Explorer \cite{CE}.
-All of these near-future improvements to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
+All of these near-future additions to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
 early enough to witness a gamma-ray burst as it happens? In other words, can we forecast GRBs using GW detections?
@@
 In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd}.
-It then took an additional $\sim 10$ hours to locate the optical transient. %designated AT 2017gfo.
+It then took an additional $ 10$ hours to locate the optical transient. %designated AT 2017gfo.
 
@@
 used in the ALV pipeline).
-We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time difference
-between the merger and the instant of detection (detector trigger) defined in terms of a certain threshold signal-to-noise ratio.
+We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time interval
+between the merger and the instant of detection defined in terms of a certain threshold signal-to-noise ratio.
 To this end, we consider the ALV network of 2020s composed of three L-shaped interferometers operating at their design sensitivities
-and Einstein Telescope of 2030s made up of triangular interferometers.
+and Einstein Telescope of 2030s made up of V-shaped interferometers.
 Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distances
@@
 the GW emission from the system due to the time variance of the quadrupole moment of the binary.
-Though the Newtonian (leading-order) evolution is better than $ 95\%$ accurate
-we nonetheless supplement it with results from post-Newtonian theory up to 3.5 post-Newtonian order \cite{Blanchet_LRR}.
-The evolution of a BNS system in the strong-field regime, where speeds $\gtrsim 0.1c$, is a very complex and complicated problem requiring fully relativistic, magnetohydrodynamic codes 
+Though the Newtonian (leading-order) treatment gives the 
+inspiral time with better than $ 95\%$ accuracy,
+we nonetheless supplement it with post-Newtonian corrections up to 3.5 post-Newtonian order (3.5PN) \cite{Blanchet_LRR}.
+However, even that fails to provide an accurate depiction of the binary
+evolution in the strong-field regime, where speeds $\gtrsim 0.1c$. This is a very complex and complicated problem requiring fully
+numerical treatment formulated in terms of general relativistic, magnetohydrodynamic codes 
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
 (see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm} for the latest developments and references therein).
-Despite its simplicity, our quadrupole radiation driven adiabatic
+Despite its failures, our quadrupole radiation driven Newtonian
 evolution is more than sufficient to provide reliable estimations of advance warning times.
@@
 Sec.~\ref{sec:idealizations} lists the various idealizations we employ to simplify our treatment and supplies justification for each.
-Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding GW data.
+Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding observations.
 Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020}, \ref{table:ET}; 
@@
 e.g., $\pi \simeq 3.142$, $\pi \approx 3$, $\pi \sim \ord(1)$. %Kepler's third law: $f_K^2\sim r^{-3}$.
-Overdots denote time derivative with respect to detector-frame time, e.g., $\dot{E} =dE/dt$, and $\propto$ denotes proportionalities. 
+Overdots denote time derivatives with respect to detector-frame time, e.g., $\dot{E} =dE/dt$, and $\propto$ denotes proportionalities. 
 Unless otherwise noted, we use standard SI units.
@@
 is the expression for the power emitted in GWs given by 
+the celebrated Einstein quadrupole formula \cite{1918SPAW}
 %for the generated by the time-variance of the mass quadrupole moment
@@
 %
-This is the celebrated Einstein quadrupole formula \cite{1918SPAW}. 
 Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
@@
 
-Here, we are specifically interested in the motion of two point masses in bound motion around a common center of mass.
-Labelling the masses by $m_1 \le m_2$, we have, for a binary in a circular orbit with Keplerian angular frequency $\Omega$ and separation $2r$,
+Here, we are specifically interested in the motion of two point masses in a circular orbit around a common center of mass.
+Labelling the masses by $m_1 \le m_2$, we have, for a binary in a circular orbit with Keplerian angular frequency $\Omega$ and separation $r$,
 %
@@
 referred to as the dimensionless inverse separation $x$.
-As $x\sim v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from in Eq.~(\ref{eq:Edot2}) that $\dot{E}\sim x^5$. 
+As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from in Eq.~(\ref{eq:Edot2}) that $\dot{E}\propto x^5$. 
 %hence the common statement in the literature saying that gravitational radiation starts
 
-The emission of power in GWs decreases the total energy of the binary thus making the orbit more bound. 
-The total (binding) energy of the binary is given by
-%
-\be
-E_b = -\frac{G m_1 m_2}{2r}\,  \label{eq:binding_energy1}
-\ee
-%
-giving $\dot{E}_b \propto \dot{r}/r$; hence $\dot{E}_b < 0$ implies $\dot{r}<0$, i.e, the orbital separation decreases in time.
+The emission of power in GWs decreases the total energy of the binary given by
+%
+\be
+E_b = -\frac{G m_1 m_2}{2r}\,.  \label{eq:binding_energy1}
+\ee
+%
+$\dot{E}_b \propto \dot{r}/r^2$, so $\dot{E}_b < 0$ implies $\dot{r}<0$, i.e, the orbital separation decreases
+making the orbit more bound in time.
 Using Kepler's third law, $ \Omega^2 = G M r^{-3}$, and Eq.~(\ref{eq:chirp_mass}) we obtain
@@
 This can be integrated straightforwardly after defining a new time variable $\tau\equiv t_\text{coal}-t$ that equals zero when the neutron stars coalesce.
-We can now define an inspiral time at a given GW frequency
+Using $\tau$ we can now define an inspiral time at a given GW frequency
 %
@@
 where $\Phi_0 \equiv \Phi(t=t_\text{coal})$ is an integration constant. The subscript N denotes the Newtonian (leading-order) contribution. 
-Higher-order contributions can be added in terms a post-Newtonian series, which make up $\lesssim 2\%$ of the total phase.
+Higher-order contributions can be added in terms a post-Newtonian series, which make up to $\lesssim 2\%$ of the total phase.
 Although we will include contributions up to and including 3.5PN to obtain the results of Sec.~\ref{sec:results}, 
@@
 The nomenclature ``plus'' ($+$) and ``cross'' ($\times$) follows from the effects that passing GWs have on the plane transverse to their direction of propagation.
-If we were to conceive of an ``toy'' detector made up of a circular configuration of test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress the circular arrangement in a $+$ and $\times$ pattern which is the manifestation of the tidal strain of the GWs on the tranverse plane.
+If we were to conceive of a ``toy'' detector made up of a circular configuration of test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress the circular arrangement in a $+$ and $\times$ pattern
+with a $90^\circ$ phase difference.
+This is the manifestation of the tidal strain of the GWs on the tranverse plane.
 %which is why $h_{+},h_{\times}$ are often called GW strains. 
@@
 To compute the advance warning times we need to know how ``loud'' the binaries become as they sweep across the IFO's detection bandwidth.
-This is given by the signal-to-noise ratio (SNR) of the GWs in the detectors' data stream.
+This is given by the signal-to-noise ratio (SNR) of the GWs in the detectors' bandwidth.
 The SNR is computed in the frequency domain so we Fourier-transform the time-domain strains of Eqs.~(\ref{eq:hplus_TD}) and (\ref{eq:hcross_TD}) to obtain
@@
 
-The detection criterion we employ here is quantified in terms of the optimal signal-to-noise ratio SNR defined by
+The detection criterion we employ here is quantified in terms of the optimal SNR defined by
 %%
@@
 where $\sqrt{S_n(f)}$ is the {\it amplitude spectral density} (ASD) of the detector (also called spectral strain sensitivity, or simply, detector noise).
-It is usually this quantity that is shown in a typical interferometer strain sensitivity plot with the characteristic strain, $\tilde{H}_c(f)\equiv|2\tilde{h}(f)\sqrt{f}|$, 
+It is usually this quantity that is shown in a typical interferometer strain sensitivity plot with the characteristic strain, $|2\tilde{h}(f)\sqrt{f}|$, 
 due to various GW sources overlaid for comparison. 
@@
 %ASDs are given by $2\tilde{h}(f)\sqrt{f}$. This particular combination is called the characteristic strain. 
-We will show such plots in Secs.~\ref{sec:GW170817} and \ref{sec:results}.
+We show such plots in Secs.~\ref{sec:GW170817} and \ref{sec:results}.
 
@@
 As angles have zero averages in general, we can think of the RMS as the standard deviation ($\sigma =2/5$). 
-Therefore, $2\sigma= 4/5$ above the average (zero in this case) should statistically cover 95\% of the four-dimensional angle space. 
+%Therefore, $2\sigma= 4/5$ above the average (zero in this case) should statistically cover 95\% of the four-dimensional angle space. 
 %Finally, we add the case of an optimally-oriented, purely $+$-polarized source ($\psi=0,\iota=0$) that is directly overhead ($\theta=0$) simply resulting in 
@@
 \be
-\rho_\text{tot} = \left[{\sum_{i=1}^N \rho^2_i}\right]^{1/2} \label{eq:SNR_total}
-\ee
-%
-%%
-where Eq.~(\ref{eq:SNR_v2}) is employed to compute $\rho_i$ coming from individual interferometers each with a specific quality factor $Q_i$.
+\rho_\text{tot} = \left[{\sum_{i=1}^N \rho^2_i}\right]^{1/2}\, , \label{eq:SNR_total}
+\ee
+%
+%%
+where Eq.~(\ref{eq:SNR_v2}) is employed to compute $\rho^2_i$ of individual interferometers each with a specific quality factor $Q_i$.
 Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
-a \emph{model network} of three IFOs ($N=3$), where one is near-optimally oriented/positioned thus it is at $2\sigma$ above the average.
-The second IFO operates at the RMS average; thus its sensitivity is suppressed by a factor $2/5$ compared with the optimal $|Q| =1$ case.
+a \emph{model network} of three IFOs ($N=3$), where one is near-optimally oriented/positioned with $|Q|=2\sigma=4/5$.
+The second IFO operates at the RMS average; thus it has $|Q|=2/5$. %compared with the optimal $|Q| =1$ case.
 It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
@@
 from the optimal case by quality factors $|Q_i|= 4/5,2/5,$ and $4/5-\sqrt{2/5}$.
-
+%
 %as listed in Table~\ref{table:network_params}.
@@
 %
-To this, we introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
+Accordingly, we now introduce the norm of the frequency-domain strain (\ref{eq:strain_FD}) 
 %%
@@
 \centering
-\begin{tabular}{c|c|c|c}
- IFO$_i$ & GW strain %& $\langle |Q_i|^2\rangle$ 
- & $\tilde{A}_i$ & $\tilde{H}_i(f)$\\
+\begin{tabular}{c|c|c|c|c}
+ IFO$_i$  %& $\langle |Q_i|^2\rangle$ 
+ & $|Q_i|$ & $\tilde{A}_i$ & $\tilde{H}_i(f)$ & IFO response \\
  %\hline
  \hline
- 1 & high ($h$) &  $\tfrac{4}{5}A$ & $\tfrac{4}{5}A h_0\, f^{-7/6}$ \T\\
- 2 & medium ($m$) & $\tfrac{2}{5}A$ & $ \tfrac{2}{5}A h_0 \, f^{-7/6}$\B\T \\
- 3 & low ($l$)  & $\left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A$ & $ \left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A h_0 \, f^{-7/6}$\B \\
+ 1 &  $\tfrac{4}{5} $&  $\tfrac{4}{5}A$ & $\tfrac{4}{5}A h_0\, f^{-7/6}$ & high ($h$) \T\\
+ 2 &  $\tfrac{2}{5} $ & $\tfrac{2}{5}A$ & $ \tfrac{2}{5}A h_0 \, f^{-7/6}$ & medium ($m$)\B\T \\
+ 3 &  $\tfrac{4}{5}-\sqrt{\tfrac{2}{5}} $ & $\left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A$ & $ \left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A h_0 \, f^{-7/6}$& low ($l$) \B \\
  \hline
@@
 Our model for the Advanced-LIGO-Virgo network ca. 2020. %of three L-shaped interferometers (IFOs). 
+Column two shows the quality factor $Q_i$ for each IFO and column three the corresponding amplitude scalar $\tilde{A}_i$ introduced
+in Eq.~(\ref{eq:Hi_s}).
 Column four lists the magnitude of the frequency-domain strain at each IFO via Eq.~(\ref{eq:Hi_s}).
-The second column shows how loud the GW strain is at a given IFO due source sky position and IFO orientation. 
+The last column shows how loud the GW strain is at a given IFO due source sky position and IFO orientation. 
 %oriented/positioned an IFO is with respect to a compact binary source. 
@@
 %Medium is the RMS-averaged (one $\sigma$) response. 
-Recall $A= \pi^{-2/3} \sqrt{5/24}$. Maximum value for $\tilde{A}_i$ is 1, and minimum is 0.
+Recall $A= \pi^{-2/3} \sqrt{5/24}$. Maximum value for $|Q_i|$ is 1, and minimum is 0.
 %Note that for an interferometer where the angle between the arms is $\alpha$, $A$ rescales to $A\sin\alpha$.
@@
 Within this equilateral triangle, ET will consist of three V-shaped cryogenic interferometers housed underground to
-sigificantly reduce seismic and gravity-gradient noises \cite{ET_doc}.
+significantly reduce seismic and gravity-gradient noises \cite{ET_doc}.
 This closed topology will allow the detector to form a null stream completely devoid of a signal \cite{Sathyaprakash:2012jk},
 which can be used to rule out spurious events \cite{Wen:2005ui}.
-As we will show below, the response function and the quality factor of the triangular configuration are independent of the azimuthal angle $\phi$
+Additionally, as we show below, the response function and the quality factor of the triangular configuration are independent of the azimuthal angle $\phi$
 hence ET will have no blind spots \cite{Regimbau:2012ir}.
@@
 \begin{enumerate}
- \item {\it Neglecting strong-field gravity and finite-size effects.}
+ \item {\it Neglecting strong-field gravity.}
 As our aim here is to provide a good order-of-magnitude estimation for the advance warning times, we model the neutron stars as point masses %and carry out this treatment 
@@
 $\tau_\text{insp}(f=100\,\text{Hz})\simeq 2.161\,$seconds according to Eq.~(\ref{eq:tau_insp}).
-And even at $f=100\,$Hz, a $m_1=m_2=1.4M_\odot$ neutron-star binary has separation $2r\approx 310\,$km, which translates to a dimensionless strength of gravity of $\approx 1.3\%$.
+And even at $f=100\,$Hz, a $m_1=m_2=1.4M_\odot$ neutron-star binary has separation $r\approx 155\,$km, which translates to a dimensionless strength of gravity of $\approx 2.6\%$.
 This percentage is mostly accounted for by the post-Newtonian
 corrections to our Newtonian (leading order) evolution. 
-Here, we will go up to 3.5 post-Newtonian order (3.5pN) for our
+Here, we will go up to 3.5pN for our
 advance warning time computations.
@@
 \item {\it Truncating the inspiral at the Schwarzschild ISCO.}
-We artificially end the inspirals at the Schwarzschild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6M$ and angular frequency $\Omega_\text{ISCO}$ %= (M/r^3_\text{ISCO})^{1/2}$ in natural units,
+We artificially end the inspirals at the Schwarzschild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6GM/c^2$ and angular frequency $\Omega_\text{ISCO}$ %= (M/r^3_\text{ISCO})^{1/2}$ in natural units,
 given by Eq.~(\ref{eq:Sch_f_isco}) which translates to the following dominant-mode (quadrupole) GW frequency
@@
 for $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$ with frequency possibly up to 1.7\,kHz \cite{Marronetti:2003hx}, 
-however, there is no simple expression for it.
+however, there is no simple expression for it akin to Eq.~(\ref{eq:f_isco}) and its extraction from numerical simulations is a rather involved procedure.
 Therefore, we employ Eq.~(\ref{eq:f_isco}) as our cut-off for
@@
 Let us briefly explore what the cost of setting $m_1=m_2=1.4 M_\odot$ is for our calculations. 
-Including the error bars, the known range for neutron star masses runs from $\sim 0.5 M_\odot$ to $ \sim 3 M_\odot$ with the actual values restricted
-between $\sim 1 M_\odot$ and $\sim 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
-Of these measured masses, a subset comprised of double neutron stars (NSs), such as the famed Hulse-Taylor binary, have the smallest error bars with masses
-ranging from $\sim 1.2 M_\odot$ to $\sim 1.5 M_\odot$. 
+Including the error bars, the known range for neutron star masses runs from $\approx 0.5 M_\odot$ to $ \approx 3 M_\odot$ with the actual values restricted
+between $\approx 1 M_\odot$ and $\approx 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
+Of these measured masses, a subset comprised of double neutron stars, such as the famed Hulse-Taylor binary, have the smallest error bars with masses
+ranging from $\approx 1.2 M_\odot$ to $\approx 1.5 M_\odot$. 
 Additionally, the masses involved in GW170817 are inferred to be between $1.17 M_\odot$ and $1.60 M_\odot$ \cite{GW170817}.
@@
 the quantities of interest for us, which are %the GW/orbital frequency ($f/f_K$), %the radiated power in GWs ($\dot{E}$), the rate of change of GW/orbital frequencies ($\dot{f}$), 
-the inspiral time ($\tau_\text{insp}$), the GW strain at the detector in the frequency domain ($\tilde{H}$) and
+the inspiral time ($\tau_\text{insp}$), the frequency domain strain ($\tilde{H}$), and
 the frequency of the innermost stable circular orbit ($f_\text{ISCO}$) given by Eq.~(\ref{eq:f_isco}) above.
@@
 %$f=2f_K$ & $M^{1/2}$& $(m_1+m_2)^{1/2}$& $1.2 \le 1.41 \le 1.69 $\\
-$\tau_\text{insp}$ & $M_c^{-5/3} $ & $(m_1 m_2)^{-1}(m_1+m_2)^{-1} $&\quad& $0.335\le 0.5\le 0.794 $ \\
-$\tilde{H}$ & $M_c^{5/6} $ & $(m_1 m_2)(m_1+m_2)^{3/2} $&\quad& $ 0.7834\le 0.891 \le 0.996 $ \\
-$f_\text{ISCO}$ & $M^{-1} $ & $(m_1+m_2)^{-1} $&\quad& $0.4375\le 0.5\le 0.583 $\\
+$\tau_\text{insp}$ & $M_c^{-5/3} $ & $(m_1 m_2)^{-1}(m_1+m_2)^{-1} $&\quad& $0.335\le 0.5\le 0.794 $\T \\
+$\tilde{H}$ & $M_c^{5/6} $ & $(m_1 m_2)(m_1+m_2)^{3/2} $&\quad& $ 0.7834\le 0.891 \le 0.996 $ \T\B\\
+$f_\text{ISCO}$ & $M^{-1} $ & $(m_1+m_2)^{-1} $&\quad& $0.4375\le 0.5\le 0.583 $\B\\
 \hline
@@
 As our intent is to provide an estimation for advance warning times in terms of orders of magnitude, this variation is tolerable.
-Moreoever, it seems that the variation in mass tends to lengthen $\tau_\text{insp}$ more than shorten it thus our setting
+Moreoever, it seems that this variation tends to lengthen $\tau_\text{insp}$ more than shorten it thus our setting
 $m_1=m_2=1.4 M_\odot$ is more likely to underestimate $T_\text{AW}$ than overestimate it which is something we can live with.
-So we set the NS masses to equal $1.4 M_\odot$ henceforth.
+So we set $m_1=m_2=1.4 M_\odot$ henceforth.
 %
@@
 %is less than a second before the merger. 
-Thus, we can treat the binary's motion
-as quasi-circular for our estimations of advance warning times.
+%Thus, we can treat the binary's motion
+%as quasi-circular for our estimations of advance warning times.
 %
@@
 \item {\it Neglecting neutron star spins.}
-It is generally believed that NSs do not have large enough angular momentum to impart detectable spin effects into the GWs emitted by the BNS systems.
-The dominant effect due to the spins is the spin-orbit (SO) precession which contributes to the energy flux at the 1.5pN order [$\ord(v^3/c^3)$] with respect to the leading-order quadrupole $\dot{E}$ of Eq.~(\ref{eq:Edot}) \cite{Blanchet_LRR}.
+It is generally believed that neutron stars do not have large enough angular momentum to impart detectable spin effects into the GWs emitted by the BNS inspirals.
+The dominant effect due to the spins is the spin-orbit (SO) precession which contributes to the energy flux at the 1.5PN order [$\ord(v^3/c^3)$] with respect to the leading-order quadrupole $\dot{E}$ of Eq.~(\ref{eq:Edot}) \cite{Blanchet_LRR}.
 %Writing this contribution as a ratio to $\dot{E}$ and 
@@
 %
-where we introduced the dimensionless Kerr spin parameter $\chi\equiv {S}/({G m^2})$ which, for a NS with spin $S$ and mass $m$, can be written as
+where we introduced the dimensionless Kerr spin parameter $\chi\equiv {S}/({G m^2})$ which, for a neutron star (NS) with spin $S$ and mass $m$, can be written as
 %
@@
 On the other hand, the spin-spin effects contribute at $\ord(v^4/c^4)\times\dot{E}$ hence $\lesssim \dot{E}_\text{SO}$.
-Thus, NS spins do not significantly affect our estimation of advance warning times. %$T_\text{AW}$.
+Thus, NS spins can be neglected for our estimation of advance warning times. %$T_\text{AW}$.
 %we have justified our negligence of the effects of NS spins.
@@
 we consider a maximum value of 200\,Mpc for $D$,
-which corresponds to $z \approx 0.022$ which redshifts $f_\text{ISCO}$ by $\approx 2\%$ and reduces $\tau_\text{insp}$ by $\approx 7\%$.
+which corresponds to $z \approx 0.02$ which redshifts $f_\text{ISCO}$ by $\approx 2\%$ and reduces $\tau_\text{insp}$ by $\approx 7\%$.
 Therefore, we will neglect the effects of cosmological redshift 
@@
 If we wish to do better, we can add all of the known post-Newtonian contributions 
-(up to 3.5PN\footnote{Though the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
-explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$ though we suspect that a few PN experts have already obtained these.}) resulting in
+(up to 3.5PN\footnote{Although the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
+explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$. Be that as it may, we suspect that a few PN experts have already obtained these.}) resulting in
 %%
@@
 by computing the SNRs accumulated by each individual IFO and by the entire network.
-To do so, we take the best-inferred values for $M,M_c,D$ from GW170817 given in Eq.(\ref{eq:GW170817_params}) above and compute the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
+To do so, we take the best-inferred values for $M,M_c,D$ from GW170817 given in Eq.~(\ref{eq:GW170817_params}) above and compute the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
 %%
@@
 We also show the Hanford detector's sensitivity in light blue for comparison. The dashed, solid and dotted lines represent the 
-frequency-domain GW strains due to the inspiral of
-a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}) ($2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$).
+frequency-domain GW strains ($2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$) due to the inspiral of
+a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}).
 %each interferometer's frequency-domain response
@@
 %of the $Q=1$ case. 
-The shading represents the region of likelihood for the strain due to an inspiralling BNS. In the case of a three-IFO
+The shading represents the region of likelihood for the strain due to an inspiralling BNS with parameters of Eq.~(\ref{eq:GW170817_params}). In the case of a three-IFO
 network, we would expect all three strains to exist somewhere in the shaded region most of the time for an inspiral with GW170817's intrinsic parameters. %.and two out of three every time.
@@
 %inspiralling BNS systems sweeping across the most sensitive interferometer frequencies.
-The solid (black), dotted (blue), and dashed (green) lines are the RMS-averaged strains ($2\sqrt{f}\tilde{H}_m(f)$) at luminosity distances of $D=50, 100, 200\,$Mpc, respectively.
+The solid (black), dotted (blue), and dashed (green) lines are the RMS-averaged strains ($2\sqrt{f}\tilde{H}_m$) at luminosity distances of $D=50, 100, 200\,$Mpc, respectively.
 The accompanying shaded regions span from the near-optimally oriented IFO
-($2\sqrt{f}\tilde{H}_h(f)$) to
-sub-optimally oriented IFO ($2\sqrt{f}\tilde{H}_l(f)$) as explained in Fig.~\ref{fig:figGW170817}.
-The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals,
-but as can be seen, the SNRs hardly increase beyond $\sim 1000\,$Hz.
+($2\sqrt{f}\tilde{H}_h$) to
+sub-optimally oriented IFO ($2\sqrt{f}\tilde{H}_l$) as explained in Fig.~\ref{fig:figGW170817}.
+The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals.
+%but as can be seen, the SNRs hardly increase beyond $\sim 1000\,$Hz.
 %Recall that we deliberately neglect the tidal and strong-field effects that modify the plotted $f^{-2/3}$ power law beyond $\sim 100\,$Hz.
@@
 one 40-Mpc inspiral per a three-year period.
-Therefore, we do not expect to be able forecast GRBs in the Advanced LIGO-Virgo era given that we might at best have a couple of minutes of warning time. 
+Given that we might at best have a couple of minutes of warning time for a once-a-decade event, we do not expect to be able forecast GRBs in the Advanced LIGO-Virgo era. 
 %we prefer to remain optimistic about the prospects of forecasting at least one GRB in the 2020s. %that this latency can be reduced to minutes.
@@
 \hline
-$D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}$(sec)& $\bar{\rho}_F$\T\B\\
+$D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T\B\\
 \hline
@@
 inspirals that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
-$M_c, M$ \cite{Farr:2015lna}; (ii) sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};
+$M_c, M$ \cite{Farr:2015lna}; (ii) source sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};
 (iii) $ \lesssim 10\%$ precision in the inferred NS masses \cite{Rodriguez:2013oaa} and the effective spin parameter $\chi_\text{eff}$ \cite{Zhu:2017znf}; and
@@
 where recall $\mathcal{M}_c = (1+z)M_c$.
-For the detector noise $\sqrt{S^\text{ET}_n(f)}$, we adopt the ASD for the B and C configurations known as ET-B and ET-C, respectively \cite{Hild:2010id} which we plot as the solid dark (red) and light (brown) curves in Fig.~\ref{fig:ETB2030}.
+For the detector noise $\sqrt{S^\text{ET}_n(f)}$, we adopt the ASD for the B and C configurations known as ET-B and ET-C, respectively \cite{Hild:2010id}, which we plot as the solid dark (red) and light (brown) curves in Fig.~\ref{fig:ETB2030}.
 Sweeping across these are four BNS inspirals at $D=100,200,400,1000\,$Mpc represented by solid (black), dotted (blue), dashed (green),
@@
 The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the redshift-corrected
-RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}(f)$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
-The vertical lines with correspondingly identical patterns (colors) mark the redshifted ISCO frequencies ($(1+z)^{-1} f_\text{ISCO}$) at which point we terminate each inspiral.
+RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
+The vertical lines with correspondingly identical patterns (colors) mark the redshifted ISCO frequencies $(1+z)^{-1} f_\text{ISCO}$ at which point we terminate each inspiral.
 As the true ISCO frequency is likely larger than $f_\text{ISCO}$ \cite{Marronetti:2003hx}, the inspirals would continue to nearly 2\,kHz indicated by the 
@@
 %
-which then gives us our redshift-accounted advance warning time via $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp_redshifted}) which we can slightly improve by using the 3.5PN expression.
+which then gives us our redshift-incorporated advance warning time via $T_\text{AW}=\tau_\text{insp}(\bar{f}_\text{ET})$ using Eq.~(\ref{eq:tau_insp_redshifted}) which we can slightly improve by using the 3.5PN expression.
 Therefore, we proceed as summarized in Fig.~\ref{fig:flow} and compute the 0PN and 3.5PN advance warning times 
@@
 Blanchet's review \cite{Blanchet_LRR} for details).
-The final accumulated SNR is given by
+The final accumulated SNRs are given by
 %
@@
 Table~\ref{table:ET} summarizes our results for both ET-B and ET-C where we chose to only display the 3.5PN-accurate inspiral time as $T_\text{AW}$,
-but we computed this quantity using both 0PN and 2PN expressions as a consistency check.
+but we computed this quantity also using both 0PN and 2PN expressions as a consistency check.
 
@@
 ET-B/C accumulate SNR of 15 which we take to be our detection criterion. Note that both $T_\text{AW}$ and $\bar\rho_F$ are larger for ET-C
-due to its improved sensitivity in the $f\lesssim 30\,$Hz regime compared to ET-B as it is clear in Fig.~\ref{fig:ETB2030}.
+due to its improved sensitivity in the $1\,\text{Hz}\lesssim f\lesssim 30\,$Hz regime compared to ET-B as is clear in Fig.~\ref{fig:ETB2030}.
 These results and those of Table.~\ref{table:LIGO2020} are summarized in Fig.~\ref{fig:summary}.}\label{table:ET}
@@
 Instead of speculating whether or not this is enough to forecast GRBs, we turn our attention to ET-C's forecasting capabilities.
-As can be seen from Fig.~\ref{fig:ETB2030}, ET-C's increased sensitivity in the $f\lesssim 30\,$Hz regime will significantly lengthen the advance warning times.
+As can be seen from Fig.~\ref{fig:ETB2030}, ET-C's increased sensitivity in the $1\,\text{Hz}\lesssim f\lesssim 30\,$Hz regime will significantly lengthen the advance warning times.
 This is best highlighted by the sixth colum of Table~\ref{table:ET}, 
 where we show that ET-C will provide up to \emph{five hours} of early warning time for nearby ($D\lesssim 100\,$Mpc) neutron star mergers.
-Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's horizon distance) will persist in the ET-C sensitivity band for a few hours after their initial detection.
+Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's horizon distance) will persist in the ET-C sensitivity band for a few hours after their initial detection ($T_\text{AW} > 2\,$ hours).
 Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET.
@@
 $\approx 355^{+730}_{-280}\,\text{year}^{-1}$ for ET-C. Additionally, each source within $D_H$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
-in the ET-B, ET-C bands, respectively. These are summarized in Table~\ref{table:horizon}.
+in the ET-B, ET-C bands, respectively. These results are summarized in Table~\ref{table:horizon}.
 
@@
 we can expect ET to localize sources within its horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
-Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens of gamma ray bursts
+Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts
 \footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
@@
 obtained by rescaling the rate inferred from Advanced LIGO's O1, O2 observing periods \cite{GW170817}.
-$\bar\rho_F(D_H)$ is the total SNR accumulated in ET due to a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
+$\bar\rho_F(D_H)$ is the total SNR accumulated due to a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
 \end{table}
@@
  However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
- \item Low black hole mass. In the geodesic case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
+ \item Low black hole mass. In the test-mass case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
  Hence, $M_\text{BH}$ must also be minimized. 
- As was the case with $r$, there is also a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models, which currently yield $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
+ As is the case with $r$, there is also a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models, which currently yield $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
  \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
- For instance, for the maximum dimensionless BH spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value ($6GM_\text{BH}/c^2$) whereas for $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
+ For instance, for the maximum dimensionless BH spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value $6GM_\text{BH}/c^2$ whereas for $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
  With smaller ISCO separation, there is much more tidal force exerted on the NS before it plunges in.
@@
 
-Although the results from each numerical study may somewhat vary what is clear is that we must have high spin and low black hole mass. We are thus led to set $M_\text{BH} =5 M_\odot$. 
+Although the results from each numerical study of BH-NS mergers may somewhat vary what is clear is that we must have high spin and low mass for the black hole for tidal disruption to happen. 
+We are thus led to set $M_\text{BH} =5 M_\odot$. 
 This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
@@
 There is additional motivation to choose low BH mass as 
- $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv M_\text{BH}/M_text{NS} > 1$, which scales as $Q^{-2/3}$ as $Q\to\infty$ , i.e., heavier binaries inspiral faster.
- We once again set $M_\text{NS}=1.4 M_\odot$ giving $Q=5/1.4  \simeq 3.571$. $c_\text{NS}$ is determined by the radius of the NS constrained in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
+ $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv M_\text{BH}/M_\text{NS} > 1$, which scales as $Q^{-2/3}$ as $Q\to\infty$ , i.e., heavier binaries inspiral faster
+ so it is desirable to minimize $Q$.
+ Setting $M_\text{NS}=1.4 M_\odot$ as before gives $Q=5/1.4  \simeq 3.571$. $c_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
  which results in $0.13\lesssim c_\text{NS} \lesssim 0.15$ 

### 2018-04-03 Paper/Manuscript.tex
Final updates

@@
 
-Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. Given that
-it takes $\gtrsim \mathcal{O}(1)\,$\emph{day} for a BNS source to inspiral from $f_0\sim 1\,$Hz to $\bar{f}_\text{ET}$ of Eq.~(\ref{eq:ET_fbar}),
-we can expect ET to localize sources within its horizon distance to $\lesssim 1\,\text{deg}^2$ \cite{Mills:2017urp}.
+Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. 
+With such high SNRs we expect that a future network consisting of ET and LIGO Voyager will be able to localize half the sources 
+at $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ and more than half the sources at $D\lesssim 400\,$Mpc to $\approx 1\,\text{deg}^2$ \cite{Mills:2017urp}.
 Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts
-\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030 
-(this is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}).}.
+\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030,
+which is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}.}.
 %It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated

### 2018-04-15 Paper/Manuscript.tex
Corrections, new references. Added one paper as a PDF.

@@
 \begin{abstract}
-We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars early enough to alert electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very start.
+We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars sufficiently
+early to alert electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very beginning.
 We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger.
@@
 we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc in the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc in the Einstein Telescope's B and C configurations.
-In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time thus we expect no forecast of GRBs in the 2020s. 
-On the other hand, Einstein Telescope will provide us with advance warning times up to five hours.  
+In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time, thus we expect no forecast of GRBs in the 2020s. 
+On the other hand, Einstein Telescope will provide us with advance warning times of up to five hours.  
 Taking one hour as a benchmark warning time, we obtain a corresponding horizon
@@
 using a template bank of gravitational waveforms computed within the framework of post-Newtonian theory \cite{Buonanno:2009zt, Blanchet_LRR}.
-The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from approximately $ 30\,$Hz to about $ 2\,$kHz in 57 seconds
+The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from approximately $ 30\,$Hz to about $ 2\,$kHz in 57 seconds,
 executing nearly $ 3000$ gravitational wave cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
-The total mass of the system was inferred to be $2.74^{+0.04}_{-0.01} M_\odot$ with component masses in the range $1.17-1.60 M_\odot$ consistent
+The total mass of the system was inferred to be $2.74^{+0.04}_{-0.01} M_\odot$ with component masses in the range $1.17-1.60 M_\odot$, consistent
 with neutron stars (assuming low spin priors, see Sec.~\ref{sec:idealizations}).
-Moreover, both the gravitational wave (GW) and EM observations were consistent with a source luminosity distance of $\sim 40\,$Mpc
+Moreover, both the gravitational wave (GW) and EM observations were consistent with a source luminosity distance of $\sim\!\! 40\,$Mpc
 and supported the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
@@
 i.e., the lag time between the merger and the alerting of the EM observatories. 
-LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim 30$ to $60\,$minutes \cite{Abbott:2011ys} (no detections).
+LIGO-Virgo science runs in 2009-2010 yielded a latency of $\sim\!\! 30$ to $60\,$minutes \cite{Abbott:2011ys} (no detections).
 In the case of GW170817, the latency was 40\,minutes and $36^{+1.7}\,$seconds \cite{GBM:2017lvd}.
@@
 Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding observations.
-Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020}, \ref{table:ET}; 
+Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020} and \ref{table:ET}; 
 and as horizon distances and event rates in Table~\ref{table:horizon}.
@@
 %
-Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
+Here, $Q_{ij}$ is a trace-reversed {\bf MAYBE: explain this} mass quadrupole moment which
 is the dominant contribution to the power emitted %in gravitational radiation
-by a system with changing mass moments.
+by a system with changing mass moments. Details of how to obtain this expression can be found in Ref.~\cite{Maggiore}.
 
@@
 where $\mu= m_1 m_2/M$ is the reduced mass and $M=m_1+m_2$ is the total mass. 
-We justify our simplification of motion to circular orbits in Sec.~\ref{sec:idealizations}.
+We justify our simplification of the motion to circular orbits in Sec.~\ref{sec:idealizations}.
 %Our assumption of the circularity of the motion is well justified in
@@
 where $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs. 
-The quantity in parantheses in Eq.~(\ref{eq:Edot2}) is ubiquitous in post-Newtonian theory and is
-referred to as the dimensionless inverse separation $x$.
-As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from in Eq.~(\ref{eq:Edot2}) that $\dot{E}\propto x^5$. 
+The quantity in parantheses in Eq.~(\ref{eq:Edot2}) equals $x^{3/2}$ where 
+$x \equiv ({G M_c\, \Omega}/{c^3})^{2/3} $
+is the dimensionless inverse separation parameter ubiquitous in post-Newtonian theory.
+As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2}) that $\dot{E}\propto x^5$. 
 %hence the common statement in the literature saying that gravitational radiation starts
@@
 These are tensorial perturbations propagating at the speed of light in flat (Minkowski) spacetime.
-In the so-called wave zone, defined by the condition $ c/f \ll D$, where $D$ is the distance to the GW source, 
+In the so-called wave zone, defined by the condition $ \lambda= c/f \ll D$, where $\lambda$ is the GW wavelength and $D$ is the distance to the GW source, 
 these tensor modes satisfy the flat spacetime sourceless wave equation. %$\Box\bar{h}_{\mu\nu} = 0$.
@@
 When $\iota=0$ the orbit is seen face-on and we have a circularly-polarized wave: $\langle h_+ \rangle = \langle h_\times\rangle$ where $\langle \ldots \rangle$
-denote time-averages over one orbit. Note that as $f$ increases in time, so does $h(t)$ hence the characteristic ``chirping'' of GW signals.
+denote time-averages over one orbit. Note that as $f$ increases in time, so does $h(t)$, hence the characteristic ``chirping'' of GW signals.
 
@@
 where $\Phi_0 \equiv \Phi(t=t_\text{coal})$ is an integration constant. The subscript N denotes the Newtonian (leading-order) contribution. 
-Higher-order contributions can be added in terms a post-Newtonian series, which make up to $\lesssim 2\%$ of the total phase.
+Higher-order contributions can be added in terms of a post-Newtonian series, which make up to $\lesssim 2\%$ of the total phase.
 Although we will include contributions up to and including 3.5PN to obtain the results of Sec.~\ref{sec:results}, 
@@
 It remains to compute $|Q(\theta,\phi,\psi,\iota)|^2$. 
-Since we can not a priori know the direction of the source, it is appropriate to average over the angles $\theta,\phi,\psi,\iota$ which we compute
+Since we can not a priori know the direction of the source, it is appropriate to average over the angles $\theta,\phi,\psi$, and $\iota$ which we compute
 %For our computations, we will only work with one detector so we can set $\psi=0$ without loss of generality, which results in
@@
 %
-\section{Simplifications and idealizations used in evolving the inspiral}\label{sec:idealizations}
+\section{Simplifications and idealizations} %used in evolving the inspiral}
+\label{sec:idealizations}
 %In this section, we justify our simplifications with brief computations.
@@
 Let us briefly explore what the cost of setting $m_1=m_2=1.4 M_\odot$ is for our calculations. 
-Including the error bars, the known range for neutron star masses runs from $\approx 0.5 M_\odot$ to $ \approx 3 M_\odot$ with the actual values restricted
-between $\approx 1 M_\odot$ and $\approx 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
+Including the error bars, the known range for neutron star masses runs from $\approx 0.5 M_\odot$ to $ \approx 3 M_\odot$ with typical values between $\approx 1 M_\odot$ and $\approx 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
 Of these measured masses, a subset comprised of double neutron stars, such as the famed Hulse-Taylor binary, have the smallest error bars with masses
@@
 Additionally, the masses involved in GW170817 are inferred to be between $1.17 M_\odot$ and $1.60 M_\odot$ \cite{GW170817}.
-Therefore, let us restrict the masses to lie between $1.2 M_\odot$ and $1.6 M_\odot$ then focus on % ranges $R_{1,2} \in [1,2]/(1.4)$. 
+Therefore, let us restrict the masses to lie between $1.2 M_\odot$ and $1.6 M_\odot$, then focus on % ranges $R_{1,2} \in [1,2]/(1.4)$. 
 the quantities of interest for us, which are %the GW/orbital frequency ($f/f_K$), %the radiated power in GWs ($\dot{E}$), the rate of change of GW/orbital frequencies ($\dot{f}$), 
@@
 Moreoever, it seems that this variation tends to lengthen $\tau_\text{insp}$ more than shorten it thus our setting
-$m_1=m_2=1.4 M_\odot$ is more likely to underestimate $T_\text{AW}$ than overestimate it which is something we can live with.
+$m_1=m_2=1.4 M_\odot$ is more likely to underestimate $T_\text{AW}$ than overestimate it. 
+%which is something we can live with.
 So we set $m_1=m_2=1.4 M_\odot$ henceforth.
@@
 we obtain $e\approx 6\times 10^{-5}$. Thus our setting $e=0$ is very reasonable.
+
+Let us briefly discuss the possibility of eccentric BNS systems {\bf FINISH}
+\cite{1975MNRAS.172P..15F,Grindlay:2005ym}
 %

### 2018-04-15 Paper/Manuscript.tex
Finished Conor's corrections, added x-axes label to Fig. 5 and one more reference.

@@
 \affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland.}
-
-\date{\today}
+\affiliation{Friedrich-Schiller-Universit{\"a}t Jena}
+%\date{\today}
 
@@
 $a \simeq 3352\,$km and using the currently observed values $a_i \approx 1.95\times 10^6\,$km and $e_i \approx 0.617$,
-we obtain $e\approx 6\times 10^{-5}$. Thus our setting $e=0$ is very reasonable.
-
-Let us briefly discuss the possibility of eccentric BNS systems {\bf FINISH}
-\cite{1975MNRAS.172P..15F,Grindlay:2005ym}
+we obtain $e\approx 6\times 10^{-5}$. Thus our setting $e=0$ is very reasonable\footnote{
+It is possible to have 
+high-eccentricity binary black hole mergers in the vicinity of galactic nuclei due close encounter captures \cite{OLeary:2008myb}.
+However, it is not clear how much this applies to BNS systems.}.
+%for binary systems
+%non-zero eccentricity binary mergers
+%for sytems that have formed by tidal capture mechanisms in globular clusters {\bf FINISH}
+%\cite{1975MNRAS172P15F,Grindlay:2005ym}
+%but these binaries are expected to be outnumbered significantly by the circularized ones.
 %
@@
 %The event, first picked up by LIGO Hanford (H1), 
-swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz accumulating a total SNR of
+swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz, accumulating a total SNR of
 %18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
-$\rho_\text{tot} = 32.4$ \cite{GW170817}
-The inferred duration of the event in the network bandwidth was $\approx 57\,$ seconds during which $\approx 3000$ cycles of GW were emitted \cite{GW170817_Facts}.
+$\rho_\text{tot} = 32.4$ \cite{GW170817}.
+The inferred duration of the event in the network bandwidth was $\approx 57\,$ seconds during which $\approx 3000$ cycles of GWs were emitted \cite{GW170817_Facts}.
 Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following values were inferred for the total mass, the chirp mass,
@@
 
-Fig.~\ref{fig:figGW170817} shows our network. The red curve is L1's ASD (sensitivity) during GW170817. We assume our three IFOs to identically have this sensitivity,
+Fig.~\ref{fig:figGW170817} shows our network. The red curve is L1's ASD (sensitivity) during GW170817. We assume our three IFOs have identical sensitivities,
 but because their orientations and response functions differ, their sensitivity to a localized source is reduced. We represent this reduction by lowering the
@@
 For the ALV network, we consider $D=50,100,200\,$Mpc 
- as A-LIGO horizon will be slightly over 200\,Mpc and A-Virgo's around 130\,Mpc.
+ as A-LIGO's horizon will be slightly over 200\,Mpc and A-Virgo's around 130\,Mpc.
  %and BNS systems at $D=200, 400, 1000\,$Mpc for the ET network. 
@@
 one 40-Mpc inspiral per a three-year period.
-Given that we might at best have a couple of minutes of warning time for a once-a-decade event, we do not expect to be able forecast GRBs in the Advanced LIGO-Virgo era. 
+Given that we might at best have a couple of minutes of warning time for a potentially once-a-decade event, we do not expect to be able forecast GRBs in the Advanced LIGO-Virgo era. 
 %we prefer to remain optimistic about the prospects of forecasting at least one GRB in the 2020s. %that this latency can be reduced to minutes.
@@
 However, if the spin of the BH comes from the supernova explosion mechanism itself as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
-low-mass BH in a binary system\footnote{We thank Dr. Morgan Fraser
+low-mass BH in a binary system\footnote{We thank Dr. Morgan Fraser of UCD Astrophysics
 for pointing this out.}.
@@
 \acknowledgements 
-SA thanks Conor O'Toole for endless feedback and Niels Warburton for a careful reading of this article.
+SA thanks Conor O'Toole and Niels Warburton for endless feedback and a thorough perusal of this article.
 

### 2018-04-22 Paper/Manuscript.tex
Niels's corrections, a few more references.

@@
 to be forecast by the same detector.
-%Our main conclusions are: (i) we expect ALV network to forecast 1 to 3 GRBs in the 2020s, (ii)
-
+This article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
+Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
+Though many of our results may be known to the experts, they might nonetheless find this article motivating and exciting.
 \end{abstract}
@@
 with neutron stars (assuming low spin priors, see Sec.~\ref{sec:idealizations}).
-Moreover, both the gravitational wave (GW) and EM observations were consistent with a source luminosity distance of $\sim\!\! 40\,$Mpc
+Moreover, both the gravitational wave (GW) and EM observations were consistent with a source location in the galaxy in NGC4993 
+at a luminosity distance of $\sim\!\! 40\,$Mpc,
 and supported the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
-causing the prompt short-hard gamma-ray burst (GRB170817A) in NGC4993 as first suggested by Ref.~\cite{Eichler:1989ve}.
+causing a prompt short-hard gamma-ray burst (GRB170817A) as first suggested by Ref.~\cite{Eichler:1989ve}.
 
@@
 
-The short answer is in the affirmative.
-The long answer is still affirmative, but depends on many factors such as source distance and sky position, detector sensitivity and orientation.
+The short answer is ``yes''.
+The long answer is still ``yes'', but depends on many factors such as source distance and sky position, detector sensitivity and orientation.
 One also needs to account for the fact that GRBs are thought to be collimated emissions with narrow outburst angles \cite{Kumar:2014upa}.
@@
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
-(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm} for the latest developments and references therein).
-Despite its failures, our quadrupole radiation driven Newtonian
+(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm} for the latest developments and references therein).
+Despite its simple formulation, our quadrupole radiation driven Newtonian
 evolution is more than sufficient to provide reliable estimations of advance warning times.
@@
 
-Let us emphasize that this article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
-Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
-Be that as it may, even the experts might find our results motivating and exciting.
-
+%Let us emphasize that this article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
+%Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
+%Be that as it may, even the experts might find our results motivating and exciting.
+%
 This article is organized as follows. Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
@@
 
-Throughout the text, $f$ denotes the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
+Throughout the text, $t$ denotes observer/detector time and $f$ denotes the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
 %Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
@@
 %
-Here, $Q_{ij}$ is a trace-reversed {\bf MAYBE: explain this} mass quadrupole moment which
+Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
 is the dominant contribution to the power emitted %in gravitational radiation
@@
 \be
-\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}, \label{eq:Edot2}
-\ee
-%
-where $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs. 
-The quantity in parantheses in Eq.~(\ref{eq:Edot2}) equals $x^{3/2}$ where 
-$x \equiv ({G M_c\, \Omega}/{c^3})^{2/3} $
-is the dimensionless inverse separation parameter ubiquitous in post-Newtonian theory.
+\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}= \f{32}{5}\f{c^5}{G}x^5, \label{eq:Edot2}
+\ee
+%
+where $x = ({G M_c\, \Omega}/{c^3})^{2/3} $ is the dimensionless inverse separation parameter ubiquitous in post- Newtonian theory and $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs.
 As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2}) that $\dot{E}\propto x^5$. 
@@
 %
-where $1.219 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$.
+where $1.219 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$. This is the canonical value for the 
+mass of a neutron star due to Chandrasekhar limit \cite{Chandra}.
 
@@
 %
-We will see in Sec.~\ref{sec:idealizations} that $f_\text{ISCO} \sim 1000\,$Hz for a system with $M\approx 2 M_\odot$. 
-On the other hand, the frequencies of interest for our advance warning time estimations will be $\lesssim 10\,$Hz
+We will see in Sec.~\ref{sec:idealizations} that $f_\text{ISCO} \sim \ord(10^3)\,$Hz for a system with $M =2.8 M_\odot$. 
+On the other hand, the frequencies of interest for our advance warning time estimations are $\lesssim 10\,$Hz
 meaning that $f^{-5/3} \gg f_\text{ISCO}^{-5/3}$. Therefore, at the leading (Newtonian) order, the number of GW cycles can be approximated by
@@
 %when interacting with masses away from the source.
-For a binary in a circular orbit, these states read
+For a binary in a circular orbit, these states read \cite{Maggiore}
 %
@@
 
-In a network of $N$ interferometers, the total SNR is defined as follows
+In a network of $N$ interferometers, the total SNR is defined as follows \cite{Finn:2000hj}
 %%
@@
 It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
-but it would be pointless to simply set $Q=0$. We therefore somewhat arbitrarily set $\psi=0,\iota=0$
-and introduce the following $\theta,\phi$-only averages
+but it would be pointless to simply set $Q=0$. We therefore pick the values $\iota=0$ (i.e, $|h_+|=|h_\times|$)
+and $\psi=0$ for simplicity %(aligning the $x$-axis of the ``$+$'' with the of the IFO
+then introduce the following $\theta,\phi$-only averages
 %
@@
 This may seem somewhat ad hoc, 
-but it is our way of representing the response of a three-IFO network to a single source.
-In other words, we map the three different IFO responses due to a single source to a single IFO's response to three different sources differing in amplitudes
+but it is our way of representing the sub-RMS-average response of the third IFO due to its sub-optimal configuration. 
+One may very well use another scheme to generate this below average response.
+
+To summarize, we introduced a model for a three-IFO network in which each IFO has identical sensitivity,
+but varying response to GWs due to IFO orientation and source polarization and sky position. This response is encoded in the quality factor $|Q_i|$.
+We simulate this network's response to a single source by mapping the three different IFO responses to a single IFO's response to three distinct sources differing in amplitudes 
 from the optimal case by quality factors $|Q_i|= 4/5,2/5,$ and $4/5-\sqrt{2/5}$.
@@
 \ee
-for $M \equiv m_1+m_2 = 2.8 M_\odot$. The true ISCO is located at $r< r_\text{ISCO}$ with frequency possibly up to 1.7\,kHz \cite{Marronetti:2003hx}, 
-however, there is no simple expression for it akin to Eq.~(\ref{eq:f_isco}) and its extraction from numerical simulations is a rather involved procedure.
+for $M \equiv m_1+m_2 = 2.8 M_\odot$. In the strong-field, highly-dynamical spacetime of the last few orbits, the
+concept of an ISCO becomes fuzzy due to strong dissipative effects. However, an ISCO can nonetheless be dynamically determined
+with frequency possibly up to 1.7\,kHz \cite{Marronetti:2003hx}, 
+but there is no simple expression for it akin to Eq.~(\ref{eq:f_isco}) and its extraction from numerical simulations is a rather involved procedure.
 Therefore, we employ Eq.~(\ref{eq:f_isco}) as our cut-off for

### 2018-04-26 Paper/Manuscript.tex
Added a citation

@@
 Explicit expressions for $\Psi_{+,\times}$ show that they are out of phase by $\pi/2$
-(the details of the Fourier transformation can be found in Sec.~4.5 of Ref.~\cite{Maggiore}).
+(the details of the Fourier transformation can be found in Sec.~4.5 of Ref.~\cite{Maggiore} or in \cite{Moore:2014lga}).
 Accordingly, the Fourier transform of the detector strain (\ref{eq:detector_strain}) is given by

### 2018-05-03 Paper/Manuscript.tex
Corrections up to page 10 and one new reference.

--- 2018-04-22 Paper/Manuscript.tex
@@
 \author{Sarp Akcay}
-\affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland.}
-\affiliation{Friedrich-Schiller-Universit{\"a}t Jena}
+\affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland}
+\affiliation{Theoretisch-Physikalisches Institut, Friedrich-Schiller-Universit{\"a}t Jena, 07743, Jena, Germany}
 %\date{\today}
@@
 In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time, thus we expect no forecast of GRBs in the 2020s. 
-On the other hand, Einstein Telescope will provide us with advance warning times of up to five hours.  
-Taking one hour as a benchmark warning time, we obtain a corresponding horizon
+On the other hand, Einstein Telescope will provide us with advance warning times of more than five hours for $D \le 100\,$Mpc.
+Taking one hour as a benchmark advance warning time, we obtain a corresponding horizon
 distance of roughly 600 Mpc for the Einstein Telescope C configuration.
@@
 %for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
-Using current BNS event rates within this horizon distance, we show that this translates to forecasts of $\gtrsim \ord(10^2)$ GRBs in the 2030s.
+Using current BNS merger event rates within this volume, we show that Einstein C will forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s.
 %with Einstein C.
@@
 first picked up by the One-Meter, Two Hemisphere team less than 11 hours after the merger \cite{Coulter2017, Coulter:2017wya}.
-This subsequently launched the largest-ever campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum which is still ongoing
+This subsequently launched a massive campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum which is still ongoing
 more than half a year after the initial GRB \cite{GBM:2017lvd}.
@@
 We instead focus on the forecasting capabilities of the ground-based interferometers at their \emph{full design} sensitivity by computing the time interval
-between the merger and the instant of detection defined in terms of a certain threshold signal-to-noise ratio.
+between the merger and the instant of detection defined in terms of a certain detection criterion which we describe below.
 To this end, we consider the ALV network of 2020s composed of three L-shaped interferometers operating at their design sensitivities
@@
 %which reduce an individual interferometer's sensitivity to a particular source. 
-(${iii}$) We determine the detection time by computing the frequency at which the network's accumulated signal-to-noise ratio (SNR) for the BNS inspiral equals 15.
-($iv$) We define the advance warning time, $T_\text{AW}$, to be the remaining inspiral time to the merger from the instant of detection.
+(${iii}$) We determine the detection time by computing the frequency at which the network's accumulated signal-to-noise ratio for the BNS inspiral equals 15.
+($iv$) We define the advance warning time, $T_\text{AW}$, to be the time interval between the instant of detection and the merger.
 We repeat this procedure for BNSs at luminosity distances varying from 50\,Mpc to 1\,Gpc with the smaller values intended for the ALV network and 
@@
 evolution in the strong-field regime, where speeds $\gtrsim 0.1c$. This is a very complex and complicated problem requiring fully
-numerical treatment formulated in terms of general relativistic, magnetohydrodynamic codes 
+numerical treatment in terms of general relativistic, magnetohydrodynamic codes 
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
@@
 and as horizon distances and event rates in Table~\ref{table:horizon}.
-In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of black hole - neutron star inspirals to see whether or not 
+In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of binary black hole - neutron star inspirals to see whether or not 
 future detectors can forecast a tidal disruption event, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
 
-Throughout the text, $t$ denotes observer/detector time and $f$ denotes the GW frequency of the dominant quadrupole mode, which is twice the orbital (Keplerian) frequency $f_K$. 
+Throughout the text, $t$ denotes observer/detector time and $f$ denotes the GW frequency of the dominant quadrupole mode in observer/detector frame. 
+%$f$ is twice the orbital (Keplerian) frequency $f_K$. 
 %Relatedly, we define the following angular frequencies: $\omega = 2\pi f, \Omega=2\pi f_K$ with $\omega=2\Omega$.
@@
 by a system with changing mass moments. Details of how to obtain this expression can be found in Ref.~\cite{Maggiore}.
+There is no monopole radiation due to conservation of mass and no dipole radiation due to conservation of linear and angular momenta
+(cf. Ref.~\cite{Mono}).
 
 Here, we are specifically interested in the motion of two point masses in a circular orbit around a common center of mass.
-Labelling the masses by $m_1 \le m_2$, we have, for a binary in a circular orbit with Keplerian angular frequency $\Omega$ and separation $r$,
+For a binary in a circular orbit with Keplerian angular frequency $\Omega$, separation $r$, and masses $m_1 \le m_2$, we have \cite{Maggiore}
 %
@@
 where $x = ({G M_c\, \Omega}/{c^3})^{2/3} $ is the dimensionless inverse separation parameter ubiquitous in post- Newtonian theory and $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs.
-As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2}) that $\dot{E}\propto x^5$. 
+As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2}) that 
+at the leading order, power emitted in GWs scales as $x^5$.
 %hence the common statement in the literature saying that gravitational radiation starts
@@
 This can be integrated straightforwardly after defining a new time variable $\tau\equiv t_\text{coal}-t$ that equals zero when the neutron stars coalesce.
-Using $\tau$ we can now define an inspiral time at a given GW frequency
+Using $\tau$ we can now define the inspiral time, i.e, time left to coalesence at a given GW frequency $f$
 %
@@
 where $1.219 M_\odot$ is the chirp mass corresponding to $m_1=m_2=1.4 M_\odot$. This is the canonical value for the 
-mass of a neutron star due to Chandrasekhar limit \cite{Chandra}.
+mass of a neutron star due to the Chandrasekhar limit \cite{Chandra}.
 
@@
 %
-We now introduce a cut-off for the inspiral imposed by the frequency of the innermost stable circular (ISCO) orbit in Schwarzschild spacetime
+We now introduce a cut-off for the inspiral imposed by the frequency of the innermost stable circular orbit (ISCO) in Schwarzschild spacetime
 \be
@@
 In a suitable gauge, such as the commonly used transverse-traceless gauge, 
-it can be shown that there exist only two physical degrees of freedom which manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$.
+it can be shown that there exist only two physical degrees of freedom which manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs.
 %when interacting with masses away from the source.
@@
 Although we will include contributions up to and including 3.5PN to obtain the results of Sec.~\ref{sec:results}, 
-we will not show these expressions here, but they can be found in Ref.~\cite{Blanchet_LRR}.
+we will not show these expressions here, but they can be found, e.g., in Ref.~\cite{Blanchet_LRR}.
 
 The nomenclature ``plus'' ($+$) and ``cross'' ($\times$) follows from the effects that passing GWs have on the plane transverse to their direction of propagation.
-If we were to conceive of a ``toy'' detector made up of a circular configuration of test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress the circular arrangement in a $+$ and $\times$ pattern
-with a $90^\circ$ phase difference.
+If we were to conceive of a ``toy'' detector made up of a circular configuration of test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress this circular arrangement in a $+$ and $\times$ pattern
+with a $90^\circ$ phase difference between the two states.
 This is the manifestation of the tidal strain of the GWs on the tranverse plane.
@@
 are the antenna pattern functions of the detectors; $\theta,\phi$ are the sky coordinates; and $\psi$ is
-an additional angle coming from the respective rotations of detectors' frames to source frame. %(there is no need for $\psi$ in the case of a single detector).
+the angle of orientation of a detector's frame with respect to the source frame. %(there is no need for $\psi$ in the case of a single detector).
 %In principle, $\psi$ can be aligned with the polarization of the incoming GWs 
 %
-We can't apriori know $\theta, \phi,\psi$, however, we can extract their values with some limited precision over the course of an inspiral.
+We can not apriori know $\theta, \phi,\psi$, however, we can extract their values with some limited precision over the course of an inspiral.
 The longer the inspiral stays in the detector bandwidth, the better we can estimate these angles.
@@
 Explicit expressions for $\Psi_{+,\times}$ show that they are out of phase by $\pi/2$
-(the details of the Fourier transformation can be found in Sec.~4.5 of Ref.~\cite{Maggiore}).
+(the details of the Fourier transformation can be found in Sec.~4.5 of Ref.~\cite{Maggiore} or in Ref.~\cite{Moore:2014lga}).
 Accordingly, the Fourier transform of the detector strain (\ref{eq:detector_strain}) is given by
@@
 \be
-Q(\theta,\phi,\psi,\iota) = F_+(\theta,\phi,\psi)\f{1+\cos^2\iota}{2}  + i F_\times(\theta,\phi,\psi) \cos\iota \label{eq:Q},
+Q(\theta,\phi,\psi,\iota) = F_+(\theta,\phi,\psi)\f{1+\cos^2\iota}{2}  + i F_\times(\theta,\phi,\psi) \cos\iota \label{eq:Q}
 \ee
@@
 %
-Higher-order contributions up to and including 3.5PN can be found in Ref.~\cite{SchutzLRR}.
+Higher-order contributions to $\Psi_{+,\times}$ up to and including 3.5PN can be found in Ref.~\cite{SchutzLRR}.
 
@@
 %
-As angles have zero averages in general, we can think of the RMS as the standard deviation ($\sigma =2/5$). 
+As angles have zero averages in general, we can think of the RMS average as the standard deviation ($\sigma =2/5$). 
 %Therefore, $2\sigma= 4/5$ above the average (zero in this case) should statistically cover 95\% of the four-dimensional angle space. 
@@
 and $\psi=0$ for simplicity %(aligning the $x$-axis of the ``$+$'' with the of the IFO
-then introduce the following $\theta,\phi$-only averages
+then introduce the following $\{\theta,\phi\}$-only averages
 %
@@
 but it is our way of representing the sub-RMS-average response of the third IFO due to its sub-optimal configuration. 
-One may very well use another scheme to generate this below average response.
+One may very well use another scheme to generate this below-average response.
 
 To summarize, we introduced a model for a three-IFO network in which each IFO has identical sensitivity,
-but varying response to GWs due to IFO orientation and source polarization and sky position. This response is encoded in the quality factor $|Q_i|$.
+but varying response to GWs due to differing IFO orientations and source polarization and sky position. This response is encoded in the quality factor $|Q_i|$.
 We simulate this network's response to a single source by mapping the three different IFO responses to a single IFO's response to three distinct sources differing in amplitudes 
@@
 Column four lists the magnitude of the frequency-domain strain at each IFO via Eq.~(\ref{eq:Hi_s}).
-The last column shows how loud the GW strain is at a given IFO due source sky position and IFO orientation. 
+The last column states each IFO's response, e.g., high means high strain, thus high SNR.
+%shows how loud the GW strain is at a given IFO due source sky position and IFO orientation. 
 %oriented/positioned an IFO is with respect to a compact binary source. 
@@
 %Medium is the RMS-averaged (one $\sigma$) response. 
-Recall $A= \pi^{-2/3} \sqrt{5/24}$. Maximum value for $|Q_i|$ is 1, and minimum is 0.
+Recall $A= \pi^{-2/3} \sqrt{5/24}$. Maximum value for $|Q_i|$ is 1 and minimum is 0.
 %Note that for an interferometer where the angle between the arms is $\alpha$, $A$ rescales to $A\sin\alpha$.
@@
 However, the $60^\circ$ arm separation reduces the strain sensitivity of a V-shaped interferometer by a factor of $\sin 60^\circ=\sqrt{3}/2$ compared
-to an L-shaped interferometer with the same armlength. So for a single V-IFO the antenna patterns of (\ref{eq:F_plus}, \ref{eq:F_cross}) become
+to an L-shaped interferometer with the same armlength. Thus, for a single V-IFO the antenna patterns of Eqs.~(\ref{eq:F_plus}, \ref{eq:F_cross}) become
 %
@@
 \rho^2_{\text{tot},\bigtriangleup} & = \sum_{A=1}^3 \rho_A^2 \nn \\ % \f{c^2}{D^2}\left(\f{G M_c}{c^3}\right)^{5/3}
- & =  \f{5}{6}\, \pi^{-4/3} h_0^2\,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \, ,\label{eq:ET_SNRsq}
+ & =  4 A^2 h_0^2\,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \, ,\label{eq:ET_SNRsq}
 \end{align}
-where
+where $h_0$ is given by Eq.~(\ref{eq:h0}) and $A=\pi^{-2/3}\sqrt{5/24}$ as before and
 %
@@
 
-As we can not a priori know the source sky position or orientation we will model the response of ET using the RMS-averaged SNR %(\ref{eq:ET_SNRsq})
+As we can not a priori know the source sky position or polarization we model the response of ET using the RMS-averaged SNR %(\ref{eq:ET_SNRsq})
 %
@@
 \ee
-where $h_0$ is given by Eq.~(\ref{eq:h0}) and $A=\pi^{-2/3}\sqrt{5/24}$ as before. % from Sec.\ref{sec:LIGO_topo}. 
+% from Sec.\ref{sec:LIGO_topo}. 
 Accordingly, we define an RMS-averaged frequency-domain strain
@@
 \tilde{H}_\bigtriangleup(f)&\equiv A\,  \bar{Q}_\bigtriangleup\, h_0 f^{-7/6} \nn \\
-   & = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} f^{-7/6}. \label{eq:H_delta}
+   & = \f{1}{2}\sqrt{\f{3}{10}}\,{\pi^{-2/3}}\, \f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6} f^{-7/6}. \label{eq:H_delta}
 \end{align}
@@
 To compute the resulting SNRs, we will slightly modify the integrals in Eqs.~(\ref{eq:SNR_i}, \ref{eq:ET_SNR}) and 
-use design sensitivities of A-LIGO and ET's B and C configurations for $\sqrt{S_n(f)}$.
+use design sensitivities of A-LIGO and ET for $\sqrt{S_n(f)}$.
 Before we present our results, we list the various idealizations that we have adopted to simplify our computations.

### 2018-05-07 Paper/Manuscript.tex
Finished the corrections

@@
 To compute the resulting SNRs, we will slightly modify the integrals in Eqs.~(\ref{eq:SNR_i}, \ref{eq:ET_SNR}) and 
-use design sensitivities of A-LIGO and ET for $\sqrt{S_n(f)}$.
+use design sensitivities of Advanced LIGO (A-LIGO) and ET for $\sqrt{S_n(f)}$.
 Before we present our results, we list the various idealizations that we have adopted to simplify our computations.
@@
 $\tau_\text{insp}(f=100\,\text{Hz})\simeq 2.161\,$seconds according to Eq.~(\ref{eq:tau_insp}).
-And even at $f=100\,$Hz, a $m_1=m_2=1.4M_\odot$ neutron-star binary has separation $r\approx 155\,$km, which translates to a dimensionless strength of gravity of $\approx 2.6\%$.
+Moreoever, at $f=100\,$Hz, a $m_1=m_2=1.4M_\odot$ neutron-star binary has separation $r\approx 155\,$km, which translates to a dimensionless strength of gravity of $\approx 2.6\%$.
 This percentage is mostly accounted for by the post-Newtonian
@@
 but let us add that a faithful evaluation of BNS systems above $f\gtrsim 100\,$Hz is a very active and important branch of general relativity and gravitational-wave astronomy. 
+See the green dot-dashed curve in Fig.~\ref{fig:figGW170817} for an illustration of these effects.
 %, but beyond the scope of this article.
@@
 We artificially end the inspirals at the Schwarzschild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6GM/c^2$ and angular frequency $\Omega_\text{ISCO}$ %= (M/r^3_\text{ISCO})^{1/2}$ in natural units,
-given by Eq.~(\ref{eq:Sch_f_isco}) which translates to the following dominant-mode (quadrupole) GW frequency
+given by Eq.~(\ref{eq:Sch_f_isco}) which translates to the following dominant-mode (quadrupole) GW frequency at the ISCO
 \be
@@
 \end{tabular}
-\caption{The scaling of the physical quantities of interest in this article in terms the binary masses $m_1, m_2$ restricted to lie between $1.2M_\odot$ and $1.6 M_\odot$. 
+\parbox{16cm}{\caption{The scaling of the physical quantities of interest in this article in terms the binary masses $m_1, m_2$ restricted to lie between $1.2M_\odot$ and $1.6 M_\odot$. 
 %We used Kepler's third law to obtain $f \sim f_K \sim M^{1/2}$.
-Value$_{1.4M_\odot}$ represents the value of the quantities in column three evaluated at $m_1=m_2=1\, \text{mass unit}$ corresponding to $1.4 M_\odot$.
+Value$_{1.4M_\odot}$ represents the value of the quantities in column three evaluated at $m_1=m_2=1.4 M_\odot$ then rescaled to unity.
 %Unlike the orbital frequency $f_K$, the ISCO frequency $f_\text{ISCO}$ scales as $M^{-1}$ as shown in Eq.~(\ref{eq:f_isco}).
-}
+}}
 \label{tbl:scalings}
@@
 Moreoever, it seems that this variation tends to lengthen $\tau_\text{insp}$ more than shorten it thus our setting
-$m_1=m_2=1.4 M_\odot$ is more likely to underestimate $T_\text{AW}$ than overestimate it. 
+$m_1=m_2=1.4 M_\odot$ is more likely to underestimate $T_\text{AW}$ than overestimate it thus erring on the side of caution.
 %which is something we can live with.
-So we set $m_1=m_2=1.4 M_\odot$ henceforth.
+%So we set $m_1=m_2=1.4 M_\odot$ henceforth.
 %
@@
 yields zero, but if we consider $m_1=1.2 M_\odot, m_2=1.6 M_\odot$ then it gives $\approx 2\times 10^{-2}$ hence the ratio in Eq.~(\ref{eq:Oct_quad_ratio}) $\lesssim 10^{-3}$.
-Thus, we can neglect the current-quadrupole radiation completely. In a similar fashion, it can be shown that the power radiated by the mass octupole ($\ell=3$)
+Thus, we can neglect the current-quadrupole radiation completely. In a similar fashion, it can be shown that the power radiated by the mass octupole %($\ell=3$)
 scales the same way as in Eq.~(\ref{eq:Oct_quad_ratio}) with respect to the dominant mass quadrupole radiation, but is $\sim 50$ times smaller hence we can neglect it as well \cite{Maggiore}.
@@
 %
-where we introduced the dimensionless Kerr spin parameter $\chi\equiv {S}/({G m^2})$ which, for a neutron star (NS) with spin $S$ and mass $m$, can be written as
+where we introduced the dimensionless Kerr spin parameter $\chi\equiv {J}/({G m^2})$ which, for a neutron star (NS) with spin $J$ and mass $m$, can be written as
 %
@@
 A rather compact NS with $m=1.4 M_\odot, R=11\,\text{km}, P= 10\,\text{ms}$ has $\chi\lesssim 0.05$ whereas
-the fastest observed NS spin $\lesssim 0.04$ \cite{FastestNSspin}.
+the fastest observed NS spin is $\lesssim 0.04$ \cite{FastestNSspin}.
 Therefore, at $f= 100\,$Hz, the first term on the right-hand-side of Eq.~(\ref{eq:spin_orbit}) gives $\approx 4\times 10^{-4}$. 
-On the other hand, the spin-spin effects contribute at $\ord(v^4/c^4)\times\dot{E}$ hence $\lesssim \dot{E}_\text{SO}$.
+The other spin effect, the spin-spin coupling, contributes at $\ord(v^4/c^4)\times\dot{E}$ hence it is $\lesssim \dot{E}_\text{SO}$.
 Thus, NS spins can be neglected for our estimation of advance warning times. %$T_\text{AW}$.
@@
 When we take into account the effects of the large-scale structure of the universe, many quantities of interest are scaled by $(1+z)^\alpha$ where $\alpha$
-is the appropriate power. The standard treatment adopts a Friedmann-Robertson-Walker cosmology with scale factor $a(t)$ and curvature $k=\pm 1, \text{ or } 0$.
+is the appropriate power. The standard treatment adopts a Friedmann-Le Ma\^{i}tre-Robertson-Walker cosmology with scale factor $a(t)$ and curvature $k=\pm 1, \text{ or } 0$ \cite{cosm_book}.
 Introducing the subscript $s$ to denote quantities evaluated at the source frame, we have the following cosmological corrections
@@
 %
-Looking at Eqs.~(\ref{eq:fdot}, \ref{eq:tau_insp}, \ref{eq:h_c}) we spot a common factor of $M_c^{5/3}$ in all of them.
+We see that all three equations are rescaled by $(1+z)^{\pm5/3}$. 
+Now, looking at Eqs.~(\ref{eq:fdot}, \ref{eq:tau_insp}, \ref{eq:h_c}) we spot a common factor of $M_c^{\pm5/3}$ in all of them.
 Therefore, we can accommodate the cosmological effects by introducing the redshifted chirp mass $\mathcal{M}_c\equiv (1+z) M_c$
@@
 where $f$ is the usual frequency in the observer/detector frame.
-So we see that the effects of the cosmological redshifting can be accounted for by the transformation $M_c\rightarrow \mathcal{M}_c$.
+In short, the effects of the cosmological redshifting can be accounted for by the transformation $M_c\rightarrow \mathcal{M}_c$.
 This is because both $\dot{f}$ and the GW amplitude are governed by the time scale $G M_c/c^3$.
@@
 which corresponds to $z \approx 0.02$ which redshifts $f_\text{ISCO}$ by $\approx 2\%$ and reduces $\tau_\text{insp}$ by $\approx 7\%$.
-Therefore, we will neglect the effects of cosmological redshift 
+Therefore, we neglect the effects of cosmological redshift 
 when considering sources for the ALV network.
-On the other hand, for Einstein Telescope, we will go out to $D=1\,\text{Gpc}\implies z\approx 0.2$
-which reduces $\tau_\text{insp}$ by $\sim 25\%$, thus we shall include the redshift effects in our computations of advance warning times and SNRs
+On the other hand, for Einstein Telescope, we go out to $D=1\,\text{Gpc}\implies z\approx 0.2$
+which reduces $\tau_\text{insp}$ by $\approx 25\%$, thus we shall include the redshift effects in our computations of advance warning times and SNRs
 for which we provide the details in Sec.~\ref{Sec:ETB} (additional details can be found in, e.g., Ref.~\cite{Phinney:2001di}).
@@
 %The event, first picked up by LIGO Hanford (H1), 
-swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz, accumulating a total SNR of
+swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz, accumulating a total network SNR of
 %18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
@@
 
-For $S_\text{n}(f)$ we use actual [noise-subtracted] LIGO-Livingstone (L1) data for GW170817 from LIGO's website \cite{LIGO_L1_data}.
+For $S_\text{n}(f)$ we use actual [noise-subtracted] LIGO-Livingstone (L1) data for GW170817 available at LIGO's website \cite{LIGO_L1_data}.
 The data, sampled at 4096\,Hz, is given as a discrete time series $h(t_i)$ for a duration of 2048\,seconds in time steps of $\Delta t=1/4096\simeq 2.44\times 10^{-4}\,$seconds.
@@
 Hence it accumulated a much smaller SNR for GW170817.
-By 2020, Virgo should be operating at nearly the same sensitivity of LIGO.}.
+By 2020, Virgo should be operating at nearly the same sensitivity as LIGO.}.
 %To accommodate more realistic orientations, we show two shaded regions in Fig.~\ref{fig:figGW170817}. The inspirals in the lighter region yield SNR$\ge 22.34$ as
@@
 and rescaled to match our solid line at $f=10\,$Hz.
-The breakdown of the $\sqrt{f}f^{-7/6}=f^{-2/3}$ behavior of
-the strain around $f\sim100\,$Hz due to tidal effects is clear.
+The breakdown of the leading-order $\sqrt{f}f^{-7/6}=f^{-2/3}$ behavior of
+the inspiral around $f\sim100\,$Hz due to tidal effects is clear.
 %Note that although we extend the $\sqrt{f}f^{-7/6}=f^{-2/3}$ power law behavior of the strains all the way to ISCO, in actuality, this  starts breaking down .
@@
  Our predictive capabilities depend on how much advance warning the future networks will give us prior to the merger/GRB.
- Our definition of advance warning is the inspiral time to the merger from a certain threshold instant $\bar{t}$ at which point the network ``agrees'' that there is a GW transient
- statistically significant enough to issue warnings to electromagnetic telescopes.
+ Our definition of advance warning is the inspiral time to the merger from a certain threshold instant $\bar{t}$ at which point the network ``agrees'' that there is
+ an event statistically significant enough to issue warnings to electromagnetic telescopes.
  We define this threshold instant to be given at a frequency $\bar{f}$ when the total SNR equals 15. 
@@
 We now wish to quantify the forecasting capabilities of Einstein Telescope. To this end, we consider the inspiral of BNS systems
-at luminosity distances of $100,200,400,1000\,$Mpc entering the ET band. 
-These correspond to cosmological redshifts of $z\approx 0.0222,0.0437, 0.085, 0.198$, respectively.
+at luminosity distances of $100,200,400,1000\,$Mpc corresponding to cosmological redshifts of $z\approx 0.0222,0.0437, 0.085, 0.198$, respectively.
 To compute these, we used a flat $\Lambda$CDM model ($\Omega_k=0$) with the latest Planck satellite parameters: 
@@
 For the detector noise $\sqrt{S^\text{ET}_n(f)}$, we adopt the ASD for the B and C configurations known as ET-B and ET-C, respectively \cite{Hild:2010id}, which we plot as the solid dark (red) and light (brown) curves in Fig.~\ref{fig:ETB2030}.
-Sweeping across these are four BNS inspirals at $D=100,200,400,1000\,$Mpc represented by solid (black), dotted (blue), dashed (green),
+Sweeping across these are the RMS-averaged strains of four BNS inspirals at $D=100,200,400,1000\,$Mpc represented by solid (black), dotted (blue), dashed (green),
 and dot-dashed lines (gray), respectively. These strains sit much higher than the detector noise
@@
 the Einstein Telescope's sensitivity band for both B and C configurations.
-The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the redshift-corrected
+The solid (black), dotted (blue), dashed (green), and dot-dashed (gray) lines are the redshift-corrected
 RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
 The vertical lines with correspondingly identical patterns (colors) mark the redshifted ISCO frequencies $(1+z)^{-1} f_\text{ISCO}$ at which point we terminate each inspiral.
-As the true ISCO frequency is likely larger than $f_\text{ISCO}$ \cite{Marronetti:2003hx}, the inspirals would continue to nearly 2\,kHz indicated by the 
-faded lines in the plot (drawn to 5\,kHz for aesthetic reasons).
+In actuality, the inspirals continue beyond the test-mass $f_\text{ISCO}$, which we illustrate using the faded lines in the plot (drawn to 5\,kHz for aesthetic reasons).
+The plunge to merger is expected to occur at $f\approx 2\,$ kHz \cite{Marronetti:2003hx}.
 %However, numerical simulations indicate that the actual ISCO is smaller than the Schwarzschild value $6GM/c^2$ hence the true ISCO
@@
 %
-where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively for $D=100,200,400, 1000\,$Mpc.
-Table~\ref{table:ET} summarizes our results for both ET-B and ET-C where we chose to only display the 3.5PN-accurate inspiral time as $T_\text{AW}$,
+where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively for $D=100$ ,200,400, 1000\,Mpc.
+Table~\ref{table:ET} summarizes our results for both ET-B and ET-C where we chose to only display the 3.5PN-accurate inspiral time for $T_\text{AW}$,
 but we computed this quantity also using both 0PN and 2PN expressions as a consistency check.
@@
 \section{Binary black hole neutron star systems}\label{sec:BH_NS}
-In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
+We now investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
 The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
-such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $c_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$. 
+such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $c_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$,
+where $R_\text{NS}$ is the radius of the NS and $M$ denotes mass. 
 The evolution of black hole-neutron star (BH-NS) binaries is a very active field of research at the interface of numerical relativity and high-energy astrophysics
@@
 \ee
-where $r$ is the orbital radius, $R_\text{NS}$ is the radius of the NS and $M$ denotes masses. 
+where $r$ is the orbital separation.
 $c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to leading order with
 $c_R >1 $. %Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, 
-The above conditions roughly implies
+The above condition roughly implies
 %
@@
 %
+
 We wish to maximize the chances of observing a TD event, therefore we ingrain the BH-NS binary with certain desirable features
@@
  However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
- \item Low black hole mass. In the test-mass case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
+ \item Low black hole mass. In the test-mass case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force at the ISCO scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
  Hence, $M_\text{BH}$ must also be minimized. 
  As is the case with $r$, there is also a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models, which currently yield $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
- \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
- For instance, for the maximum dimensionless BH spin value of $a\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value $6GM_\text{BH}/c^2$ whereas for $a=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
+ \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black 
+ hole\footnote{Prograde orbits have $\hat{\mathbf{L}}\cdot\mathbf{J}=|\mathbf{J}|$ whereas for retrograde orbits $\hat{\mathbf{L}}\cdot\mathbf{J}=-|\mathbf{J}|$,
+ where $\mathbf{J}$ is the spin vector of the Kerr black hole.}.
+ For instance, for the maximum dimensionless BH spin value of $\chi\equiv c J_\text{BH}/(G M^2_\text{BH})=1$, $r_\text{ISCO}$ for prograde orbits is 1/6th of the Schwarzschild value $6GM_\text{BH}/c^2$ whereas for $\chi=1$ retrograde orbits, $r_\text{ISCO}$ is 3/2 of the Schwarzschild value.
  With smaller ISCO separation, there is much more tidal force exerted on the NS before it plunges in.
@@
 
-Although the results from each numerical study of BH-NS mergers may somewhat vary what is clear is that we must have high spin and low mass for the black hole for tidal disruption to happen. 
+Although the results from each numerical study of BH-NS mergers may somewhat vary, it is clear is that the BH-NS binary must have a high-spin, low-mass black hole for tidal disruption to happen. 
 We are thus led to set $M_\text{BH} =5 M_\odot$. 
 This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
-they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, thus they will have to gain mass.
+they are spun up by accretion from their secondary (that will later become a NS) in binary systems, thus inevitably gaining mass.
 It is possible that the mass gain pushes $M_\text{BH}$ too high to either cause a direct plunge of the NS before TD or decrease $\tau_\text{insp}$ considerably
 to eliminate any chances of getting an advance warning.
-However, if the spin of the BH comes from the supernova explosion mechanism itself as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
+However, if the spin of the BH comes from the supernova explosion mechanism as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
 low-mass BH in a binary system\footnote{We thank Dr. Morgan Fraser of UCD Astrophysics
@@
 %justify our choice for the chosen parameters above. 
-If we pick the more pessimistic $c_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $a\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}
-and $Q< 3$ in the case of $a=0$ \cite{Kyutoku:2011vz}.
+If we pick the more pessimistic $c_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $\chi\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}
+and $Q< 3$ in the case of $\chi=0$ \cite{Kyutoku:2011vz}.
 
@@
 From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
-Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
-there could be $\approx 30$ such mergers per year within ET-C's horizon distance of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
+Given that the A-LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
+there could be $\approx 30$ advance warnings of such mergers per year. %within ET-C's horizon distance of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
 We must emphasize that this should be viewed
@@
 \acknowledgements 
-SA thanks Conor O'Toole and Niels Warburton for endless feedback and a thorough perusal of this article.
+SA thanks Conor O'Toole for endless feedback, and Niels Warburton and L\'{a}na Salmon for a thorough perusal of this article.
 

### 2018-05-12 Paper/Manuscript.tex
Tweaked the figures

--- 2018-05-03 Paper/Manuscript.tex
@@
 \be
-\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}= \f{32}{5}\f{c^5}{G}x^5, \label{eq:Edot2}
-\ee
-%
-where $x = ({G M_c\, \Omega}/{c^3})^{2/3} $ is the dimensionless inverse separation parameter ubiquitous in post- Newtonian theory and $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs.
+\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}= \f{32}{5}\f{c^5}{G} \nu^2 x^5, \label{eq:Edot2}
+\ee
+%
+where $\omega=2\Omega$ is the angular frequency of the quadrupolar GWs, $\nu\equiv \mu/M$ is the symmetric mass ratio and $x = ({G M\, \Omega}/{c^3})^{2/3} $ is the dimensionless inverse separation parameter ubiquitous
+in post- Newtonian theory. 
 As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2}) that 
@@
 ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV2020 (dotted), ET-B (dashed), and ET-C (solid), respectively.
-The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (brown) lines coming from the $D^{-1}$ powerlaw of the SNR [see Eq.~(\ref{eq:ET_SNRv2})] which is plotted on the right axis.
+The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (blue) lines coming from the $D^{-1}$ powerlaw of the SNR [see Eq.~(\ref{eq:ET_SNRv2})] which is plotted on the right axis.
 We used $D=50,100,200\,$Mpc to obtain the ALV results (Sec.~\ref{Sec:ALIGO2020}) and $D=100,200,400,1000\,$Mpc for the ET results.}\label{fig:summary}

### 2018-06-11 Paper/Manuscript.tex
Change of reference
Added 3 new references and text accordingly

@@
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
-(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm} for the latest developments and references therein).
+(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm, Dietrich:2018phi} for the latest developments and references therein).
 Despite its simple formulation, our quadrupole radiation driven Newtonian
@@
 A rather compact NS with $m=1.4 M_\odot, R=11\,\text{km}, P= 10\,\text{ms}$ has $\chi\lesssim 0.05$ whereas
-the fastest observed NS spin $\lesssim 0.04$ \cite{FastestNSspin}.
+the fastest observed NS spin in a BNS system is $\lesssim 0.04$ \cite{0264-9381-26-7-073001}.
 Therefore, at $f= 100\,$Hz, the first term on the right-hand-side of Eq.~(\ref{eq:spin_orbit}) gives $\approx 4\times 10^{-4}$. 
@@
 due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}).
+In fact, detailed follow-up analyses (\cite{GW170817_2018}) have recently restricted the above-values to
+%
+$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001} ,  40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
+%
+where the errors in $D$ are at $1\sigma$ level.
 
@@
 by computing the SNRs accumulated by each individual IFO and by the entire network.
-To do so, we take the best-inferred values for $M,M_c,D$ from GW170817 given in Eq.~(\ref{eq:GW170817_params}) above and compute the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
+To do so, we take the originally-inferred values for $M,M_c,D$ from GW170817 given in Eq.~(\ref{eq:GW170817_params}) above and compute the SNRs $\rho_i, i=h,m,l$ via a slightly modified version of Eq.~(\ref{eq:SNR_i})
 %%
@@
  so it is desirable to minimize $Q$.
- Setting $M_\text{NS}=1.4 M_\odot$ as before gives $Q=5/1.4  \simeq 3.571$. $c_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range \cite{Ozel:2016oaf}
+ Setting $M_\text{NS}=1.4 M_\odot$ as before gives $Q=5/1.4  \simeq 3.571$.
+$c_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range \footnote{Recent work by the ALV collaboration \cite{GW170817_radii}) give bounds of $R_\text{NS}=9.1 -11.8\,$km, more or less consistent with astrophysical results.}\cite{Ozel:2016oaf}
  which results in $0.13\lesssim c_\text{NS} \lesssim 0.15$ 

### 2018-08-06 Paper/Manuscript.tex
Shibata's book aded

@@
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
-(see Ref.~\cite{Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm, Dietrich:2018phi} for the latest developments and references therein).
+(see Ref.~\cite{Shibata_book, Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm, Dietrich:2018phi} for the latest developments and references therein).
 Despite its simple formulation, our quadrupole radiation driven Newtonian

### 2018-08-06 Paper/Manuscript.tex
Fixed 2 typos

@@
 We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger.
-We define the moment of detection to be the instant at which the inteferometer network accumulates a signal-to-noise ratio of 15.
+We define the moment of detection to be the instant at which the interferometer network accumulates a signal-to-noise ratio of 15.
 %for the BNS inspiral.
@@
 %would be if L1was optimally positioned and oriented 
-(quality factor $|Q|=4/5=80\%$). Similarly, the solid line represents the strain in an identical inteferometer with 
+(quality factor $|Q|=4/5=80\%$). Similarly, the solid line represents the strain in an identical interferometer with 
 %a randomly oriented IFO with randomized source sky location, hence

### 2018-08-07 Paper/Manuscript.tex
Rewrite of a few sentences in Intro

@@
 we nonetheless supplement it with post-Newtonian corrections up to 3.5 post-Newtonian order (3.5PN) \cite{Blanchet_LRR}.
-However, even that fails to provide an accurate depiction of the binary
-evolution in the strong-field regime, where speeds $\gtrsim 0.1c$. This is a very complex and complicated problem requiring fully
-numerical treatment in terms of general relativistic, magnetohydrodynamic codes 
+However, beyond frequencies of $\sim 100\,$Hz the binary enters the strong-field regime where post-Newtonian
+approximation become insufficient to provide an accurate depiction of the inspiral.
+%evolution in the strong-field regime, where speeds exceed $0.1c$. 
+Instead, the strong-field evolution requires fully
+numerical treatment using general relativistic, magnetohydrodynamic codes 
 with neutrino transport running on large-scale computing clusters and taking up to millions of CPU hours 
 (see Ref.~\cite{Shibata_book, Faber:2012rw} for a review, and Refs.~\cite{Baiotti:2016qnr,Kyutoku:2017voj, Zappa:2017xba, Dietrich:2018upm, Dietrich:2018phi} for the latest developments and references therein).
-Despite its simple formulation, our quadrupole radiation driven Newtonian
-evolution is more than sufficient to provide reliable estimations of advance warning times.
-We support this claim in Sec.~\ref{sec:idealizations} with an extensive list of computations showing how much each of our approximations affects the inspiral time.
+Nonetheless, despite its simple formulation, our quadrupole radiation driven [post]-Newtonian
+evolution is more than sufficient to provide reliable estimations of advance warning times with an error of $\lesssim 1\,$second.
+We support this claim in Sec.~\ref{sec:idealizations} with an extensive list of computations which show how much each one of our approximations affects the inspiral time.
 

### 2018-08-10 Paper/Manuscript.tex
Vivek paper added to Refs and mentioned in footnote 2.
Some minor corrections

@@
 high-eccentricity binary black hole mergers in the vicinity of galactic nuclei due close encounter captures \cite{OLeary:2008myb}.
-However, it is not clear how much this applies to BNS systems.}.
+However, it is not clear how much this applies to BNS systems, nonetheless see Ref.~\cite{Chaurasia:2018zhg} for a recent numerical study of an eccentric BNS merger.}.
 %for binary systems
@@
 In other words, all inspiralling BNSs closer than $D_H$ will give us more than an hour's leeway before the GRB (employing the detection criterion $\text{SNR} =15$ as before).
-The volume set by $D=D_H$ translates to a BNS merger rate of $\sim\mathcal{O}(1)$ for ET-B and
-$\approx 355^{+730}_{-280}\,\text{year}^{-1}$ for ET-C. Additionally, each source within $D_H$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
+The volume set by $D=D_H$ translates to a BNS merger rate of $\sim\mathcal{O}(1)\,\text{yr}^{-1}$ for ET-B and
+$\approx 355^{+730}_{-280}\,\text{yr}^{-1}$ for ET-C. Additionally, each source within $D_H$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
 in the ET-B, ET-C bands, respectively. These results are summarized in Table~\ref{table:horizon}.
@@
 The treatment of the inspiral is the same as before, however the fate of the neutron star depends strongly on the system's intrinsic parameters
-such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $c_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$. 
+such as the black hole mass and spin, and the neutron star's equation of state (EOS) and compactness $\mathcal{C}_\text{NS}\equiv G M_\text{NS}/(R_\text{NS}c^2)$. 
 The evolution of black hole-neutron star (BH-NS) binaries is a very active field of research at the interface of numerical relativity and high-energy astrophysics
@@
  With smaller ISCO separation, there is much more tidal force exerted on the NS before it plunges in.
- \item Less compact neutron stars. Eq.~(\ref{eq:TD_cond1}) can be rearranged to isolate $c_\text{NS}$
- on the right hand side. Smaller values for $c_\text{NS}$ mean that TD is more likely to occur for $r>r_\text{ISCO}$.
+ \item Less compact neutron stars. Eq.~(\ref{eq:TD_cond1}) can be rearranged to isolate $\mathcal{C}_\text{NS}$
+ on the right hand side. Smaller values for $\mathcal{C}_\text{NS}$ mean that TD is more likely to occur for $r>r_\text{ISCO}$.
 \end{enumerate}
@@
  Setting $M_\text{NS}=1.4 M_\odot$ as before gives $Q=5/1.4  \simeq 3.571$.
-$c_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range \footnote{Recent work by the ALV collaboration \cite{GW170817_radii}) give bounds of $R_\text{NS}=9.1 -11.8\,$km, more or less consistent with astrophysical results.}\cite{Ozel:2016oaf}
- which results in $0.13\lesssim c_\text{NS} \lesssim 0.15$ 
+$\mathcal{C}_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range \footnote{Recent work by the ALV collaboration \cite{GW170817_radii}) give bounds of $R_\text{NS}=9.1 -11.8\,$km, more or less consistent with astrophysical results.}\cite{Ozel:2016oaf}
+ which results in $0.13\lesssim \mathcal{C}_\text{NS} \lesssim 0.15$ 
  for our chosen NS mass. 
@@
 %justify our choice for the chosen parameters above. 
-If we pick the more pessimistic $c_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $a\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}
+If we pick the more pessimistic $\mathcal{C}_\text{NS} = 0.15$ bound then we must have $Q\lesssim 5$ and $a\gtrsim 0.5$ (prograde) for TD to occur \cite{Ferrari:2008nr}
 and $Q< 3$ in the case of $a=0$ \cite{Kyutoku:2011vz}.

### 2018-08-16 Paper/Manuscript.tex
Final review, modulo figures and TT gauge sentence

@@
 For our computations, %of advance warning times, 
-we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc in the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc in the Einstein Telescope's B and C configurations.
+we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc for the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc for Einstein Telescope's B and C configurations.
 In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time, thus we expect no forecast of GRBs in the 2020s. 
@@
 The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \simeq 95\%$ significance hence 6.95 overall.}
-gravitational-wave merger events detected by the Advanced Ligo-Virgo network have firmly established gravitational-wave astronomy
+gravitational-wave merger events detected by the Advanced LIGO-Virgo network have firmly established gravitational-wave astronomy
 as an observational science \cite{TheLIGOScientific:2016pea, Abbott:2017gyy, Abbott:2017oio, Abbott:2017vtc, GW170817}. 
@@
 This subsequently launched a massive campaign of multi-messenger astronomy across the entire electromagnetic (EM) spectrum which is still ongoing
-more than half a year after the initial GRB \cite{GBM:2017lvd}.
+a year after the initial GRB \cite{GBM:2017lvd}.
 
@@
 using a template bank of gravitational waveforms computed within the framework of post-Newtonian theory \cite{Buonanno:2009zt, Blanchet_LRR}.
-The inspiral swept across the Advanced Ligo-Virgo (ALV) network's bandwidth from approximately $ 30\,$Hz to about $ 2\,$kHz in 57 seconds,
+The inspiral swept across the Advanced LIGO-Virgo (ALV) network's bandwidth from approximately $ 30\,$Hz to about $ 2\,$kHz in 57 seconds,
 executing nearly $ 3000$ gravitational wave cycles and accumulating a network signal-to-noise ratio of 32.4 with a false-alarm rate of one per $8.0\times 10^4$ years \cite{GW170817}. 
@@
 Moreover, both the gravitational wave (GW) and EM observations were consistent with a source location in the galaxy in NGC4993 
-at a luminosity distance of $\sim\!\! 40\,$Mpc,
-and supported the hypothesis that GW170817 resulted from the inspiral and merger of two neutron stars, 
-causing a prompt short-hard gamma-ray burst (GRB170817A) as first suggested by Ref.~\cite{Eichler:1989ve}.
+at a luminosity distance of $\sim\! 40\,$Mpc, and supported the hypothesis that GW170817 resulted from the
+inspiral and merger of two neutron stars, causing the prompt short-hard gamma-ray burst GRB170817A. %as 
+This BNS-GRB connection was first proposed in Ref.~\cite{Eichler:1989ve} and the events of 17 August 2017 are
+the first astrophysical evidence for it.
 
 A week after GW170817, the ALV network was taken offline for upgrades for the third observation run (O3) 
-scheduled to start in Autumn 2018 with roughly twice the sensitivity of O2.
+scheduled to start in early 2019 with roughly twice the sensitivity of O2.
 In addition, the Japanese cryogenic interferometer KAGRA (\cite{KAGRA, KAGRA2}) will start its test runs in 2018-2019 and reach its design sensitivity circa 2021-2022 \cite{Akutsu:2017thy, Aasi:2013wya}.
@@
 Around this time, the construction of the first third-generation ground-based interferometer, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
-Meanwhile, the US is currently considering a mid-2020s update to LIGO called Voyager \cite{LIGO_Voy} and the construction of a more ambitious 40\,km long interferometer dubbed The Cosmic Explorer \cite{CE}.
+Meanwhile, the US is currently considering a mid-2020s update to LIGO called Voyager \cite{LIGO_Voy} and the construction of a more ambitious 40\,km long interferometer dubbed Cosmic Explorer \cite{CE}.
 All of these near-future additions to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
@@
 As such, most GRBs that occur in the universe are electromagnetically undetectable. Fortunately, this was not the case with GRB170817A, 
-but even for a reasonable GRB jet opening angle of $\sim 10^\circ$, we expect to observe $\sim 10\%$ of neutron star mergers as GRBs \cite{Patricelli:2016bkt}. 
+but even for a reasonable GRB jet opening angle of $\sim 10^\circ$, we expect to observe at best $\sim 10\%$ of neutron star mergers as GRBs \cite{Patricelli:2016bkt}. 
 However, it is possible that some of the near-Earth pointing short hard GRBs may be observed as long-duration GRBs or X-ray flashes thus increasing this percentage \cite{Bucciantini:2011kx}.
@@
 %thus leave the task of reducing the latency to the experts.
-More specifically, we wish to find out how much early warning the GW detectors can provide us before the merger/GRB.
+More specifically, we wish to find out how much early warning future GW detectors can provide us before the merger/GRB.
 Ref.~\cite{Cannon:2011vi} approached this from an algorithmic perspective by developing computationally inexpensive methods to detect inspiral
@@
 This article is organized as follows. Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
-Sec.~\ref{sec:IFO_response} details the interferometer response to GWs based on topology.
+Sec.~\ref{sec:IFO_response} details the interferometer response to GWs based on interferometer topology.
 Sec.~\ref{sec:idealizations} lists the various idealizations we employ to simplify our treatment and supplies justification for each.
@@
 In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of binary black hole - neutron star inspirals to see whether or not 
-future detectors can forecast a tidal disruption event, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
-
-Throughout the text, $t$ denotes observer/detector time and $f$ denotes the GW frequency of the dominant quadrupole mode in observer/detector frame. 
+future detectors can forecast tidal disruption events, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
+
+Throughout the text, $t$ denotes observer/detector time and $f$ denotes the \emph{GW frequency} of the dominant quadrupole mode in observer/detector frame. 
 %$f$ is twice the orbital (Keplerian) frequency $f_K$. 
@@
 Here, $Q_{ij}$ is a trace-reversed mass quadrupole moment which
-is the dominant contribution to the power emitted %in gravitational radiation
+gives the dominant contribution to the power emitted %in gravitational radiation
 by a system with changing mass moments. Details of how to obtain this expression can be found in Ref.~\cite{Maggiore}.
@@
 in post- Newtonian theory. 
-As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2}) that 
-at the leading order, power emitted in GWs scales as $x^5$.
+As $x\propto v^2/c^2$, it is used to keep track of post-Newtonian orders and we can see from Eq.~(\ref{eq:Edot2})
+that, at the leading order, power emitted in GWs scales as $x^5$.
 %hence the common statement in the literature saying that gravitational radiation starts
@@
 
-We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T_K(t)$ varies over a time scale much larger than $T_K$ itself
+We can also compute the number of GW cycles over the course of an inspiral. Given that the orbital period $T_K(t)$ varies over a time scale much larger than itself
 we can write
@@
 %meaning that we are considering the solutions far from the GW source, 
-In a suitable gauge, such as the commonly used transverse-traceless gauge, 
-it can be shown that there exist only two physical degrees of freedom which manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs.
-%when interacting with masses away from the source.
-For a binary in a circular orbit, these states read \cite{Maggiore}
+%
+It can further be shown that there exist only two radiative degrees of freedom which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs 
+This fact is most easily demonstrated in the so-called transverse-traceless gauge (cf. Sec.~2.1 of Ref.~\cite{Flanagan:2005yc}). %when interacting with masses away from the source.
+
+%In a suitable gauge, such as the commonly used transverse-traceless gauge, 
+%In the ``lab'' frame, usually taken to be the transverse-traceless gauge, 
+The two polarization states generated by a binary in a circular orbit read \cite{Maggiore}
 %
@@
 The nomenclature ``plus'' ($+$) and ``cross'' ($\times$) follows from the effects that passing GWs have on the plane transverse to their direction of propagation.
-If we were to conceive of a ``toy'' detector made up of a circular configuration of test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress this circular arrangement in a $+$ and $\times$ pattern
+If we were to conceive of a ``toy'' detector made up of a circularly arranged test-masses lying in the $x$-$y$ plane, a GW propagating along the $z$ direction would stretch/compress this circular arrangement in a $+$ and $\times$ pattern
 with a $90^\circ$ phase difference between the two states.
@@
 We start by first considering the L-shaped interferometer topology dating back to Michelson \cite{Michelson:1887zz}.
-Although the GWs are described by propagating tensor modes, an interferometer (IFO) can only measure a scalar quantity
+Although GWs are described by propagating tensor modes, an interferometer (IFO) can only measure a scalar quantity
 known as the response function (or GW strain) which is a linear combination of the polarizations given by
@@
 In the the case of GW170817 which swept the ALV network over roughly 3000 GW cycles, 
-the source sky localization was 28\,deg$^2$ using data from three IFOs \cite{GW170817}. 
+the initial source sky localization was 31\,deg$^2$ (later reduced to 28\,deg$^2$) using data from three IFOs \cite{GW170817}. 
 For our estimations, we employ suitable averages of these angles as explained below.
@@
 
-To compute the advance warning times we need to know how ``loud'' the binaries become as they sweep across the IFO's detection bandwidth.
-This is given by the signal-to-noise ratio (SNR) of the GWs in the detectors' bandwidth.
-The SNR is computed in the frequency domain so we Fourier-transform the time-domain strains of Eqs.~(\ref{eq:hplus_TD}) and (\ref{eq:hcross_TD}) to obtain
+To compute advance warning times we need to know how ``loud'' neutron star binaries become as they sweep across an IFO's detection bandwidth.
+This is quantified in terms of the GW signal-to-noise ratio (SNR) accumulated in a detector's bandwidth during the inspiral.
+The SNR is computed in the frequency domain so we first Fourier-transform the time-domain strains of Eqs.~(\ref{eq:hplus_TD}) and (\ref{eq:hcross_TD}) to obtain
 %
@@
 but varying response to GWs due to differing IFO orientations and source polarization and sky position. This response is encoded in the quality factor $|Q_i|$.
-We simulate this network's response to a single source by mapping the three different IFO responses to a single IFO's response to three distinct sources differing in amplitudes 
-from the optimal case by quality factors $|Q_i|= 4/5,2/5,$ and $4/5-\sqrt{2/5}$.
+%We simulate this network's response to a single source by mapping the three different IFO responses to a single IFO's response to three distinct sources differing in amplitudes 
+%from the optimal case by quality factors $|Q_i|= 4/5,2/5,$ and $4/5-\sqrt{2/5}$.
 %
@@
 %
-which is independent of $\phi$ \cite{Regimbau:2012ir}. We once again take the RMS average of this quantity
+which is independent of $\phi$ \cite{Regimbau:2012ir}. We once again take the RMS average of this quantity:
 %$Q(\theta,\phi,\psi,\iota)$ is the quality factor of the detector.
@@
 %
-This is ET's sky-averaged response to a BNS inspiral at luminosity distance $D$ and chirp mass $M_c$.
+This is ET's sky-averaged response to a binary inspiral at luminosity distance $D$ and chirp mass $M_c$.
 %It is this strain that we use as a typical ET BNS source; 
@@
 \be
-f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571\,\text{Hz} \label{eq:f_isco}
-\ee
-for $M \equiv m_1+m_2 = 2.8 M_\odot$. In the strong-field, highly-dynamical spacetime of the last few orbits, the
+f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571 \left(\f{2.8M_\odot}{M}\right)\text{Hz} \label{eq:f_isco}.
+\ee
+%for $M \equiv m_1+m_2 = 2.8 M_\odot$. 
+In the strong-field, highly-dynamical spacetime of the last few orbits, the
 concept of an ISCO becomes fuzzy due to strong dissipative effects. However, an ISCO can nonetheless be dynamically determined
@@
 ranging from $\approx 1.2 M_\odot$ to $\approx 1.5 M_\odot$. 
-Additionally, the masses involved in GW170817 are inferred to be between $1.17 M_\odot$ and $1.60 M_\odot$ \cite{GW170817}.
+On the other hand, the masses involved in GW170817 are inferred to be between $1.17 M_\odot$ and $1.60 M_\odot$ \cite{GW170817}.
 Therefore, let us restrict the masses to lie between $1.2 M_\odot$ and $1.6 M_\odot$, then focus on % ranges $R_{1,2} \in [1,2]/(1.4)$. 
@@
 The ranges in column four show that $\tilde{H}$ changes roughly by $\pm 10\%$ across the $1.2M_\odot-1.6M_\odot$ mass range whereas the variation
-in $f_\text{ISCO}$ matters not as it affects the advance warning times by less than a second (see above).
+in $f_\text{ISCO}$ should not matter as it affects the advance warning times by less than a second (see above).
 The inspiral time seems to be more sensitive to our chosen mass values as indicated by the $\sim{}^{+60\%}_{-30\%}$ variation 
@@
 %which is something we can live with.
-So we set $m_1=m_2=1.4 M_\odot$ henceforth.
+%So we set $m_1=m_2=1.4 M_\odot$ henceforth.
 %
@@
 for a system with initial parameters $a_i, e_i$.
-Let us apply this to the Hulse-Taylor binary pulsar \cite{Hulse:1974eb,Weisberg:2010zz} to show that the BNS orbits circularize by the time they enter the interferometers' bandwidth.
-Letting $f = 1\,\text{Hz}=2f_K$, i.e., 
+Let us apply this to the Hulse-Taylor binary pulsar \cite{Hulse:1974eb,Weisberg:2010zz} to show that the BNS orbits circularize by the time they enter the interferometers' bandwidth (ca. $1-10\,$Hz).
+Therfore, letting $f =2f_K= 1\,\text{Hz}$, i.e., 
 $a \simeq 3352\,$km and using the currently observed values $a_i \approx 1.95\times 10^6\,$km and $e_i \approx 0.617$,
-we obtain $e\approx 6\times 10^{-5}$. Thus our setting $e=0$ is very reasonable\footnote{
+we obtain $e\approx 6\times 10^{-5}$ at 1\,Hz. Thus our setting $e=0$ is very reasonable\footnote{
 It is possible to have 
@@
 the next-to-leading order contribution is two orders of magnitude smaller.
-The ratio in Eq.~(\ref{eq:Oct_quad_ratio}) is further supressed by $(m_2-m_1)/M^2$ which, for our idealized equal-mass system, 
+The ratio in Eq.~(\ref{eq:Oct_quad_ratio}) is further supressed by $(m_2-m_1)^2/M^2$ which, for our idealized equal-mass system, 
 yields zero, but if we consider $m_1=1.2 M_\odot, m_2=1.6 M_\odot$ then it gives $\approx 2\times 10^{-2}$ hence the ratio in Eq.~(\ref{eq:Oct_quad_ratio}) $\lesssim 10^{-3}$.
@@
 Therefore, at $f= 100\,$Hz, the first term on the right-hand-side of Eq.~(\ref{eq:spin_orbit}) gives $\approx 4\times 10^{-4}$. 
-On the other hand, the spin-spin effects contribute at $\ord(v^4/c^4)\times\dot{E}$ hence $\lesssim \dot{E}_\text{SO}$.
+On the other hand, the spin-spin coupling contributes at $\ord(v^4/c^4)\times\dot{E}$ hence $\lesssim \dot{E}_\text{SO}$.
 Thus, NS spins can be neglected for our estimation of advance warning times. %$T_\text{AW}$.
@@
 %
-Looking at Eqs.~(\ref{eq:fdot}, \ref{eq:tau_insp}, \ref{eq:h_c}) we spot a common factor of $M_c^{5/3}$ in all of them.
+Looking at Eqs.~(\ref{eq:fdot}, \ref{eq:tau_insp}, \ref{eq:h_c}) we spot a common factor of $M_c^{\pm5/3}$ in all of them.
 Therefore, we can accommodate the cosmological effects by introducing the redshifted chirp mass $\mathcal{M}_c\equiv (1+z) M_c$
@@
 %
-where $f$ is the usual frequency in the observer/detector frame.
-So we see that the effects of the cosmological redshifting can be accounted for by the transformation $M_c\rightarrow \mathcal{M}_c$.
+where $f$ is the usual GW frequency in the observer/detector frame.
+So, we see that the effects of the cosmological redshifting can be accounted for by the transformation $M_c\rightarrow \mathcal{M}_c$.
 This is because both $\dot{f}$ and the GW amplitude are governed by the time scale $G M_c/c^3$.
-Therefore, the inspiral evolves faster in the lab frame %because $\dot{f}$ has increased and the cut-off frequency has decreased.
+Accordingly, the inspiral evolves faster in the lab frame %because $\dot{f}$ has increased and the cut-off frequency has decreased.
 and we must now terminate it at a redshifted GW ISCO frequency which is less than $f_\text{ISCO}$ of Eq.~(\ref{eq:f_isco}).
@@
 %
-$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001} ,  40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
+$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001}M_\odot , 40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
 %
@@
 How well does the ``naive'' Newtonian evolution based on the quadrupole formula perform? 
-To test this, let us first compute the inspiral time, $\tau_\text{insp}$, and the number of GW cycles, $\mathcal{N}_\text{cyc}$, for this BNS system with initial frequency $f_i=30\,$Hz and final frequency $f_\text{ISCO} \simeq 1605\,$Hz.
+To test this, let us first compute the inspiral time, $\tau_\text{insp}$, and the number of GW cycles, $\mathcal{N}_\text{cyc}$, for this BNS system with initial frequency $f_0=30\,$Hz and final frequency $f_\text{ISCO} \simeq 1605\,$Hz.
 Eqs.~(\ref{eq:tau_insp}) and (\ref{eq:Ncyc1}) provide us with the leading-order values
@@
 If we wish to do better, we can add all of the known post-Newtonian contributions 
-(up to 3.5PN\footnote{Although the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
-explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$. Be that as it may, we suspect that a few PN experts have already obtained these.}) resulting in
+up to 3.5PN\footnote{Although the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
+explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$. Be that as it may, we suspect that a few PN experts have already obtained these.} resulting in
 %%
@@
 We also show the Hanford detector's sensitivity in light blue for comparison. The dashed, solid and dotted lines represent the 
-frequency-domain GW strains ($2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$) due to the inspiral of
+frequency-domain GW strains [$2\sqrt{f} \tilde{H}_i(f)$ with $i=h,m,l$] due to the inspiral of
 a binary neutron star system with parameters given in Eq.~(\ref{eq:GW170817_params}).
@@
  and the Einstein Telescope era in the 2030s.
- Our predictive capabilities depend on how much advance warning the future networks will give us prior to the merger/GRB.
+ Our EM follow-up capabilities will depend on how much advance warning the future networks will give us prior to the merger/GRB.
  Our definition of advance warning is the inspiral time to the merger from a certain threshold instant $\bar{t}$ at which point the network ``agrees'' that there is a GW transient
@@
   \caption{Flow diagram summarizing our procedure for computing advance warning times $T_\text{AW}$ with the Advanced-LIGO-Virgo network. 
-  We compute $T_\text{AW}$ for BNS systems with $M=2.8M_\odot$ inspiralling at $D=50,100,200\,$Mpc. 
+  We compute $T_\text{AW}$ for BNS systems with $m_1=m_2=1.4M_\odot$ inspiralling at $D=50,100,200\,$Mpc. 
   %for A-LIGO and $D=200,400,1000\,$Mpc for the ET.
@@
 \be
-\bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2} \label{eq:SNR_bar_FINAL}\, .
-\ee
-%
-%
+\bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2} \label{eq:SNR_bar_FINAL}\, ,
+\ee
+%
+%
+where $f_\text{ISCO}$ is given by Eq.~(\ref{eq:f_isco}).
 We will introduce the corresponding expressions for ET in Sec.~\ref{Sec:ETB}.
@@
 \includegraphics[width=\linewidth]{../Figures/ALigo_strains.pdf}
-\caption{Typical $m_1=m_2=1.4 M_\odot$ BNS inspirals sweeping across the Advanced LIGO-Virgo network in the 2020s.
-These may be the harbingers of short-hard GRBs.
+\caption{Typical $m_1=m_2=1.4 M_\odot$ BNS inspirals sweeping across the Advanced LIGO-Virgo network in the 2020s
+which may be the harbingers of short-hard GRBs.
 %inspiralling BNS systems sweeping across the most sensitive interferometer frequencies.
@@
 the Einstein Telescope's sensitivity band for both B and C configurations.
-The solid (black), dotted (blue), dashed (green), and dot-dashed lines (gray) lines are the redshift-corrected
+The solid (black), dotted (blue), dashed (green), and dot-dashed (gray) lines are the redshift-corrected
 RMS-averaged strains, $2\sqrt{f}\tilde{H}_\text{ET}$, at luminosity distances of $D=100, 200, 400, 1000\,$Mpc, respectively. 
@@
 As the true ISCO frequency is likely larger than $f_\text{ISCO}$ \cite{Marronetti:2003hx}, the inspirals would continue to nearly 2\,kHz indicated by the 
-faded lines in the plot (drawn to 5\,kHz for aesthetic reasons).
+faded lines in the plot (drawn to ca. 5\,kHz for aesthetic reasons).
 %However, numerical simulations indicate that the actual ISCO is smaller than the Schwarzschild value $6GM/c^2$ hence the true ISCO
@@
 %
-where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively for $D=100,200,400, 1000\,$Mpc.
+where $f_\text{ISCO}$ is now the redshifted version of Eq.~(\ref{eq:f_isco}), equalling $1537, 1505, 1448, 1311\,$Hz, respectively for $D=100,200,400,$ 1000\,Mpc.
 Table~\ref{table:ET} summarizes our results for both ET-B and ET-C where we chose to only display the 3.5PN-accurate inspiral time as $T_\text{AW}$,
@@
 \end{tabular}
-\caption{Forecasting capabilities of Einstein Telescope summarized. 
+\caption{Forecasting capabilities of Einstein Telescope. 
 %We can expect over \emph{five} hours of early warning for nearby sources. 
@@
 Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's horizon distance) will persist in the ET-C sensitivity band for a few hours after their initial detection ($T_\text{AW} > 2\,$ hours).
-Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET.
+Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET-C.
 
@@
 \caption{Summary of our major findings for both the Advanced-LIGO-Virgo (ALV) network circa 2020 and the Einstein Telescope's B and C configurations
-ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV2020 (dotted), ET-B (dashed), and ET-C (solid), respectively.
+ca. 2030. The light coloured (gray) data shows $T_\text{AW}$ for the ALV2020 (dotted), ET-B (dashed), and ET-C (solid), respectively, with the corresponding axis on the left.
 The connecting light (gray) lines are drawn only for visualization purposes unlike the dark (blue) lines coming from the $D^{-1}$ powerlaw of the SNR [see Eq.~(\ref{eq:ET_SNRv2})] which is plotted on the right axis.
@@
 where $r$ is the orbital radius, $R_\text{NS}$ is the radius of the NS and $M$ denotes masses. 
-$c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shaped of the NS to leading order with
+$c_R R_\text{NS}$ is the semi-major axis of the elongated oblate spheroid that represents the tidally distorted shape of the NS to leading order with
 $c_R >1 $. %Setting $m_2= M_\text{BH}, m_1 = M_\text{NS}$, and $r_1=r_\text{NS}$, 
-The above conditions roughly implies
+The above condition roughly implies
 %
@@
  However, for $r< r_\text{ISCO}$ the NS simply plunges into the BH; therefore the minium separation is given by the ISCO radius.
- \item Low black hole mass. In the test-mass case, $r_\text{ISCO} \propto M_\text{BH}$, so the Newtonian tidal force roughly scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
+ \item Low black hole mass. In the test-mass case, $r_\text{ISCO} \propto M_\text{BH}$, so the maximum Newtonian tidal force roughly scales as $M_\text{BH}/r_\text{ISCO}^3\propto M_\text{BH}^{-2}$. 
  Hence, $M_\text{BH}$ must also be minimized. 
- As is the case with $r$, there is also a lower bound to $M_\text{BH}$ set from astrophysical observations and stellar evolution models, which currently yield $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
+ There is a lower bound to it set from astrophysical observations and stellar evolution models, which currently yield $M_\text{BH} \gtrsim 5 M_\odot$ \cite{Farr:2010tu, Raithel:2017nlc, Ozel:2010su, Wiktorowicz:2013dua, Christian:2018mjv}.
  \item High black hole spins. $r_\text{ISCO}$ is much smaller in the case of a prograde NS orbit around a spinning Kerr black hole.
@@
 We are thus led to set $M_\text{BH} =5 M_\odot$. 
-This raises an interesting astrophysical question as to whether it is possible to have such light-weight high-spin black holes assuming that
+This raises an interesting astrophysical question as to whether it is possible to have such light-weight, high-spin black holes assuming that
 they are spun up by accretion from their secondary (that will later on become a NS) in binary systems, thus they will have to gain mass.
@@
 to eliminate any chances of getting an advance warning.
-However, if the spin of the BH comes from the supernova explosion mechanism itself as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
-low-mass BH in a binary system\footnote{We thank Dr. Morgan Fraser of UCD Astrophysics
+However, if the spin of the BH comes from the supernova explosion mechanism as argued for G1915 in Ref.~\cite{McClintock:2006xd} then it is possible to have a 
+low-mass, high-spin BH in a binary system\footnote{We thank Dr. Morgan Fraser of UCD Astrophysics
 for pointing this out.}.
@@
 There is additional motivation to choose low BH mass as 
- $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv M_\text{BH}/M_\text{NS} > 1$, which scales as $Q^{-2/3}$ as $Q\to\infty$ , i.e., heavier binaries inspiral faster
+ $\tau_\text{insp} \propto M_c^{-5/3} = (1+Q)^{1/3}/Q$ for $Q\equiv M_\text{BH}/M_\text{NS} > 1$, which scales as $Q^{-2/3}$ as $Q\to\infty$ , i.e., binaries with heavier BHs inspiral faster
  so it is desirable to minimize $Q$.
  Setting $M_\text{NS}=1.4 M_\odot$ as before gives $Q=5/1.4  \simeq 3.571$.
-$\mathcal{C}_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range \footnote{Recent work by the ALV collaboration \cite{GW170817_radii}) give bounds of $R_\text{NS}=9.1 -11.8\,$km, more or less consistent with astrophysical results.}\cite{Ozel:2016oaf}
+$\mathcal{C}_\text{NS}$ is determined by the radius of the NS constrained to be in the $9.9 - 11.2\,$km range\footnote{Recent work by the ALV collaboration \cite{GW170817_radii}) give bounds of $R_\text{NS}=9.1 -11.8\,$km, more or less consistent with astrophysical results.}\,\cite{Ozel:2016oaf}
  which results in $0.13\lesssim \mathcal{C}_\text{NS} \lesssim 0.15$ 
@@
 \acknowledgements 
-SA thanks Conor O'Toole and Niels Warburton for endless feedback and a thorough perusal of this article.
+I am grateful to Conor O'Toole for endless feedback and Niels Warburton, Richard A. Matzner and Alberto Sesana for reviewing this manuscript.
 

### 2018-08-26 Paper/Manuscript.tex
Tables stylized, final tweaks. Ready modulo Sesana input. Might want to MaTeX the figures later in Mathematica

@@
 %
-It can further be shown that there exist only two radiative degrees of freedom which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs 
-This fact is most easily demonstrated in the so-called transverse-traceless gauge (cf. Sec.~2.1 of Ref.~\cite{Flanagan:2005yc}). %when interacting with masses away from the source.
+It can further be shown that there exist only two radiative degrees of freedom (cf.
+Sec.~1.2 of Ref.~\cite{Maggiore}) which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs
+This fact is most easily demonstrated in the so-called transverse-traceless gauge (cf. Sec.~2.1 of Ref.~\cite{Flanagan:2005yc}),
+ but is a gauge-invariant consequence of linearized vacuum solutions. %when interacting with masses away from the source.
 
@@
 \centering
-\begin{tabular}{c|c|c|c|c}
+\begin{tabular}{ccccc}
+\hline\hline
  IFO$_i$  %& $\langle |Q_i|^2\rangle$ 
- & $|Q_i|$ & $\tilde{A}_i$ & $\tilde{H}_i(f)$ & IFO response \\
+ & $|Q_i|$ & $\tilde{A}_i$ & $\tilde{H}_i(f)$ & IFO response\T\B \\
  %\hline
@@
  2 &  $\tfrac{2}{5} $ & $\tfrac{2}{5}A$ & $ \tfrac{2}{5}A h_0 \, f^{-7/6}$ & medium ($m$)\B\T \\
- 3 &  $\tfrac{4}{5}-\sqrt{\tfrac{2}{5}} $ & $\left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A$ & $ \left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A h_0 \, f^{-7/6}$& low ($l$) \B \\
- \hline
+ 3 &  $\quad \tfrac{4}{5}-\sqrt{\tfrac{2}{5}} \quad $
+ & $\quad\left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A \quad$ & $\quad \left(\tfrac{4}{5}-\sqrt{\tfrac{2}{5}}\right)A h_0 \, f^{-7/6}\quad$& low ($l$) \B \\
+ \hline\hline
 \end{tabular}
@@
 \begin{table}[ht]
-\begin{tabular}{|l|cccc|}
-\hline
- Quantity & Standard Scaling & \hspace{3mm}Scaling in terms of $m_1,m_2$ & &\hspace{0.5cm} Min $\le$ Value$_{1.4M_\odot} \le$ Max\T\B\\
+\begin{tabular}{lcccc}
+\hline\hline
+ Quantity\hspace{5mm} & Standard Scaling & \hspace{3mm}Scaling in terms of $m_1,m_2$ & &\hspace{0.5cm} Min $\le$ Value$_{1.4M_\odot} \le$ Max\T\B\\
 \hline
@@
 $f_\text{ISCO}$ & $M^{-1} $ & $(m_1+m_2)^{-1} $&\quad& $0.4375\le 0.5\le 0.583 $\B\\
-\hline
+\hline\hline
 \end{tabular}
@@
 \begin{tabular}{lcccccc}
-\hline
+\hline\hline
 $D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T\B\\
@@
 200 & $\approx\,$121 & & 1.291 &\quad & 1.300 & 17.6 \\
-\hline
+\hline\hline
 \end{tabular}
@@
 \centering
-\begin{tabular}{l|ccccccc}
+\begin{tabular}{lccccccc}
 %toprule
-\hline
+\hline\hline
 $D\,$(Mpc) & \multicolumn{3}{c}{ET-B} &  & \multicolumn{3}{c}{ET-C}\T\B\\
@@
 %1000 & 41.3537 &17.2 & 29.79& \qquad & 6.7553 & 2138 & 35.60  \\
-\hline
+\hline\hline
 %bottomrule
@@
 \centering
-\begin{tabular}{l|ccc}
+\begin{tabular}{lccc}
 %toprule
-\hline
+\hline\hline
  & ET-B & & ET-C\T\B\\
@@
   $\bar\rho_F(D_H)$ & 420 &&{58}\T\B\\
-\hline
+\hline\hline
 \end{tabular}
@@
 \centering
-\begin{tabular}{l|ccccc}
+\begin{tabular}{lccccc}
 %toprule
-\hline
+\hline\hline
 $D\,$(Mpc) & \multicolumn{2}{c}{ET-B} &  & \multicolumn{2}{c}{ET-C}\T\B\\
@@
 1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
-\hline
+\hline\hline
 %bottomrule

### 2018-08-27 Paper/Manuscript.tex
Sesana corrections finished.

@@
 On the other hand, Einstein Telescope will provide us with advance warning times of more than five hours for $D \le 100\,$Mpc.
-Taking one hour as a benchmark advance warning time, we obtain a corresponding horizon
-distance of roughly 600 Mpc for the Einstein Telescope C configuration.
+Taking one hour as a benchmark advance warning time, we obtain a corresponding range of roughly 600 Mpc for the Einstein Telescope C configuration.
 %, more specifically, greater than an hour
@@
 and Einstein Telescope of 2030s made up of V-shaped interferometers.
-Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their horizon distances
+Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their ranges
 to inspiralling BNSs and their sky-localization of these sources. Our work here is somewhat complementary in the sense that we are mostly concerned with
@@
 Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020} and \ref{table:ET}; 
-and as horizon distances and event rates in Table~\ref{table:horizon}.
+and as ranges and event rates in Table~\ref{table:horizon}.
 In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of binary black hole - neutron star inspirals to see whether or not 
@@
 \be
-\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 20.37\,\text{hours}\, \left(\f{T_K}{1\,\text{s}}\right)^{8/3} \left(\f{2.8M_\odot}{M}\right)^{2/3}\,\left(\f{0.7M_\odot}{\mu}\right) \label{eq:tau_of_r},
+\tau_i = \f{5}{256}\, \f{c^5 r_i^4}{G^3 M^2 \mu}\simeq 1.024\,\text{hr} \left(\f{r_i}{1000\,\text{km}}\right)^4 \left(\f{2.8M_\odot}{M}\right)^2\,\left(\f{0.7M_\odot}{\mu}\right)
+%\simeq 20.37\,\text{hours}\, \left(\f{T_K}{1\,\text{s}}\right)^{8/3} \left(\f{2.8M_\odot}{M}\right)^{2/3}\,\left(\f{0.7M_\odot}{\mu}\right)
+\label{eq:tau_of_r},
 \ee
@@
 In the the case of GW170817 which swept the ALV network over roughly 3000 GW cycles, 
-the initial source sky localization was 31\,deg$^2$ (later reduced to 28\,deg$^2$) using data from three IFOs \cite{GW170817}. 
+the initial rapid source sky localization was 31\,deg$^2$ (later reduced to 28\,deg$^2$) using data from three IFOs \cite{GW170817}. 
 For our estimations, we employ suitable averages of these angles as explained below.
@@
 Let us briefly explore what the cost of setting $m_1=m_2=1.4 M_\odot$ is for our calculations. 
-Including the error bars, the known range for neutron star masses runs from $\approx 0.5 M_\odot$ to $ \approx 3 M_\odot$ with typical values between $\approx 1 M_\odot$ and $\approx 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}).
+Including the error bars, the known range for neutron star masses runs from $\approx 0.5 M_\odot$ to $ \approx 3 M_\odot$ with typical values between $\approx 1 M_\odot$ and $\approx 2 M_\odot$ \cite{Ozel_Freire} (one exception being J1748-2021B with mass $2.74^{+0.21}_{-0.21} M_\odot $ \cite{Freire_et_al_2007}, but this measurement is not secure \cite{Lattimer:2012nd}\footnote{We thank Dr.
+Alberto Sesana of University of Birmingham for pointing this out.}).
 Of these measured masses, a subset comprised of double neutron stars, such as the famed Hulse-Taylor binary, have the smallest error bars with masses
@@
 For the ALV network, we consider $D=50,100,200\,$Mpc 
- as A-LIGO's horizon will be slightly over 200\,Mpc and A-Virgo's around 130\,Mpc.
+ as A-LIGO's range will be slightly over 200\,Mpc and A-Virgo's around 130\,Mpc.
  %and BNS systems at $D=200, 400, 1000\,$Mpc for the ET network. 
@@
 \be
-\tilde{H}_\text{ET}(f) = \f{1}{2}\sqrt{\f{3}{10}}\, \f{c}{D}\f{1}{(1+z)}\left(\f{G \mathcal{M}_c}{c^3}\right)^{5/6} f^{-7/6}\, , \label{eq:H_delta_redshifted}
+\tilde{H}_\text{ET}(f) = \f{1}{2}\sqrt{\f{3}{10}}\,\pi^{-2/3} \f{c}{D}\f{1}{(1+z)}\left(\f{G \mathcal{M}_c}{c^3}\right)^{5/6} f^{-7/6}\, , \label{eq:H_delta_redshifted}
 \ee
@@
 where we show that ET-C will provide up to \emph{five hours} of early warning time for nearby ($D\lesssim 100\,$Mpc) neutron star mergers.
-Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's horizon distance) will persist in the ET-C sensitivity band for a few hours after their initial detection ($T_\text{AW} > 2\,$ hours).
+Moreover, BNS inspirals as far as 200\,Mpc (the ALV network's range) will persist in the ET-C sensitivity band for a few hours after their initial detection ($T_\text{AW} > 2\,$ hours).
 Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET-C.
@@
 we speculate that the advances in the detection, localization and early-warning algorithms in the next decade will reduce the required advance
-warning time to less than an hour; thus we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS horizon distances of $D_H=87$ and $613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
-In other words, all inspiralling BNSs closer than $D_H$ will give us more than an hour's leeway before the GRB (employing the detection criterion $\text{SNR} =15$ as before).
-The volume set by $D=D_H$ translates to a BNS merger rate of $\sim\mathcal{O}(1)\,\text{yr}^{-1}$ for ET-B and
-$\approx 355^{+730}_{-280}\,\text{yr}^{-1}$ for ET-C. Additionally, each source within $D_H$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
+warning time to less than an hour; thus we set $T_\text{AW} = 1\,\text{hour}$ and obtain corresponding BNS ranges of $D_\text{BNS}=87$ and $613\,$Mpc ($z\approx 0.02,0.127$) for ET-B and ET-C, respectively.
+In other words, all inspiralling BNSs closer than $D_\text{BNS}$ will give us more than an hour's leeway before the GRB (employing the detection criterion $\text{SNR} =15$ as before).
+The volume set by $D_\text{BNS}$ translates to a BNS merger rate of $\sim\mathcal{O}(1)\,\text{yr}^{-1}$ for ET-B and
+$\approx 355^{+730}_{-280}\,\text{yr}^{-1}$ for ET-C. Additionally, each source within $D_\text{BNS}$ will accumulate $\bar\rho_F \gtrsim 420, 58$ over its inspiral
 in the ET-B, ET-C bands, respectively. These results are summarized in Table~\ref{table:horizon}.
@@
 Both Tables~\ref{table:ET} and \ref{table:horizon} clearly show that ET will yield superb SNRs for sources out to 1\,Gpc. 
-With such high SNRs we expect that a future network consisting of ET and LIGO Voyager will be able to localize half the sources 
-at $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ and more than half the sources at $D\lesssim 400\,$Mpc to $\approx 1\,\text{deg}^2$ \cite{Mills:2017urp}.
-Therefore, we optimistically conclude that 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts
+With such high SNRs we expect that a future network consisting of ET \emph{and} LIGO Voyager will be able to localize half the sources 
+inside a radius of $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ and more than half the sources within $D\lesssim 400\,$Mpc to $\approx 1\,\text{deg}^2$ \cite{Mills:2017urp}.
+Let us reemphasize that such good localization requires at least a second detector with comparable sensitivity to ET as ET alone has rather poor localization.
+Erring on the side of optimism, we conclude that the 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts
 \footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030,
@@
 \hline
-  $D_H $& 87\,Mpc& &{613\,Mpc}\T\\
-  $R(D_H) $& $1^{+2}_{-1}\,\text{yr}^{-1}$&\hspace{5mm} &{$355^{+730}_{-280}\,\text{yr}^{-1}$}\T\\
-  $\bar\rho_F(D_H)$ & 420 &&{58}\T\B\\
+  $D_\text{BNS} $& 87\,Mpc& &{613\,Mpc}\T\\
+  $R(D_\text{BNS}) $& $1^{+2}_{-1}\,\text{yr}^{-1}$&\hspace{5mm} &{$355^{+730}_{-280}\,\text{yr}^{-1}$}\T\\
+  $\bar\rho_F(D_\text{BNS})$ & 420 &&{58}\T\B\\
 \hline\hline
 \end{tabular}
-\caption{Horizon distances of ET-B and ET-C assuming $T_\text{AW} =1\,$hour. $R(D_H)$ is the BNS merger rate within a volume of $D_H^3$
+\caption{Horizon distances of ET-B and ET-C assuming $T_\text{AW} =1\,$hour. $R(D_\text{BNS})$ is the BNS merger rate within a volume of $D_\text{BNS}^3$
 obtained by rescaling the rate inferred from Advanced LIGO's O1, O2 observing periods \cite{GW170817}.
-$\bar\rho_F(D_H)$ is the total SNR accumulated due to a BNS inspiralling at $D_H$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
+$\bar\rho_F(D_\text{BNS})$ is the total SNR accumulated due to a BNS inspiralling at $D_\text{BNS}$ [see Eq.~(\ref{eq:rhoF_ET})].}\label{table:horizon}
 \end{table}
@@
 
-From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
+From the table, we can see that the range of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
 Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
-there could be $\approx 30$ such mergers per year within ET-C's horizon distance of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
+there could be $\approx 30$ such mergers per year within ET-C's range of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
 We must emphasize that this should be viewed

### 2018-08-29 Paper/Manuscript.tex
ERC Acknowledged

@@
 \definecolor{darkgreen}{rgb}{0.2,0.7,0.2}
-
-\newcommand{\beq}{\begin{equation}}
-\newcommand{\eeq}{\end{equation}}
 
@@
 \acknowledgements 
-I am grateful to Conor O'Toole for endless feedback and Niels Warburton, Richard A. Matzner and Alberto Sesana for reviewing this manuscript.
+I acknowledge support by the EU H2020 under ERC Starting Grant, no. BinGraSp-714626.
+I am additionally grateful to Conor O'Toole for endless feedback and Niels Warburton, Richard A. Matzner, and Alberto Sesana for reviewing this manuscript.
 

### 2018-10-30 Sabanci_talk/Sabanci_talk.tex
LaTeX for the talk added

\documentclass[xcolor=dvipsnames,handout,t]{beamer}
% use handout in document class to stop transitions

\mode<presentation>
{
  \usetheme{Madrid}%{Madrid}
  % or ..AnnArbor, Boadilla, CambridgeUS, Copenhagen, default, Frankfurt, Goettingen, Hannover
  %       Montpellier, PaloAlto, Rochester, Szeged,

  \setbeamercovered{invisible}
  % or whatever (possibly just delete it)
}
\usepackage{color,empheq}
\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{xmpmulti,animate}
\usecolortheme{seahorse} %this makes the colors less strong.

\usepackage{times}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.
\usepackage{graphicx}
%\usepackage{tcolorbox}
\usepackage{tikz,lipsum,lmodern}
\usepackage[most]{tcolorbox}
\usepackage{amsfonts,amssymb,amsmath,mathtools}
      % use Times fonts if available on your TeX system
\usepackage{epsfig}
\usepackage{hyperref}
\usepackage{changepage}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{animate,movie15,media9}
%\usepackage{multimedia}

\newcommand{\todo}[1]{\textcolor{orange}{\texttt{TODO: #1}}} 
\newcommand{\red}[1]{\textcolor{red}{#1}} 
\newcommand{\bl}[1]{\textcolor{blue}{#1}}

\usetikzlibrary{shapes}

\title[] % (optional, use only with long paper titles)

%\subtitle
%{Presentation Subtitle} % (optional)

\title[Forecasting GRBs w/ GWs] % (optional, use only with long paper titles)
{Forecasting Gamma-ray Bursts with Gravitational Waves}

%\subtitle
%{Presentation Subtitle} % (optional)

\author[Sarp Akcay]{Sarp Akcay\inst{1}\inst{2} }
\institute[FSU Jena - UCD] % (optional, but mostly needed)
{
  \inst{1}%
  FSU Jena %and University College Dublin
  \inst{2}%
  University College Dublin
  }

%\vspace{-3cm}
%\titlegraphic{
%  \vspace{1.75cm}  \includegraphics[width=1.0cm]{figs/ucd.png}%\hspace*{1cm}~\includegraphics[height=1cm]{figs/missing_inch.jpg} \hspace*{1cm}  \includegraphics[width=1.0cm]{figs/ucd.png}
%}
\date[Sabanci University]{14 November 2018}

\subject{Talks}

\usefonttheme[onlymath]{serif}
\setbeamerfont{frametitle}{size=\huge}
\setbeamercolor{frametitle}{fg=Black,bg=White}

\newcommand{\Mag}{\textcolor{magenta}}
\newcommand{\Red}{\textcolor{red}}
\newcommand{\Blue}{\textcolor{blue}}
\renewcommand{\c}{\cos}
\renewcommand{\t}{\theta}
\renewcommand{\b}{\bar}
\newcommand{\f}{\frac}
\newcommand{\bt}{\beta}
%\newcommand{\s}{\sin}
\newcommand{\ph}{\phi}
\newcommand{\g}{\gamma}
\newcommand{\nn}{\nonumber}
\newcommand{\la}{\lambda}
\newcommand{\al}{\alpha}
\newcommand{\La}{\Lambda}
\newcommand{\el}{\ell}
\newcommand{\h}{\hat}
\newcommand{\mrm}{\mathrm}
\newcommand{\ord}{\mathcal{O}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bef}{\begin{frame}}
\newcommand{\ef}{\end{frame}}
%\newcommand{\h}{\bar{h}}
\newcommand{\bs}{\begin{small}}
\newcommand{\es}{\end{small}}
\newcommand{\parallelsum}{\mathbin{\!/\mkern-5mu/\!}}
\newcommand{\Lim}[1]{\raisebox{0.5ex}{\scalebox{0.8}{$\displaystyle \lim_{#1}\;$}}}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%------------------ for coloured boxes in math modes --------------------
% Syntax: \colorboxed[<color model>]{<color specification>}{<math formula>}
\newcommand*{\colorboxed}{}
\def\colorboxed#1#{%
  \colorboxedAux{#1}%
}
\newcommand*{\colorboxedAux}[3]{%
  % #1: optional argument for color model
  % #2: color specification
  % #3: formula
  \begingroup
    \colorlet{cb@saved}{.}%
    \color#1{#2}%
    \boxed{%
      \color{cb@saved}%
      #3%
    }%
  \endgroup
}
%%-------------------------------------------------------------------------

% tikz boxes
\newcommand\TBox[3][]{%
  \tikz\node[draw,ultra thick,red,text width=#2,align=left,#1] {#3};}

\setbeamertemplate{frametitle}[default][center]

\begin{document}
%{
%\usebackgroundtemplate{\includegraphics[width=1\paperwidth,height=\paperheight]{../Figures/ET_strains_redshifted_v2.pdf}}
\begin{frame}
 \titlepage
\end{frame}
%}

\begin{frame}{Motivation: Multi-messenger Astronomy}
\begin{itemize}
 \item \emph{Multi}: two fundamentally different waves from common events.
 \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
 \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
 \item GW170817-GRB170817A-AT2017gfo: the ``event'' \\
 \quad inspiral + merger of two neutron stars (GWs) \\
 \ \ = short-hard gamma-ray burst + kilonova (EWs)
 \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
 \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
 \item A personal motivation, a simple question \\
{\small ``What can we offer to the astronomy community with future GW detections?''}
 \end{itemize}

 \end{frame}

\begin{frame}{Gravitational waves: Einstein 1916}
  \begin{center}
\begin{tikzpicture}
            \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/Einstein1916.png}};
            %\draw<1>[red,ultra thick,rounded corners] (1.6,1) rectangle (\textheight-1cm,5);
           \uncover<3->{\draw<3->[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
        \end{tikzpicture}
        \\
         \uncover<2->{Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
         \end{center}
          \begin{itemize}
 \item  \uncover<3->{Spacetime metric $g_{\mu\nu} = \eta_{\mu\nu} + h_{\mu\nu}$, \quad with $| h_{\mu\nu} | \ll 1$.}
 \item  \uncover<4->{Insert into $G_{\mu\nu} = 0$. Keep only $\mathcal{O}(h)$. Pick a gauge.} %(e.g. Lorenz).}
  \uncover<5->{\[ \Rightarrow\quad \Box \bar{h}_{\mu\nu}= 0, \quad \text{wave equation!} \]}
  \item \uncover<6->{\alert{Plane-waves:} $ \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{i k_\mu x^\mu}\right] =\Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/c )}\right]$.}
 \end{itemize}
\end{frame}

\begin{frame}{Gravitational waves: d.o.f.'s}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
 \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
 \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %\uncover<7->{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}

{\begin{center} \includegraphics[height=2.79875cm]{figs/white_box.png}\end{center}}
\end{frame}

\begin{frame}{Gravitational waves: d.o.f.'s}
%\begin{center}
%\animategraphics[loop,controls,width=3cm]{12}{GWs_frame-}{0}{29} 
%\end{center}
$A_{\mu\nu} $ is the polarization tensor.
\begin{itemize}
{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
 {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0${ $\Rightarrow10-4 = \,6$ d.o.f.}}
 {\item Residual gauge freedom \hspace{2.25cm}{ $\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
 %{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
\end{itemize}
{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
{\begin{center} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_plus-}{0}{20} \hspace{1cm} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_cross-}{0}{20}\end{center}}
\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
 \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
 \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}}
 \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
 \uncover<4->{\begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}}
 \uncover<5->{{\bf Binary systems:} 2 points masses in circular orbit. }

\end{frame}

\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
 \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
 Gravitational-wave luminosity: \alert{quadrupole} radiation
 \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\ \vspace{2mm}
 \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
 {\bf Binary systems:} 2 points masses in circular orbit. \todo{Make $\dot{E}$s consistent}
 \begin{tikzpicture}[overlay,remember picture]
\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.4cm]{12}{Circ_Orb-}{0}{20}};
\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$M=m_1+m_2,\ x(t) = R \cos\Omega t, \ y(t) = R \sin\Omega t .$};
\onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \quad \boxed{\dot{E} = \f{128}{5}\f{G}{c^5} \Omega^6 M^2 R^4}$.};
\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \red{$e$} (Peters \& Mathews).};
\onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \dot{E} = \textcolor{red}{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}} \f{32}{5}\f{G}{c^5}\f{M m_1^2 m_2^2}{a^5}.$};
\end{tikzpicture}
\end{frame}

 \begin{frame}{Binary Neutron Star Inspirals}

 \end{frame}

 \begin{frame}{GW Detectors: Interferometers}
  Geodesic deviation
 \end{frame}

\end{document}

### 2018-10-31 Paper/Manuscript.tex
Swapped the order of my institutions
Minor corrections to paper More added to the talk

@@
 \author{Sarp Akcay}
+\affiliation{Theoretisch-Physikalisches Institut, Friedrich-Schiller-Universit{\"a}t Jena, 07743, Jena, Germany}
 \affiliation{School of Mathematics \& Statistics, University College Dublin, Belfield, Dublin 4, Ireland}
-\affiliation{Theoretisch-Physikalisches Institut, Friedrich-Schiller-Universit{\"a}t Jena, 07743, Jena, Germany}
 %\date{\today}
@@
 It can further be shown that there exist only two radiative degrees of freedom (cf.
-Sec.~1.2 of Ref.~\cite{Maggiore}) which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs
+Sec.~1.2 of Ref.~\cite{Maggiore}) which physically manifest themselves as two independent polarization amplitudes $h_+$ and $h_\times$ of the GWs.
 This fact is most easily demonstrated in the so-called transverse-traceless gauge (cf. Sec.~2.1 of Ref.~\cite{Flanagan:2005yc}),
@@
 %
-\item {\it Truncating the inspiral at the Schwarzschild ISCO.}
+\item {\it Terminating the inspiral at the Schwarzschild ISCO.}
 We artificially end the inspirals at the Schwarzschild ISCO of the BNS with coordinate radius $r_\text{ISCO} = 6GM/c^2$ and angular frequency $\Omega_\text{ISCO}$ %= (M/r^3_\text{ISCO})^{1/2}$ in natural units,
@@
 Let us apply this to the Hulse-Taylor binary pulsar \cite{Hulse:1974eb,Weisberg:2010zz} to show that the BNS orbits circularize by the time they enter the interferometers' bandwidth (ca. $1-10\,$Hz).
-Therfore, letting $f =2f_K= 1\,\text{Hz}$, i.e., 
+Letting $f =2f_K= 1\,\text{Hz}$, i.e., 
 $a \simeq 3352\,$km and using the currently observed values $a_i \approx 1.95\times 10^6\,$km and $e_i \approx 0.617$,
@@
 \be
-\f{\dot\Omega}{\Omega^2} = \f{96}{5} \f{(G M_c)}{c^5}^{5/3}\Omega^{5/3} \ll 1 \label{eq:omega_dot_over_omegasq}
+\f{|\dot\Omega|}{\Omega^2} = \f{96}{5} \f{(G M_c)}{c^5}^{5/3}\Omega^{5/3} \ll 1 \label{eq:omega_dot_over_omegasq}
 \ee
@@
 %Setting $\dot{\Omega}/\Omega^2 = 10^{-3}$ yields $f= \Omega/\pi %\simeq 443.4\,$Hz which, as explained above, 
-This expression yields $\dot{\Omega}/\Omega^2\approx 5.5\times 10^{-4}$ at $f=100\,$Hz, which, as shown above, is a few seconds
+This expression yields $|\dot{\Omega}|/\Omega^2\approx 5.5\times 10^{-4}$ at $f=100\,$Hz, which, as shown above, is a few seconds
 before the merger so the quasi-circularity assumption seems to

### 2018-10-31 Sabanci_talk/Sabanci_talk.tex
Minor corrections to paper More added to the talk

@@
 
-%\subtitle
-%{Presentation Subtitle} % (optional)
+\subtitle{\todo{Add background image}} % (optional)
 
@@
 
+\begin{frame}{Outline}
+\begin{itemize}
+ \item Motivation
+ \item Gravitational waves
+ \item Binary neutron star inspirals
+ \item Gravitational-wave detectors
+ \item Event rates 
+\end{itemize}
+\todo{finish this slide remove later if short on time}
+
+\end{frame}
+
 \begin{frame}{Motivation: Multi-messenger Astronomy}
@@
  \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
- \item GW170817-GRB170817A-AT2017gfo: the ``event'' \\
+ \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
  \quad inspiral + merger of two neutron stars (GWs) \\
@@
  \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
- \item A personal motivation, a simple question \\
+ \item A simple question \\
 {\small ``What can we offer to the astronomy community with future GW detections?''}
@@
 \uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
-
+\\
+\todo{Replace with Maggiore's discussion?}
 {\begin{center} \includegraphics[height=2.79875cm]{figs/white_box.png}\end{center}}
@@
 {$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
+\\
+\todo{Replace with Maggiore's discussion?}
 {\begin{center} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_plus-}{0}{20} \hspace{1cm} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_cross-}{0}{20}\end{center}}
@@
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
- \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}}
+ \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}  (leading-order)}
  \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
@@
  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
- Gravitational-wave luminosity: \alert{quadrupole} radiation
+ Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\ \vspace{2mm}
  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
- {\bf Binary systems:} 2 points masses in circular orbit. \todo{Make $\dot{E}$s consistent}
+ {\bf Binary systems:} 2 points masses in circular orbit.\todo{$R\to r$ in vid}
  \begin{tikzpicture}[overlay,remember picture]
 \onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.4cm]{12}{Circ_Orb-}{0}{20}};
-\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$M=m_1+m_2,\ x(t) = R \cos\Omega t, \ y(t) = R \sin\Omega t .$};
-\onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \quad \boxed{\dot{E} = \f{128}{5}\f{G}{c^5} \Omega^6 M^2 R^4}$.};
-\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \red{$e$} (Peters \& Mathews).};
-\onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \dot{E} = \textcolor{red}{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}} \f{32}{5}\f{G}{c^5}\f{M m_1^2 m_2^2}{a^5}.$};
+\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
+\onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
+\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
+\onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
 \end{tikzpicture}
@@
  \begin{frame}{Binary Neutron Star Inspirals}
+ Notation:
+ \begin{itemize}
+  \item $\red{f} $: GW frequency.
+  \item $\omega\equiv2\pi f = 2\Omega$: GW angular frequency.
+  \item $t$: observer/detector time \quad$ \Longrightarrow\quad\dot{Y}= dY/dt$.
+ \end{itemize}
+
+  Assumptions:
+  \begin{itemize}
+   \item Quasi-circular orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ at $f=100\,$Hz.
+   \item Point masses: tidal effects for $f \gtrsim 100\,$Hz
+   \item Set $m_1 =m_2 = 1.4 M_\odot$, constraints: $1.2 M_\odot \lesssim m_\text{NS}\lesssim 1.6M_\odot$.
+   \item Use Newtonian/post-Newtonian theory ($\le$3.5{\bf PN}).
+   \item Terminate inspiral at Schwarzschild ISCO \todo{add ISCO curve?}
+   \begin{footnotesize}
+   \[f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571 \left(\f{2.8M_\odot}{M}\right)\text{Hz}\] 
+   \end{footnotesize}
+   \item Quadrupolar GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
+   \item \todo{what about the 21 mode?}
+   \item Neglect spins: spin-orbit $\tfrac{\dot{E}_\text{SO}}{\dot{E}} \sim \tfrac{v_s}{c}\tfrac{v}{c}\tfrac{R_\text{NS}}{r}$, spin-spin $\sim \tfrac{v^4}{c^4}$
+  \end{itemize}
+
+ \end{frame}
+
+\begin{frame}{Binary Neutron Star Inspirals}{Newtonian evolution}
+ Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
+ %and symmetric mass ratio\qquad $\nu \equiv \tfrac{\mu}{M} =\tfrac{m_1 m_2}{M^2}$\\
+ \vspace{1mm}
+ which gives, using Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$   
+ \begin{footnotesize}
+  $$ \boxed{\dot{E} = \f{32}{5}\f{c^5}{G} \left(\f{G M_c\, \omega}{2c^3}\right)^{10/3}}$$
+ \end{footnotesize}\\
+%
+{\bf Key idea:} \red{energy balance} between $\dot{E}$ and \\
+$\tfrac{d}{dt}$ of gravitational binding energy
+$ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
+%
+\[ 
+ \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }
+ \]
+\[
+ \red{ \dot{f} \propto f^{11/3}\quad(1)}
+\]
+
+\begin{tikzpicture}[overlay,remember picture]
+\node[draw, red,thick,minimum width=3cm,minimum height=0.75cm] (b) at (5.9,0.85){};
+\end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{Binary Neutron Star Inspirals}{Inspiral time}
+Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
+\\
+\vspace{1mm}
+Fix integration constant $\tau = t_\text{coal} - t >0$. \\
+\vspace{2mm}
+Introduce \red{inspiral time}, i.e, time to BNS \bl{coal}escence
+%
+\begin{align}
+ \red{\tau_\text{insp}(f)} &= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
+ &\simeq \red{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
+\end{align}
+Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim f^{-5/3}$ %$\int df {f}/\dot{f}$
+\begin{align}
+ \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
+ &\approx 1.605\times \red{10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\quad \red{(3)}\nn
+\end{align}
+
+\begin{tikzpicture}[overlay,remember picture]
+\node[draw, red,thick,minimum width=8.2cm,minimum height=1.3cm] (b) at (7.,3.35){};
+\node[draw, red,thick,minimum width=10cm,minimum height=1.3cm] (b) at (6.2,1){};
+\end{tikzpicture}
 

### 2018-11-01 Sabanci_talk/Sabanci_talk.tex
More slides

@@
 \end{itemize}
-\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
-\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
+\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
+\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
 \\
@@
 \end{itemize}
-{\quad \ Consistent with $\pm 2$ helicities of a \alert{massless} spin 2 boson.\\}
-{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = h_\oplus  \\ A_{xy}=\ \ A_{yx} = h_\otimes  \\ \end{array}$}}
+{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
+{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
 \\
@@
    \item Quadrupolar GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
-   \item \todo{what about the 21 mode?}
    \item Neglect spins: spin-orbit $\tfrac{\dot{E}_\text{SO}}{\dot{E}} \sim \tfrac{v_s}{c}\tfrac{v}{c}\tfrac{R_\text{NS}}{r}$, spin-spin $\sim \tfrac{v^4}{c^4}$
@@
 \end{align}
-
+%
 \begin{tikzpicture}[overlay,remember picture]
@@
 \end{tikzpicture}
+%
+\end{frame}
+
+\begin{frame}{Gravitational waves from BNS}
+TT gauge, multipole, slow-velocity expansions give \todo{add suppl. slide}
+\[
+ h_{ij}^\text{TT} = \tfrac{1}{D}\tfrac{2G}{c^4} \ddot{Q}_{il}^\text{TT}(t-z/c)
+\]
+%
+ \begin{align}
+ h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\label{eq:hplus_TD}\\
+ h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi(t)]\label{eq:hcross_TD},
+\end{align}
+%
+%
+where
+%
+\begin{align}
+h_c(t) &=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3} \nn\\
+\Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN corrections}
+\end{align}
+
+Frequecny increases as $f^{11/3}$\\
+Amplitude increases as $f^{2/3} \Longrightarrow$ \red{Chirp!}
 
@@
 
+\begin{frame}{Supplement 1: mode suppression}
+\begin{itemize}
+ \item For $q=1$ due to symmetry only (2,2), (3,2), (4,2), (4,4) are nonzero 
+ \item For $q\ne 1$ all $\ell \ge 2$ modes exist, but are much smaller than $(2,2)$
+\end{itemize}
+
+\end{frame}
+
 \end{document}

### 2018-11-02 Sabanci_talk/Sabanci_talk.tex
Slides, paper minor

@@
 
-\begin{frame}{Binary Neutron Star Inspirals}{Inspiral time}
+\begin{frame}{Binary Neutron Star Inspirals}{\todo{Add $r(t)$ plot? }}
 Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
@@
 \begin{align}
- \red{\tau_\text{insp}(f)} &= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
- &\simeq \red{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
+ \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
+ &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
 \end{align}
-Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim f^{-5/3}$ %$\int df {f}/\dot{f}$
+Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
 \begin{align}
  \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
- &\approx 1.605\times \red{10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\quad \red{(3)}\nn
+ &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\red{ \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\quad \red{(3)}\nn
 \end{align}
@@
 %
+\[ 
+\tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}}
+\]
+
 \end{frame}
@@
 \end{itemize}
+\end{frame}
+
+\begin{frame}{Supplement 2: The expression for $h_c(t)$}
+Maggiore chapters 1, 3 and 4
+\begin{itemize}
+ \item Eq. (3.3) expanded to (3.9), (3.14) to (3.34) to (3.55) to (3.59)
+ \item Eq. (3.72): $h(t)$ as angular distribution with mass moments $\ddot{M}_{ij}$'s
+ \item At that point we get the scaling $h \sim \tfrac{1}{D}\tfrac{G}{c^4}\ddot{Q}_{ij}$.
+ \item Eq. (3.275) shows it expanded in tensor harmonics so up to $\partial^2 Y^{\ell m}$
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Supplement 3: Direction of GW emission}
+ Mostly off the orbital plane and slightly forward
+ \begin{itemize}
+  \item Eqs. (3.337-3.338) and Fig. 3.7 show that $\tfrac{d\dot{E}}{d\Omega}$ is max at the poles
+  \item Eqs. (4.347), (4.348) with Fig. 4.24 (page 228) show that even for $v=0.99$ the beaming
+  is much less significant compared to EM beaming shown in Fig. 4.23.
+ \end{itemize}
 

### 2018-11-04 Sabanci_talk/Sabanci_talk.tex
More slides

@@
 %
-{\bf Key idea:} \red{energy balance} between $\dot{E}$ and \\
-$\tfrac{d}{dt}$ of gravitational binding energy
-$ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
+{\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$\\
+ %of gravitational binding energy
+\quad where $ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
 %
@@
  \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
- &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,\red{\left(\f{10\,\text{Hz}}{f}\right)^{8/3}\quad(2)}\nn
+ &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad(2)}\nn
 \end{align}
@@
  \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
- &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\red{ \left(\f{10\,\text{Hz}}{f} \right)^{5/3}}\quad \red{(3)}\nn
+ &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn
 \end{align}
@@
 TT gauge, multipole, slow-velocity expansions give \todo{add suppl. slide}
+\begin{small}
 \[
- h_{ij}^\text{TT} = \tfrac{1}{D}\tfrac{2G}{c^4} \ddot{Q}_{il}^\text{TT}(t-z/c)
+ h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}%(t-z/c)
 \]
@@
 \end{align}
+\end{small}
 %
@@
 where
+\vspace{-3mm}
 %
+\begin{small}
 \begin{align}
-h_c(t) &=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3} \nn\\
+h_c(t) %&=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\nn\\
+&\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \nn\\
 \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN corrections}
 \end{align}
-
-Frequecny increases as $f^{11/3}$\\
-Amplitude increases as $f^{2/3} \Longrightarrow$ \red{Chirp!}
+\end{small}\\
+%
+Frequency increases as $f^{11/3}$\\
+Amplitude increases as $f^{10/3} \Longrightarrow$ \red{Chirp!} \todo{Insert chirp movie}
 
@@
 
- \begin{frame}{GW Detectors: Interferometers}
-  Geodesic deviation
+ \begin{frame}{GW Detectors: \red{Interferometers}}
+  Two geodesics separated by $\xi^\mu$:
+  %\[
+  % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
+  %\]
+$ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
+%\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
+\vspace{-3mm}
+\[
+\hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
+\]
+%
+%
+GW along $\mathbf{z}$: 
+\[
+ h_{ij}^\text{TT} = \left(\begin{array}{cc}
+                           h_+ & h_\times \\
+                           h_\times & - h_+
+                          \end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
+\]
+Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
+\begin{small}
+\begin{align*}
+  s_{12} &= \int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} \\
+			      & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] \\
+s_{13} &\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]
+\end{align*}
+\end{small}
+%
+\begin{tikzpicture}[overlay,remember picture]
+%\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
+\end{tikzpicture}
  \end{frame}
@@
 \end{itemize}
+\end{frame}
 
+\begin{frame}{Supp: coord. vs. proper distance in TT gauge}
+  Geodesic deviation 
+  \[
+   \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
+  \]
+In TT gauge,\qquad  $\Longrightarrow \quad\left.\tfrac{d^2 \xi^i}{d\tau^2}\right|_{\tau=0} = -\left. \dot{h}_{ij} \tfrac{d\xi^i}{d\tau}\right|_{\tau=0}$\\
+i.e., if mirrors are initially at rest w.r.t to each other ( $\left. \tfrac{d\xi^i}{d\tau}\right|_{\tau=0} =0$ )\\
+then $\tfrac{d^2 \xi^i}{d\tau^2}=0\quad \forall t$ \\
+$\Longrightarrow$ coordinate separation $\xi^i = \text{constant}$ for all time \\
+BUT, proper distance is NOT! \\
+Consider mirrors at $\mathbf{x}=x_1$ and at $\mathbf{x}=x_2=x_1+\mathbf{\xi}$
+\begin{align*}
+  s = \int_1^2 \tfrac{ds}{dx}dx &= (x_2-x_1) \left[ 1 + h_+ \cos(\omega\t)\right]^{1/2} \\
+			      & \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] 
+\end{align*}
  \end{frame}
@@
 
+\begin{frame}{Supplemet 5: Mass-inclination degeneracy}
+
+\end{frame}
+
 \end{document}

### 2018-11-05 Sabanci_talk/Sabanci_talk.tex
More slides, new fig from Mathematica

@@
 
- \begin{frame}{Binary Neutron Star Inspirals}
+ \begin{frame}{Compact Binary Inspirals}
  Notation:
  \begin{itemize}
-  \item $\red{f} $: GW frequency.
-  \item $\omega\equiv2\pi f = 2\Omega$: GW angular frequency.
+  \item $\red{f} $: GW frequency, \hspace{1.5cm} $\Longrightarrow\quad \omega\equiv2\pi f = 2\Omega$.
+  %\item $\omega\equiv2\pi f = 2\Omega$: GW angular frequency.
   \item $t$: observer/detector time \quad$ \Longrightarrow\quad\dot{Y}= dY/dt$.
@@
    \item Quasi-circular orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ at $f=100\,$Hz.
-   \item Point masses: tidal effects for $f \gtrsim 100\,$Hz
-   \item Set $m_1 =m_2 = 1.4 M_\odot$, constraints: $1.2 M_\odot \lesssim m_\text{NS}\lesssim 1.6M_\odot$.
+   \item Quadrupolar GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
    \item Use Newtonian/post-Newtonian theory ($\le$3.5{\bf PN}).
@@
    \begin{footnotesize}
-   \[f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571 \left(\f{2.8M_\odot}{M}\right)\text{Hz}\] 
+   \[f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571\,\text{Hz}\, \left(\f{2.8M_\odot}{M}\right)\] 
    \end{footnotesize}
-   \item Quadrupolar GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
+   \end{itemize}
+   %
+   For binary neutron stars ({\bf BNS})
+   \begin{itemize}
+   \item Point masses: tidal effects for $f \gtrsim 100\,$Hz
+   \item Set $m_1 =m_2 = 1.4 M_\odot$, constraints: $1.2 M_\odot \lesssim m_\text{NS}\lesssim 1.6M_\odot$.
    \item Neglect spins: spin-orbit $\tfrac{\dot{E}_\text{SO}}{\dot{E}} \sim \tfrac{v_s}{c}\tfrac{v}{c}\tfrac{R_\text{NS}}{r}$, spin-spin $\sim \tfrac{v^4}{c^4}$
@@
 
-\begin{frame}{Binary Neutron Star Inspirals}{Newtonian evolution}
+\begin{frame}{Compact Binary Inspirals}{Newtonian evolution}
  Define \bl{chirp mass} \hspace{1.cm} $\red{M_c} \equiv \mu^{3/5} M^{2/5} = \tfrac{(m_1 m_2)^{3/5}}{(m_1+m_2)^{1/5}}$ \\
@@
 
-\begin{frame}{Binary Neutron Star Inspirals}{\todo{Add $r(t)$ plot? }}
+\begin{frame}{Compact Binary Inspirals}{Inspiral time \todo{Add $r(t)$ plot? }}
 Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
@@
  \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
- &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad(2)}\nn
+ &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn
 \end{align}
@@
 %
- \begin{align}
- h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\label{eq:hplus_TD}\\
- h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi(t)]\label{eq:hcross_TD},
-\end{align}
+ \begin{align*}
+ h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\\
+ h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi(t)],
+\end{align*}
 \end{small}
@@
 %
-where
+$\iota =\,$ orbital \bl{inclination}, and
 \vspace{-3mm}
@@
 \begin{small}
-\begin{align}
+\begin{align*}
 h_c(t) %&=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\nn\\
@@
 \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN corrections}
-\end{align}
+\end{align*}
 \end{small}\\
@@
 \end{tikzpicture}
+ \end{frame}
+
+\begin{frame}{Interferometers : \red{L}-topology}{LIGO, Virgo, KAGRA}
+\vspace{-2mm}
+  Interferometers ({\bf IFO}s) measure only the response function (\bl{GW strain})
+  \begin{footnotesize}
+  \begin{align*}
+   h(t) &= F_+(\theta,\phi,\psi) \,h_+(t)+F_\times(\theta,\phi,\psi)\, h_\times(t) , \\
+    F_+ &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\cos 2\psi-\cos\theta \sin2\phi \sin2\psi, \\
+    F_\times &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\sin2\psi+\cos\theta \sin2\phi \cos2\psi
+    \end{align*}
+    \end{footnotesize}
+   %
+   Fourier transform to frequency domain 
+  \begin{footnotesize}
+  \begin{align*}
+  &\red{\tilde{h}(f)} =A\, \underbrace{\f{c}{D}\left(\f{G M_c}{c^3}\right)^{5/6}}_{\bl{h_0}} \,\red{f^{-7/6}}\, e^{i\Psi}\, Q(\theta,\phi,\psi,\iota),\hspace{5cm} \\
+     &\quad Q(\theta,\phi,\psi,\iota) = F_+\f{1+\cos^2\iota}{2}  + i F_\times \cos\iota \\
+   &\quad A\equiv \pi^{-2/3}\sqrt{\tfrac{5}{24}}\\
+   &\quad \Psi = \Psi_N(f) + \text{PN corrections}
+    \end{align*}
+    \end{footnotesize}
+   \red{Four} angles: $\{\theta,\phi,\iota,\psi \}$
+   %
+  \begin{tikzpicture}[overlay,remember picture]
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-1.8cm)}]current page.center) {\includegraphics[height=5cm]{figs/Schutz_LRR_Fig3_half.jpg}};
+  \end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{Interferometers : \red{Triangular}-topology}{Einstein Telescope}
+\vspace{-2mm}
+  Three $60^\circ$ V-IFOs, one redundant (null stream), $\sin 60^\circ =\sqrt{3}/2$.
+  \begin{footnotesize}
+  \begin{align*}
+    &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \qquad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\hspace{2cm}\\
+    & F^2_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi+2\pi/3,\psi)\qquad (\text{rotation by 120}^\circ),\\
+    & F^3_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \qquad(\text{rotation by 240}^\circ),\\
+    &  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
+    \end{align*}
+    \end{footnotesize}
+   %
+   No blind spots!
+   \begin{footnotesize}
+  \begin{align*}
+   F^2_\bigtriangleup &\equiv \sum_{A=1}^3 \left(F^A_+\right)^2+\left(F^A_\times\right)^2 \hspace{8cm}\\ 
+   &= \f{9}{32}\left(1+6\cos^2\theta + \cos^4\theta\right)
+  \end{align*}
+  \end{footnotesize}
+  %
+  %
+  \begin{tikzpicture}[overlay,remember picture]
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
+   \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0.4cm,-2.5cm)}]current page.center) {\includegraphics[height=4cm]{../Figures/ET_no_blind_spots.pdf}};
+   \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
+  \end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{Optimal Signal-to-Noise Ratio}
+ RMS Average over the angles \\
+ Then introduce SNR for both LIGO and ET
 \end{frame}

### 2018-11-07 Sabanci_talk/Sabanci_talk.tex
More slides

@@
 
-\begin{frame}{Optimal Signal-to-Noise Ratio}
- RMS Average over the angles \\
- Then introduce SNR for both LIGO and ET
+\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio {\bf SNR}}
+\vspace{-5mm}
+\begin{footnotesize} 
+\[
+ \rho=\left[ \int_0^\infty d\ln f\, \f{|\red{2\tilde{h}(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
+\]
+\\
+\end{footnotesize}
+$\sqrt{S_n(f)}\equiv$ {\it amplitude spectral density} ({\bf ASD}) or  detector noise
+
+For compact binary inspirals, $\tilde{h}(f) \sqrt{f} \sim f^{-7/6} f^{1/2} = \red{f^{-2/3}}$
+\begin{footnotesize} 
+\[
+ \rho^2 =  (2A)^2 h_0^2 |Q(\theta,\phi,\psi,\iota)|^2 \int_0^{\bl{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)} 
+\]
+\end{footnotesize}
+%
+RMS \red{average} over the angles $ \langle \ldots \rangle \equiv \int \sin\theta d\theta d\phi \int d\psi \int\sin\iota d\iota $
+\begin{footnotesize} 
+\[
+ \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\llcorner = \f{4}{25}, \qquad \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\triangle = \f{9}{25}
+\]
+\end{footnotesize}
+Our Network: \red{three L}-IFOs: 
+\begin{footnotesize} 
+\begin{align*}
+\rho_\text{tot} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
+	= \boxed{\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
+\rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \tilde{A}_h = \tfrac{4}{5}A, \quad \tilde{A}_m =\tfrac{2}{5}A, \quad \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}
+\end{align*}
+\end{footnotesize}
+%
+\begin{tikzpicture}[overlay,remember picture]
+\node[draw, red,thick,minimum width=4.5cm,minimum height=1.25cm] (b) at (3.3,0.7){};
+\end{tikzpicture}
+%
+% 
+\end{frame}
+
+\begin{frame}{Detection criteria}{Triangular topology SNR}
+%\vspace{-5mm}
+\red{Three V-}IFOs
+\begin{footnotesize} 
+\[
+ \rho^2_{\text{tot},\bigtriangleup} = \sum_{A=1}^3 \left(\rho^A\right)^2  =  4 A^2 h_0^2\,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 \int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
+\]
+\end{footnotesize}
+\\
+Use \bl{RMS-averaged} $|Q|^2$
+\begin{footnotesize}
+\begin{align*}
+\rho_{\text{tot},\bigtriangleup} &= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
+=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
+\end{align*}
+\end{footnotesize}
+\\
+where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
+\vspace{2mm}
+Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
+%
+%
+\begin{tikzpicture}[overlay,remember picture]
+\node[draw, red,thick,minimum width=4.5cm,minimum height=1.25cm] (b) at (-0.2,2.5){};
+\end{tikzpicture}
+%
+% 
 \end{frame}

### 2018-11-07 Sabanci_talk/Sabanci_talk.tex
Improved many slides, added new figs

--- 2018-11-05 Sabanci_talk/Sabanci_talk.tex
@@
  \item Motivation
+ \item Gamma-ray bursts
  \item Gravitational waves
@@
   \end{itemize}
+\end{frame}
 
+\begin{frame}{Gamma-ray bursts}{Most energetic explosions in the universe}
+ \todo{Use Pawan's slides}\\
+ Brief history: spy satellites ...\\
+ Two main types, short long,  etc.
+
+\end{frame}
+
+\begin{frame}{Neutron Stars}{Most extreme stars in the universe}
+  Stellar evolution -> white dwarf, NS -> BH \\
+  Density, mass, radius, spin, nuclear equation of state\\
+  Tea spoon of neutron star matter trillion tons
 \end{frame}
@@
  \item  \uncover<4->{Insert into $G_{\mu\nu} = 0$. Keep only $\mathcal{O}(h)$. Pick a gauge.} %(e.g. Lorenz).}
-  \uncover<5->{\[ \Rightarrow\quad \Box \bar{h}_{\mu\nu}= 0, \quad \text{wave equation!} \]}
+  \uncover<5->{\[ \Rightarrow\quad \boxed{\Box \bar{h}_{\mu\nu}= 0}, \quad \text{wave equation!} \]}
   \item \uncover<6->{\alert{Plane-waves:} $ \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{i k_\mu x^\mu}\right] =\Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/c )}\right]$.}
@@
 \\
-\todo{Replace with Maggiore's discussion?}
-{\begin{center} \includegraphics[height=2.79875cm]{figs/white_box.png}\end{center}}
-\end{frame}
-
-\begin{frame}{Gravitational waves: d.o.f.'s}
-%\begin{center}
-%\animategraphics[loop,controls,width=3cm]{12}{GWs_frame-}{0}{29} 
-%\end{center}
-$A_{\mu\nu} $ is the polarization tensor.
-\begin{itemize}
-{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
- {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0${ $\Rightarrow10-4 = \,6$ d.o.f.}}
- {\item Residual gauge freedom \hspace{2.25cm}{ $\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
- %{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
-\end{itemize}
-{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
-{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
-\\
-\todo{Replace with Maggiore's discussion?}
-{\begin{center} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_plus-}{0}{20} \hspace{1cm} \animategraphics[loop,controls,height=2.4cm]{12}{GWs_cross-}{0}{20}\end{center}}
-\end{frame}
-
-\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
- \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
- \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}  (leading-order)}
- \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
- \uncover<4->{\begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}}
- \uncover<5->{{\bf Binary systems:} 2 points masses in circular orbit. }
-
+\begin{tikzpicture}[overlay,remember picture]
+\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
+\node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
+\end{tikzpicture}
 \end{frame}
@@
   Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
- \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\ \vspace{2mm}
+  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
+  \vspace{2mm}
   \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
- {\bf Binary systems:} 2 points masses in circular orbit.\todo{$R\to r$ in vid}
+  \onslide<2->{{\bf Binary systems:} 2 points masses in circular orbit.}
   \begin{tikzpicture}[overlay,remember picture]
-\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.4cm]{12}{Circ_Orb-}{0}{20}};
-\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
-\onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
-\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
-\onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
+    \onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
+    \onslide<3->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
+    \onslide<4->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
+    \onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
+    \onslide<6->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
   \end{tikzpicture}
@@
 \begin{frame}{Compact Binary Inspirals}
+  \vspace{-3mm}
   Notation:
@@
     %\item $\omega\equiv2\pi f = 2\Omega$: GW angular frequency.
-  \item $t$: observer/detector time \quad$ \Longrightarrow\quad\dot{Y}= dY/dt$.
+    \item $\red{t}$: observer/detector time \quad$ \Longrightarrow\quad\dot{Y}= dY/dt$.
   \end{itemize}
-
+  \onslide<2->
+  {
     Assumptions:
     \begin{itemize}
-   \item Quasi-circular orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ at $f=100\,$Hz.
-   \item Quadrupolar GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
+      \item \bl{Quasi-circular} orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ at $f=100\,$Hz.
+      \item \bl{Quadrupolar} GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
       \item Use Newtonian/post-Newtonian theory ($\le$3.5{\bf PN}).
-   \item Terminate inspiral at Schwarzschild ISCO \todo{add ISCO curve?}
+      \item \red{Terminate} inspiral at Schwarzschild \red{ISCO} 
       \begin{footnotesize}
-   \[f_\text{ISCO} = \f{c^3}{6^{3/2}\pi G M} \simeq 1571\,\text{Hz}\, \left(\f{2.8M_\odot}{M}\right)\] 
+      \begin{align*}
+      f_\text{ISCO} &= \f{c^3}{6^{3/2}\pi G M} \simeq \bl{1571}\,\text{Hz}\, \left(\f{2.8M_\odot}{M}\right)\hspace{2cm}\\ 
+      r_\text{ISCO} &\simeq 25\,\text{km}\left(\frac{M}{2.8 M_\odot}\right)
+      \end{align*}
       \end{footnotesize}
     \end{itemize}
+   } 
   %
+  \onslide<3->
+  {
+    \vspace{1mm}
     For binary neutron stars ({\bf BNS})
@@
     \end{itemize}
-
+  }
+  \onslide<2->
+  {
+    \begin{tikzpicture}[overlay,remember picture]
+    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/OrbitPotential.pdf}};    
+    \end{tikzpicture}
+  }  
 \end{frame}
@@
 
-\begin{frame}{Compact Binary Inspirals}{Inspiral time \todo{Add $r(t)$ plot? }}
+\begin{frame}{Compact Binary Inspirals}
+\vspace{-3mm}
 Integrate $\dot{f} \sim f^{11/3} \quad \Longrightarrow \quad \int dt \sim \int f^{-11/3}df \quad\Rightarrow\quad t \sim \red{f^{-8/3}}$
@@
 %
+\begin{small}
 \begin{align}
  \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
- &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn
+ &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2cm}
 \end{align}
+\end{small}
 Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
+\begin{small}
 \begin{align}
  \red{\mathcal{N}_\text{cyc}(f)} %&=\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right]\nn \\
- &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn
+ &\approx 1.605\times \bl{10^4}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}{ \left(\f{10\,\text{Hz}}{\red{f}} \right)^{\red{5/3}}}\quad \red{(3)}\nn\hspace{3.2cm}
 \end{align}
+\end{small}
 %
 \begin{tikzpicture}[overlay,remember picture]
-\node[draw, red,thick,minimum width=8.2cm,minimum height=1.3cm] (b) at (7.,3.35){};
-\node[draw, red,thick,minimum width=10cm,minimum height=1.3cm] (b) at (6.2,1){};
+  \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (5.,3.35){};
+  \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.4,1){};
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
 \end{tikzpicture}
@@
 \[ 
-\tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}}
+\tfrac{\dot{r}}{r}\sim \tfrac{\dot{f}}{f} \Longrightarrow \red{r(\tau)}=r_i \left(\f{\red{\tau}}{\tau_i}\right)^{\red{1/4}} \hspace{4cm}
 \]
@@
     %
+    \vspace{-5mm}
     \begin{align*}
@@
     &\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \nn\\
-\Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN corrections}
+    \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN}
     \end{align*}
@@
   Frequency increases as $f^{11/3}$\\
-Amplitude increases as $f^{10/3} \Longrightarrow$ \red{Chirp!} \todo{Insert chirp movie}
-
+  Amplitude increases as $f^{10/3} $
+  %
+  %
+  \begin{tikzpicture}[overlay,remember picture]
+    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/Chirp.pdf}};
+     \node[anchor=center,scale=1.4,opacity=1] at ([shift={(1cm,-2.4cm)}]current page.center) {\href{https://www.youtube.com/watch?v=CH9JSqUfnSw}{\red{Chirp!}}};
+  \end{tikzpicture}
 \end{frame}
@@
 \begin{tikzpicture}[overlay,remember picture]
+ \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
 %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
@@
 
-\begin{frame}{Optimal Signal-to-Noise Ratio}
- RMS Average over the angles \\
- Then introduce SNR for both LIGO and ET
+\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio {\bf SNR}}
+\vspace{-5mm}
+\begin{footnotesize} 
+\[
+ \rho=\left[ \int_0^\infty d\ln f\, \f{|\red{2\tilde{h}(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
+\]
+\\
+\end{footnotesize}
+$\sqrt{S_n(f)}\equiv$ {\it amplitude spectral density} ({\bf ASD}) or  detector noise
+\\
+\vspace{3mm}
+Recall, $\tilde{h}(f) \sqrt{f} \sim f^{-7/6} f^{1/2} = \red{f^{-2/3}}$
+\begin{footnotesize} 
+\[
+ \rho^2 =  (2A)^2 h_0^2 |Q(\theta,\phi,\psi,\iota)|^2 \int_0^{\bl{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)} 
+\]
+\end{footnotesize}
+%
+RMS \red{average} over the angles 
+\begin{small}
+$ \langle \ldots \rangle \equiv \int \sin\theta d\theta d\phi \int d\psi \int\sin\iota d\iota $
+\end{small}
+\begin{footnotesize} 
+\[
+ \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\llcorner = \f{4}{25}, \qquad \langle |Q(\theta,\phi,\psi,\iota)|^2 \rangle_\triangle = \f{9}{25}
+\]
+\end{footnotesize}
+%
+Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
+\begin{footnotesize} 
+\[
+0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q(\theta=\tfrac{\pi}{2},\phi,\psi=0,\iota=0)}_{Q_\text{max}}
+\]
+\end{footnotesize}
+% 
+\end{frame}
+
+\begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
+\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
+%
+\begin{footnotesize} 
+\begin{align*}
+\rho_{\text{tot},\llcorner} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
+	= {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
+\rho_c &\equiv 2 h_0 \left[ \int_0^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2}, \quad \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}
+\end{align*}
+\end{footnotesize}
+%
+\begin{tikzpicture}[overlay,remember picture]
+\node[draw, red,thick,minimum width=3.5cm,minimum height=0.8cm] (b) at (8.8,1.9){};
+\end{tikzpicture}
+\\
+%\vspace{2mm}
+$\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
+\begin{footnotesize} 
+\[
+ \rho^2_{\text{tot},\bigtriangleup} = \sum_{A=1}^3 \left(\rho^A\right)^2  =  A^2 \rho_c^2 \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
+\]
+\end{footnotesize}
+\\
+Use \bl{RMS-averaged} $|Q|^2$
+\begin{footnotesize}
+\begin{align*}
+\rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
+&=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
+\end{align*}
+\end{footnotesize}
+\\
+%where \begin{small}$\tilde{H}_\bigtriangleup(f)\equiv A\,  \langle |Q|^2_\bigtriangleup\rangle\, h_0 f^{-7/6}= \f{3}{5} A h_0 f^{-7/6}$ \end{small}\\
+\vspace{-5mm}
+Compare with three-L network's \begin{small}$\rho_\text{tot} \approx \tfrac{4}{5}A\, h_0 \left[ \int df \ldots \right]^{1/2} $ \end{small}
+\vspace{10mm}
+%
+%
+\begin{tikzpicture}[overlay,remember picture]
+\node[draw, red,thick,minimum width=5.5cm,minimum height=1.25cm] (b) at (-3.2,1.05){};
+\end{tikzpicture}
+%
+% 
 \end{frame}
@@
 \end{document}
+
+\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
+ \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
+ \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}  (leading-order)}
+ \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
+ \uncover<4->{\begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}}
+ \uncover<5->{{\bf Binary systems:} 2 points masses in circular orbit. }
+ \end{frame}

### 2018-11-08 Sabanci_talk/Sabanci_talk.tex
Figs added, slide on GRBs finished

@@
 \begin{frame}{Gamma-ray bursts}{Most energetic explosions in the universe}
- \todo{Use Pawan's slides}\\
- Brief history: spy satellites ...\\
- Two main types, short long,  etc.
-
+\begin{small}
+    \begin{itemize}
+      \item Discovered by Vela satellites in 1967
+      \uncover<2->\item Non-thermal spectrum: $10-10^4\,$keV
+      \uncover<3->{\item Highly energetic $10^{48}-10^{52}\,$ergs 
+      \item 1000s detected, $\sim 1$ per day}
+      \uncover<4->\item Far away: $z\approx 9.4 \sim 13\,$billion light years!
+      \uncover<5->\item Afterglow from X-rays to radio \\
+      over timescales of hours to months
+      \uncover<6->\item Two types: short and long
+      \uncover<7->{\item Short GRBs:\\ 
+      mergers of binary neutron stars\\
+      \red{GW170817}-\bl{GRB170817A}}
+    \end{itemize}
+  \end{small}
+  \begin{tikzpicture}[overlay,remember picture]
+      \onslide<2>\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,1.4cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_spectrum.jpg}};    
+      \onslide<3>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/Fermi_GRB_sky2.png}};  
+      \onslide<4>\node (img2 )[anchor=center,scale=1,opacity=1] at ([shift={(3.6cm,-0.15cm)}]current page.center) {\includegraphics[height=3.8cm]{figs/GRB_vs_redshift.png}};  % from:1401.5069
+      \onslide<5>\node (img3 )[anchor=center,scale=1,opacity=1] at ([shift={(3.4cm,-1.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_afterglow.jpg}}; 
+      \onslide<6>\node (img4 )[anchor=center,scale=1,opacity=1] at ([shift={(3.2cm,-2.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_burst_durations.jpg}};    
+    \end{tikzpicture}
 \end{frame}

### 2018-11-08 Sabanci_talk/Sabanci_talk.tex
New figs added, more work on slides

@@
+%\documentclass[xcolor=dvipsnames,t]{beamer}
 \documentclass[xcolor=dvipsnames,handout,t]{beamer}
@@
       \item Discovered by Vela satellites in 1967
-      \uncover<2->\item Non-thermal spectrum: $10-10^4\,$keV
-      \uncover<3->{\item Highly energetic $10^{48}-10^{52}\,$ergs 
-      \item 1000s detected, $\sim 1$ per day}
-      \uncover<4->\item Far away: $z\approx 9.4 \sim 13\,$billion light years!
-      \uncover<5->\item Afterglow from X-rays to radio \\
+      \onslide<2->\item Non-thermal spectrum: $10-10^4\,$keV
+      \item Highly energetic $10^{48}-10^{52}\,$ergs 
+      \onslide<3->{\item 1000s detected, $\sim 1$ per day}
+      \onslide<4->\item Far away: $z\approx 9.4 \sim 13\,$billion light years!
+      \onslide<5->\item Afterglow from X-rays to radio \\
       over timescales of hours to months
-      \uncover<6->\item Two types: short and long
-      \uncover<7->{\item Short GRBs:\\ 
+      \onslide<6->\item Two types: short and long
+      \onslide<7->{\item Short GRBs:\\ 
       mergers of binary neutron stars\\
@@
       \onslide<2>\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,1.4cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_spectrum.jpg}};    
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.5cm,1.cm)}]current page.center) { Mon.Not.Roy.Astron.Soc. 433 (2013) 2739};
       \onslide<3>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/Fermi_GRB_sky2.png}};  
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5.5cm,1.9cm)}]current page.center) {NASA/Fermi};
       \onslide<4>\node (img2 )[anchor=center,scale=1,opacity=1] at ([shift={(3.6cm,-0.15cm)}]current page.center) {\includegraphics[height=3.8cm]{figs/GRB_vs_redshift.png}};  % from:1401.5069
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.cm,1.4cm)}]current page.center) {Astrophys.J.Suppl. 211 (2014) 12};
       \onslide<5>\node (img3 )[anchor=center,scale=1,opacity=1] at ([shift={(3.4cm,-1.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_afterglow.jpg}}; 
-      \onslide<6>\node (img4 )[anchor=center,scale=1,opacity=1] at ([shift={(3.2cm,-2.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_burst_durations.jpg}};    
+      \onslide<6->\node (img4 )[anchor=center,scale=1,opacity=1] at ([shift={(3.2cm,-2.5cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/GRB_burst_durations.jpg}};
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(2.cm,-1.2cm)}]current page.center) {NASA/GSFC};
     \end{tikzpicture}
@@
 \begin{frame}{Neutron Stars}{Most extreme stars in the universe}  
-  Stellar evolution -> white dwarf, NS -> BH \\
-  Density, mass, radius, spin, nuclear equation of state\\
-  Tea spoon of neutron star matter trillion tons
+  \begin{small}
+    \begin{itemize}
+      \item Core-collapse supernova remnants
+      \item Mass: $\sim M_\odot$ to $3 M_\odot$
+      \item Very \red{compact}: radius $\sim 9$ to 15\,km
+      \onslide<2->\item High spins: up to 700 times/second
+      \onslide<3->\item Extremely dense: teaspoon $\sim 10^9\,$tons
+      \onslide<3->{\item Large magnetic fields: $10^4$ to $10^{11}\,$T}
+      \item Hot: surface temperature $10^6\,$K
+      \onslide<4->\item Equation of state \\
+      Piecewise polytropes
+      \[ p = K_i \rho^{\Gamma_i},\quad (\rho_{i-1}\le \rho \le \rho_i) \hspace{8cm}\]
+    \end{itemize}
+  \end{small}
+  \begin{tikzpicture}[overlay,remember picture]
+      \onslide<1>
+	\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.2cm,1.5cm)}]current page.center) {\includegraphics[height=3.2cm]{figs/Core_collapseSXS.jpg}};    
+	\node[anchor=center,scale=1,opacity=1] at ([shift={(5.4cm,2.9cm)}]current page.center) {\textcolor{white}{SXS}};
+      \onslide<2>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=6cm]{figs/Millisecond_NS.png}}; 
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.8cm,-1.cm)}]current page.center) {Class.Quant.Grav. 30 (2013) 224003};
+      \onslide<3>\node (img2 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.6cm,0.0cm)}]current page.center) {\includegraphics[height=4cm]{figs/NS_cross_section.png}}; 
+      \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.6cm,-1.5cm)}]current page.center) {Robert Schulze};
+       \onslide<4>\node (img3 )[anchor=center,scale=0.8,opacity=1] at ([shift={(2.7cm,-2.5cm)}]current page.center) {\includegraphics[height=5cm]{figs/NS_EOS_Lattimer2012.png}}; 
+      \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.cm,-3.8cm)}]current page.center) {Lattimer arXiv:1305.3510};
+    \end{tikzpicture}
 \end{frame}
@@
  \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
- %\uncover<7->{\vspace{2mm}\begin{center}$ \bar{h}'_{\mu\nu} = \bar{h}_{\mu\nu} - \xi_{\mu,\nu} - \xi_{\nu,\mu} + \eta_{\mu\nu} \nabla_\alpha \xi^\alpha . $ \end{center}\vspace{2mm}}
  \end{itemize}
 \uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
-\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<10->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
+\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<9->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
 \\
+
 \begin{tikzpicture}[overlay,remember picture]
-\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\includegraphics[height=2.6cm]{figs/white_box.png}};
+  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\includegraphics[height=2.6cm]{figs/white_box.png}};
+\end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Gravitational waves: d.o.f.'s}
+$A_{\mu\nu} $ is the polarization tensor.
+\begin{itemize}
+  {\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
+  {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ {$\Rightarrow10-4 = \, 6$ d.o.f.}}
+  {\item Residual gauge freedom \hspace{2.25cm} {$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
+ \end{itemize}
+{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
+{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
+\\
+%
+\begin{tikzpicture}[overlay,remember picture]
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
   \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
+\end{tikzpicture}
+\end{frame}
+
+%  Two of the same slide next for the right transition effects %%%%%%%%%%%%%%%%%%%%%%%
+
+ \begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
+  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
+  Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
+  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
+  \vspace{2mm}
+  \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
+  \textcolor{white}{{\bf Binary systems:} 2 points masses in circular orbit.}
+  \begin{tikzpicture}[overlay,remember picture]
+    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
   \end{tikzpicture}
@@
   \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
-  \onslide<2->{{\bf Binary systems:} 2 points masses in circular orbit.}
+  {\bf Binary systems:} 2 points masses in circular orbit.
   \begin{tikzpicture}[overlay,remember picture]
-    \onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
-    \onslide<3->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
-    \onslide<4->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
-    \onslide<5->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
-    \onslide<6->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
+    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\animategraphics[loop,controls,height=2.9cm]{12}{Circ_Orb-}{0}{20}};
+    %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.8cm,-2.7cm)}]current page.center) {\includegraphics[height=2.9cm]{figs/white_box.png}};
+    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
+    \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
+    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
+    \node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
   \end{tikzpicture}
 \end{frame}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
  \vspace{1mm}
- which gives, using Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$   
+  which gives, via Kepler's \bl{third law}: $\Omega^2 = G M r^{-3}=\omega^2/4$,   
+ \onslide<2->
+ {
   \begin{footnotesize}
@@
   \end{footnotesize}\\
+ } 
 %
+  \onslide<3->
+  {
     {\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$\\
@@
     \quad where $ E_b= -\tfrac{G m_1 m_2}{2r} = -\left(\tfrac{G^2 M_c^5 \omega^2}{32}\right)^{1/3} $
+  }
 %
+  \onslide<4->
+  {
     \[ 
@@
     \]
-
     \begin{tikzpicture}[overlay,remember picture]
@@
     \end{tikzpicture}
+  }
 
@@
   \vspace{2mm}
-Introduce \red{inspiral time}, i.e, time to BNS \bl{coal}escence
+  Introduce \red{inspiral time}, i.e, time to \bl{coal}escence
   %
@@
   \red{\tau_\text{insp}(f)} %&= \f{5}{256\pi}\f{c^5}{(\pi G M_c)^{5/3}} \,{f^{-8/3}}\nn\\
- &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2cm}
+  &\simeq \bl{16.72\,\text{minutes}} \, \left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\,{\left(\f{10\,\text{Hz}}{\red{f}}\right)^{\red{8/3}}\quad \red{(2)}}\nn\hspace{2.7cm}
   \end{align}
   \end{small}
+  \\
+  \onslide<2->
+  {
     Number of GW cycles to coalescence: $\int \tfrac{f}{\dot{f}}df\sim \red{f^{-5/3}}$ %$\int df {f}/\dot{f}$
@@
     \end{small}
+  }
   %
+  \onslide<3->
+  {
     \begin{tikzpicture}[overlay,remember picture]
-  \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (5.,3.35){};
-  \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.4,1){};
+      \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (4.2,3.35){};
+      \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.1,1){};
       \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
@@
     \]
-
+  }
 \end{frame}
@@
 \begin{frame}{Gravitational waves from BNS}
-  TT gauge, multipole, slow-velocity expansions give \todo{add suppl. slide}
+  TT gauge, multipole, slow-velocity expansions give 
   \begin{small}
     \[
-    h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}%(t-z/c)
+    h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}\hspace{6cm}
     \]
@@
     \vspace{-5mm}
+    \uncover<2->
+    {
       \begin{align*}
-    h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\\
+      h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\hspace{5cm}\\
       h_\times(t) & =h_c(t)\,\cos\iota \sin[\Phi(t)],
       \end{align*}
+    }
   \end{small}
@@
   %
-  $\iota =\,$ orbital \bl{inclination}, and
+  \uncover<2->{$\iota =\,$ orbital \bl{inclination}}
   \vspace{-3mm}
   %
+  \uncover<3->
+  {
     \begin{small}
@@
       h_c(t) %&=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\nn\\
-    &\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \nn\\
+      &\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \\
       \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN}
       \end{align*}
-  \end{small}\\
+    \end{small}
+    \\
+  }
   %
+  \uncover<4->
+  {
     Frequency increases as $f^{11/3}$\\
     Amplitude increases as $f^{10/3} $
+  }  
   %
   %
+  \uncover<2->
+  {
     \begin{tikzpicture}[overlay,remember picture]
-    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/Chirp.pdf}};
+      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.5cm,1.2cm)}]current page.center) {\includegraphics[height=3cm]{figs/orbit_inc.png}};
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(3.7cm,-0.1cm)}]current page.center) {\textcolor{white}{\url{www.handprint.com/ASTRO/bineye3.html}}};
+      \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/white_box.png}};
+      \node[anchor=center,scale=1.4,opacity=1] at ([shift={(1cm,-2.4cm)}]current page.center) {\href{https://www.youtube.com/watch?v=CH9JSqUfnSw}{\textcolor{white}{Chirp!}}};
+    \end{tikzpicture}
+  }
+  \uncover<5->
+  {
+      \begin{tikzpicture}[overlay,remember picture]
+      \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(2.7cm,-3.2cm)}]current page.center) {\includegraphics[height=2.5cm]{figs/Chirp.pdf}};
       \node[anchor=center,scale=1.4,opacity=1] at ([shift={(1cm,-2.4cm)}]current page.center) {\href{https://www.youtube.com/watch?v=CH9JSqUfnSw}{\red{Chirp!}}};
     \end{tikzpicture}
+  }  
 \end{frame}
@@
 
-\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio {\bf SNR}}
+\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
 \vspace{-5mm}
@@
 \[
-0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q(\theta=\tfrac{\pi}{2},\phi,\psi=0,\iota=0)}_{Q_\text{max}}
+0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
 \]
@@
 % 
+\end{frame}
+
+\begin{frame}{Case study: GW170817}
+
+\end{frame}
+
+\begin{frame}{GW Astronomy in the 2020s}
+
+\end{frame}
+
+\begin{frame}{GW Astronomy in the 2030s}{The era of Einstein Telescope}
+
 \end{frame}

### 2018-11-09 Sabanci_talk/Sabanci_talk.tex
2 more slides, several more figures

@@
 \begin{frame}{Case study: GW170817}
+\begin{itemize}
+  \item 17 August 2017, signal swept from $f\approx 30\,$Hz to $2000\,$Hz 
+  \item The event lasted $\approx 57\,$seconds, $\approx 3000$ GW cycles, $\rho_\text{tot} = 32.4$
+  \item Followed by GRB170817A 1.7 seconds later
+  \item Rapid localization using L1-H1-V1 $\sim 30\,\text{deg}^2$
+  \item Optical counterpart in NGC 4993 11 hours later
+\end{itemize}
 
+  \begin{columns}
+  \begin{column}{0.5\textwidth}  %%<--- here
+      \begin{center}
+      \includegraphics[height=4cm]{figs/GW_GRB170817.jpg}
+      \end{center}
+  \end{column}
+  \begin{column}{0.5\textwidth}
+  %
+    Assuming low spin priors\\
+    $ M=2.73^{+0.04}_{-0.01} M_\odot$ \\
+    $ M_c =1.186^{+0.001}_{-0.001}M_\odot $ \\ 
+    $ D=40.7^{+2.36}_{-2.36}\text{Mpc} $ \\
+    \red{Note:} $M_c$ has the best precision: 
+  \begin{small}${\dot{f}} = \f{96}{5}\pi^{8/3} \left(\tfrac{G M_c}{c^3}\right)^{5/3}\, {f^{11/3}}$ \end{small}
+
+    \end{column}
+  \end{columns}
+
+\end{frame}
+
+\begin{frame}{Case study: GW170817}  {Let's put our knowledge to the \red{test}}
+\vspace{-7mm}
+  \begin{footnotesize}
+    \begin{align*}
+      &\tau_\text{insp}^{0\text{PN}} \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2680 \hspace{2cm} (M=2.74 M_\odot) \\
+      &\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \hspace{2cm} (f_\text{ISCO}\simeq 1605\,\text{Hz}) 
+    \end{align*}
+  \end{footnotesize}
+  What about the SNR? \quad
+  \begin{small}$\rho_{\text{tot},\llcorner}  = {\bar\rho_c(f_0)\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}$   
+  \end{small}
+  %
+
+%
+\begin{tikzpicture}[overlay,remember picture]
+    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2cm,-2.cm)}]current page.center) {\includegraphics[height=5cm]{../Figures/GW170817_strains.pdf}};
+    \onslide<1->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-0.3cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
+    \end{footnotesize}}; 
+    \onslide<1->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-1.3cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $ \left\{ \tilde{A}_h = \tfrac{4}{5}A,  \tilde{A}_m =\tfrac{2}{5}A,  \tilde{A}_l  < \tfrac{\tilde{A}_m}{2}\right\}$    
+    \end{footnotesize}};  
+    \onslide<1->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.3cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\bar\rho_h = 29.2,\quad \bar\rho_m = 14.6,\quad \bar\rho_l = 6.11 $    
+    \end{footnotesize}}; 
+    \onslide<1->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.6cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\bar\rho_\text{L1} = 26.4 \quad 18.8 \quad 2.0 $    
+    \end{footnotesize}};
+    \onslide<1->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(3cm,-2.6cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\rho_\text{tot} = 32.6 $    
+    \end{footnotesize}};
+  \end{tikzpicture}
 \end{frame}
@@
 \end{itemize}
+\begin{align*}
+      x &=1
+	  %
+	  %\\
+	  %
+      \end{align*}
 \end{frame}

### 2018-11-09 Sabanci_talk/Sabanci_talk.tex
More slides more figures

--- 2018-11-08 Sabanci_talk/Sabanci_talk.tex
@@
-%\documentclass[xcolor=dvipsnames,t]{beamer}
-\documentclass[xcolor=dvipsnames,handout,t]{beamer}
+\documentclass[xcolor=dvipsnames,t]{beamer}
+%\documentclass[xcolor=dvipsnames,handout,t]{beamer}
 % use handout in document class to stop transitions
@@
 \newcommand{\Lim}[1]{\raisebox{0.5ex}{\scalebox{0.8}{$\displaystyle \lim_{#1}\;$}}}
+\newcommand\T{\rule{0pt}{2.6ex}}       % Top strut for vertical spacing in tables
+\newcommand\B{\rule[-1.2ex]{0pt}{0pt}} % Bottom strut
 \newcommand*\circled[1]{\tikz[baseline=(char.base)]{\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
@@
  \item Gravitational-wave detectors
- \item Event rates 
+ \item Future detectors, event rates, \red{early warning} prospects
 \end{itemize}
@@
     {\small ``What can we offer to the astronomy community with future GW detections?''}
+    Advance warning!
   \end{itemize}
@@
     %
+    \onslide<2->
+    {
       GW along $\mathbf{z}$: 
@@
       \]
+    }
+    \onslide<3->
+    {
       Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
@@
       \end{small}
+    }
     %
+    \onslide<4->
+    {
       \begin{tikzpicture}[overlay,remember picture]
       \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
-%\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
+      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{30}};
       \end{tikzpicture}
+    }
  \end{frame}
@@
    %
+   \onslide<2->
+   {
       Fourier transform to frequency domain 
@@
 	\end{footnotesize}
+    }
+    \onslide<3->
+    {
       \red{Four} angles: $\{\theta,\phi,\iota,\psi \}$
@@
       \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-1.8cm)}]current page.center) {\includegraphics[height=5cm]{figs/Schutz_LRR_Fig3_half.jpg}};
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.1cm,-4.4cm)}]current page.center){Sathyaprakash, Schutz, Living Rev. Relativ. (2009) 12:2} ;
       \end{tikzpicture}
-
+    }   
 \end{frame}
@@
    %
+    \begin{tikzpicture}[overlay,remember picture]
+    \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
+    \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
+    \end{tikzpicture}
+    %
+   \onslide<2->
+   {
       No blind spots!
@@
   \begin{tikzpicture}[overlay,remember picture]
-  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.4cm,-1.cm)}]current page.center) {\includegraphics[height=3cm]{figs/gr_qc_12013563.png}};
+
    \node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0.4cm,-2.5cm)}]current page.center) {\includegraphics[height=4cm]{../Figures/ET_no_blind_spots.pdf}};
-    \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
     \end{tikzpicture}
+  }
 
@@
   \\
+  \onslide<2->
+  {
     \vspace{3mm}
@@
     \end{footnotesize}
+  }
   %
+  \onslide<3->
   RMS \red{average} over the angles 
@@
   %\vspace{2mm}
+  \onslide<2->
+  {
     $\bigtriangleup$ = \red{Three V-}IFOs: Einstein Telescope
@@
     \\
+  }
+  \onslide<3->
   Use \bl{RMS-averaged} $|Q|^2$
@@
 \begin{frame}{Case study: GW170817}
+  \begin{itemize}
+    \item 17 August 2017, signal swept from $f\approx \red{30}\,$Hz to $\bl{2000}\,$Hz 
+    \onslide<2->\item The event lasted $\approx \red{57}\,$seconds, $\approx \bl{3000}$ GW cycles, $\rho_\text{tot} = \red{32.4}$
+    \onslide<3->\item Followed by \red{GRB}170817A 1.7 seconds later
+    \onslide<4->\item Rapid localization using L1-H1-V1 $\sim \bl{30}\,\text{deg}^2$
+    \onslide<5->\item \red{Optical} counterpart in NGC 4993 11 hours later
+  \end{itemize}
+
+  \begin{columns}
+  \begin{column}{0.5\textwidth}  %%<--- here
+      \begin{center}
+      \onslide<3->\includegraphics[height=4cm]{figs/GW_GRB170817.jpg}
+      \end{center}
+  \end{column}
+  \begin{column}{0.5\textwidth}
+  %
+  \onslide<6->
+  {
+    Assuming low spin priors
+    \begin{align*}
+     M&=2.73^{+0.04}_{-0.01} M_\odot \\
+     M_c &=1.186^{+0.001}_{-0.001}M_\odot  \\ 
+     D&=40.7^{+2.36}_{-2.36}\text{Mpc}
+    \end{align*}
+  }
+  \onslide<7->
+  {
+    \red{Note:} $M_c$ has the best precision: 
+   \begin{small}$${\dot{f}} = \f{96}{5}\pi^{8/3} \left(\tfrac{G M_c}{c^3}\right)^{5/3}\, {f^{11/3}}$$ \end{small}
+  }
+
+    \end{column}
+  \end{columns}
 
@@
 
-\begin{frame}{GW Astronomy in the 2020s}
+\begin{frame}{Case study: GW170817}  {Let's put our knowledge to the \red{test}}
+\vspace{-7mm}
+  \begin{footnotesize}
+    \begin{align*}
+      &\tau_\text{insp}^{0\text{PN}} \ \ \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \ \ \simeq 2680 \hspace{2cm} (M=2.74 M_\odot) \\
+      &\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \hspace{2cm} (f_\text{ISCO}\simeq 1605\,\text{Hz}) 
+    \end{align*}
+  \end{footnotesize}
+  \onslide<2->
+  {
+  What about the SNR? \quad
+  \begin{small}$\rho_{\text{tot},\llcorner}  = {\bar\rho_c(f_0)\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}$   
+  \end{small}
+  }
+  %
+
+%
+\begin{tikzpicture}[overlay,remember picture]
+    \onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2cm,-2.cm)}]current page.center) {\includegraphics[height=5cm]{../Figures/GW170817_strains.pdf}};
+    \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
+    \end{footnotesize}}; 
+    \onslide<2->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(4.1cm,0.1cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $ \tilde{A}_{i=h,m,l}=A\left\{\tfrac{4}{5},  \tfrac{2}{5},   < \tfrac{1}{5}\right\}$    
+    \end{footnotesize}};  
+    \onslide<3->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.2cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\bar\rho_{i} = \left\{29.2, \ 14.6, \ 6.11 \right\}$    
+    \end{footnotesize}}; 
+    \onslide<4->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-2.6cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\bar\rho_\text{LHV} = \{ 26.4, 18.8 , 2.0\} $    
+    \end{footnotesize}};
+    \onslide<3->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.7cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\rho_\text{tot} = 32.6 $    
+    \end{footnotesize}};
+    \onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
+  \red{BIG question:} how long before the GRB can we {\bf detect} BNS inspirals?\\
+  Detection criterion: SNR = \red{15}\\
+  Three identical L-IFOs with $Q_{i=h,m,l}$
+  %\[  \bar\rho_\text{tot}= \sqrt{\left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2}=15\]
+  % 
+  \begin{tikzpicture}[overlay,remember picture]
+      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.7cm)}]current page.center) {\includegraphics[height=5.5cm]{../Figures/ALigo_strains.pdf}};
+      %\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
+      %{\begin{footnotesize} 
+      %  $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
+      %\end{footnotesize}}; 
+      %\onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
+  \end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
+Detection moment: $t(f=\bar{f})$ such that
+%There exists $\bar{f}$ such that
+\begin{small}
+  \[
+    \bar\rho_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
+  \]
+\end{small}
+
+  \begin{tikzpicture}[overlay,remember picture]
+      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.7cm)}]current page.center) {\includegraphics[height=5.5cm]{../Figures/ALigo_strains.pdf}};
+      %\onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(3.65cm,0.8cm)}]current page.center) 
+      %{\begin{footnotesize} 
+      %  $   \bar\rho_c(\red{f_0}) \equiv 2 h_0 \left[ \int_{\red{f_0}}^{{f_\text{ISCO}}} df \f{f^{-7/3}}{S_n(f)}  \right]^{1/2} $      
+      %\end{footnotesize}}; 
+      %\onslide<3->\node[draw, red,thick,minimum width=3.8cm,minimum height=1.1cm] (b) at (10.1,-2.15){};
+  \end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
+  Detection moment: $t(f=\bar{f})$ such that
+  \begin{small}
+    \[
+	\bar\rho_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
+    % \textcolor{black}{\bar\rho_\text{tot}=} \onslide<1>\left[\rho_h(f_0^h,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<2>\left[\rho_m(f_0^m,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<3->\left[\rho_l(f_0^l,\bar{f})\right]^2\textcolor{white}{=\red{15}^2}
+    \]
+  \end{small}
+
+  \begin{tikzpicture}[overlay,remember picture]
+      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.7cm)}]current page.center) {\includegraphics[height=5.5cm]{../Figures/ALIGO2020_int_50Mpc.pdf}};
+      \onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.7cm)}]current page.center) {\includegraphics[height=5.5cm]{../Figures/ALIGO2020_int_100Mpc.pdf}};
+      \onslide<3->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.7cm)}]current page.center) {\includegraphics[height=5.5cm]{../Figures/ALIGO2020_int_200Mpc.pdf}};
+    \end{tikzpicture}
+
+\end{frame}
+
+\begin{frame}{GW Astronomy in the 2020s}{Advanced LIGO-Virgo}
+  Advance \red{warning time}: inspiral time from $\bar{f}$
+  \[
+    T_\text{AW} = \tau_\text{insp}(\bar{f})
+  \]
+  \onslide<2->
+  {
+    Total accumulated SNR over the inspiral
+    \begin{footnotesize}
+      \[
+      \bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2}
+      \]
+      \begin{table}[h]
+	\centering
+	\begin{tabular}{lcccccc}
+	  \hline\hline
+	  $D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T \B \\
+	  \hline
+	  50 & $\approx\,$25.3 & & 84.25 & & 85.86 & 70.3 \\
+	  100 & $\approx\,$41.6 & & 22.39 & & 22.86 & 35.2 \\
+	  200 & $\approx\,$121 & & 1.291 &\quad & 1.300 & 17.6 \\
+	  \hline\hline
+	\end{tabular}
+      \end{table}
+    \end{footnotesize}
+  }
+%
+\onslide<3->$\Longrightarrow$ NO likely FORECASTS  in the 2020s
+\begin{tikzpicture}[overlay,remember picture]
+  \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.6,5.3){};
+\end{tikzpicture}
 

### 2018-11-10 Sabanci_talk/Sabanci_talk.tex
One more slide

@@
-\documentclass[xcolor=dvipsnames,t]{beamer}
-%\documentclass[xcolor=dvipsnames,handout,t]{beamer}
+%\documentclass[xcolor=dvipsnames,t]{beamer}
+\documentclass[xcolor=dvipsnames,handout,t]{beamer}
 % use handout in document class to stop transitions
@@
       \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
-      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{30}};
+      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
       \end{tikzpicture}
@@
   \[
-    \bar\rho_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
+    \bar\rho^2_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
   \]
@@
     \[
-	\bar\rho_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
+	\bar\rho^2_\text{tot}= \left[\rho_h(f_0^h,\bar{f})\right]^2+\left[\rho_m(f_0^m,\bar{f})\right]^2+\left[\rho_l(f_0^l,\bar{f})\right]^2=\red{15}^2
     % \textcolor{black}{\bar\rho_\text{tot}=} \onslide<1>\left[\rho_h(f_0^h,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<2>\left[\rho_m(f_0^m,\bar{f})\right]^2 \, \textcolor{white}{+}\onslide<3->\left[\rho_l(f_0^l,\bar{f})\right]^2\textcolor{white}{=\red{15}^2}
@@
 	  \hline\hline
-	  $D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T \B \\
+	  $D\,$(Mpc) & $\bar{f}\,$(Hz) &{}& $T^\text{0PN}_\text{AW}$(sec) &\hspace{1mm} & $T^\text{3.5PN}_\text{AW}\text{ (sec)}\hspace{2mm}$& $\bar{\rho}_F$\T \B \\
 	  \hline
@@
 \begin{tikzpicture}[overlay,remember picture]
-  \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.6,5.3){};
+  \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.7,5.3){};
 \end{tikzpicture}
@@
 \begin{frame}{GW Astronomy in the 2030s}{The era of Einstein Telescope}
+ One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.\\
+ Underground,cryogenic, \bl{xylophone} (high, low-frequency modes)\\
+ \vspace{1mm}
+ Cosmological range $\Rightarrow$ sky-averaged,\red{red}-shifted strain and SNR
+ \begin{footnotesize}
+ \begin{align*} 
+  \tilde{H}_\text{ET}(f) &= \f{3}{5}A h_0 \red{(1+z)^{-1}} f^{-7/6}\\
+  \bar\rho_{\text{ET}}(f_0,f)&\equiv \f{6}{5}A h_0\, \red{(1+z)^{-1/6}}\left[\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')}\right]^{1/2}
+ \end{align*} 
+ \end{footnotesize}
+Consider BNS at \\
+$$ D=\{100,200, 400, 600\}\,\text{Mpc} \Longrightarrow z=\{0.022, 0.044, 0.085, 0.12\}$$
+$\Omega_\Lambda = 0.6911, \Omega_m = 0.3089, H_0 = 67.74\,$km\,s$^{-1}\,$Mpc$^{-1}$
 
@@
  \end{frame}
+
+  One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.\\
+ Underground,cryogenic, \blue{xylophone} (high, low-frequency modes)\\
+
+ Cosmological range $\Rightarrow$ sky-averaged,\red{red}-shifted strain and SNR
+ \begin{footnotesize}
+ \begin{align*} 
+  \tilde{H}_\text{ET}(f) &= \f{3}{5}A h_0 \red{(1+z)^{-1}} f^{-7/6}\\
+  \bar\rho_{\text{ET}}(f_0,f)&\equiv \f{6}{5}A h_0\, \red{(1+z)^{-1/6}}\left[\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')}\right]^{1/2}
+ \end{align*} 
+ \end{footnotesize}

### 2018-11-11 Sabanci_talk/Sabanci_talk.tex
More slides

@@
       \onslide<3>\node (img2 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.6cm,0.0cm)}]current page.center) {\includegraphics[height=4cm]{figs/NS_cross_section.png}}; 
+      % Use Fig 3 of http://science.sciencemag.org/content/304/5670/536/tab-figures-data ?
       \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.6cm,-1.5cm)}]current page.center) {Robert Schulze};
@@
   \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.7,5.3){};
+  \onslide<3->\node[draw, red,thick,minimum width=1.1cm,minimum height=1.2cm] (b) at (1.6,1.35){};
 \end{tikzpicture}
@@
 \begin{frame}{GW Astronomy in the 2030s}{The era of Einstein Telescope}
- One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.\\
- Underground,cryogenic, \bl{xylophone} (high, low-frequency modes)\\
- \vspace{1mm}
- Cosmological range $\Rightarrow$ sky-averaged,\red{red}-shifted strain and SNR
+  \vspace{-1mm}
+  \begin{itemize}
+    \item[] One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.
+    \item[] Underground,cryogenic, \bl{xylophone} (high, low-frequency modes)
+    \uncover<2->{
+    \item[] Recall: \red{RMS}-average over all four angles
+    \item[] Cosmological range $\Rightarrow$ \red{red}-shifted strain and SNR}
+  \end{itemize}
+  \onslide<2->
     \begin{footnotesize}
@@
     \end{footnotesize}
-Consider BNS at \\
-$$ D=\{100,200, 400, 600\}\,\text{Mpc} \Longrightarrow z=\{0.022, 0.044, 0.085, 0.12\}$$
-$\Omega_\Lambda = 0.6911, \Omega_m = 0.3089, H_0 = 67.74\,$km\,s$^{-1}\,$Mpc$^{-1}$
+    \vspace{-1mm}
+  \onslide<3->
+    Consider BNS at
+    \begin{footnotesize}
+      $$ \bl{D}=\{100,200, 400, 600\}\,\text{Mpc} \Longrightarrow \red{z}=\{0.022, 0.044, 0.085, 0.12\}$$
+      $$ \left(\text{Using } \Omega_\Lambda = 0.6911, \Omega_m = 0.3089, H_0 = 67.74\,\text{km}\,\text{s}^{-1}\,\text{Mpc}^{-1}\right)\qquad  $$
+    \end{footnotesize}
+  \onslide<4->
+  {{\bf Note}: for binary black holes, ET's range $>\,1$Gpc, but inspirals too quick.}
+\end{frame}
+
+\begin{frame}{The era of Einstein Telescope}{BNS detections}
+ Same detection criterion:\qquad $\bar{\rho}_\text{ET}(f_0, \bar{f}_\text{ET}) =15$ \todo{ADD LIGO2017}\\
+ \red{Two} ET configurations: B (high $f$), C (low $f$)\todo{2020 to plot}
+ \begin{tikzpicture}[overlay,remember picture]
+      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
+      %\onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
+      %\onslide<3->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
+      %\onslide<4->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
+\end{tikzpicture}      
+\end{frame}
+
+\begin{frame}{The era of Einstein Telescope}{GRB \red{Forecast} Prospects} 
+  \vspace{-8mm}
+  \begin{footnotesize}
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{lccccccc}
+  %toprule
+  \hline\hline
+  $D\,$(Mpc) & \multicolumn{3}{c}{ET-B} & $R_\text{av}{}^\text{max}_\text{min} $ & \multicolumn{3}{c}{ET-C}\T\B\\
+  \hline
+  {}& $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{3mm} $T_\text{AW}$ \ \hspace{3mm} & $\bar{\rho}_{F}$ & {}  & $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{3mm} $T_\text{AW}\hspace{3mm}$& $\bar{\rho}_{F}$\T\B\\
+  %midrule
+  100 & $\approx\,$6.72 &  47.0\,minutes & 306 & $ 1.54^{4.7}_{0.3}$ & $\approx\,$3.27 & 5.34\,hours\ & 365\T\\
+  200 & $\approx\,$11.2 & 11.6\,minutes & 152 &  $ 12.3^{38}_{2.6} $ & $\approx\,$4.10 & 2.87\,hours\ & 182 \\
+  400 & $\approx\,$18.2 & 3.00\,minutes & 75.7 &$ 98.6^{300}_{20} $ & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
+  600 & $\approx\,$?  &?\,seconds & ?& $ 333^{1020}_{69} $ &    $\approx\,$5.7 & 1.03\,hours & 60.?  \\
+  \hline\hline
+  %bottomrule
+  \end{tabular}
+  \caption*{Event rates using $R=1540^{+3200}_{-1220}\,\text{Gpc}^{-3}\,\text{yr}^{-1}$ inferred from GW170817}
+  \end{table}
+  \end{footnotesize}
+  %
+  \vspace{-3mm}
+  \onslide<2->Very \red{high SNRs} $\Rightarrow \ord(\rho_F^{\red{-1}})$-precision parameter estimation afterward \\
+  \vspace{2mm}
+  \onslide<3->\bl{ET-B} $\Longrightarrow $ forecasts not likely \\
+  \vspace{2mm}
+  \onslide<4->\red{ET-C} $\Longrightarrow T_\text{AW} \ge 1\,$hour within 600\,Mpc\\
+  \vspace{1mm}
+  \textcolor{white}{ET-C} $\Longrightarrow \red{\ord(100)}$ {\bf BNS forecasts} yearly! $\Rightarrow $ 1 per day!\\
+  \vspace{1mm}
+  \onslide<5->\textcolor{white}{ET-C} $\Longrightarrow \red{\ord(10)}$ with \red{3\,hours} of warning \\
+  \vspace{1mm}
+  \onslide<6->\textcolor{white}{ET-C} $\Longrightarrow \red{\ord(2)}$ with \red{5\,hours} of warning
+  \begin{tikzpicture}[overlay,remember picture]
+      \onslide<3>\node[draw, blue,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (-2.3,5.3){};
+      \onslide<4->\node[draw, red,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (3.6,5.3){};
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{The era of Einstein Telescope}{Source localization before the merger} 
+  ET is very sensitive, but all 3 IFOs are at one place. \\
+  \vspace{1mm}
+  $\Longrightarrow$ \red{poor} sky localization \\
+  \vspace{1mm}
+  \onslide<2->BUT \ldots \\
+  \begin{itemize}
+  \item With $T_\text{AW} \sim\,$hours, Earth's rotation matters!
+  \item Two hours $\Rightarrow 30^\circ \Rightarrow \approx 2000\,$km of IFO distance $\sim\,$L1-H1 separation
+  \end{itemize}
+  \onslide<3->So, within 1\,Gpc, ET {\bf alone} will localize
+  \begin{itemize}
+  \item 20\% of the sources to within 100\,deg$^2$
+  \item 2\% to within 20\,deg$^2$
+  \item 0.5\% to within 10\,deg$^2$ 
+  \onslide<4->\item[]$\Longrightarrow \red{\ord(5)}$ sources within 400\,Mpc
+  \end{itemize}
+  \onslide<5->10\,deg$^2$: LSST's field of view\\
+  \onslide<6-> Numbers improve with \bl{Cosmic Explorer} ($f\gtrsim \red{5}\,$Hz)
+  %
+  \begin{tikzpicture}[overlay,remember picture]
+	\onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.2cm,2.25cm)}]current page.center) {\includegraphics[height=3cm]{figs/Earth_rot.png}};
+	\onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(4.3cm,-2.25cm)}]current page.center) {\includegraphics[height=3.9cm]{figs/LSST.jpg}};
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{The era of Einstein Telescope}{Black hole - neutron star binaries}
 

### 2018-11-12 Sabanci_talk/Sabanci_talk.tex
Early draft finished

@@
     {\small ``What can we offer to the astronomy community with future GW detections?''}
-    Advance warning!
+    \item[] \red{GRB Forecasts!}
   \end{itemize}
@@
 
-\begin{frame}{The era of Einstein Telescope}{Black hole - neutron star binaries}
+\begin{frame}{Black hole - neutron star binaries}{Forecasting \red{tidal disruption} events}
+  Necessary, but insufficient \bl{condition}:
+  $   \f{M_\text{BH}}{M_\text{NS}} \gtrsim \left(\f{r}{R_\text{NS}}\right)^3  $
+  %
+  \onslide<2->
+  \begin{itemize}
+  \item Small separation $r\to r_\text{ISCO}$
+  \item Low black hole mass, stellar evolution models: $M_\text{BH}\gtrsim 5M_\odot$
+  \item High black hole spin: $\tilde{r}_\text{ISCO}\to 1$ from 6.
+  \item Larger neutron star radii, $r_\text{NS}\sim15\,$km
+  \end{itemize}
+  \onslide<3->
+  $\red{5} M_\odot -1.4 M_\odot$ BH-NS inspirals are \red{faster} because $\tau_\text{insp} \propto M^{-5/3}$
+  %
+  \onslide<4->
+  \begin{footnotesize}
+  \begin{table}[h]
+  \centering
+  \begin{tabular}{lccccc}
+  %toprule
+  \hline\hline
+  $D\,$(Mpc) & \multicolumn{2}{c}{ET-B} &  & \multicolumn{2}{c}{ET-C}\T\B\\
+  \hline
+  {}&  \ \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$ &{}  & $\hspace{6mm}T_\text{AW} \hspace{10mm}$ & $\bar{\rho}_{F}$\T\B\\
+  %
+  100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
+  200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
+  %400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
+  %1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
+  \hline\hline
+  %bottomrule
+  \end{tabular}
+  \end{table}
+  \end{footnotesize}
+  %
+  \onslide<5->
+  $T_\text{AW} \gtrsim 1\,$hour $\Longrightarrow D \lesssim 200\,$Mpc \\
+  O1 rate $R < 3600 \text{Gpc}^{-3}\text{yr}^{-1} \Longrightarrow 30\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$ \\
+  BH population studies: $\Longrightarrow \text{ \red{Forecast} } \red{3}\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$
+  % 
+  %
+  \begin{tikzpicture}[overlay,remember picture]
+	  \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(5.6cm,2.25cm)}]current page.center) {\includegraphics[height=2.8cm]{figs/BH_NS_1.png}};
+	  \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.7cm)}]current page.center) {Phys.Rev. D92 (2015) 044028};
+  \end{tikzpicture}
+\end{frame}
+
+\begin{frame}{}{}%{Summary and Outlook}
+{\bf Summary}
+\begin{itemize}
+ \item \bl{Quadrupole} + \bl{Newtonian} evolution = inspiral time $\tau_\text{insp}\propto \red{f^{-8/3}}$
+ \item Detector sensitivity + GW strain = advance warning time $T_\text{AW}$
+ \onslide<2->
+ \item Advanced LIGO-Virgo will detect \bl{many} BNS, but NOT forecast.
+ \onslide<3->
+ \item Einstein Telescope will \bl{detect} $\bl{\ord(1000)}$ of BNS out to 1\,Gpc .
+ \item Einstein-C will \red{forecast $\ord(100)$ BNS} with $T_\text{AW}>1\,$hour.
+ \item Additionally forecast $< \ord(10)$ tidal disruption events.
+ \item 5 to 10 BNS inspirals will be \red{localized} to $\red{10\,\text{deg}^2}$.
+ \end{itemize}
+ \onslide<4->{
+  {\bf Outlook}
+  \begin{itemize}
+    \item Forecast/localize $\Rightarrow$ Mobilize EM telescopes \\
+  \hspace{-5.6mm}$\Rightarrow$ \red{Observe} the merger/kilonova from  $\gamma$-rays to radio
+  \item Pre-, post-merger image comparisons with LSST
+ }
+ \onslide<5->
+ \item Contaminants? Type Ia supernovae, AGN, CV
+\end{itemize}
+\begin{tikzpicture}[overlay,remember picture]
+	  \onslide<5->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-2.6cm,-3.8cm)}]current page.center) {\includegraphics[height=1.2cm]{figs/AAletter.png}};
+	  \onslide<5->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(4.6cm,-3.cm)}]current page.center) {\includegraphics[height=2.7cm]{figs/SNIa_lim22mag.pdf}};
+\end{tikzpicture}
 

### 2018-11-12 Sabanci_talk/Sabanci_talk.tex
New figs, v2 fnished

@@
 
+%\setlength{\droptitle}{10em}
+
 \usetikzlibrary{shapes}
@@
 
-\title[Forecasting GRBs w/ GWs] % (optional, use only with long paper titles)
-{Forecasting Gamma-ray Bursts with Gravitational Waves}
-
-\subtitle{\todo{Add background image}} % (optional)
-
-\author[Sarp Akcay]{Sarp Akcay\inst{1}\inst{2} }
+\title[Forecasting GRBs with GWs] % (optional, use only with long paper titles)
+{\vspace{0mm}Forecasting Gamma-ray Bursts with Gravitational Waves}
+
+\subtitle{} % (optional)
+%\vspace{2cm}
+\author[Sarp Ak\c{c}ay]{\vspace{-2cm}Sarp Ak\c cay\inst{1}\inst{2} }
 \institute[FSU Jena - UCD] % (optional, but mostly needed)
-{
+{\vspace{-2.25cm}
   \inst{1}%
@@
 
+\date[Sabanc\i~Universitesi]{\vspace{-2.5cm}14 November 2018}
 %\vspace{-3cm}
@@
 %}
-\date[Sabanci University]{14 November 2018}
 
@@
 \newcommand{\Blue}{\textcolor{blue}}
-\renewcommand{\c}{\cos}
+%\renewcommand{\c}{\cos}  \c{c} gives cecedille
 \renewcommand{\t}{\theta}
@@
 \begin{document}
-%{
-%\usebackgroundtemplate{\includegraphics[width=1\paperwidth,height=\paperheight]{../Figures/ET_strains_redshifted_v2.pdf}}
+{
+  \usebackgroundtemplate{\includegraphics[width=1\paperwidth,height=\paperheight]{figs/kilonova.jpg}}
+  % image credit [University of Warwick/Mark Garlick]
   \begin{frame}
+  \vspace{-2cm}
     \titlepage
   \end{frame}
-%}
+} % these brackets are needed to insure that the background image is used ONLY in the title slide
 
@@
  \item Motivation 
- \item Gamma-ray bursts
- \item Gravitational waves
- \item Binary neutron star inspirals
+ \item \bl{Gamma-ray bursts}
+ \item Neutron stars
+ \item \bl{Gravitational waves}
+ \item Compact binary \red{inspirals}
  \item Gravitational-wave detectors
- \item Future detectors, event rates, \red{early warning} prospects
-\end{itemize}
-\todo{finish this slide remove later if short on time}
+ \item Gravitational-wave astronomy in the 2020s and the 2030s
+ \item \red{Forecasting} prospects, event rates etc.
+\end{itemize}
 
@@
   \begin{itemize}
-    \item \emph{Multi}: two fundamentally different waves from common events.
-    \item[]\quad Gravitational waves (GWs): ``hearing''  the universe.
+    \onslide<1->
+    \item \red{\emph{Multi}}: two fundamentally different waves from common events.
+    \item[]\quad Gravitational waves ({\bf GW}s): ``hearing''  the universe.
     \item[]\quad Electromagnetic waves (EWs): ``seeing'' the universe.
-    \item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
+    \onslide<2->\item \red{GW170817}-\bl{GRB170817A}-\textcolor{brown}{AT2017gfo}: the ``event'' \\
     \quad inspiral + merger of two neutron stars (GWs) \\
-    \ \ = short-hard gamma-ray burst + kilonova (EWs)
-    \item[] Broad-band in gravitational waves: 10Hz - 2000Hz
+    \ \ \ = short-hard gamma-ray burst + kilonova (EWs)
+    \item[] Broad-band in gravitational waves: 20Hz - 2000Hz
     \item[] Ultra broad-band in electromagnetic waves: gamma rays to radio.
-    \item A simple question \\
+    \onslide<3->\item A simple question: \\
     {\small ``What can we offer to the astronomy community with future GW detections?''}
-    \item[] \red{GRB Forecasts!}
+    \item[] \red{GRB/kilonova Forecasts!}
+    \item[] Observe NOT 11 hours \underline{after} the merger, but ``live''
   \end{itemize}
@@
     \begin{itemize}
-      \item Discovered by Vela satellites in 1967
-      \onslide<2->\item Non-thermal spectrum: $10-10^4\,$keV
-      \item Highly energetic $10^{48}-10^{52}\,$ergs 
-      \onslide<3->{\item 1000s detected, $\sim 1$ per day}
-      \onslide<4->\item Far away: $z\approx 9.4 \sim 13\,$billion light years!
+      \item Discovered by Vela satellites in \red{1967}
+      \onslide<2->\item Non-thermal spectrum: $10-10^4\,$\red{keV}
+      \item Highly energetic $10^{48}-10^{\red{52}}\,$ergs 
+      \onslide<3->{\item \bl{1000s} detected, $\sim 1$ per day}
+      \onslide<4->\item Far away: $z\approx 1 \sim 8\,$billion years! %$9.4\sim 13\,$billion light years!
       \onslide<5->\item Afterglow from X-rays to radio \\
       over timescales of hours to months
-      \onslide<6->\item Two types: short and long
+      \onslide<6->\item \bl{Two types}: \red{short} and long
       \onslide<7->{\item Short GRBs:\\ 
-      mergers of binary neutron stars\\
+      mergers of binary neutron stars (1989)\\
       \red{GW170817}-\bl{GRB170817A}}
@@
       \item Core-collapse supernova remnants
-      \item Mass: $\sim M_\odot$ to $3 M_\odot$
+      \item Mass: $\sim $ \red{1} to \red{3} solar masses ($M_\odot$)
       \item Very \red{compact}: radius $\sim 9$ to 15\,km
       \onslide<2->\item High spins: up to 700 times/second
-      \onslide<3->\item Extremely dense: teaspoon $\sim 10^9\,$tons
-      \onslide<3->{\item Large magnetic fields: $10^4$ to $10^{11}\,$T}
-      \item Hot: surface temperature $10^6\,$K
-      \onslide<4->\item Equation of state \\
-      Piecewise polytropes
-      \[ p = K_i \rho^{\Gamma_i},\quad (\rho_{i-1}\le \rho \le \rho_i) \hspace{8cm}\]
+      \onslide<3->\item Extremely \bl{dense}: teaspoon $\sim 10^9\,$tons
+      \onslide<3->{\item Large magnetic fields: $10^4$ to $10^{\red{11}}\,$T}
+      \onslide<4->\item Hot: surface temperature $10^5 - 10^6\,$K
+      \onslide<5->\item They can come in \red{pairs} (binary) \\
+      \onslide<6->Orbit \red{decays} over time due\\
+      $\Longrightarrow$ \underline{Gravitational wave emission}!\\
+      Observations \red{match} theoretical \\predictions very well
+      %Equation of state \\
+      %Piecewise polytropes
+      %\[ p = K_i \rho^{\Gamma_i},\quad (\rho_{i-1}\le \rho \le \rho_i) \hspace{8cm}\]
     \end{itemize}
@@
 	\node[anchor=center,scale=1,opacity=1] at ([shift={(5.4cm,2.9cm)}]current page.center) {\textcolor{white}{SXS}};
-      \onslide<2>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=6cm]{figs/Millisecond_NS.png}}; 
-      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.8cm,-1.cm)}]current page.center) {Class.Quant.Grav. 30 (2013) 224003};
+      \onslide<2>\node (img1 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.8cm,0.9cm)}]current page.center) {\includegraphics[height=6cm]{figs/Millisecond_NS2.png}}; 
+      \node[anchor=center,scale=0.5,opacity=1] at ([shift={(4.8cm,3.2cm)}]current page.center) {Class.Quant.Grav. 30 (2013) 224003};
       \onslide<3>\node (img2 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.6cm,0.0cm)}]current page.center) {\includegraphics[height=4cm]{figs/NS_cross_section.png}}; 
@@
       \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.6cm,-1.5cm)}]current page.center) {Robert Schulze};
-       \onslide<4>\node (img3 )[anchor=center,scale=0.8,opacity=1] at ([shift={(2.7cm,-2.5cm)}]current page.center) {\includegraphics[height=5cm]{figs/NS_EOS_Lattimer2012.png}}; 
-      \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.cm,-3.8cm)}]current page.center) {Lattimer arXiv:1305.3510};
+      \onslide<4>\node (img2 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.6cm,0.0cm)}]current page.center) {\includegraphics[height=5cm]{figs/NS_temp.jpg}}; 
+      %
+      \node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.6cm,2.2cm)}]current page.center) {Science 304, 5670, pp. 536-542};
+       \onslide<5->\node (img3 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.cm,-2.8cm)}]current page.center){\includegraphics[height=3.8cm]{figs/HT_pulsar.jpg}};
+       \onslide<6>\node (img3 )[anchor=center,scale=0.8,opacity=1] at ([shift={(3.2cm,0.9cm)}]current page.center){\includegraphics[height=5cm]{figs/HT_decay.jpg}}; 
+       \node[anchor=center,scale=0.5,opacity=0.7] at ([shift={(2.5cm,-0.5cm)}]current page.center) {ApJ 829: 55 (2016)};
+       %{\includegraphics[height=5cm]{figs/NS_EOS_Lattimer2012.png}}; 
+      %\node[anchor=center,scale=0.6,opacity=1] at ([shift={(4.cm,-3.8cm)}]current page.center) {Lattimer arXiv:1305.3510};
     \end{tikzpicture}
@@
   \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
-  Gravitational-wave luminosity: \alert{quadrupole} radiation (leading-order)
+  Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
   \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
@@
     \onslide<2->\node (t1 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-1.3cm)}]current page.center) {$\mu=m_1 m_2/M^2,\ x(t) = r \cos\Omega t, \ y(t) = r \sin\Omega t $};
-    \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  2 M\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
-    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to \bl{$e$} (Peters \& Mathews).};
+    \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  \mu\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
+    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to eccentricity \bl{$e$}};
     \node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
@@
 \begin{frame}{Compact Binary Inspirals}
-  \vspace{-3mm}
+  \vspace{-4mm}
   Notation:
@@
     \begin{itemize}
-      \item \bl{Quasi-circular} orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ at $f=100\,$Hz.
+      \item \bl{Quasi-circular} orbits: $e \ll 1$ and $\tfrac{|\dot{r}|}{r\Omega} <10^{-3} $ %at $f=100\,$Hz.
       \item \bl{Quadrupolar} GWs only: higher modes suppressed by $\tfrac{m_1-m_2}{M}\tfrac{v^2}{c^2}$
       \item Use Newtonian/post-Newtonian theory ($\le$3.5{\bf PN}).
+      \vspace{0.5mm}
       \item \red{Terminate} inspiral at Schwarzschild \red{ISCO} 
@@
       \begin{align*}
-      f_\text{ISCO} &= \f{c^3}{6^{3/2}\pi G M} \simeq \bl{1571}\,\text{Hz}\, \left(\f{2.8M_\odot}{M}\right)\hspace{2cm}\\ 
+      f_\text{ISCO} &= \f{c^3}{\red{6}^{3/2}\pi G M} \simeq \bl{1571}\,\text{Hz}\, \left(\f{2.8M_\odot}{M}\right)\hspace{2cm}\\ 
       r_\text{ISCO} &\simeq 25\,\text{km}\left(\frac{M}{2.8 M_\odot}\right)
@@
     \begin{itemize}
-      \item Point masses: tidal effects for $f \gtrsim 100\,$Hz
+      \item Point masses: tidal effects beyond $f \gtrsim 100\,$Hz
       \item Set $m_1 =m_2 = 1.4 M_\odot$, constraints: $1.2 M_\odot \lesssim m_\text{NS}\lesssim 1.6M_\odot$.
@@
     \[ 
-    \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }
+    \dot{E}(f) = -\dot{E}_b(f) \Longrightarrow \boxed{\red{\dot{f}} = \f{96}{5}\pi^{8/3} \f{(G M_c)}{c^5}^{5/3}\, \red{f^{11/3}} }\hspace{2cm}
     \]
@@
   \vspace{2mm}
-  Introduce \red{inspiral time}, i.e, time to \bl{coal}escence
+  Introduce \red{inspiral time}, i.e, time to \bl{coal}escence (merger)
   %
@@
       \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
-    \end{tikzpicture}
-    %
+    \end{tikzpicture}\\
+    %
+    %\vspace{2mm}
+    Binary separation \\
+    \vspace{-1mm}
     \[ 
@@
       h_c(t) %&=\f{4}{D}\left(\f{G M_c}{c^2}\right)^{5/3}\, \left(\f{\pi f(t)}{c}\right)^{2/3}\nn\\
-      &\approx 1.9\times \bl{10^{-23}} \left(\f{40\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \\
+      &\approx 7.5\times \bl{10^{-24}} \left(\f{100\,\text{Mpc}}{D}\right)\left(\f{M_c}{1.219 M_\odot}\right)^{5/3}\left(\frac{\red{f}}{10\,\text{Hz}}\right)^{\red{2/3}} \\
       \Phi(t) &=\int_{t_i}^t dt' \omega(t') + \text{PN}
@@
   \begin{align*}
-   h(t) &= F_+(\theta,\phi,\psi) \,h_+(t)+F_\times(\theta,\phi,\psi)\, h_\times(t) , \\
+   \bl{h(t)} &= F_+(\theta,\phi,\psi) \,h_+(t)+F_\times(\theta,\phi,\psi)\, h_\times(t) , \\
     F_+ &=\f{1}{2}\left(1+\cos^2\theta\right)\cos2\phi\cos 2\psi-\cos\theta \sin2\phi \sin2\psi, \\
@@
 \begin{frame}{The era of Einstein Telescope}{BNS detections}
- Same detection criterion:\qquad $\bar{\rho}_\text{ET}(f_0, \bar{f}_\text{ET}) =15$ \todo{ADD LIGO2017}\\
- \red{Two} ET configurations: B (high $f$), C (low $f$)\todo{2020 to plot}
- \begin{tikzpicture}[overlay,remember picture]
-      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
-      %\onslide<2->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
-      %\onslide<3->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
-      %\onslide<4->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted.pdf}};
-\end{tikzpicture}      
-\end{frame}
-
-\begin{frame}{The era of Einstein Telescope}{GRB \red{Forecast} Prospects} 
+ Same detection criterion:\qquad $\bar{\rho}_\text{ET}(f_0, \bar{f}_\text{ET}) =15$\\
+ \red{Two} ET configurations:\qquad \textcolor{brown}{B} (high $f$), \red{C} (low $f$)
+ \begin{tikzpicture}[overlay,remember picture]
+      \onslide<1->\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_strains_redshifted_pres.pdf}};
+      \onslide<2->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_B_SNR_int.pdf}};
+      \onslide<3->\node (img1 )[anchor=center,scale=1,opacity=1] at ([shift={(0cm,-1.5cm)}]current page.center) {\includegraphics[height=6cm]{../Figures/ET_C_SNR_int.pdf}};
+\end{tikzpicture}      
+\end{frame}
+
+\begin{frame}{The era of Einstein Telescope}{GRB \red{Forecast} Prospects } 
   \vspace{-8mm}
@@
   400 & $\approx\,$18.2 & 3.00\,minutes & 75.7 &$ 98.6^{300}_{20} $ & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
-  600 & $\approx\,$?  &?\,seconds & ?& $ 333^{1020}_{69} $ &    $\approx\,$5.7 & 1.03\,hours & 60.?  \\
+  600 & $\approx\,$26.0  &65.8\,seconds & 50.2& $ 333^{1020}_{69} $ &    $\approx\,$5.7 & 1.03\,hours & 60.0  \\
   \hline\hline

### 2018-11-12 Sabanci_talk/Sabanci_talk.tex
v3 finished

@@
   \vspace{-2mm}
-  Three $60^\circ$ V-IFOs, one redundant (null stream), $\sin 60^\circ =\sqrt{3}/2$.
-  \begin{footnotesize}
-  \begin{align*}
-    &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \qquad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\hspace{2cm}\\
+  \bl{Three} $60^\circ$ \red{V}-IFOs, one redundant (null stream), $L=10\,$km
+  \onslide<2->
+  {
+    \begin{footnotesize}
+    \begin{align*}
+      &F^1_+(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_+(\theta,\phi,\psi), \quad F^1_\times(\theta,\phi,\psi)= \f{\sqrt{3}}{2} F_\times(\theta,\phi,\psi),\quad (\sin 60^\circ =\sqrt{3}/2)\\
       & F^2_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi+2\pi/3,\psi)\qquad (\text{rotation by 120}^\circ),\\
       & F^3_{+,\times}(\theta,\phi,\psi) = F^1_{+,\times}(\theta,\phi-2\pi/3,\psi) \qquad(\text{rotation by 240}^\circ),\\
-    &  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
-    \end{align*}
-    \end{footnotesize}
+      %&  |Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 = \sum_{A=1}^3 \left(F^A_+\right)^2\f{1+\cos^2\iota}{2}  + \left(F^A_\times\right)^2 \cos\iota
+      \end{align*}
+      \end{footnotesize}
+    }
    %
@@
     \node[anchor=center,scale=0.5,opacity=1] at ([shift={(5cm,0.4cm)}]current page.center) {Phys. Rev. D 86, 122001 };
-    \end{tikzpicture}
-    %
-   \onslide<2->
+    \end{tikzpicture}\\
+    %
+   \onslide<3->
    {
@@
     \vspace{3mm}
-    Recall, $\tilde{h}(f) \sqrt{f} \sim f^{-7/6} f^{1/2} = \red{f^{-2/3}}$
+    Recall, $\tilde{h}(f) \propto f^{-7/6}$ so $\tilde{h}(f) \sqrt{f} \propto \red{f^{-2/3}}$
     \begin{footnotesize} 
@@
   \begin{align*}
-  \rho_{\text{tot},\llcorner} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
+  \rho_{\text{tot},\red{\llcorner}} &= \left[{\sum_{i=1}^3 \rho^2_i}\right]^{1/2} =\left[ \rho_h^2 + \rho_m^2 + \rho^2_l \right]^{1/2} 
 	  = {\rho_c\left[\tilde{A}_h^2 + \tilde{A}_m^2 + \tilde{A}_l^2 \right]^{1/2}}\\
@@
     \[
-    \rho^2_{\text{tot},\bigtriangleup} = \sum_{A=1}^3 \left(\rho^A\right)^2  =  A^2 \rho_c^2 \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup^2 %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
+    \rho_{\text{tot},\bigtriangleup} = \left[\sum_{A=1}^3 \left(\rho^A\right)^2\right]^{1/2}  =  A \rho_c \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
     \]
@@
     \begin{align*}
-      &\tau_\text{insp}^{0\text{PN}} \ \ \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \ \ \simeq 2680 \hspace{2cm} (M=2.74 M_\odot) \\
-      &\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \hspace{2cm} (f_\text{ISCO}\simeq 1605\,\text{Hz}) 
+      &\tau_\text{insp}^{0\text{PN}}  \simeq 56.06\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2687 \hspace{2cm} (M=2.73 M_\odot) \\
+      &\tau_\text{insp}^{2\text{PN}} \simeq 57.06\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{2\text{PN}} \simeq 2735 \hspace{2cm} (f_\text{ISCO}\simeq 1611\,\text{Hz}) 
     \end{align*}
@@
     {\begin{footnotesize} 
-      $\bar\rho_{i} = \left\{29.2, \ 14.6, \ 6.11 \right\}$    
+      $\bar\rho_{i} = \left\{28.7, \ 14.3, \ 6.00 \right\}$    
     \end{footnotesize}}; 
@@
     \end{footnotesize}};
-    \onslide<3->\node (t4 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.7cm)}]current page.center) 
+    \onslide<3->\node (t5 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-1.7cm)}]current page.center) 
     {\begin{footnotesize} 
-      $\rho_\text{tot} = 32.6 $    
+      $\rho_\text{tot} = 32.0 $    
+    \end{footnotesize}};
+        \onslide<4->\node (t6 )[anchor=center,scale=1,opacity=1] at ([shift={(4cm,-3.1cm)}]current page.center) 
+    {\begin{footnotesize} 
+      $\rho_\text{tot} = 32.4 $    
     \end{footnotesize}};
@@
  Same detection criterion:\qquad $\bar{\rho}_\text{ET}(f_0, \bar{f}_\text{ET}) =15$\\
+ \vspace{1mm}
  \red{Two} ET configurations:\qquad \textcolor{brown}{B} (high $f$), \red{C} (low $f$)
@@
   \hline\hline
-  $D\,$(Mpc) & \multicolumn{3}{c}{ET-B} & $R_\text{av}{}^\text{max}_\text{min} $ & \multicolumn{3}{c}{ET-C}\T\B\\
+  $D\,$(Mpc) & $R_\text{av}{}^\text{max}_\text{min} $ &  \multicolumn{3}{c}{ET-B}  & \multicolumn{3}{c}{ET-C}\T\B\\
   \hline
-  {}& $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{3mm} $T_\text{AW}$ \ \hspace{3mm} & $\bar{\rho}_{F}$ & {}  & $\bar{f}_\text{ET}\,$(Hz) & \ \hspace{3mm} $T_\text{AW}\hspace{3mm}$& $\bar{\rho}_{F}$\T\B\\
+  {}& {} & $\bar{f}_\text{ET}\,$(Hz) & \hspace{2mm} $T_\text{AW}$ \hspace{2mm} & $\bar{\rho}_{F}$  & $\bar{f}_\text{ET}\,$(Hz) & \hspace{2mm} $T_\text{AW}\hspace{2mm}$& $\bar{\rho}_{F}$\T\B\\
   %midrule
-  100 & $\approx\,$6.72 &  47.0\,minutes & 306 & $ 1.54^{4.7}_{0.3}$ & $\approx\,$3.27 & 5.34\,hours\ & 365\T\\
-  200 & $\approx\,$11.2 & 11.6\,minutes & 152 &  $ 12.3^{38}_{2.6} $ & $\approx\,$4.10 & 2.87\,hours\ & 182 \\
-  400 & $\approx\,$18.2 & 3.00\,minutes & 75.7 &$ 98.6^{300}_{20} $ & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
-  600 & $\approx\,$26.0  &65.8\,seconds & 50.2& $ 333^{1020}_{69} $ &    $\approx\,$5.7 & 1.03\,hours & 60.0  \\
+  100 & $ 1.54^{4.7}_{0.3}$ & $\approx\,$6.72 &  47.0\,minutes & 306  & $\approx\,$3.27 & 5.34\,hours\ & 365\T\\
+  200 &  $ 12.3^{38}_{2.6} $ & $\approx\,$11.2 & 11.6\,minutes & 152  & $\approx\,$4.10 & 2.87\,hours\ & 182 \\
+  400 &$ 98.6^{300}_{20} $ & $\approx\,$18.2 & 3.00\,minutes & 75.7  & $\approx\,$5.06 & 1.51\,hours\ & 90.5\\
+  600 & $ 333^{1020}_{69} $ & $\approx\,$26.0  &65.8\,seconds & 50.2 &    $\approx\,$5.7 & 1.03\,hours & 60.0  \\
   \hline\hline
@@
   \begin{tikzpicture}[overlay,remember picture]
-      \onslide<3>\node[draw, blue,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (-2.3,5.3){};
+      \onslide<3>\node[draw, blue,thick,minimum width=1.4cm,minimum height=1.6cm] (b) at (-2.6,5.3){};
       \onslide<4->\node[draw, red,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (3.6,5.3){};
@@
   \item 0.5\% to within 10\,deg$^2$ 
-  \onslide<4->\item[]$\Longrightarrow \red{\ord(5)}$ sources within 400\,Mpc
+  \onslide<4->\item[]$\Longrightarrow \red{5}$ to \red{10} sources within 400\,Mpc
   \end{itemize}
@@
   Necessary, but insufficient \bl{condition}:
-  $   \f{M_\text{BH}}{M_\text{NS}} \gtrsim \left(\f{r}{R_\text{NS}}\right)^3  $
+  $   \f{M_\text{BH}}{m_\text{NS}} \gtrsim \left(\f{r}{R_\text{NS}}\right)^3  $
   %
@@
   \item High black hole spin: $\tilde{r}_\text{ISCO}\to 1$ from 6.
-  \item Larger neutron star radii, $r_\text{NS}\sim15\,$km
+  \item Larger neutron star radii, $R_\text{NS}\sim15\,$km
   \end{itemize}
   \onslide<3->
-  $\red{5} M_\odot -1.4 M_\odot$ BH-NS inspirals are \red{faster} because $\tau_\text{insp} \propto M^{-5/3}$
+  $\red{5} M_\odot -1.4 M_\odot$ BH-NS inspirals are \red{faster} because $\tau_\text{insp} \propto M^{-2/3}$
   %
@@
   $T_\text{AW} \gtrsim 1\,$hour $\Longrightarrow D \lesssim 200\,$Mpc \\
-  O1 rate $R < 3600 \text{Gpc}^{-3}\text{yr}^{-1} \Longrightarrow 30\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$ \\
+  O1 rate $ < 3600 \text{Gpc}^{-3}\text{yr}^{-1} \Longrightarrow 30\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$ \\
   BH population studies: $\Longrightarrow \text{ \red{Forecast} } \red{3}\text{yr}^{-1}$ within $(200\,\text{Mpc})^3$
@@
 \end{itemize}
-\begin{align*}
-      x &=1
-	  %
-	  %\\
-  %
-      \end{align*}
+%\begin{align*}
+%\end{align*}
 \end{frame}
@@
 
+\end{document}
+
 \begin{frame}{Supplemet 5: Mass-inclination degeneracy}
@@
 \end{frame}
-
-\end{document}
-
-\begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
- \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\% (BICEP 2).\\
- \uncover<2->{Gravitational-wave luminosity: \uncover<3->{\alert{quadrupole} radiation}  (leading-order)}
- \uncover<3->{\begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\\vspace{2mm}}
- \uncover<4->{\begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}}
- \uncover<5->{{\bf Binary systems:} 2 points masses in circular orbit. }
- \end{frame}
-
-  One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.\\
- Underground,cryogenic, \blue{xylophone} (high, low-frequency modes)\\
-
- Cosmological range $\Rightarrow$ sky-averaged,\red{red}-shifted strain and SNR
- \begin{footnotesize}
- \begin{align*} 
-  \tilde{H}_\text{ET}(f) &= \f{3}{5}A h_0 \red{(1+z)^{-1}} f^{-7/6}\\
-  \bar\rho_{\text{ET}}(f_0,f)&\equiv \f{6}{5}A h_0\, \red{(1+z)^{-1/6}}\left[\int_{f_0}^{f} d f'\, \f{f'^{-7/3}}{S^\text{ET}_n(f')}\right]^{1/2}
- \end{align*} 
- \end{footnotesize}

### 2018-11-13 Sabanci_talk/Sabanci_talk.tex
Finalish version

@@
 \newcommand{\bl}[1]{\textcolor{blue}{#1}} 
+\newcommand{\w}[1]{\textcolor{white}{#1}}
 
@@
 \begin{frame}{Gravitational waves: Einstein 1916}
+\vspace{-5mm}
 \begin{center}
-\begin{tikzpicture}
-            \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/Einstein1916.png}};
-            %\draw<1>[red,ultra thick,rounded corners] (1.6,1) rectangle (\textheight-1cm,5);
-           \uncover<3->{\draw<3->[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
+  \begin{tikzpicture}%[overlay,remember picture]
+	      \onslide<1-4>\node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/Einstein1916.png}};
+	      \onslide<2-4>{\draw[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
   \end{tikzpicture}
   \\
-         \uncover<2->{Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
+  \vspace{5mm}
+  \onslide<2->{Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
 \end{center}
-          \begin{itemize}
- \item  \uncover<3->{Spacetime metric $g_{\mu\nu} = \eta_{\mu\nu} + h_{\mu\nu}$, \quad with $| h_{\mu\nu} | \ll 1$.}
- \item  \uncover<4->{Insert into $G_{\mu\nu} = 0$. Keep only $\mathcal{O}(h)$. Pick a gauge.} %(e.g. Lorenz).}
-  \uncover<5->{\[ \Rightarrow\quad \boxed{\Box \bar{h}_{\mu\nu}= 0}, \quad \text{wave equation!} \]}
-  \item \uncover<6->{\alert{Plane-waves:} $ \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{i k_\mu x^\mu}\right] =\Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/c )}\right]$.}
- \end{itemize}
-\end{frame}
-
-\begin{frame}{Gravitational waves: d.o.f.'s}
-$A_{\mu\nu} $ is the polarization tensor.
-\begin{itemize}
- \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
- \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
- \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
- \end{itemize}
-\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
-\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<9->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
+    %      
+  \onslide<3->
+  \[\text{Wave equation: } \boxed{\Box \bar{h}_{\mu\nu}= 0} \ \ \Longrightarrow
+  \alert{\text{Plane-waves: }}  \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/\red{c} )}\right]
+  \]
+  %
+ \onslide<4-> $A_{\mu\nu} $: polarization tensor, \\
+ $\Longrightarrow$ \emph{only} \red{2} polarizations (\bl{transverse}):
+  $\begin{array}{l} \w{A_{xx}=-A_{yy} = h_+}  \\ \w{A_{xy}=\ \ A_{yx} = h_\times} \\ \end{array}$
+ \end{frame}
+
+\begin{frame}{Gravitational waves: Einstein 1916}
+\vspace{-5mm}
+\begin{center}
+  \begin{tikzpicture}%[overlay,remember picture]
+	      \onslide<1>\node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[height=3.5cm]{figs/white_box.png}};
+	      %\onslide<2-4>{\draw[red,thick] (1.7,0.04) rectangle (3.1,0.27);}
+  \end{tikzpicture}
   \\
-
-\begin{tikzpicture}[overlay,remember picture]
-  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\includegraphics[height=2.6cm]{figs/white_box.png}};
-  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\includegraphics[height=2.6cm]{figs/white_box.png}};
-\end{tikzpicture}
-\end{frame}
-
-\begin{frame}{Gravitational waves: d.o.f.'s}
-$A_{\mu\nu} $ is the polarization tensor.
-\begin{itemize}
-  {\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
-  {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ {$\Rightarrow10-4 = \, 6$ d.o.f.}}
-  {\item Residual gauge freedom \hspace{2.25cm} {$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
- \end{itemize}
-{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
-{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
-\\
-%
-\begin{tikzpicture}[overlay,remember picture]
-  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
-  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
+  \vspace{5mm}
+  {Perturbations of spacetime with speed $=c$, sourced by accelerating masses.}
+\end{center}
+  %        
+  %
+  \[\text{Wave equation: } \boxed{\Box \bar{h}_{\mu\nu}= 0} \ \ \Longrightarrow
+  \alert{\text{Plane-waves: }}  \bar{h}_{\mu\nu} = \Re\left[A_{\mu\nu}\, \text{e}^{-i\omega (t-z/\red{c} )}\right]
+  \]
+  %
+ $A_{\mu\nu} $: polarization tensor, \\
+ $\Longrightarrow$ \emph{only} \red{2} polarizations (\bl{transverse}):
+  $\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$
+ \begin{tikzpicture}[overlay,remember picture]
+	      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,1.5cm)}]current page.center){\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
+	      \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,1.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
 \end{tikzpicture}
@@
   \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
-  \textcolor{white}{{\bf Binary systems:} 2 points masses in circular orbit.}
+  \textcolor{white}{{\bf Binary systems:} 2 points masses in a circular orbit $M=m_1+m_2$}
   \begin{tikzpicture}[overlay,remember picture]
@@
   \begin{small}$ \quad \bar{Q}_{ij} = Q_{ij}-\frac{1}{3}\delta_{ij}Q^k_k, \quad Q^{ij} = \int \rho(t,{\mathbf x})x^i x^j d^3 x $ \end{small} \end{center}
-  {\bf Binary systems:} 2 points masses in circular orbit.
+  {\bf Binary systems:} 2 points masses in a circular orbit $M=m_1+m_2$
   \begin{tikzpicture}[overlay,remember picture]
@@
   {
-    {\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$\\
+    {\bf Key idea:} \red{energy balance} between $\dot{E}$ and $\dot{E}_b$ (\bl{binding energy})\\
     %of gravitational binding energy
@@
   \vspace{2mm}
+  \onslide<2->
   Introduce \red{inspiral time}, i.e, time to \bl{coal}escence (merger)
@@
   \\
-  \onslide<2->
+  \onslide<3->
   {
@@
   %
-  \onslide<3->
-  {
-    \begin{tikzpicture}[overlay,remember picture]
-      \node[draw, red,thick,minimum width=9.2cm,minimum height=1.3cm] (b) at (4.2,3.35){};
-      \node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.1,1){};
-      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.2cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
+  \onslide<4->
+      \begin{tikzpicture}[overlay,remember picture]
+      \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.9cm,-3.25cm)}]current page.center) {\includegraphics[height=3.5cm]{figs/R_of_Tau.pdf}};
+      \onslide<5->\node[draw, red,thick,minimum width=9.5cm,minimum height=1.3cm] (b) at (4.4,3.35){};
+      \onslide<5->\node[draw, red,thick,minimum width=9cm,minimum height=1.3cm] (b) at (4.1,1){};      
     \end{tikzpicture}\\
@@
     \]
-  }
+  %
 \end{frame}
@@
 
- \begin{frame}{GW Detectors: \red{Interferometers}}
+ \begin{frame}{GW Detectors: \red{Interferometers}}{Geodesic deviation}
     Two geodesics separated by $\xi^\mu$:
@@
     \onslide<2->
-    {
     GW along $\mathbf{z}$: 
@@
       \]
-    }
       \onslide<3->
-    {
       Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
+      \begin{tikzpicture}[overlay,remember picture]
+	%\node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
+	\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\includegraphics[height=2.39cm]{figs/white_box.png}};
+      \end{tikzpicture}
+          \begin{small}
+      \begin{align*}
+	\w{s_{12} }& \w{=\int_1^2 \tfrac{ds}{dx}dx = (x_2-x_1) \left[ 1 + h_+ \cos(\omega t)\right]^{1/2}\hspace{4cm} }\\
+	   &\w{ \approx L \left[ 1+\tfrac{1}{2} h_+ \cos\omega t \right] }\\
+      \w{s_{13}} &\w{\approx L \left[ 1-\tfrac{1}{2} h_+ \cos\omega t \right]}
+      \end{align*}
+      \end{small}
+    %
+    %
+ \end{frame}
+
+ \begin{frame}{GW Detectors: \red{Interferometers}}{Geodesic deviation}
+    Two geodesics separated by $\xi^\mu$:
+    %\[
+    % \frac{D^2 \xi^\alpha}{D\tau^2} = -R^\alpha_{\beta \gamma\delta}\, \xi^\gamma u^\beta u^\delta 
+    %\]
+    $ \tfrac{d^2 \xi^i}{d\tau^2} = -R^i_{0j0} \xi^j\left(\tfrac{dx^0}{d\tau}\right)^2$ \hfill (detector frame)\\
+    %\hspace{4cm} $\Longrightarrow \ddot{\xi^i} = -c^2 R^i_{0j0} \xi^j $ \hfill (detector time)\ \\
+    \vspace{-3mm}
+    \[
+    \hspace{4.5cm} \boxed{\ddot{\xi^i} = \frac{1}{2} \ddot{h}_{ij}^\text{TT} \xi^j} \hspace{2.5cm} \text{(detector time)}
+    \]
+    %
+    %
+    %
+    GW along $\mathbf{z}$: 
+      \[
+      h_{ij}^\text{TT} = \left(\begin{array}{cc}
+				h_+ & h_\times \\
+				h_\times & - h_+
+				\end{array}\right) \cos\left(\omega\left( t-\tfrac{z}{c}\right)\right)
+      \]
+      %
+      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
+      \begin{tikzpicture}[overlay,remember picture]
+	%\node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
+	\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
+      \end{tikzpicture}
+    \onslide<2->      
       \begin{small}
@@
       \end{small}
-    }
-    %
-    \onslide<4->
-    {
-      \begin{tikzpicture}[overlay,remember picture]
-      \node[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-3.4cm)}]current page.center){\todo{Make sure the vid here works}} ;
-      %\node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(3.8cm,-2.8cm)}]current page.center) {\animategraphics[loop,controls,height=2.39cm]{12}{LIGO_int-}{0}{102}};
-      \end{tikzpicture}
-    }
+    %
+    %
  \end{frame}
@@
   \rho_{\text{tot},\bigtriangleup} %&= \left[ \int_0^\infty d\ln f\, \f{|{2\tilde{H}_\bigtriangleup(f)\sqrt{f}}|^2}{S_n(f)}\right]^{1/2} 
-  &=\f{6}{5}A\, h_0 \left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
+  &=\f{6}{5}A\, h_0 \rho_c \\%\left[\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)}\right]^{1/2} \\
   \end{align*}
@@
   \begin{tikzpicture}[overlay,remember picture]
-  \node[draw, red,thick,minimum width=5.5cm,minimum height=1.25cm] (b) at (-3.2,1.05){};
+  \node[draw, red,thick,minimum width=3.cm,minimum height=0.9cm] (b) at (-3.2,0.9){};
   \end{tikzpicture}
@@
   \red{BIG question:} how long before the GRB can we {\bf detect} BNS inspirals?\\
-  Detection criterion: SNR = \red{15}\\
+  Detection criterion: SNR = \red{15}. Set $m_1=m_2=1.4 M_\odot$\\
   Three identical L-IFOs with $Q_{i=h,m,l}$
@@
     \item[] One detector, \red{three V}-IFOs, $60^\circ$ 10\,km arms.
-    \item[] Underground,cryogenic, \bl{xylophone} (high, low-frequency modes)
+    \item[] Underground, cryogenic, \bl{xylophone} (high, low-frequency modes)
     \uncover<2->{
@@
 \end{frame}
+
+\begin{frame}{Gravitational waves: d.o.f.'s}
+$A_{\mu\nu} $ is the polarization tensor.
+\begin{itemize}
+ \uncover<2->{\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric \uncover<3->{$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
+ \uncover<4->{\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ \uncover<5->{$\Rightarrow10-4 = \, 6$ d.o.f.}}
+ \uncover<6->{\item Residual gauge freedom \hspace{2.25cm} \uncover<7->{$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
+ \end{itemize}
+\uncover<7->{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
+\uncover<8->{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): \uncover<9->{$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
+\\
+
+\begin{tikzpicture}[overlay,remember picture]
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\includegraphics[height=2.6cm]{figs/white_box.png}};
+  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\includegraphics[height=2.6cm]{figs/white_box.png}};
+\end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Gravitational waves: d.o.f.'s}
+$A_{\mu\nu} $ is the polarization tensor.
+\begin{itemize}
+  {\item $\{ \bar{h}_{\mu\nu}, A_{\mu\nu} \}$: $4\times4$, symmetric {$\hspace{1.5cm}\Rightarrow \f{4\times 5}{2}\ \ \ = 10$ d.o.f.}}
+  {\item Gauge condition: $\nabla_\mu \bar{h}^{\mu\nu} =  A_{\mu\nu} k^\nu= 0$ {$\Rightarrow10-4 = \, 6$ d.o.f.}}
+  {\item Residual gauge freedom \hspace{2.25cm} {$\Rightarrow 6-4 \ \ = \alert{2}$ \alert{d.o.f.}}}
+ \end{itemize}
+{\quad \ Consistent with $\pm 2$ helicities of a \bl{massless} spin 2 boson.\\}
+{$\Rightarrow$ \alert{2} POLARIZATIONS (\alert{transverse}): {$\begin{array}{l}A_{xx}=-A_{yy} = \red{h_+}  \\ A_{xy}=\ \ A_{yx} = \red{h_\times}  \\ \end{array}$}}
+\\
+%
+\begin{tikzpicture}[overlay,remember picture]
+  \node (img0 )[anchor=center,scale=1,opacity=1] at ([shift={(-3.5cm,-2.5cm)}]current page.center){\animategraphics[loop,controls,height=2.6cm]{12}{GWs_plus-}{0}{20}};
+  \node (img1 )[anchor=center,scale=1.,opacity=1] at ([shift={(3.5cm,-2.5cm)}]current page.center) {\animategraphics[loop,controls,height=2.6cm]{12}{GWs_cross-}{0}{20}};
+\end{tikzpicture}
+\end{frame}

### 2018-11-13 Sabanci_talk/Sabanci_talk.tex
FINAL version

@@
  \begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
-  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
+  \alert{Inspirals}, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
   Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
-  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
+  \begin{center} $ \boxed{\dot{E} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
   \vspace{2mm}
@@
 \begin{frame}{Making gravitational waves}{non-spherical, accelerated motion}
-  \alert{Inspirals}, GRBs, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
+  \alert{Inspirals}, bumps on neutron stars, supernovae, the Big Bang. \\%  (BICEP 2).\\
   Gravitational-wave emission: \alert{quadrupole} radiation (leading-order)
-  \begin{center} $ \boxed{\dot{E}=L_\text{GW} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
+  \begin{center} $ \boxed{\dot{E} = \f{G}{c^5} \langle (\partial_t^3 \bar{Q}_{ij})^2 \rangle}$\\
   \vspace{2mm}
@@
     \onslide<3->\node (t2 )[anchor=center,scale=1,opacity=1] at ([shift={(2.25cm,-2.2cm)}]current page.center) {$ Q^{ij} =  \mu\, x^i x^j, \qquad \boxed{\dot{E} = \f{32}{5}\f{G\mu^2}{c^5}r^4 \Omega^6}$};
-    \onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to eccentricity \bl{$e$}};
-    \node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
+    %\onslide<4->\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2.5cm,-3.2cm)}]current page.center) {Enhancement due to eccentricity \bl{$e$}};
+    %\node (t3 )[anchor=center,scale=1,opacity=1] at ([shift={(2cm,-4cm)}]current page.center) {$ \bl{\f{\left(1 + \f{73}{24}e^2+ \f{37}{96} e^4 \right)}{(1-e^2)^{7/2}}}$};
   \end{tikzpicture}
@@
 \begin{frame}{Gravitational waves from BNS}
-  TT gauge, multipole, slow-velocity expansions give 
+  %TT gauge, multipole, slow-velocity expansions give 
+  %\begin{small}
+   % \[
+    %h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}\hspace{6cm}
+    %\]
+    %
+    %\vspace{-5mm}
+    Recall $h_{\mu \nu} \approx A_{\mu\nu}\cos\left[\omega (t-z/c)\right]$ \\
+    %  
     \begin{small}
-    \[
-    h_{ij}^\text{TT} = \tfrac{2}{D}\tfrac{G}{c^4} \ddot{Q}_{ij}^\text{TT}\hspace{6cm}
-    \]
-    %
-    \vspace{-5mm}
     \uncover<2->
@@
       \begin{align*}
+      A_{xx}&=h_+, A_{xy} = h_\times, \\
       h_+(t) &= h_c(t)\, \left(\f{1+\cos^2\iota}{2}\right)\, \cos[\Phi(t)],\hspace{5cm}\\
@@
       \onslide<3->
-      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
+      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(0,L)_3$
       \begin{tikzpicture}[overlay,remember picture]
@@
       %
-      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(L,L)_3$
+      Consider mirrors at $(0,0)_1, (L,0)_2$ and $(0,L)_3$
       \begin{tikzpicture}[overlay,remember picture]
@@
 
-\begin{frame}{Detection criteria}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
+\begin{frame}{Detection criterion}{Optimal Signal-to-Noise Ratio ({\bf SNR})}
   \vspace{-5mm}
@@
   %
-  Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
-  \begin{footnotesize} 
-  \[
-  0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
-  \]
-  \end{footnotesize}
+  %Sources will have random $\{\theta,\phi,\psi,\iota\}$ \\
+  %\begin{footnotesize} 
+  %\[
+  %0 \le Q(\theta,\phi,\psi,\iota) \le \underbrace{Q_\text{max}(\theta,\phi,\psi,\iota)}_{\theta=\tfrac{\pi}{2},\psi=0,\iota=0}
+  %\]
+  %\end{footnotesize}
   % 
@@
 \begin{frame}{L-IFO vs. $\bigtriangleup$-IFO Networks}
-\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo
+\red{Three L}-IFOs, e.g., LIGO L1, H1 + Virgo; or ($h$)igh, ($m$)edium, ($l$)ow
 %
@@
     \[
-    \rho_{\text{tot},\bigtriangleup} = \left[\sum_{A=1}^3 \left(\rho^A\right)^2\right]^{1/2}  =  A \rho_c \,|Q(\theta,\phi,\psi,\iota)|_\bigtriangleup %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
+    \rho_{\text{tot},\bigtriangleup} = \left[\sum_{A=1}^3 \left(\rho^A\right)^2\right]^{1/2}  =  A \rho_c \,\langle|Q(\theta,\phi,\psi,\iota)|^2\rangle^{1/2}_\bigtriangleup %\int_0^{f_\text{ISCO}} d f\, \f{f^{-7/3}}{S_n(f)} \,
     \]
@@
   \onslide<3->
-  Use \bl{RMS-averaged} $|Q|^2$
+  \bl{RMS-averaged} %$|Q|^2$
   \begin{footnotesize}
@@
   {
-    Assuming low spin priors
+    System parameters
     \begin{align*}
@@
   \red{BIG question:} how long before the GRB can we {\bf detect} BNS inspirals?\\
-  Detection criterion: SNR = \red{15}. Set $m_1=m_2=1.4 M_\odot$\\
+  Detection criterion: SNR = \red{15} \\ %Set $m_1=m_2=1.4 M_\odot$\\
   Three identical L-IFOs with $Q_{i=h,m,l}$
@@
   \onslide<2->
-  {
-    Total accumulated SNR over the inspiral
-    \begin{footnotesize}
-      \[
-      \bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2}
-      \]
+  \begin{footnotesize}
          \begin{table}[h]
@@
   \end{footnotesize}
-  }
   %
@@
   \begin{tikzpicture}[overlay,remember picture]
-  \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.7,5.3){};
+    \onslide<1->\node[draw, red,thick,minimum width=2.8cm,minimum height=1.0cm] (b) at (-0.7,4.){};
     \onslide<3->\node[draw, red,thick,minimum width=1.1cm,minimum height=1.2cm] (b) at (1.6,1.35){};
   \end{tikzpicture}
-
+  \\
+  \vspace{2mm}
+  \onslide<4->
+      Total accumulated SNR over the inspiral
+    \begin{footnotesize}
+      \[
+      \bar{\rho}_\text{F}\equiv\sqrt{\left[{\rho}_h(f_0^h,{f}_\text{ISCO})\right]^2+\left[{\rho}_m(f_0^m,{f}_\text{ISCO})\right]^2+\left[{\rho}_l(f_0^l,{f}_\text{ISCO})\right]^2}
+      \]
+    \end{footnotesize}
 \end{frame}
@@
   \begin{tikzpicture}[overlay,remember picture]
-      \onslide<3>\node[draw, blue,thick,minimum width=1.4cm,minimum height=1.6cm] (b) at (-2.6,5.3){};
+      \onslide<3>\node[draw, blue,thick,minimum width=2.cm,minimum height=1.6cm] (b) at (-0.9,5.3){};
       \onslide<4->\node[draw, red,thick,minimum width=1.8cm,minimum height=1.6cm] (b) at (3.6,5.3){};
@@
   \begin{itemize}
-  \item 20\% of the sources to within 100\,deg$^2$
+  %\item 20\% of the sources to within 100\,deg$^2$
   \item 2\% to within 20\,deg$^2$
@@
   \onslide<5->10\,deg$^2$: LSST's field of view\\
+  \vspace{2mm}
   \onslide<6-> Numbers improve with \bl{Cosmic Explorer} ($f\gtrsim \red{5}\,$Hz)
@@
  \item Einstein-C will \red{forecast $\ord(100)$ BNS} with $T_\text{AW}>1\,$hour.
+ \item 5 to 10 BNS inspirals will be \red{localized} to $\red{10\,\text{deg}^2}$.
  \item Additionally forecast $< \ord(10)$ tidal disruption events.
- \item 5 to 10 BNS inspirals will be \red{localized} to $\red{10\,\text{deg}^2}$.
  \end{itemize}

### 2018-11-16 Paper/Manuscript.tex
What?
Slides, paper minor
update

@@
 \newcommand{\bi}{\begin{itemize}}
+\newcommand{\todo}[1]{{\textcolor{red}{\texttt{todo: #1}} }}
 \newcommand{\ei}{\end{itemize}}
@@
 By 2025, LIGO-India detector will join the global interferometer network hence improving both the overall sensitivity and the sky-localization capabilities \cite{Aasi:2013wya}.
-Around this time, the construction of the first third-generation ground-based interferometer, Einstein Telescope, will begin in Europe \cite{ET_doc}. 
-Meanwhile, the US is currently considering a mid-2020s update to LIGO called Voyager \cite{LIGO_Voy} and the construction of a more ambitious 40\,km long interferometer dubbed Cosmic Explorer \cite{CE}.
-All of these near-future additions to the GW-detector network beg a simple question: can we detect the inspiral of a binary neutron star system
-early enough to witness a gamma-ray burst as it happens? In other words, can we forecast GRBs using GW detections?
-
+Around this time, the construction of the first third-generation (3G) ground-based interferometer, Einstein Telescope, should begin in Europe \cite{ET_doc}\footnote{The decision for the funding of Einstein Telescope
+is expected to be announced in 2019-2020 with the final technical design report to be submitted in 2023-24, and the commissioning to begin in 2030-31 followed by full operations in 2032-33.}.
+Meanwhile, the US is currently considering a mid-2020s update to LIGO called Voyager \cite{LIGO_Voy} and the construction of an ambitious 40-km long 3G interferometer dubbed Cosmic Explorer \cite{CE}.
+
+The science goals of the 3G detectors is very exciting. For example,
+Einstein Telescope will be able to (i) distinguish between different neutron star equations of state, (ii) conduct high-precision measurements 
+of source parameters to test alternate theories of gravity,
+%(projected SNR of GW150914 at ET is 800, at CE 2400 vs. ALV 25)
+(iii) detect binary black hole populations out to redhifts of $\sim 15$
+hence  (a) measure the Hubble parameter, dark matter and dark energy densities, as well as the dark energy equation-of-state parameter;
+(b) study the cosmological evolution of the stellar mass black holes (see Sec.~2 of Ref.~\cite{ET_doc} for an excellent summary and further details).
+
+The prospect of having extremely sensitive 3G GW detectors begs a simple question: can we detect the inspirals of binary neutron star systems
+early enough to witness gamma-ray bursts as they happen? In other words, can we forecast GRBs using GW detections?
 The short answer is ``yes''.
@@
 \be
-\mathcal{N}_\text{cyc}(f)\approx 1.605\times 10^4 \left(\f{10\,\text{Hz}}{f} \right)^{5/3}\,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\label{eq:Ncyc3}\, .
+\mathcal{N}_\text{cyc}(f)\approx 1.605\times 10^4 \,\left(\f{1.219 M_\odot}{M_c}\right)^{5/3}\, \left(\f{10\,\text{Hz}}{f} \right)^{5/3}\label{eq:Ncyc3}\, .
 \ee
@@
 a \emph{model network} of three IFOs ($N=3$), where one is near-optimally oriented/positioned with $|Q|=2\sigma=4/5$.
+\todo{ADD some discussion here as to why we don't use specific LV Q's}
 The second IFO operates at the RMS average; thus it has $|Q|=2/5$. %compared with the optimal $|Q| =1$ case.
@@
 for which we provide the details in Sec.~\ref{Sec:ETB} (additional details can be found in, e.g., Ref.~\cite{Phinney:2001di}). 
-
+%
+\item {\it Changing the detection threshold from $\bar{\rho}_\text{tot}=15$.}\\
+\todo{ADD SNR=12 and 20 computations for ET-C}
+$\bar\rho$ is defined in Sec. V
+%
 %
@@
 %
-
+%
 \section{GW170817 as a test of our model for the Advanced LIGO-Virgo network}\label{sec:GW170817}
@@
 We use a $\verb|Mathematica|$ based code developed at UCD to do the same for GW170817.
-
-Fig.~\ref{fig:figGW170817} shows our network. The red curve is L1's ASD (sensitivity) during GW170817. We assume our three IFOs have identical sensitivities,
-but because their orientations and response functions differ, their sensitivity to a localized source is reduced. We represent this reduction by lowering the
-amplitude of the GW strain by appropriate quality factors ($|Q_i|$) explained in Sec.~\ref{sec:BNS_inspiral} and shown in Table~\ref{table:network_params}.
-The amplitude-adjusted strains $ \tilde{H}_i(f)$ are represented by the dashed ($i=h$), solid ($i=m$), and dotted ($i=l$) lines in the figure where we actually plot
-$2\sqrt{f} \tilde{H}_i(f)$ as is standard. 
-Using Eq.~(\ref{eq:SNR_i_with_fi}) we can immediately compute the SNRs accumulated by our network
-%%
-%
-\be
-\bar\rho_h = 29.2,\quad \bar\rho_m = 14.6,\quad \bar\rho_l = 6.11 \label{eq:GW170817_SNRs}.
-\ee
-%
-%%
-These are comparable to actual SNRs of L1, H1, and V1 for GW170817, which are, 26.4, 18.8, and 2.0, respectively\footnote{At the time of GW170817, Virgo's sensitivity had not reached the level of LIGO's.
-Hence it accumulated a much smaller SNR for GW170817.
-By 2020, Virgo should be operating at nearly the same sensitivity of LIGO.}.
-%To accommodate more realistic orientations, we show two shaded regions in Fig.~\ref{fig:figGW170817}. The inspirals in the lighter region yield SNR$\ge 22.34$ as
-%they sweep from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz whereas inspirals in the darker region accumulate $ \bar\rho_l \le \text{SNR} \le 22.34$.
-The shaded region in Fig.~\ref{fig:figGW170817} covers strains between $\tilde{H}_l(f)$ and $\tilde{H}_h(f)$. %which we expect to represent mo
-Given a randomly positioned/oriented BNS inspiral at 40 Mpc, we would in general expect a randomly oriented IFO's response to lie in this shaded region.
-%Given a network of three equally sensitive, randomly oriented IFOs we expect that a single 40-Mpc BNS inspiral would produce three distinct detector response strains that fall within this shaded region.
-%
 %
@@
 \label{fig:figGW170817}
-\end{figure}
+\end{figure}\\
+%
+%
+Fig.~\ref{fig:figGW170817} shows our network. The red curve is L1's ASD (sensitivity) during GW170817. We assume our three IFOs have identical sensitivities,
+but because their orientations and response functions differ, their sensitivity to a localized source is reduced. We represent this reduction by lowering the
+amplitude of the GW strain by appropriate quality factors ($|Q_i|$) explained in Sec.~\ref{sec:BNS_inspiral} and shown in Table~\ref{table:network_params}.
+The amplitude-adjusted strains $ \tilde{H}_i(f)$ are represented by the dashed ($i=h$), solid ($i=m$), and dotted ($i=l$) lines in the figure where we actually plot
+$2\sqrt{f} \tilde{H}_i(f)$ as is standard. 
+Using Eq.~(\ref{eq:SNR_i_with_fi}) we can immediately compute the SNRs accumulated by our network
+%%
+%
+\be
+\bar\rho_h = 29.2,\quad \bar\rho_m = 14.6,\quad \bar\rho_l = 6.11 \label{eq:GW170817_SNRs}.
+\ee
+%
+%%
+These are comparable to actual SNRs of L1, H1, and V1 for GW170817, which are, 26.4, 18.8, and 2.0, respectively\footnote{At the time of GW170817, Virgo's sensitivity had not reached the level of LIGO's.
+Hence it accumulated a much smaller SNR for GW170817.
+By 2020, Virgo should be operating at nearly the same sensitivity of LIGO.}.
+%To accommodate more realistic orientations, we show two shaded regions in Fig.~\ref{fig:figGW170817}. The inspirals in the lighter region yield SNR$\ge 22.34$ as
+%they sweep from 10\,Hz to $f_\text{ISCO} \simeq1605\,$Hz whereas inspirals in the darker region accumulate $ \bar\rho_l \le \text{SNR} \le 22.34$.
+The shaded region in Fig.~\ref{fig:figGW170817} covers strains between $\tilde{H}_l(f)$ and $\tilde{H}_h(f)$. %which we expect to represent mo
+Given a randomly positioned/oriented BNS inspiral at 40 Mpc, we would in general expect a randomly oriented IFO's response to lie in this shaded region.
+%Given a network of three equally sensitive, randomly oriented IFOs we expect that a single 40-Mpc BNS inspiral would produce three distinct detector response strains that fall within this shaded region.
+%
+
 %

### 2018-11-18 Paper/Manuscript.tex
Changes for the referee report

@@
 Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
-a \emph{model network} of three IFOs ($N=3$), where one is near-optimally oriented/positioned with $|Q|=2\sigma=4/5$.
-\todo{ADD some discussion here as to why we don't use specific LV Q's}
-The second IFO operates at the RMS average; thus it has $|Q|=2/5$. %compared with the optimal $|Q| =1$ case.
+a \emph{model network} of three IFOs ($N=3$), where one operates at the RMS average; thus it has $|Q|=2/5$. 
+The second IFO is near-optimally oriented/positioned so we assign it a quality
+factor one $\sigma$ above the average: $|Q|=2/5+\sigma=4/5$.
 It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
@@
 One may very well use another scheme to generate this below-average response.
+Given that $\rho_\text{tot}$ is a sum of quadratures the lowest SNR contributes a small percentage to this [cf. Eq.~(\ref{eq:SNR_total})].
 
@@
 Column four lists the magnitude of the frequency-domain strain at each IFO via Eq.~(\ref{eq:Hi_s}).
-The last column states each IFO's response, e.g., high means high strain, thus high SNR.
+The last column states each IFO's response, e.g., high means high sensitivity, thus high SNR.
 %shows how loud the GW strain is at a given IFO due source sky position and IFO orientation. 
@@
 %For our advance warning times we will further use separate initial frequencies for each inteferometer as we will explain in Sec.~\ref{sec:results}.
+
+Let us conclude this subsection with a brief discussion on 
+%our particular choice to represent the sensitivities of the near-future ALV network.
+an alternate approach to construct a model for the near-future ALV network.
+This involves selecting one IFO as the ``base'' detector, e.g., LIGO Livingstone then running Monte-Carlo simulations over the four random angles $\{\theta,\phi,\psi,\iota\}$. 
+We would subsequently compute the quality factor of the base IFO using the
+simulation results for the four angles.
+We can then obtain the quality factors of the remaining two IFOs 
+--- in this particular case, LIGO Hanford and Virgo --- via their positions and orientations with respect to the base IFO. Given that the four angles
+are completely random, there should be no preferred point in the angle parameter space, thus the result of the Monte-Carlo runs should converge
+to the RMS average. Correspondingly, we would expect one of the other two IFOs to have somewhat higher sensitivity, and the other one to have lower sensitivity.
+This network can be further expanded using exact positions of LIGO India
+and KAGRA detectors. The expansion of the detector network from three to five IFOs will offer significant improvements in source localization.
+However, given that the total network SNR is a sum of quadratures, the 
+expanded network will not accumulate significantly higher SNR than
+our model ALV network. As such our model network should serve as a good proxy for the advance warning time computations.
 
@@
 A rather compact NS with $m=1.4 M_\odot, R=11\,\text{km}, P= 10\,\text{ms}$ has $\chi\lesssim 0.05$ whereas
-the fastest observed NS spin in a BNS system is $\lesssim 0.04$ \cite{0264-9381-26-7-073001}.
+the fastest observed NS spin in a BNS system is $\lesssim 0.04-0.05$ \cite{0264-9381-26-7-073001, Stovall:2018ouw}.
 Therefore, at $f= 100\,$Hz, the first term on the right-hand-side of Eq.~(\ref{eq:spin_orbit}) gives $\approx 4\times 10^{-4}$. 
@@
 The LIGO Open Science Center has a detailed Python-based tutorial on how to do this using the data from the very first GW detection (GW150914) \cite{LIGO_tutorial}. 
-We use a $\verb|Mathematica|$ based code developed at UCD to do the same for GW170817.
+We use a $\verb|Mathematica|$ based code developed at University College Dublin (UCD) to do the same for GW170817.
 %
@@
 \be
-\bar\rho_h = 29.2,\quad \bar\rho_m = 14.6,\quad \bar\rho_l = 6.11 \label{eq:GW170817_SNRs}.
+\bar\rho_h = 28.7,\quad \bar\rho_m = 14.3,\quad \bar\rho_l = 6.00 \label{eq:GW170817_SNRs}.
 \ee
@@
 \be
-\bar\rho_\text{tot}= \sqrt{\bar\rho^2_h+\bar\rho^2_m+\bar\rho^2_l}= 32.6 \, \label{eq:SNR_total_GW170817} .
+\bar\rho_\text{tot}= \sqrt{\bar\rho^2_h+\bar\rho^2_m+\bar\rho^2_l}= 32.0 \, \label{eq:SNR_total_GW170817} .
 \ee

### 2018-11-18 Paper/Manuscript.tex
Updates modulo ref report

@@
 Though many of our results may be known to the experts, they might nonetheless find this article motivating and exciting.
+
+\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals}
 \end{abstract}
@@
 future detectors can forecast tidal disruption events, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
+We then reapply our framework to binary black hole inspirals in Sec.~\ref{sec:BH_BH}.
 
@@
 %
-\section{Binary black hole neutron star systems}\label{sec:BH_NS}
+\section{Black hole neutron star inspirals}\label{sec:BH_NS}
 In this section, we investigate the possibility of witnessing the tidal distruption of a neutron star by a black hole before the merger.
@@
 %\ee
+%
+\section{Bnary black hole inspirals}\label{sec:BH_BH}
+We briefly repeat our computations for binary black hole (BBH) inspirals.
+As it is clear that heavier systems inspiral too fast, we limit ourselves
+to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
+\todo{Finish this}
+
 \section{Outlook}

### 2018-11-19 Paper/Manuscript.tex
More workon ref comments

@@
 
-\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals}
+\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote}
 \end{abstract}
@@
 Ref.~\cite{Nissanke:2012dj} investigated the capabilities of three to five-interferometer detector networks of 2020s in terms of their ranges
-to inspiralling BNSs and their sky-localization of these sources. Our work here is somewhat complementary in the sense that we are mostly concerned with
-how early the GW networks can detect the inspiral before the merger.
+to inspiralling BNSs and their sky-localization of these sources. 
+More recently, Ref.~\cite{Chan:2018csa} added to this results pertaining to the future networks of 2030s both in terms of source localization and advance
+warning prospects.
+Our work here is complementary to these articles in the sense that we focus on
+the details of how to quantify the advance warning.
+%we are mostly concerned with how early the GW networks can detect the inspiral before the merger.
 
@@
 --- in this particular case, LIGO Hanford and Virgo --- via their positions and orientations with respect to the base IFO. Given that the four angles
-are completely random, there should be no preferred point in the angle parameter space, thus the result of the Monte-Carlo runs should converge
-to the RMS average. Correspondingly, we would expect one of the other two IFOs to have somewhat higher sensitivity, and the other one to have lower sensitivity.
+are completely random, there should be no preferred point in the angle parameter space, thus the result of the Monte-Carlo runs should more or less agree with the RMS average.
+Correspondingly, we would expect one of the other two IFOs to have somewhat higher sensitivity, and the other one to have lower sensitivity.
 This network can be further expanded using exact positions of LIGO India
@@
 The inferred duration of the event in the network bandwidth was $\approx 57\,$ seconds during which $\approx 3000$ cycles of GWs were emitted \cite{GW170817_Facts}.
-Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following values were inferred for the total mass, the chirp mass,
-and the luminosity distance of the source with 90\% confidence:
-%
-\be
-M = 2.74^{+0.04}_{-0.01} M_\odot,\quad M_c = 1.188^{+0.004}_{-0.002} M_\odot,\quad D= 40^{+8}_{-14}\,\text{Mpc}. \label{eq:GW170817_params}
+Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following updated values were inferred for the total mass, the chirp mass,
+and the luminosity distance of the source with 90\% confidence \cite{GW170817_2018}:
+%
+\be
+M = 2.73^{+0.04}_{-0.01} M_\odot,\quad M_c = 1.186^{+0.001}_{-0.001} M_\odot,\quad D= 40.7^{+2.36}_{-2.36}\,\text{Mpc}. \label{eq:GW170817_params}
 \ee
@@
 due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}). 
-In fact, detailed follow-up analyses (\cite{GW170817_2018}) have recently restricted the above-values to
-%
-$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001}M_\odot , 40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
-%
-where the errors in $D$ are at $1\sigma$ level.
+%In fact, detailed follow-up analyses () have recently restricted the above-values to
+%
+%$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001}M_\odot , 40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
+%
+%where the errors in $D$ are at $1\sigma$ level.
 
@@
 \be
-\tau_\text{insp}^{0\text{PN}} \simeq 55.91\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2680\,\label{eq:GW170817_values_0PN}. 
-\ee
-%
-%%
-If we wish to do better, we can add all of the known post-Newtonian contributions 
-up to 3.5PN\footnote{Although the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
-explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$. Be that as it may, we suspect that a few PN experts have already obtained these.} resulting in
-%%
-%
-\be
-\tau_\text{insp}^{3.5\text{PN}} \simeq 56.65\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{3.5\text{PN}} \simeq 2711 \label{eq:GW170817_values_3p5PN}\, ,
-\ee
-%
-%%
-which more or less match the values above. %of $\tau_\text{insp}\approx 60$\,seconds and $\mathcal{N}_\text{cyc} \approx 3000$ which we can obtain if we use $f_i \approx 28-29\,$Hz.
+\tau_\text{insp}^{0\text{PN}} \simeq 56.06\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{0\text{PN}} \simeq 2687\,\label{eq:GW170817_values_0PN}. 
+\ee
+%
+%%
+If we wish to do better, we can add all the post-Newtonian contributions up to 2PN resulting in
+%%
+%
+\be
+\tau_\text{insp}^{2\text{PN}} \simeq 57.06\,\text{seconds}, \quad \mathcal{N}_\text{cyc}^{2\text{PN}} \simeq 2735 \label{eq:GW170817_values_3p5PN}\, ,
+\ee
+%
+%%
+which more or less match the detected inspiral time and number of cycles. We stop at 2PN because the currently available 3.5PN expressions require the value of $\nu$
+which is not well known for GW170817.
+%
+%\footnote{Although the equations of motion for circular orbits is now known up to 4PN \cite{4PN_EoM_paper}, we are not aware of any publications
+%explicitly showing the 4PN contributions to $\tau_\text{insp}$ and $\mathcal{N}_\text{cyc}$. Be that as it may, we suspect that a few PN experts have already obtained these.} 
+%of $\tau_\text{insp}\approx 60$\,seconds and $\mathcal{N}_\text{cyc} \approx 3000$ which we can obtain if we use $f_i \approx 28-29\,$Hz.
 %Our PN-only computation underestimates $\mathcal{N}_\text{cyc}$ because we artificially end the inspiral at the Schwarzschild ISCO whereas
@@
 
+In mid 2020s LIGO will first be upgraded to A+ then to Voyager. 
+However, both versions will have comparable sensitivities to Advanced LIGO
+at low frequencies (see Fig.~1 of Ref.~\cite{Mills:2017urp}).
+Therefore, they will not start accumulating significant SNR until $f\approx 10\,$Hz, thus offering us gains of mere minutes compared to $T_\text{AW}$ in Table~\ref{table:LIGO2020}.
+For this reason, we move on to 2030s: the
+era of Einstein Telescope.
+
 \subsubsection{Forecasting GRBs in the 2030s using the Einstein Telescope}\label{Sec:ETB}
@@
 Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET-C. 
+Our values for $T_\text{AW}$ for 200 and 400\,Mpc are roughly consistent
+with the findings of Ref.~\cite{Chan:2018csa}.
 
@@
 With such high SNRs we expect that a future network consisting of ET \emph{and} LIGO Voyager will be able to localize half the sources 
-inside a radius of $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ and more than half the sources within $D\lesssim 400\,$Mpc to $\approx 1\,\text{deg}^2$ \cite{Mills:2017urp}.
-Let us reemphasize that such good localization requires at least a second detector with comparable sensitivity to ET as ET alone has rather poor localization.
-Erring on the side of optimism, we conclude that the 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts
-\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational after 2030,
-which is roughly in line with the milli-Hertz space interferometer LISA's timeline \cite{Audley:2017drz}.}.
+inside a radius of $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ \cite{Mills:2017urp}, but mostly after the merger.
+%and more than half the sources within $D\lesssim 400\,$Mpc to $\approx 1\,\text{deg}^2$ . 
+On the other hand, ET with CE together will localize 
+$\sim 80, 20\%$ of the BNSs
+within 200, 400\,Mpc to $1\,$deg$^2$, respectively \cite{Chan:2018csa},
+%Let us reemphasize that such good localization requires at least a second detector %with comparable sensitivity to ET as ET alone has rather poor localization.
+since CE will be sensitive enough to start accumulating SNR at $f\approx 5\,$Hz from BNSs within 400\,Mpc corresponding to $T_\text{AW}\gtrsim 1.5\,$hours.
+Even without the help of a second detector, it will be possible
+to localize $\sim 5\%$ of these transients to within $10\,$deg$^2$ using
+the Earth's rotation because these nearby sources will spend hours in the ET-C band \cite{Zhao:2017cbb}.
+This percentage amounts to $\sim 5$ events per year.
+%Additionally, these localizations are mostly post-merger as neither Voyager,
+Erring on the side of optimism, we conclude that the 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts and the subsequent kilonovae
+\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
+which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and may be five to ten years ahead of CE \todo{citation}}.
 %It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated

### 2018-11-21 Paper/Manuscript.tex
finished the Mathematica

@@
 
-\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote}
+\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote, 4) fix TAble VI}
 \end{abstract}
@@
 \end{tabular}
-\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
+\caption{\todo{FIX these numbers}Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
 The SNRs are even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
@@
 We briefly repeat our computations for binary black hole (BBH) inspirals.
-As it is clear that heavier systems inspiral too fast, we limit ourselves
+As heavier systems inspiral too fast, we limit ourselves
 to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
-\todo{Finish this}
+For these systems, we find that $T_\text{AW} \lesssim 1\,$hour for $D\gtrsim 190\,$Mpc, but $\bar{\rho}_F$ will exceed 500. As such lightweight black holes
+are expected to be rare and given the BBH merger rate inferred from the previous LIGO detections \todo{FInd the event rate}, we expect no forecasts
+for these events. Nonetheless, ET will detect hundreds to thousands of BBH mergers.
 

### 2018-11-21 Paper/Manuscript.tex
New manuscript finished post referee report.

--- 2018-11-19 Paper/Manuscript.tex
@@
 Though many of our results may be known to the experts, they might nonetheless find this article motivating and exciting.
-
-\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote}
 \end{abstract}
@@
 future detectors can forecast tidal disruption events, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
-We then reapply our framework to binary black hole inspirals in Sec.~\ref{sec:BH_BH}.
+%We then reapply our framework to binary black hole inspirals in Sec.~\ref{sec:BH_BH}.
 
@@
 a \emph{model network} of three IFOs ($N=3$), where one operates at the RMS average; thus it has $|Q|=2/5$. 
-The second IFO is near-optimally oriented/positioned so we assign it a quality
+The second IFO is better oriented/positioned so we assign it a quality
 factor one $\sigma$ above the average: $|Q|=2/5+\sigma=4/5$.
@@
 %
-\item {\it Changing the detection threshold from $\bar{\rho}_\text{tot}=15$.}\\
-\todo{ADD SNR=12 and 20 computations for ET-C}
-$\bar\rho$ is defined in Sec. V
+\item {\it Changing the detection criterion from} $\bar{\rho}_\text{tot}=15$. 
+In sections \ref{sec:results} - \ref{sec:BH_NS}, we present our results for advance warning times based on a detection criterion
+given by total network SNR equalling 15 [cf. Eq.~(\ref{eq:SNR_bar})].
+It is quite common in the literature to select 8 or 12 for $ \bar\rho_\text{tot} $.
+So, here, we briefly explore the consequences of (i) relaxing our detection criterion to $\bar{\rho}_\text{tot}=12$, and (ii) making it more strict by setting $\bar{\rho}_\text{tot}=20$.
+The former choice provides longer warning times and the latter less.
+We recommend first the reading of Secs.~\ref{sec:GW170817}, \ref{sec:results} before continuing here.
+
+For the ALV network of 2020s, it is clear from the results in Table~\ref{table:LIGO2020} that
+there is no point in discussing the $\bar{\rho}_\text{tot}=20$ case as that would result in advance
+warning times of mere seconds.
+So we only consider $\bar{\rho}_\text{tot}=12$ and BNS inspirals at $D=50,100\,$Mpc for which we find that the advance warning times increase to 120 and 36 seconds from 86 and 23, respectively.
+Though this is an improvement, it does not change our conclusion to Sec.~\ref{Sec:ALIGO2020}, that we expect no forecasts in the 2020s.
+
+For Einstein Telescope, we consider both $\bar{\rho}_\text{tot}=12$ and 20 given its low-frequency sensitivity.
+We present the resulting advance warning times ($T_\text{AW}$) in Table~\ref{table:SNR_12_20_results}
+on the next page. Comparing these with the corresponding ones in Table~\ref{table:ET}, we see that setting
+$\bar{\rho}_\text{tot}=12$ increases ET-B, C warning times by $\gtrsim 50\%, \sim 20\%$, respectively.
+On the other hand, $\bar{\rho}_\text{tot}=20$ decreases them by $\sim 40\%, 20\%$.
+Be that as it may, we see that ET-C sensitivity still yields advance warning times $> 1\,$hour for sources within $\approx 450$\,Mpc.
+Therefore, our conclusions that we expect ET-C to forecast $\gtrsim 5$ yearly
+BNS mergers holds.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lccccc}
+%toprule
+\hline\hline
+$D\,$(Mpc)\hspace{2mm} & \multicolumn{2}{c}{$T_\text{AW}(\bar{\rho}_\text{tot}=12)$} & & \multicolumn{2}{c}{$T_\text{AW}(\bar{\rho}_\text{tot}=20)$}\T\B\\
+\hline
+{}& ET-B & ET-C &\hspace{5mm} & ET-B & ET-C  \T\B\\
+%midrule
+100 & 70\,minutes & 6.6\,hours & & 28\,minutes & 4.2\,hours \\
+200 & 18\,minutes & 3.4\,hours & & 7.0\,minutes & 2.2\,hours \\
+400 & 4.6\,minutes & 1.8\,hours & & 1.5\,minutes & 1.2\,hours \\
+1000 & 31\,seconds & 44\,minutes & & 6.2\,seconds & 24\,minutes \\
+\hline\hline
+\end{tabular}
+\caption{Alternative advance warning times obtained using detection criteria of $\bar{\rho}_\text{tot}=12,20$ as opposed to 15 which is our standard choice throughout this article for which the ET-B/C results are displayed in Table~\ref{table:ET}.}\label{table:SNR_12_20_results}
+\end{table}
+%
+%
 %
@@
 inspirals that yield high SNRs ($\bar\rho_F\gtrsim 40$) will enable (i) high precision measurements of 
-$M_c, M$ \cite{Farr:2015lna}; (ii) source sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};
+$M_c, M$ \cite{Farr:2015lna}; (ii) source sky localization to $\lesssim 5\,\text{deg}^2$ \cite{Rodriguez:2013oaa};
 (iii) $ \lesssim 10\%$ precision in the inferred NS masses \cite{Rodriguez:2013oaa} and the effective spin parameter $\chi_\text{eff}$ \cite{Zhu:2017znf}; and
@@
 %Additionally, these localizations are mostly post-merger as neither Voyager,
-Erring on the side of optimism, we conclude that the 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts and the subsequent kilonovae
+Therefore, erring on the side of optimism, we conclude that the 2030s hold in store real-time 
+electromagnetic observations of at least dozens of gamma-ray bursts and the subsequent kilonovae
 \footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
-which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and may be five to ten years ahead of CE \todo{citation}}.
+which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.}.
 %It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated
@@
 
-100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
+100 &   28.2\,minutes & 503 &{\qquad} &  2.17\,hours & 601\T\\
 200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
 400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
-1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
+1000 & 14.3\,seconds & 49.0 &{\qquad} & 13.9\,minutes& 58.5\\
 \hline\hline
@@
 %
-\section{Bnary black hole inspirals}\label{sec:BH_BH}
-We briefly repeat our computations for binary black hole (BBH) inspirals.
-As it is clear that heavier systems inspiral too fast, we limit ourselves
-to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
-\todo{Finish this}
+
+%\section{Binary black hole inspirals}\label{sec:BH_BH}
+For the curious reader, we briefly repeat our computations for binary black hole (BBH) inspirals.
+As heavier systems inspiral too fast, we limit ourselves
+to $5M_\odot-5M_\odot$ BBHs and only consider only ET-C.
+For these systems, we find that $T_\text{AW} \lesssim 1\,$hour for $D\gtrsim 190\,$Mpc, but $\bar{\rho}_F$ exceeds 500 due to the increased total mass.
+Even for a source at 100\,Mpc, we obtain $T_\text{AW}\approx 35\,$minutes at best.
+As such lightweight black holes
+are expected to be rare and given the current BBH merger rate of 12-213\,Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2017vtc}, which translates to $\ord(0.1) - \ord(1)$ BBH mergers yearly
+within 190\,Mpc, we statistically expect no forecasts of these events. 
+Nonetheless, ET and CE will detect hundreds to thousands of BBH mergers out to redshifts of $z> 10$.
 

### 2018-11-21 Paper/Manuscript.tex
Minor/final. It is ready for referees modulo prettying up figures and typos

@@
 hence  (a) measure the Hubble parameter, dark matter and dark energy densities, as well as the dark energy equation-of-state parameter;
-(b) study the cosmological evolution of the stellar mass black holes (see Sec.~2 of Ref.~\cite{ET_doc} for an excellent summary and further details).
+(b) study the cosmological evolution of the stellar mass black holes (see Sec.~2 of Ref.~\cite{ET_doc} for an excellent summary of the science goals and further details).
 
 The prospect of having extremely sensitive 3G GW detectors begs a simple question: can we detect the inspirals of binary neutron star systems
-early enough to witness gamma-ray bursts as they happen? In other words, can we forecast GRBs using GW detections?
+early enough to witness gamma-ray bursts and the birth of the subsequent kilonovae as they happen? 
+In other words, can we forecast GRBs using GW detections?
 The short answer is ``yes''.
@@
 However, it is possible that some of the near-Earth pointing short hard GRBs may be observed as long-duration GRBs or X-ray flashes thus increasing this percentage \cite{Bucciantini:2011kx}.
+On the other hand, the optical emission from the kilonova should be less collimated, thus much more likely
+to be detected \cite{Troja:2017nqp}.
 
@@
 an alternate approach to construct a model for the near-future ALV network.
-This involves selecting one IFO as the ``base'' detector, e.g., LIGO Livingstone then running Monte-Carlo simulations over the four random angles $\{\theta,\phi,\psi,\iota\}$. 
+This involves selecting one IFO as the ``base'' detector, e.g., LIGO Livingstone, then running Monte-Carlo simulations over the four random angles $\{\theta,\phi,\psi,\iota\}$. 
 We would subsequently compute the quality factor of the base IFO using the
@@
 --- in this particular case, LIGO Hanford and Virgo --- via their positions and orientations with respect to the base IFO. Given that the four angles
-are completely random, there should be no preferred point in the angle parameter space, thus the result of the Monte-Carlo runs should more or less agree with the RMS average.
+are completely random, there should be no preferred region in the angle parameter space, thus the result of the Monte-Carlo runs should more or less agree with the RMS average.
 Correspondingly, we would expect one of the other two IFOs to have somewhat higher sensitivity, and the other one to have lower sensitivity.
@@
 A rather compact NS with $m=1.4 M_\odot, R=11\,\text{km}, P= 10\,\text{ms}$ has $\chi\lesssim 0.05$ whereas
-the fastest observed NS spin in a BNS system is $\lesssim 0.04-0.05$ \cite{0264-9381-26-7-073001, Stovall:2018ouw}.
+the fastest observed NS spin in a BNS system is $\approx 0.04-0.05$ \cite{0264-9381-26-7-073001, Stovall:2018ouw}.
 Therefore, at $f= 100\,$Hz, the first term on the right-hand-side of Eq.~(\ref{eq:spin_orbit}) gives $\approx 4\times 10^{-4}$. 
@@
 at low frequencies (see Fig.~1 of Ref.~\cite{Mills:2017urp}).
-Therefore, they will not start accumulating significant SNR until $f\approx 10\,$Hz, thus offering us gains of mere minutes compared to $T_\text{AW}$ in Table~\ref{table:LIGO2020}.
+Therefore, they will not start accumulating significant SNR until $f\approx 10\,$Hz, thus offering us gains of a few minutes over $T_\text{AW}$ in Table~\ref{table:LIGO2020}.
 For this reason, we move on to 2030s: the
@@
 Current BNS merger rate, inferred from A-LIGO's O1-O2 periods, implies that $\sim 40$ to $\sim600$ sources within a volume of $(200\,\text{Mpc})^3$ will be detected yearly by ET-C. 
-Our values for $T_\text{AW}$ for 200 and 400\,Mpc are roughly consistent
+Our values for $T_\text{AW}$ for $D=200, 400\,$Mpc are roughly consistent
 with the findings of Ref.~\cite{Chan:2018csa}.
@@
 With such high SNRs we expect that a future network consisting of ET \emph{and} LIGO Voyager will be able to localize half the sources 
-inside a radius of $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ \cite{Mills:2017urp}, but mostly after the merger.
+inside a radius of $D\approx 1000\,$Mpc to within $ 10\,\text{deg}^2$ \cite{Mills:2017urp}, but mostly \emph{after} the merger.
 %and more than half the sources within $D\lesssim 400\,$Mpc to $\approx 1\,\text{deg}^2$ . 
-On the other hand, ET with CE together will localize 
+On the other hand, ET together with CE will localize 
 $\sim 80, 20\%$ of the BNSs
-within 200, 400\,Mpc to $1\,$deg$^2$, respectively \cite{Chan:2018csa},
+within 200, 400\,Mpc to $1\,$deg$^2$, respectively \cite{Chan:2018csa}.
 %Let us reemphasize that such good localization requires at least a second detector %with comparable sensitivity to ET as ET alone has rather poor localization.
-since CE will be sensitive enough to start accumulating SNR at $f\approx 5\,$Hz from BNSs within 400\,Mpc corresponding to $T_\text{AW}\gtrsim 1.5\,$hours.
-Even without the help of a second detector, it will be possible
+This is thanks to CE's low-frequency sensitivity which is sufficient to start accumulating SNR at $f\approx 5\,$Hz from BNSs within 400\,Mpc corresponding to $T_\text{AW}\gtrsim 1.5\,$hours.
+Even without the help of a second detector, ET-C will be able
 to localize $\sim 5\%$ of these transients to within $10\,$deg$^2$ using
-the Earth's rotation because these nearby sources will spend hours in the ET-C band \cite{Zhao:2017cbb}.
+the Earth's rotation because these nearby sources will spend hours in its frequency band \cite{Zhao:2017cbb}.
 This percentage amounts to $\sim 5$ events per year.
@@
 Therefore, erring on the side of optimism, we conclude that the 2030s hold in store real-time 
-electromagnetic observations of at least dozens of gamma-ray bursts and the subsequent kilonovae
-\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
+electromagnetic observations of at least dozens of gamma-ray bursts and the subsequent kilonovae\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
 which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.}.
@@
 As heavier systems inspiral too fast, we limit ourselves
-to $5M_\odot-5M_\odot$ BBHs and only consider only ET-C.
-For these systems, we find that $T_\text{AW} \lesssim 1\,$hour for $D\gtrsim 190\,$Mpc, but $\bar{\rho}_F$ exceeds 500 due to the increased total mass.
+to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
+For these systems, we find that $T_\text{AW} \gtrsim 1\,$hour only for $D\lesssim 190\,$Mpc, with $\bar{\rho}_F$ exceeding 500 due to the increased total mass.
 Even for a source at 100\,Mpc, we obtain $T_\text{AW}\approx 35\,$minutes at best.

### 2018-11-22 Paper/Manuscript.tex
Minor
Minor updates

@@
 Be that as it may, we see that ET-C sensitivity still yields advance warning times $> 1\,$hour for sources within $\approx 450$\,Mpc.
-Therefore, our conclusions that we expect ET-C to forecast $\gtrsim 5$ yearly
+Therefore, our conclusions that we expect ET-C to forecast $\sim \ord(100)$ yearly
 BNS mergers holds.
@@
 sub-optimally oriented IFO ($2\sqrt{f}\tilde{H}_l$) as explained in Fig.~\ref{fig:figGW170817}.
-The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals.
+The vertical dashed (black) line marks the ISCO frequency $f_\text{ISCO} \simeq 1571\,$Hz at which point we terminate the inspirals. The light red curve shows the L1 ASD during GW170817.
 %but as can be seen, the SNRs hardly increase beyond $\sim 1000\,$Hz.
@@
 %Additionally, these localizations are mostly post-merger as neither Voyager,
-Therefore, erring on the side of optimism, we conclude that the 2030s hold in store real-time 
-electromagnetic observations of at least dozens of gamma-ray bursts and the subsequent kilonovae\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
-which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.}.
+Therefore, erring on the side of optimism, we conclude that the 2030s\footnote{As the ET construction/commissioning timeline is currently uncertain, we can only speculate that ET-C will be operational in mid 2030s,
+which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.} 
+hold in store 
+(i) forecasts of $\gtrsim \ord(100)$ short gamma-ray bursts and
+(ii) real-time electromagnetic observations of $\gtrsim \ord(10)$ of these and the subsequent kilonovae.
 %It is also reasonable to speculate that by that time the detection, localization and early-warning algorithms will have become sufficiently sophisticated

### 2018-12-17 Paper/Manuscript.tex
Minor update before replacing the arxiv version.

@@
 %with the C configuration of Einstein Telescope.
-We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
+We reapply our warning-time computation to black hole - neutron star inspirals and find that we expect one to three tidal disruption events 
 to be forecast by the same detector.
@@
 The 6.95\footnote{There have thus far been six detections with $5\sigma$ statistical significance and one additional event, LVT151012 \cite{TheLIGOScientific:2016pea}, with $2\sigma \simeq 95\%$ significance hence 6.95 overall.}
+\footnote{As of December 2018, the count has been updated to ten including LVT151012 \cite{LIGOScientific:2018mvr}.} 
 gravitational-wave merger events detected by the Advanced LIGO-Virgo network have firmly established gravitational-wave astronomy
@@
 \be
-\mathcal{N}_\text{cyc}(f) = \int_f^{f_\text{max}} \f{f'}{\dot{f'}}\, df' =\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right] \label{eq:Ncyc1}
+\mathcal{N}_\text{cyc}(f) = \int_f^{f_\text{max}} \f{f'}{\dot{f'}}\, df' =\f{1}{32\pi} \f{c^5}{(\pi G M_c)^{5/3}}\left[ f^{-5/3}-f_\text{max}^{-5/3}\right] \label{eq:Ncyc1}\, .
 \ee
